### 2020-09-05 paper.tex
ok, scripts.

%% This is file `elsarticle-template-1-num.tex',
%%
%% Copyright 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%%
%% $Id: elsarticle-template-1-num.tex 149 2009-10-08 05:01:15Z rishi $
%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-1-num.tex $
%%
\documentclass[preprint,5p, twocolumn, authoryear]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% The graphicx package provides the includegraphics command.
\usepackage{graphicx}
%% The amssymb package provides various useful mathematical symbols
\usepackage{amsmath}   % Extra math commands and environments from the AMS
\usepackage{amssymb}   % Special symbols from the AMS
\usepackage{amsthm}    % Enhanced theorem and proof environments from the AMS
\usepackage{latexsym}  % A few extra LaTeX symbols
\usepackage{array}
\usepackage{makecell}
\usepackage{units}
%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
\usepackage{lineno}
\usepackage[singlelinecheck=false]{caption}

%\biboptions{longnamesfirst, semicolon}
%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

% \biboptions{}
\newcommand{\useq}{\mathbf{u}}
\newcommand{\xseq}{\mathbf{x}}
\newcommand{\bbR}{\mathbb{R}}
\newcommand{\bbW}{\mathbb{W}}
\newcommand{\bbU}{\mathbb{U}}
\newcommand{\bbI}{\mathbb{I}}
\newcommand{\bbX}{\mathbb{X}}
\newcommand{\bbP}{\mathbb{P}}

\graphicspath{{./}{./figures/}{./figures/paper/}}

\newdefinition{assumption}{Assumption}
\newdefinition{prop}{Proposition}
\newdefinition{definition}{Definition}
\newdefinition{rmk}{Remark}
\newtheorem{thm}{Theorem}

\journal{Elsevier}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

\title{Industrial, large-scale model predictive control 
with structured neural networks}

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
\author[label1]{Pratyush Kumar\corref{cor1}}
\ead{pratyushkumar@ucsb.edu}
%% \ead[url]{home page}
%% \fntext[label2]{}
\cortext[cor1]{Corresponding Author}
%% \fntext[label3]{}

\author[label1]{James B. Rawlings}
\ead{jbraw@ucsb.edu}

\author[label2]{Stephen J. Wright}
\ead{swright@cs.wisc.edu}

\address[label1]{Department of Chemical Engineering, University of California, Santa Barbara, CA 93106, United States}
\address[label2]{Computer Sciences Department, University of Wisconsin-Madison, Madison, WI 53706, United States}

\begin{abstract}
The design of neural networks (NNs) is presented 
for treating large, linear model predictive control (MPC) applications that 
are out of reach with available quadratic programming (QP)
solvers. First, we introduce a new feedforward
network architecture that enables practitioners to 
obtain offset-free closed-loop performance with NNs.
Second, we discuss the data generation procedure 
to sample the relevant state-space for the network 
training based on anticipated online setpoint changes and
plant disturbances. Third, we use the 
input-to-state stability results 
available in the MPC literature
and establish robustness 
properties of NN controllers.
Finally, we present illustrative
simulation studies on 
process control examples. 
We apply the NN design approach
and compare the performance with online QP based MPC on an industrial crude
distillation unit model with 252 states, 32 control inputs, 
and a control-sample horizon length of 145. Parallel computing 
is used for data generation and graphical processing units are used for
network training. 
After the offline design phase, 
NNs execute MPC 
three to five orders of magnitude faster
than an available QP solver with less than $1\%$
loss in the closed-loop performance.
\end{abstract}

\begin{keyword}
Model predictive control \sep machine learning \sep 
deep neural networks \sep large-scale problems
\end{keyword}

\end{frontmatter}

%% main text
\section{Introduction} \label{sec:introduction}

Model predictive control (MPC) is an online 
optimization-based feedback control technology. A dynamic model 
of the plant is used to make forecasts of the plant measurements
in response to the actuator movements, and an optimization
is solved in real-time to determine the optimal actuator
move to be applied to the plant. For linear plant models, 
the optimization to be solved online is a quadratic program (QP).
The development 
of efficient QP algorithms 
\citep*{kouzoupis:frison:zanelli:diehl:2018, wright:2019}
allowed practitioners to adopt MPC
in process industries \citep*{qin:badgwell:2003, lahiri:2017}.

An alternative strategy to 
real-time optimization for the deployment of MPC 
is to characterize the MPC feedback law
as a piecewise affine function defined on 
polyhedral partitions of the state-space, 
and use the feedback law online
\citep*{bemporad:morari:dua:pistikopoulos:2002, 
seron:goodwin:dedona:2003}.
The real-time computation in this approach is 
reduced to a table look-up in the state-space
based on the current value of parameters 
in the QP such as the state estimate and some 
steady state targets that are computed for 
offset-free control. The number of polyhedral 
partitions of the state-space grows exponentially
with model dimensions, thereby prohibiting 
the deployment of this strategy on large systems.

The MPC feedback law can be approximated using 
parametric functions such as polynomials
\citep*{kvasnica:lofberg:fikar:2011}, 
various types of piecewise affine functions
\citep*{bemporad:oliveri:poggi:storace:2011, wen:ma:ydstie:2009},
and neural networks (NNs) \citep*{cavagnari:magni:scattolini:1999}.
Among the
function approximators, NNs that use the rectified linear unit 
(ReLU) as the activation function 
have gained attention recently 
\citep*{chen:saulnier:atanasov:lee:kumar:pappas:morari:2018, 
karg:lucia:2020, paulson:mesbah:2020, lovelett:dietrich:lee:kevrekidis:2020}
to approximate
the MPC feedback law due to their ability to represent complex 
piecewise affine functions
\citep*{montufar:pascanu:cho:bengio:2014}
and execute MPC faster in real-time than QP solvers. 
The proposed NN design approach in 
these works is to generate training 
data for the NN by solving QPs offline
for a set of feasible states of the QP, use the
collected data to train a standard feedforward network, then 
use the trained NN as the feedback controller online.

To make progress in the size of control applications 
achievable with MPC, large problems
in which QP solvers fail to deliver the 
control in the available sample time should be addressed.
The scalability of the NN approach
to such problems with large model dimensions and 
control horizon length in the QP
has not been demonstrated. Two issues arise 
in these problems:
i) In a large dimensional state-space,   
the entire set of feasible states of the QP cannot be sampled  
densely for the NN training. This issue is 
a type of the curse of dimensionality.
ii) One may sample the state-space partially
to avoid this problem, but the time required for the 
data generation can still be impractical
due to the long time required to solve a QP 
for each sampled state. 
We demonstrate in this article by case studies that
this latter issue can be resolved for a large size 
of problems with parallel 
computing, and the former issue by sampling the 
state-space for the typical plant operational scenarios.
The following feature must be present in the large-scale
application of interest for the partial sampling scheme 
proposed in this article to be applicable:
for a particular operating mode of the plant, 
the number of frequently changing setpoints
and large magnitude disturbances 
must be reasonably small 
such that the entire large
dimensional state-space is not visited during that
operation mode. 
The MPC feedback law 
can then be reliably approximated using NNs
for the different modes of plant operations driven by  
their respective set
of setpoint changes and disturbances.

From the above viewpoint, 
this article discusses the design of NNs
as an alternative to real-time optimization in MPC, 
with an emphasis on large applications which 
are challenging with QP solvers. 
The focus of this article is on setpoint tracking 
MPC problems relevant for deployment in process industries.
We present a new feedforward network architecture to obtain
offset-free closed-loop performance with NNs.
Additionally, we use the input-to-state
stability results \citep*{sontag:wang:1995}
available in the MPC literature, and establish
conditions under which the NN controller 
is robust to state estimation errors and process 
disturbances. We present case studies 
on process control examples which
demonstrate the scalability of the proposed NN design 
approach.

The closely related work by \cite*{chen:wang:atanasov:kumar:morari:2019}
demonstrates the scalability of NNs 
to approximate the MPC feedback law on systems with 
large state dimensions. The 
size of problems and the setpoint 
tracking offset-free MPC problem   
considered in this 
article is not addressed in this work. 
\cite*{drgona:picard:kvasnica:helsen:2018}
takes a different approach for the scalability
of NN controllers, in which 
the dimensionality of the parameters in the MPC QP is first 
reduced using principal component analysis, and the 
NN controller 
is developed in a low dimensional state-space.

The rest of this article is organized as follows. 
In the next section, we briefly review 
offset-free linear MPC. 
In section \ref{sec:controller_design},
we discuss the NN 
controller design procedure.
We present the robustness property
of NNs in section \ref{sec:robustness}.
Then, we present simulation studies
on two large process control examples
in section \ref{sec:simulation_studies}
and conclude at the end of this article.

Notation. The symbols $\bbI$ and $\bbR$ are 
used to denote integers and reals respectively. 
Subscripts denote restrictions 
(e.g., $\bbR_{\geq 0}$ for nonnegative reals and 
$\bbI_{a:b}$ for integers in the 
closed interval $[a, b]$). The Euclidean norm 
is denoted by $\vert \cdot \vert$. A function 
$\alpha : \bbR_{\geq 0} \rightarrow \bbR_{\geq 0}$
is of class $\mathcal{K}$ if it is continuous, zero 
at zero, and strictly increasing. It is of class 
$\mathcal{K}_{\infty}$ if it is of class $\mathcal{K}$
and unbounded ($\alpha(s) \rightarrow \infty$ as 
$s \rightarrow \infty$). A function
$\beta : \bbR_{\geq 0} \times \bbI_{\geq 0} \rightarrow \bbR_{\geq 0}$
is of class $\mathcal{K} \mathcal{L}$ if it is continuous,
for a fixed $k \in \bbI_{\geq 0}$, $\beta(\cdot, k)$ is of class $\mathcal{K}$,
and for a fixed $s \geq 0$, $\beta(s, \cdot)$ is nonincreasing
and satisfies $\textnormal{lim}_{k \rightarrow \infty} \beta(s, k) = 0$.
Given $V : X \rightarrow \bbR_{\geq 0}$ and $\tau > 0$, define 
$\textnormal{lev}_{\tau} V = \{ x \in X | V(x) \leq \tau \}$.
Bold symbols, e.g., $\mathbf{d}$ denote sequences, 
$d(k)$ denotes an element of $\mathbf{d}$ at time 
$k \in \bbI_{\geq 0}$, and $\mathbf{d}_i$ 
denotes the collection of elements of 
$\mathbf{d}$ for $k \in \bbI_{0:i-1}$.
Define $\vert \vert \mathbf{d}_i \vert \vert = 
\textnormal{max}_{k \in \bbI_{0:i-1}} \vert d(k) \vert$.
For a given vector $a$, lower and upper bounds 
($\underline{a}, \overline{a}$), define the saturation function 
as $\textnormal{sat}(a, \underline{a}, \overline{a}) = 
\{ a \ \textnormal{if} \ \underline{a} \leq a \leq \overline{a}; 
\underline{a} \ \textnormal{if} \ a < \underline{a};
\overline{a} \ \textnormal{if} \ \overline{a} < a \}$.

\section{Linear model predictive control} \label{sec:mpc}

\subsection{Model}
We consider a linear discrete time model augmented with an 
integrating disturbance model \citep{pannocchia:rawlings:2003}
\begin{align}\label{eq:ltimodel}
    x^+ = Ax + Bu + B_dd, \quad d^+ = d, \quad y = Cx + C_dd
\end{align}
in which $x \in \bbR^n$ is the state, 
$u \in \bbR^m$ is the control input, and
$d \in \bbR^d$ is the state of the disturbance
model. The matrices $A \in \bbR^{n \times n}$, 
$B \in \bbR^{n \times m}$,  
$C \in \bbR^{p \times n}$ denote the actuator to measurement 
model, and $B_d \in \bbR^{n \times d}$, $C_d \in \bbR^{p \times d}$
is the disturbance model.
The objective of the disturbance model
is to remove offset in the controlled 
plant measurements at steady
state operations and maintain
them at their setpoints.
We assume in the rest of this 
article that a Kalman filter can be constructed to 
estimate the model state ($\hat{x}$) and disturbance ($\hat{d}$) 
from measurements.

\subsection{Target selector}
Given the disturbance estimate, the
input and controlled measurement setpoints,
we consider the following target selector QP
\begin{align}
    \min_{x_s, \ u_s}  \dfrac{1}{2} |u_{sp} - u_s|^2_{R_s}
\end{align}
subject to
\begin{align}  
    \begin{bmatrix}
        I -A & -B \\
        HC & 0
    \end{bmatrix} \begin{bmatrix}
        x_s \\
        u_s
    \end{bmatrix} &= \begin{bmatrix}
        B_d\hat{d} \\
        r_{sp} - HC_d\hat{d}
    \end{bmatrix} \\
    \underline{u} \leq u_s \leq \overline{u}
\end{align}
in which ($x_s, u_s$) is the 
target steady state pair, ($u_{sp}, r_{sp}$) 
are the input and controlled measurement setpoints,
and ($\underline{u}, \overline{u}$) are the 
actuator bounds.
The equality constraint $r_{sp} = H(Cx_s + C_d\hat{d})$
can be difficult to satisfy exactly in real-time 
depending on the controlled measurement setpoint 
and disturbance estimate. 
Then, the hard setpoint equality constraint 
can be relaxed and moved to the stage cost such 
that the target selector computes a steady state
to minimize the offset in the controlled measurements. 
We assume for the simulation studies
in this article that the input setpoint ($u_{sp}$)
is fixed at some chosen steady state and 
only the controlled measurement setpoint ($r_{sp}$) 
changes in real-time.

\subsection{Regulator}
Based on the state estimate and
target steady state pair,
the following QP is solved to determine the 
actuator move to be applied to the plant
\begin{align} \label{eqn:regulator}
    V_N(\tilde{x}(0), \mathbf{\tilde{u}}) = \dfrac{1}{2}\sum_{k=0}^{N-1} & \Big(|\tilde{x}(k)|^2_Q  + |\tilde{u}(k)|^2_R \Big) + \dfrac{1}{2}|\tilde{x}(N)|^2_P
\end{align}
subject to 
\begin{align}
    \tilde{x}^+ &= A\tilde{x} + B\tilde{u}, \quad \tilde{x}(0) = \hat{x} - x_s \\
    &\underline{u} \leq \tilde{u} + u_s \leq \overline{u}
    \label{eqn:regulator_constraints}
\end{align}
in which $\hat{x}$ is the state estimate after the current measurement,
($\tilde{x}, \tilde{u}$) are the state and control 
in deviation from the current steady state targets ($x_s, u_s$). 
The penalty matrix $P$ is chosen as the 
optimal cost-to-go matrix of the unconstrained 
linear quadratic infinite horizon problem.
The decision variable in this 
QP is the control sequence 
$\mathbf{\tilde{u}} = [\tilde{u}(0)', \tilde{u}(1)', ..., \tilde{u}(N-1)']'$.
The first move of the optimal solution is denoted 
as the MPC feedback law,
$\kappa_N(\hat{x}, x_s, u_s) = 
\mathbf{\tilde{u}}^0(0;\hat{x}, x_s, u_s) + u_s$, 
that is applied to the plant. This feedback law is a function of the 
state estimate and target steady state pair. A rate-of-change 
penalty on the control can be imposed in the QP objective
by augmenting the dynamic model with a surrogate state 
for the control as discussed in \cite*{rao:rawlings:1999}. 
In this case, 
the control injected at the previous timestep
($u_{-1}$) is supplied to the QP, 
and the feedback law becomes a function of the previous control 
as well in addition to the state estimate
and target steady state pair.

Several algorithms have been proposed in the literature over
the years to solve the above MPC regulator QP. 
\cite*{kouzoupis:frison:zanelli:diehl:2018} and
\cite*{wright:2019} give recent reviews on the development 
of convex optimization algorithms to solve this linear MPC QP.
For the simulation studies in this article, we eliminate the 
state trajectory from the set of decision variables  
and formulate a dense QP. The decision variable in the dense QP
is the future control trajectory $\mathbf{\tilde{u}}$, 
and the QP solver CVXOPT \citep*{vandenberghe:2010}
is used for NN data generations and timing 
comparisons with online QP based MPC.

\section{Neural network design} \label{sec:controller_design}

In the offset-free linear MPC algorithm discussed in the previous 
section, the target selector QP is
usually small compared to the 
regulator QP, that consumes most of the online computation time. We
focus on designing a NN that approximates the 
MPC feedback law ($\kappa_N(x, x_s, u_s)$)
for an operationally relevant set of states and steady state targets, 
such that the NN 
can be used online as the feedback controller 
for the plant in place of solving the MPC regulator QP.

\subsection{Structured neural network}
An intuitive approach is to build a feedforward NN 
that takes the triple ($x, x_s, u_s$) as its input 
and outputs a control that is close to the optimal control. 
This strategy has been proposed in \cite*{karg:lucia:2020} and 
\cite*{chen:saulnier:atanasov:lee:kumar:pappas:morari:2018}
for one fixed steady state. The approach has not been 
demonstrated to scale for the size of model dimensions 
and the setpoint tracking 
offset-free MPC problem considered in this article.
An issue with this strategy 
is that the NN has no knowledge about any information 
of the MPC feedback law, and can require large amounts
of training data in large state dimensions 
to obtain a reasonable controller. At a minimum,
the MPC feedback law is such that at the origin, the 
control action taken by the MPC controller is zero. For the 
setpoint tracking MPC problem considered in this article, 
the NN control law must be such that at steady state 
operations, the NN maintains the plant at the desired steady state
such that the controlled measurements are at their setpoints.
This structure implies $u_s = \kappa_{NN}(x = x_s, x_s, u_s)$, 
in which we use $\kappa_{NN}(\cdot)$ to denote the NN control law.
To incorporate this information in a NN, we present the following
architecture

\begin{align*}
z_0 &= \begin{bmatrix}
    x', & x_s', & u_s', & x_s', & x_s', & u_s'
    \end{bmatrix}'\\
    f_i(z_{i-1}) &= \begin{bmatrix}
        W_i & 0 \\
        0 & W_i
          \end{bmatrix}z_{i-1}  + \begin{bmatrix}
            b_i \\
            b_i
            \end{bmatrix} \\
    z_i &= g(f_i(z_{i-1})), \textnormal{for} \ i \in \bbI_{1:h} \\
    u &= u_s + \begin{bmatrix}
  W_{h + 1}, & -W_{h + 1} \\
    \end{bmatrix} z_h \\
\end{align*}
in which $g(a) = \textnormal{max} (0, a)$,
is the ReLU operation applied element-wise on its vector input,
$z_i$ is the output of each hidden layer
of the network, $z_0$ is the input to the network, 
$h$ is the number of hidden layers, 
and $i \in \bbI_{1:h}$. The parameters 
to be optimized using training data are ($W_i, b_i$) 
and $W_{h+1}$, which are matrices 
of appropriate dimensions. The software tensorflow 
\citep{abadi:agarwal:barham:brevdo:et-al:2015} is used 
for NN training purposes in this article,
and the structured architecture can be built 
with symbolic differentiation tools available in tensorflow.
When a rate-of-change penalty on the control 
is included in the regulator QP, 
the input to the structured NN is modified to 
\begin{align*}
    z_0 &= 
    \begin{bmatrix}
    x', & u_{-1}', & x_s', & u_s', & x_s', & u_s', & x_s', & u_s' \\
    \end{bmatrix}'
\end{align*}
in which $u_{-1}$ is the previous control applied 
to the plant and the dimensions of the matrices 
($W_i, b_i$) and $W_{h+1}$ 
are appropriately adjusted. After 
training, the control produced by 
the NN may not obey the hard actuator constraints,
and the saturation function 
($\textnormal{sat}(\cdot, \underline{u}, \overline{u})$) 
is applied to the output of the NN.

\subsection{Data generation}

For one fixed steady state, the 
set of feasible states for the MPC QP 
defined by equations \ref{eqn:regulator}
to \ref{eqn:regulator_constraints}
is the entire $n$-dimensional state space $\bbR^n$.
Additionally, the target steady state may change
during the plant operation depending
on the setpoint and disturbance estimate. 
The domain of the MPC control law ($\kappa_N(x, x_s, u_s)$)
is therefore the state-space 
$\bbR^{n}$ and the possible set of steady state 
target pairs.
Sampling this entire domain of the
MPC control law for NN training is difficult in larger 
dimensions and not required for practical applications.

From a plant operations perspective,
a majority of the large-scale petrochemical plants
operate in scenarios. Each operational scenario is driven 
by a selected few controlled measurement 
setpoints that depend on product demands
and some large magnitude disturbances
which change frequently, 
while the setpoints for 
the other measurements remain constant for long periods 
of time. The states and steady state targets 
spanned in a closed-loop 
operation per scenario is thereby considerably less 
than the entire domain of the MPC control law.
This operation style of large chemical plants
can be exploited, and we propose the 
following data generation procedure 
to perform offline simulations using the model to 
collect the operationally 
relevant set of ($x, x_s, u_s, \kappa_N(\cdot)$) 
for the NN training:

\begin{enumerate}
    \item Determine the anticipated range of 
    controlled measurement setpoint changes ($r_{sp}$)
    to be made during the plant operational 
    scenario. We denote 
    this range of setpoints as ($\underline{r}_{sp}$, $\overline{r}_{sp}$).
    \item Identify the set of physical disturbances ($d$) 
    that may affect the plant and their range of values 
    ($\underline{d}$, $\overline{d}$). We use 
    physical disturbances in this article and assume that 
    a disturbance model identification is performed 
    to obtain the matrices $B_d$ and $C_d$.
    \item Create pseudo random binary signals (PRBS)
    of $r_{sp}$ and $d$ in their respective range of values.
    \item Initialize the model at some chosen steady state.
    Perform an offline simulation with the 
    generated PRBS signals by solving the target
    selector and regulator QPs for the transient states
    and steady state targets encountered in the simulation. 
\end{enumerate}

During the plant operation, it is expected 
that the NN does not encounter 
the same states and steady state 
target pairs used for the training. But similar
values are expected since an 
adequate model and appropriate 
range of anticipated 
setpoints and plant disturbances are 
used for the data generation. 
The NN during the closed-loop operation
produces an interpolated actuator
move that is applied to the plant.

As we consider large
MPC problem sizes in this article for the NN 
controller, the data generation step
can take impractical amounts of time if performed
serially due to the long time required to solve 
each QP. For these large problems, 
several PRBS signals of the setpoints 
and disturbances are generated and 
multiple simulations are performed parallelized over 
several cores in a CPU and across multiple CPUs as well.
The data generated from all the simulations is collected
and used for the NN training.

\subsection{Training}
The following mean squared loss is minimized 
to determine the weights for the NN controller
\begin{align}
    J (\theta) = \dfrac{1}{2}\sum_{j=1}^{N_{tr}} 
    [\kappa_{NN}(x, x_s, u_s; \theta) - \kappa_N(x, x_s, u_s)]^2 
\end{align}
in which $\theta$ is the set of parameters 
to be optimized, ($W_i, b_i, W_{h+1}$)
for $i \in \bbI_{1:h}$, and $N_{tr}$ is the number of training 
samples. The stochastic optimization algorithm Adam 
\citep*{kingma:ba:2014} is used for all the NN training
performed in the case studies in this article.

\section{Robustness of neural networks} \label{sec:robustness}

The robustness property of NN controllers 
is now presented. The optimal MPC controller
designed for a nominal linear system ignoring disturbances
is known to be inherently robust to bounded state 
estimation errors and disturbances
\citep*{heath:wills:2005, pannocchia:rawlings:wright:2011}. 
The approximation
error of the MPC feedback law by a NN can be viewed 
as an additional disturbance, and the existing
input-to-state stability
results \citep*{sontag:wang:1995} are used to establish the 
allowable approximation error in the NN for 
the NN controller to be robust to disturbances. 
The Theorem \ref{thm:nnrobustness} states this 
allowable approximation error and the size 
of disturbances for which the NN controller is robust.

The problem of steering the state of the linear 
system (\ref{eq:ltimodel}) 
to one fixed steady state ($x_s, u_s$) is considered. 
For the analysis in this section, 
the state and control are transformed in deviation variables 
as $x := x - x_s$ and $u := u -u_s$,
and define the control problem as regulation to the origin.
The optimal MPC control law is denoted as $\kappa_N(x)$, 
and the NN control law as
$\kappa_{NN}(x) = \kappa_N(x) + e_{NN}(x)$, in which 
$e_{NN}(x)$ is the approximation error 
of the optimal control law by the network. Assume 
in the analysis that the target steady state 
is such that the unconstrained linear quadratic regulator (LQR)
satisfies the actuator constraints 
in a small neighborhood near the origin.

As reviewed in \cite*{mayne:rawlings:rao:scokaert:2000},
the nominal stability of MPC can be established
using the optimal cost function ($V_N^0(x)$) of the QP
as a Lyapunov function.
The region of attraction of the closed-loop system 
$x^+ = Ax + B\kappa_N(x)$ when no hard terminal region 
constraint \citep*{limon:alamo:salas:camacho:2006}  
is included in the QP can be characterized
as $\mathcal{X}_N = \textnormal{lev}_{Nd + \tau} \ V_N^0(x)$.
In which, $N$ is the control 
horizon length used in the QP, $\tau$ is a level
set parameter of the terminal region chosen as
$\bbX_f = \textnormal{lev}_{\tau} \ x'Px$, and $d > 0$
is a constant such that $\ell(x, u) \geq d$ for all 
$x \in \bbR^n \setminus \bbX_f$ and 
$\underline{u} \leq u+u_s \leq \overline{u}$.
The parameter $\tau$ is chosen small enough such that
the unconstrained LQR satisfies the actuator constraints 
for all $x \in \bbX_f$. The optimal cost 
function is continuous and satisfies 
$c_1\vert x \vert^2 \leq V_N^0(x) \leq c_2\vert x \vert^2$
and $V_N^0(x^+) - V_N^0(x) \leq -c_1\vert x \vert^2$ 
for some $c_2 \geq c_1 > 0$.

Assume that a state estimate ($\hat{x}$) is
used by the NN to compute the control. 
To analyze robustness, the following perturbed
linear system is considered
\begin{align} \label{eq:perturbed_sys}
    \hat{x}^+ = A\hat{x} + B\kappa_N(\hat{x}) + Be_{NN}(\hat{x}) + w - Ae + e^+
\end{align}
in which $\hat{x} = x + e$ is the state estimate, 
$w$ is a process disturbance, 
and $e$, $e^+$ are the state estimation errors at the 
current and next timestep respectively. 
We use $\phi_d(k;\hat{x})$ to denote a 
solution of the perturbed system 
at time $k$ starting from an initial state $\hat{x}$,
and $\phi(k;x)$ to denote a solution 
of the nominal system when the state estimation errors and process
disturbances are zero starting 
from an initial state $x$.

We use the following
definitions of
robust positive invariance of a set
with respect to disturbances, 
input-to-state stability (ISS), ISS-Lyapunov function,
and the available result 
on the ISS property of a system if it admits 
an ISS-Lyapunov function
(\cite*{jiang:wang:2001, 
rawlings:mayne:diehl:2017}, Appendix B).

\begin{definition} \label{def:robust_pos_invariance}
(Robust positive invariance). A closed set $X$ is 
robustly positive invariant for the system $x^+ = f(x, w)$, 
$w \in \bbW$ if $x \in X$ 
implies $f(x, w) \in X$ for all $w \in \bbW$.
\end{definition}

\begin{definition} \label{def:iss}
(Input-to-state stability (ISS)). $\bbW$ is a compact 
set containing the origin and that $X$ is a closed robustly
positive invariant set for $x^+ = f(x, w)$, $w \in \bbW$. This
system is ISS in $X$ if there exist functions 
$\beta(\cdot) \in \mathcal{K}\mathcal{L}$ and 
$\sigma(\cdot) \in \mathcal{K}$, such that for all
$x \in X$ and $w(i) \in \bbW$, $i \in \bbI_{0:k-1}$, 
$\vert \psi(k; x, \mathbf{w}_k) \vert \leq \beta(\vert x\vert, k) 
+ \sigma(\vert \vert \mathbf{w}_k\vert \vert)$, in which 
$\psi(k; x, \mathbf{w}_k)$ is the solution of the system 
at time $k$.
\end{definition}

\begin{definition} \label{def:iss_lyapunov_func}
(ISS-Lyapunov function). A function $V : X \rightarrow \bbR_{\geq 0}$
is an ISS-Lyapunov function in $X$ for the system $x^+ = f(x, w)$, $w \in \bbW$
if there exist functions $\alpha_1(\cdot), \alpha_2(\cdot), \alpha_3(\cdot) 
\in \mathcal{K}_{\infty}$ and $\sigma(\cdot) \in \mathcal{K}$
such that for all $x \in X$ and $w \in \bbW$
\begin{align*}
    \alpha_1(\vert x \vert) \leq & V(x) \leq \alpha_2(\vert x \vert) \\
    V(f(x, w)) &- V(x) \leq -\alpha_3(\vert x \vert) + \sigma(\vert w \vert)
\end{align*}
\end{definition}

\begin{prop} \label{prop:lyapunov_implies_iss}
(ISS-Lyapunov function implies ISS). $\bbW$ is a compact
set containing the origin and that $X$ is a closed robustly
positive invariant set for $x^+ = f(x, w)$, $w \in \bbW$. If 
$f(\cdot)$ is continuous and there exists a continuous 
ISS-Lyapunov function in $X$ for the system $x^+ = f(x, w)$, $w \in \bbW$, 
then the system is ISS in $X$.
\end{prop}

Additionally, we require the following two 
useful propositions from 
\cite*{allan:bates:risbeck:rawlings:2017} and 
\cite*{rawlings:ji:2012},
to bound values of continuous functions and an
inequality for $\mathcal{K}$ functions respectively.

\begin{prop} \label{prop:continuous_funcs}
    Let $C \subseteq D \subseteq \bbR^n$, $C$ compact, 
    $D$ closed, and $f : D \rightarrow \bbR^n$ continuous.  
    Then there exists a $\sigma(\cdot) \in \mathcal{K}_{\infty}$
    such that for all $x \in C$ and $y \in D$, we have that 
    $\vert f(x) - f(y) \vert \leq \sigma(\vert x-y \vert)$.
\end{prop}

\begin{prop} \label{prop:Kfunction_inequality}
    Let $\sigma(\cdot) \in \mathcal{K}$, the following holds 
    for all $a_i \in \bbR_{\geq 0}$, $i \in \bbI_{1:n}$ 
    \begin{align*}
        \sigma(a_1 + a_2 + \cdot \cdot + a_n) \leq \sigma(na_1) + 
        \sigma(na_2) + \cdot \cdot + \sigma(na_n)
    \end{align*}    
\end{prop}

The above definitions and propositions 
are used to establish the 
following theoretical property for the perturbed
linear system \ref{eq:perturbed_sys}.

\begin{figure*}[!h]
    \centering
	\includegraphics[page=1, 
		width=0.7\textwidth, 
		height=0.5\textheight]{cstrs_comparision_plots.pdf}
    \caption{Transient closed-loop actuator trajectories of the CSTRs with 
    flash separator example with the NN and optimal MPC controllers.}  
    \label{fig:cl_cstrs_inputs}
\end{figure*}

\begin{figure*}[!h]
    \centering
	\includegraphics[page=2, 
		width=0.7\textwidth, 
		height=0.5\textheight]{cstrs_comparision_plots.pdf}
        \caption{Transient closed-loop controlled measurement 
        trajectories of the CSTRs with 
        flash separator example with the NN and optimal MPC controllers.}  
    \label{fig:cl_cstrs_outputs}
\end{figure*}

\begin{thm} \label{thm:nnrobustness}
For all $ 0 < \rho \leq Nd + \tau$, 
there exist constants $\delta_1, \delta_2, \delta_3 > 0$, 
functions $\beta(\cdot) \in \mathcal{K} \mathcal{L}$
and $\alpha_e(\cdot) , \alpha_w(\cdot), \alpha_{n}(\cdot) \in \mathcal{K}$,
such that for all disturbance sequences
satisfying $\vert\vert \mathbf{e}_{k+1} \vert\vert \leq \delta_1$,
$\vert\vert \mathbf{w}_k \vert\vert \leq \delta_2$,
and $\vert e_{NN}(\hat{x}) \vert \leq \delta_3$
for all $\hat{x}$ in the set $S := \textnormal{lev}_{\rho} \ V_N^0(\hat{x})$,
we have the following bound 
$\vert \phi_d(k; \hat{x}) \vert \leq \beta(\vert \hat{x} \vert, k) 
+ \alpha_e(\vert \vert\mathbf{e}_{k+1} \vert \vert) + 
\alpha_w(\vert \vert \mathbf{w}_k \vert \vert) + 
\alpha_n(\bar{e}_{NN})$, 
in which 
$\bar{e}_{NN} = \textnormal{max}_{\hat{x} \in S} \vert e_{NN}(\hat{x}) \vert$.
\end{thm}

\textbf{Proof:}
We proceed in two steps. First, 
we show that there exist constants $\delta_1, \delta_2, \delta_3 > 0$
such that the set $S$ is robustly positive invariant. Then, we 
show that $V_N^0(\hat{x})$ is an ISS Lyapunov function for 
the perturbed system on this set $S$. Denote 
$\tilde{x}^+ = A\hat{x} + B\kappa_N(\hat{x})$ as the nominal 
state evolution using the optimal MPC controller, 
and $d(k) = [ e_{NN}(\hat{x}(k))'B', w(k)', e(k)', e(k+1)']'$
as the combination of all the disturbances at a given time $k$.

To show robust positive invariance of $S$,  
we establish that if $V_N^0(\hat{x}) \leq \rho$, 
then $V_N^0(\hat{x}^+) \leq \rho$.
Since the optimal 
cost function ($V_N^0(\hat{x})$) is continuous,
using $\bbR^n$ as the closed set ($\hat{x}^+ \in \bbR^n$) 
and $S$ as the compact set ($\tilde{x} \in S$),
from proposition \ref{prop:continuous_funcs} we have
\begin{align}
    \vert V_N^0(\hat{x}^+) - V_N^0(\tilde{x}^+) \vert &\leq 
    \sigma_1(\vert \hat{x}^+ - \tilde{x}^+ \vert)  \nonumber  \\
    \vert V_N^0(\hat{x}^+) - V_N^0(\tilde{x}^+) \vert &\leq 
   \sigma_1(\vert B \vert\vert e_{NN}(\hat{x}) \vert + \vert w \vert 
   \nonumber \\
   & + \vert A\vert\vert e \vert +  \vert e^+ \vert) \nonumber \\
    \vert V_N^0(\hat{x}^+) - V_N^0(\tilde{x}^+) \vert &\leq 
   \sigma_1(\vert d \vert + \vert d \vert + \vert A \vert\vert d \vert + \vert d \vert) := \sigma_2(\vert d \vert)
   \label{eq:optimal_cost_bound}
\end{align}
in which $\sigma_2(s) := \sigma_1(\vert A\vert s +3s)$, and the last inequality 
follows because $\vert a \vert \leq \vert [a', b']' \vert$, in which $a$ and $b$
are both vectors.
We partition $S$ in outer and inner parts based on 
the value of the optimal cost $V_N^0(\hat{x})$, and bound the 
combination of disturbances $d$ in each part 
such that $V_N^0(\hat{x}^+) \leq \rho$. \\
Case 1: $\rho/2 \leq V_N^0(\hat{x}) \leq \rho $. Using the 
upper bound on the optimal cost, we have 
$\rho/(2c_2) \leq \vert \hat{x} \vert^2$ for all $\hat{x}$ 
in this part of $S$. To analyze the worst-case disturbance, 
we have from the equation \eqref{eq:optimal_cost_bound} that 
$V_N^0(\hat{x}^+) \leq V_N^0(\tilde{x}^+) + \sigma_2(\vert d \vert) $.
From nominal MPC cost decrease, we obtain  
$V_N^0(\hat{x}^+) \leq V_N^0(\hat{x}) - c_1\vert \hat{x} \vert^2 + \sigma_2(\vert d \vert)$. Thus, if $\sigma_2(\vert d \vert) \leq \rho c_1/(2c_2)$, 
at all times in this outer part of $S$, we have 
$V_N^0(\hat{x}^+) \leq \rho$. \\
Case 2: $V_N^0(\hat{x}) \leq \rho/2 $. From 
equation \eqref{eq:optimal_cost_bound} and nominal MPC 
cost decrease, we have for this part of $S$ that 
$V_N^0(\hat{x}^+) \leq \rho/2 + \sigma_2(\vert d \vert)$.
Thus, if $\sigma_2(\vert d \vert) \leq \rho/2$, 
at all times in this inner part of $S$, we have 
$V_N^0(\hat{x}^+) \leq \rho$.

Therefore, if 
$\vert d \vert \leq \textnormal{min} \{ \sigma_2^{-1}(\rho c_1/(2c_2)), 
\sigma_2^{-1}(\rho/2)\} := \delta_{\textnormal{max}}$ 
at all times, then the set $S$ is 
robustly positive invariant. The constants 
$\delta_1, \delta_2$, and $\delta_3$ are 
$\delta_{\textnormal{max}}/4$ each. The optimal
MPC cost function obeys
\begin{align*}
    V_N^0(\hat{x}^+) - V_N^0(\hat{x}) &\leq 
    -c_1\vert \hat{x} \vert^2 + \sigma_2(\vert d \vert)
\end{align*}
in the robustly positive invariant set $S$,
disturbance set $\vert d \vert \leq \delta_{\textnormal{max}}$,
and from the Definition \ref{def:iss_lyapunov_func},
satisfies the requirements of an ISS-Lyapunov function.
Hence, using the Proposition \ref{prop:lyapunov_implies_iss}, 
the perturbed linear system \ref{eq:perturbed_sys} is
ISS (Definition \ref{def:iss}), 
and there exist functions 
$\beta(\cdot) \in \mathcal{K}\mathcal{L}$ and 
$\sigma(\cdot) \in \mathcal{K}$, such that 
$\vert \phi_d(k; \hat{x}) \vert \leq \beta(\vert \hat{x} \vert, k) 
+ \sigma(\vert\vert \mathbf{d}_k\vert\vert)$. Using the Proposition
\ref{prop:Kfunction_inequality}, we have 
\begin{align*}
    \vert \phi_d(k; \hat{x}) \vert & \leq \beta(\vert \hat{x} \vert, k) \\
    + &\sigma(3\vert B\vert\bar{e}_{NN}) + 
    \sigma(3\vert \vert \mathbf{w}_k \vert \vert)
    + \sigma(3(\vert A\vert + 1)\vert \vert \mathbf{e}_{k+1} \vert\vert)
\end{align*}
Therefore, the bound in the Theorem \ref{thm:nnrobustness} is established with 
$\alpha_e(s) := \sigma(3(\vert A\vert + 1)s)$, 
$\alpha_w(s) := \sigma(3s)$, and
$\alpha_n(s) := \sigma(3\vert B\vert s)$.

In the nominal case, 
the disturbance sequences $\mathbf{e}$ and $\mathbf{w}$ are zero.
The closed-loop states in this case have the bound
$\vert \phi(k; x) \vert \leq \beta(\vert x \vert, k) + 
\alpha_n(\bar{e}_{NN})$. Any additional value of 
the NN training is to reduce the worst 
approximation error ($\bar{e}_{NN}$) 
in the state-space of interest and 
strengthen the bounds on the closed-loop states.

\section{Simulation studies} \label{sec:simulation_studies}
In this section, two case studies are presented 
which demonstrate the 
scalability of the proposed NN design approach.
The closed-loop performance of NNs and computational benefits over 
online QP based MPC are analyzed in these case studies.
After the offline design of NNs,
validation simulations are performed with 
setpoints and disturbances not present 
in the training data but within the same range 
of values chosen to generate the training data.
The closed-loop performance of the 
following alternative and 
equivalently fast controllers as NNs are also compared
in the validation simulations.
a) steady state controller (SS): the solution
of the target selector is directly applied to the plant 
$u = u_s$, b) saturated linear quadratic regulator (satK):
the unconstrained LQR gain 
$K$ is computed and used in the control law 
$u = \textnormal{sat}(K(x-x_s) + u_s, \underline{u}, \overline{u})$,
c) short horizon controller (SH): an MPC problem
with short control horizon is solved online, 
d) Unstructured NN (NN-UNS): a standard feedforward network is 
trained with the triple ($x, x_s, u_s$) as the input
and then used as the feedback controller online.

To gauge the performance of NNs in 
the validation simulations, and the offline
computational effort required to build the NNs, 
the following metrics are examined:

\begin{itemize}
    \item Controller performance index \\
    $\Lambda_k = \dfrac{1}{k}\sum_{t=1}^{k} \big(\vert x(t) - x_{s} (t) \vert^2_{Q} + \vert u(t) - u_{s} (t) \vert^2_{R} \big)$
    \item \% Performance loss = $100(\Lambda^{F}_{N_{t}} - \Lambda^{MPC}_{N_{t}})/\Lambda^{MPC}_{N_{t}}$
    \item Average and worst-case speedups
    \item Data generation and NN training times
    \item Memory required to store the weights of NNs
\end{itemize}
in which $N_t$ is the number of simulation time steps,  
$\Lambda^{F}_{N_{t}}$ and $\Lambda^{MPC}_{N_{t}}$
are the average stage costs obtained 
at the end of the simulation period by the 
fast controllers and the MPC controller.
The data generation and online timing comparisons are 
performed on a computing cluster that has 
several multi-core CPUs of clock speed 2.4GHz. 
The NN trainings are performed on a 
Tesla V100-SXM2 GPU that has 32 GB memory.
\begin{table*}[t]
    \caption{Summary of the simulation study for the
    CSTRs with a flash separator example.}   
    \begin{tabular}{ |c|c|c|c|c|c|c|c| }
        \hline
        Controller & \thead{Structured network \\ architecture} & 
        \thead{Number of \\ Parameters} & 
        \thead{Memory \\ footprint (mB)} & \thead{Training \\ time (min)} &
        \thead{\% Performance\\ loss} & \thead{Average \\ speedup} & \thead{Worst case \\ speedup} \\
        \hline
    SS &  &  & &  & 106.39 \% &  & \\ 
    satK &  &  &  &  & 27.61 \% & $2.59 \times 10^5$ & 
    $3.16 \times 10^4$ \\ 
    SH &  &  &  &  & 2.46 \% & $5.66 \times 10^3$ & $1.88 \times 10^2$ \\ 
    NN-UNS &  &  &  &  & 107.28 \% & $3.17 \times 10^4$ & $6.19 \times 10^3$ \\ 
NN-3-448 & [72, 448, 448, 448, 6] & $1.18 \times 10^5$ & 0.84 & 12.7 & 0.27 \% & $2.34 \times 10^4$ & $7.18 \times 10^3$ \\ 
NN-3-480 & [72, 480, 480, 480, 6]  & $1.34 \times 10^5$ & 0.96  & 12.6 & 0.28 \% & $2.12 \times 10^4$ & $3.12 \times 10^3$ \\ 
NN-3-512 & [72, 512, 512, 512, 6]  & $1.51 \times 10^5$ & 1.08  & 14.3 & 0.16 \% & $1.91 \times 10^4$ & $2.14 \times 10^3$ \\ 
NN-3-544 & [72, 544, 544, 544, 6]  & $1.71 \times 10^5$ & 1.22  & 18.6 & 0.39 \% & $1.80 \times 10^4$ & $4.03 \times 10^3$ \\ 
        \hline
       \end{tabular}
       \label{table:cstrs}      
\end{table*}

\begin{figure*}[!h]
    \includegraphics[page=21,
        width=0.5\textwidth, 
        height=0.3\textheight]{cstrs_comparision_plots.pdf} \hfill
    \includegraphics[page=23,
        width=0.5\textwidth, 
        height=0.3\textheight]{cstrs_comparision_plots.pdf} \vfill
    \vspace{-0.1in}
    \begin{center}\includegraphics[page=22,
        width=0.5\textwidth, 
        height=0.3\textheight]{cstrs_comparision_plots.pdf}\end{center}
    \vspace{-0.2in}
    \caption{Simulation statistics for the  
    CSTRs with a flash separator example. Data requirements to obtain accurate NN controllers (top left), online computation times of the NNs and 
    MPC controller (top right), 
    and the controller performance index obtained with the NNs, 
    SS, satK and MPC controllers (center bottom).}	
    \label{fig:cstrs_statistics}
\end{figure*}

\subsection{CSTRs with a flash separator}
For the first example, the two 
stirred tank reactors in series with a flash separator
depicted in Figure \ref{fig:schematic_cstrs} 
is considered as the plant.
In both the CSTRs, a desired product $B$ is produced 
with the reaction $A \rightarrow B$, and an undesired 
product $C$ is produced with the reaction $B \rightarrow C$. 
The reactant $A$ is the major component in the 
feed streams supplied to the 
reactors. After the second CSTR, the reaction mixture is 
sent to the non-adiabatic flash that separates the reactant $A$
from the product $B$. The $A$ rich vapor phase 
is recycled back to the first CSTR. 
The plant is simulated using the set of 
nonlinear ordinary differential equations (ODEs) available in 
\cite*{stewart:venkat:rawlings:wright:pannocchia:2010}.
The model has 12 states 
($H_r, x_{Ar}, x_{Br}, T_r, 
H_m, x_{Am}, x_{Bm}, T_m, H_b, x_{Ab}, x_{Bb}, T_b$),
6 control inputs 
($F_0, F_1, D, Q_r, Q_m, Q_b$), and 5 disturbances
($x_{A0}, x_{A1}, x_{B0}, x_{B1}, T_0$).
The controlled measurements with setpoints are the heights
and temperatures of the three units, and we
assume that all the states are measured for this example. 
The sample time for the measurements is chosen as 10 seconds. 
The parameter values used to simulate the ODEs for the plant, 
the actuator constraints, and the bounds of the controlled 
measurements and disturbances used for the data generation 
and validation simulations are 
shown in Table \ref{table:cstrs_pars}.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth, 
                     height=0.22\textheight]{cstrs_with_flash.pdf}
    \caption{Schematic of the CSTRs with a flash separator model}
    \label{fig:schematic_cstrs}
\end{figure}

\renewcommand{\arraystretch}{1.1}
\begin{table}[h]
    \centering
    \resizebox{\columnwidth}{!}{
    \begin{tabular}{|c|c|c|c|c|c|}
        \hline
        \multicolumn{6}{ |c| }{Parameters used to simulate the ODEs} \\
        \hline
        Parameter & Value & Unit & Parameter & Value & Unit\\
        \hline
        $\alpha_A$ & 3.5 &  & $k_m$ & 2.5 & \unit{m$^2$}\\ 
        $\alpha_B$ & 1.1 &  & $k_b$ & 1.5 & \unit{m$^2$} \\ 
        $\alpha_C$ & 0.5 &  & $\Delta H_1$ & -40 & \unitfrac{kJ}{kg} \\ 
        $\rho$ & 50 & \unitfrac{kg}{m$^3$} & $\Delta H_2$ & -50 
        & \unitfrac{kJ}{kg} \\ 
        $C_p$ & 3 & \unitfrac{kJ}{kg-K} & $E/R$ & 150 & \unit{K} \\ 
        $A_r$ & 0.3 & \unit{m$^2$} & $k^{\star}_1$ & $4 \times 10^{-4}$ & 
        \unit{sec$^{-1}$} \\ 
        $A_m$ & 2 & \unit{m$^2$} & $k^{\star}_2$ & $1.8 \times 10^{-6}$ & \unit{sec$^{-1}$} \\ 
        $A_b$ & 4 & \unit{m$^2$} & $T_d$ & 313 & \unit{K} \\ 
        $k_r$ & 2.5 & \unit{m$^2$} &  &  &  \\ 
        \hline
        \multicolumn{6}{ |c| }{Actuator constraints ($\underline{u}, 
        \overline{u}$)} \\
        \hline
        $F_0$ & (1.5, 2.5) & \unitfrac{kg}{m$^3$} & 
        $Q_r$ & (-500, 500) & \unit{kW} \\ 
        $F_1$ & (0.5, 1.5) & \unitfrac{kg}{m$^3$} & 
        $Q_m$ & (-500, 500) & \unit{kW} \\ 
        $D$ & (29.5, 30.5) & \unitfrac{kg}{m$^3$} & 
        $Q_b$ & (-500, 500) & \unit{kW} \\ 
        \hline
        \multicolumn{6}{ |c| }{Setpoint bounds ($\underline{r}_{sp}, 
        \overline{r}_{sp}$)} \\
        \hline
        $H_r$ & (158.8, 168.8) & \unit{m} & 
        $T_r$ & (303, 323) & \unit{K} \\ 
        $H_m$ & (169.2, 179.2) & \unit{m} & 
        $T_m$ & (310, 316) & \unit{K} \\ 
        $H_b$ & (2.2, 4.2) & \unit{m} & 
        $T_b$ & (303, 323) & \unit{K} \\ 
        \hline
        \multicolumn{6}{ |c| }{Disturbance bounds ($\underline{d}, 
        \overline{d}$)} \\
        \hline
        $x_{A0}$ & (0.7, 0.85) & & 
        $x_{B1}$ & (0, 0.15) & \\ 
        $x_{B0}$ & (0, 0.15) & & 
        $T_0$ & (305, 321) & \unit{K} \\ 
        $x_{A1}$ & (0.7, 0.85) & & 
         & & \\ 
        \hline
        \multicolumn{6}{ |c| }{Steady state used for linearization 
        ($x_s, u_s, d_s$)} \\
        \hline
        $H_r$ & 163.8 & \unit{m} & $F_0$ & 2 & \unitfrac{kg}{m$^3$} \\ 
        $x_{Ar}$ & 0.40 &  & $F_1$ & 0 & \unitfrac{kg}{m$^3$} \\ 
        $x_{Br}$ & 0.54 &  & $D$ & 1 & \unitfrac{kg}{m$^3$} \\ 
        $T_r$ & 313.1 & \unit{K} & $Q_r$ & 0
        & \unit{kW} \\ 
        $H_m$ & 174.2 & \unit{m} & $Q_m$ & 0 & \unit{KW} \\ 
        $x_{Am}$ & 0.37 &  & $Q_b$ & 0 & 
        \unit{kW} \\ 
        $x_{Bm}$ & 0.58 & & $x_{A0}$ & 0.8 &  \\ 
        $T_m$ & 313.7 & \unit{K} & $x_{B0}$ & 0.1 & \\ 
        $H_b$ & 3.24 & \unit{m} &  $x_{A1}$&  0.8&  \\ 
        $x_{Ab}$ & 0.15 &  & 
        $x_{B1}$ & 0.1 &  \\ 
        $x_{Bb}$ & 0.73 &  & 
        $T_0$ & 313 & \unit{K} \\ 
        $T_b$ & 313.7 & \unit{K} & 
         & & \\ 
        \hline
    \end{tabular}}
    \caption{Parameters used in the ODEs to 
    simulate the plant in the CSTRs in series
    with a flash separator example, 
    actuator constraints, 
    setpoint and disturbance bounds, 
    and the steady state used to obtain the 
    linear model for the MPC controller.}
    \label{table:cstrs_pars}
\end{table}

A linear discrete time model with the chosen sample time
is obtained at the steady state shown in the table 
\ref{table:cstrs_pars}.
This model, inputs and outputs are scaled 
for the MPC controller such that
$\overline{u} - \underline{u} = \mathbf{2}$ and
$\overline{y} - \underline{y} = \mathbf{2}$.
The tuning parameters and 
control horizon length for the regulator are chosen as
$Q = 10^3 C'C$, $R = 0.1 I$, $S = 0.1 I$, 
and $N = 450$.
A total $1.5 \times 10^5$ samples of 
($x, u_{-1}, x_s, u_s, \kappa_N(\cdot)$) 
is generated for NN training, parallelized in 100 
separate offline simulations. The time consumed 
for this data generation step was 4.9 hours.

Four structured NN architectures 
are considered. Each NN
has three hidden layers with 
448 (NN-3-448), 480 (NN-3-480), 
512 (NN-3-512), and 544 (NN-3-544) 
nodes in each hidden 
layer respectively. For validation simulations, 
setpoint and disturbance signals 
with 24 setpoint changes and 48 disturbance changes 
is generated for 4320 timesteps (12 hours). 
The short horizon MPC controller is constructed with a 
horizon length of $N = 10$, and the architecture 
of the unstructured NN considered 
is three hidden layers with 224 nodes in each hidden layer. 
An additional scaling of $x$ and $x_s$ is performed for the 
NN training as $x := 2x/(x_{\textnormal{max}} - x_{\textnormal{min}})$ and 
$x_s := 2x_s/(x_{\textnormal{max}} - x_{\textnormal{min}})$,
in which $x_{\textnormal{max}}$ and $x_{\textnormal{min}}$
are the maximum and minimum values of the state 
observed in the training data.
This scaling is also performed in real-time 
when the NN is used to compute the actuator move.

First, the amount of data required to obtain an accurate 
NN controller is studied. To this aim, the four chosen NN 
architectures are trained with incremental increases of 
$10^4$ training samples starting from $4 \times 10^4$
to $1.5 \times 10^5$ samples. The trained NNs 
are then used in validation simulations
with the generated validation setpoint and disturbance
signals. The closed-loop performance is compared with the optimal MPC 
controller and the $\%$ performance loss obtained
is plotted in Figure \ref{fig:cstrs_statistics} (top left)
as a function of the number of training samples.
All the trained NNs provide less than $1 \%$ loss in 
this performance metric after training with 
about $10^5$ samples. The best $\%$ performance
loss obtained by the NNs is summarized in
Table \ref{table:cstrs}.

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.45\textwidth, 
                     height=0.25\textheight]{cdu.pdf}
    \caption{Schematic of the industrial crude distillation unit model}
    \label{fig:schematic_cdu}
\end{figure}

\begin{table*}[t]
    \caption{Summary of the simulation study for the 
    industrial crude distillation unit example.}
    %\centering
\begin{tabular}{ |c|c|c|c|c|c|c|c| }
          \hline
          Controller & \thead{Structured network \\ architecture} & 
          \thead{Number of \\ Parameters} & 
          \thead{Memory \\ footprint (mB)} & \thead{Training \\ time (min)} &
          \thead{\% Performance\\ loss} & \thead{Average \\ speedup} & \thead{Worst case \\ speedup} \\
          \hline
      SS &  &  & &  & 120.59 \% &  & \\ 
  satK &  &  &   &  & 13.07 \% & $4.05 \times 10^5$ & $1.06 \times 10^5$ \\ 
  SH &  &  &  &  & 1.56 \% & $7.18 \times 10^3$  & $2.57 \times 10^3$ \\ 
  NN-3-1664 & [1072, 1664, 1664, 1664, 32] & $1.85 \times 10^6$ & 14.18 & 61.76 & 0.61 \% & $1.62 \times 10^4$ & $5.45 \times 10^3$  \\ 
  NN-3-1792 & [1072, 1792, 1792, 1792, 32]  & $2.11 \times 10^6$ & 16.15  & 56.37 & 0.71 \% & $1.42 \times 10^4$ & $5.30 \times 10^3$ \\ 
  NN-3-1920 & [1072, 1920, 1920, 1920, 32]  & $2.39 \times 10^6$ & 18.24  & 56.25 & 0.34 \% & $1.28 \times 10^4$ & $4.22 \times 10^3$ \\ 
  NN-3-2048 & [1072, 2048, 2048, 2048, 32]  & $2.68 \times 10^6$ & 20.46  & 66.01 & 0.47 \% & $1.13 \times 10^4$ & $4.42 \times 10^3$\\ 
\hline
\end{tabular}
\label{table:cdu}      
\end{table*}

\begin{figure*}[!h]
    \includegraphics[page=41,
        width=0.5\textwidth, 
        height=0.3\textheight]{cdu_comparision_plots.pdf} \hfill
    \includegraphics[page=43,
        width=0.5\textwidth, 
        height=0.3\textheight]{cdu_comparision_plots.pdf} \vfill
    \vspace{-0.1in}
    \begin{center}\includegraphics[page=42,
        width=0.5\textwidth, 
        height=0.3\textheight]{cdu_comparision_plots.pdf}\end{center}
    \vspace{-0.2in}
    \caption{Simulation statistics for the industrial 
    crude distillation unit example. Data requirements to obtain accurate NN controllers (top left), online computation times of the NNs and 
    MPC controller (top right), 
    and the controller performance index obtained with the NNs, 
    satK and MPC controllers (center bottom).}
	\label{fig:cdu_statistics}
\end{figure*}

Second, the transient closed-loop 
performance of the trained NNs is examined
for one particular simulation. The Figures 
\ref{fig:cl_cstrs_inputs} and \ref{fig:cl_cstrs_outputs}
show the transient actuator 
and controlled outputs obtained with the NN-3-448 and 
optimal MPC controllers for a simulation period of 2 hours.
The Figure \ref{fig:cstrs_statistics} (center bottom)
shows the transient values of the controller performance index
obtained in this validation simulation
with the four structured NNs, SS, satK 
and optimal MPC controllers for the full 
simulation period of 12 hours. The closed-loop 
performance obtained using NNs is almost same as the optimal MPC 
controller and the degradation in the performance 
is quantified with the $\%$ performance loss metric.

Third, the online computational benefits of NNs 
over the QP based MPC is analyzed. The Figure 
\ref{fig:cstrs_statistics} (top right)
shows a histogram of online computation times
of the NNs and QP solver in the above validation
simulation. The average and worst-case speedups
obtained using NNs are summarized in the 
Table \ref{table:cstrs}. The QP solver takes 
about 9 to 14 seconds in this example and all the 
NNs compute the control in just 0.4 to 3 milliseconds, 
and are conveniently deployable in the 
sample time of 10 seconds.

The $\%$ performance loss 
obtained using the four heuristic controllers, 
their corresponding speedups, time required to 
train each NN, number of parameters in each NN, 
and the memory required to store  
the weights of each NN is summarized in the 
Table \ref{table:cstrs}. The $\%$ performance loss 
reported for the unstructured
NN is after training with $1.5 \times 10^5$  
samples and the performance is unacceptable 
for an industrial application. 
This noticeable performance improvement with the
structured NNs is because the control law 
is exactly the same as the optimal feedback law
at steady states, and the training process improves the 
approximation of the optimal feedback law
by the NN only for the transient states.

\subsection{Large-scale crude distillation unit}

The scalability of the proposed NN design 
approach is demonstrated on an industrial crude 
distillation unit model \citep*{pannocchia:rawlings:wright:2007} 
with 252 states, 32 controls, and 90 measurements. The 
schematic of this model is shown in the Figure \ref{fig:schematic_cdu}, 
that is a typical crude unit found in petrochemical refineries.
The plant model is linear, input and outputs are scaled 
for the MPC regulator similar to the previous example.
Four measurements which represent 
the quality of the crude side products have setpoints, 
and five disturbances are used on the crude composition, 
fuel gas quality, and steam header pressure. 
The sample time for the measurements is 1 min. The tuning 
parameters and control horizon length for the 
MPC regulator are chosen as $Q = 2C'C$, $R = 0.1I$, 
and $N = 145$. A total $3.576 \times 10^5$ 
samples of ($x, x_s, u_s, \kappa_N(\cdot)$)
are generated for the NN training, parallelized over 
149 offline simulations. The time consumed 
for this data generation step was 27.8 hours.

Four structured NN architectures 
are considered for this example. Each NN
has three hidden layers, with 
1664 (NN-3-1664), 1792 (NN-3-1792), 
1920 (NN-3-1920), and 2048 (NN-3-2048) 
nodes in each hidden layer respectively. 
For the validation simulations, 
setpoint and disturbance signals 
with 24 setpoint changes and 48 disturbance changes 
is generated for 2880 timesteps (2 days). 
The short horizon MPC controller is constructed with a 
horizon length of $N = 3$. 
The states and target steady states 
($x$, $x_s$) are scaled for the NN training
similar to the previous example.

The Figure \ref{fig:cdu_statistics} shows the 
statistics for the simulation study performed for this 
example. The data requirements to obtain 
an accurate NN controller is shown in top left.
The transient controller performance index 
for one validation simulation
obtained with the four structured NNs,
satK, and MPC controllers is shown in center bottom.
The top right plot shows the 
histogram of online computation times 
of the NNs and QP solver.
The Table \ref{table:cdu} gives a summary of 
the maximum time required to train the NNs, number of parameters
in each NN, memory footprint of the NNs, and 
the $\%$ performance loss metric obtained by 
the structured NNs, SS, satK, and SH 
controllers in the validation simulations.

The offline data generation and training times 
for the NNs shows that this large-scale example
is tractable with the proposed NN approach.
This large example is challenging, 
since on average the QP solver CVXOPT takes 37 seconds
and 57 seconds in the worst-case. In comparison,  
all the NNs execute MPC in about 2 to 6 milliseconds.
As observed from the plot of the transient controller 
performance index, the performance 
degradation by the NNs compared with 
the optimal MPC controller is negligible.
The sampling of the state-space for NN training
for one particular operational scenario 
with the corresponding setpoint and disturbance signals 
is the rule to obtain scalability of the NN controllers.

\section{Conclusion} \label{sec:conclusion}
Neural networks have been demonstrated 
to approximate the MPC feedback law 
for treating large-scale, linear MPC applications
that may be challeging with QP solvers. 
The proposed no online optimization-based 
methods in the literature such as storing 
the entire MPC feedback law 
and sampling the large dimensional state-space 
for the NN training are not tractable for the size of problems 
considered in this article.

The key features for scalability of the proposed approach 
are the structure of NN and data generation for only the 
typical plant operational scenarios. 
The NN design approach was demonstrated to scale on a
industrial crude distillation unit model with state and
control dimensions of 252 and 32 respectively, and 
a control-sample horizon length of 145 in the QP. 
Parallel computing was used for the data 
generation and graphical processing units for the NN 
training. After the offline design phase, NNs execute MPC 
about three to five orders of magnitude faster than an 
available QP solver 
with less than 1$\%$ performance degradation in the closed-loop. 
The NNs are easily deployable on memory constrained hardware.
Robustness properties
of NNs were established under bounded approximation errors of the optimal 
feedback law, that provides some theoretical support 
to practitioners interested in the deployment of NNs.

As larger and wide range of
control applications are considered by practitioners, 
the presented NN controller design approach 
provides a new method to address MPC applications.

\section*{Acknowledgement}
The authors would like to acknowledge the industrial
members of the Texas-Wisconsin-California Control (TWCCC)
consortium for funding support.
The computational facilities purchased with funds from the National Science Foundation (CNS-1725797) and administered by the Center for Scientific Computing (CSC) was used for the simulation 
studies presented in this article. 
The CSC is supported by the California NanoSystems Institute and the Materials Research Science and Engineering Center 
(MRSEC; NSF DMR 1720256) at UC Santa Barbara.

%% New version of the num-names style
\bibliographystyle{elsarticle-num-names}
\bibliography{abbreviations,articles,books,unpub,proceedings}
\end{document}

### 2020-09-05 cdu_comparision_plots.py

@@ -1,0 +1,356 @@
+# [depends] cdu_parameters.pickle cdu_mpc.pickle cdu_us.pickle
+# [depends] cdu_satdlqr.pickle cdu_short_horizon.pickle cdu_train.pickle
+# [depends] cdu_neural_network.pickle
+"""
+Script to run an on-line simulation using the double integrator example
+using the optimal MPC controller.
+Since for the double integrator example, on-line simulation does not
+takes much time, both plotting and the simulation tasks are in
+the same script.
+"""
+# import custompath
+# custompath.add()
+import sys
+sys.path.append('lib/')
+import plottools
+import numpy as np
+import itertools
+import matplotlib.pyplot as plt
+from cdu_labels import (ulabels, zlabels, ylabels, pdlabels)
+from python_utils import (PickleTool, figure_size_cl, 
+                         figure_size_a4, figure_size_metrics)
+from matplotlib.backends.backend_pdf import PdfPages
+from controller_evaluation import (plot_cl_performance_and_comp_times,
+                                   plot_nn_vs_num_samples_performance,
+                                   _load_data_for_plots, _set_font_size,
+                                   _get_best_nn_plant_controllers)
+
+def _get_cdu_data_for_plotting(plant, controller, setpoints,
+                               parameters, plot_range):
+    """ Get the appropriate arrays for plotting."""
+    # Get some plotting cosmetics.
+    yscale = parameters['yscale'].squeeze(axis=-1)
+    uscale = parameters['uscale'].squeeze(axis=-1)
+    ulb = parameters['lb']['u']
+    uub = parameters['ub']['u']
+    us = parameters['us'].squeeze(axis=-1) 
+    ys = parameters['ys'].squeeze(axis=-1)
+    dist_indices = parameters['dist_indices']
+    pscale = uscale[dist_indices, ]
+    (start, end) = plot_range
+    #  Get the H matrix.
+    (Ny, _) = plant.C.shape
+    Nc = 4
+    H = np.concatenate((np.zeros((Nc, Ny-Nc)), np.eye(Nc)), axis=1)
+    # Get the plant arrays.
+    y = np.asarray(plant.y[start:end]).squeeze()*yscale + ys
+    z = y @ H.T
+    u = np.asarray(plant.u[start:end]).squeeze()*uscale + us
+    p = np.asarray(plant.p[start:end]).squeeze()#*pscale
+    t = np.asarray(plant.t[start:end]).squeeze()/60
[…]

### 2020-09-05 cdu_mpc.py

@@ -1,0 +1,18 @@
+# [depends] cdu_parameters.pickle
+# [makes] pickle
+"""
+Script to run an on-line simulation using the double integrator example
+using the optimal MPC controller.
+Since for the double integrator example, on-line simulation does not
+takes much time, both plotting and the simulation tasks are in 
+the same script.
+"""
+import sys
+sys.path.append('lib/')
+from python_utils import PickleTool
+from controller_evaluation import _simulate_scenarios
+
+# Simulate all the scenarios.
+_simulate_scenarios(plant_name='cdu', 
+                    controller_name='mpc',
+                    Nsim=2880)

### 2020-09-05 cdu_mpc_plot.py

@@ -1,0 +1,184 @@
+# [depends] cdu_parameters.pickle cdu_mpc.pickle
+"""
+Script to run an on-line simulation using the double integrator example
+using the optimal MPC controller.
+Since for the double integrator example, on-line simulation does not
+takes much time, both plotting and the simulation tasks are in
+the same script.
+"""
+import sys
+sys.path.append('lib/')
+import numpy as np
+import itertools
+from cdu_labels import (ylabels, ulabels, zlabels, pdlabels)
+import matplotlib.pyplot as plt
+from python_utils import (PickleTool, figure_size_a4)
+from matplotlib.backends.backend_pdf import PdfPages
+from cdu_comparision_plots import _get_cdu_data_for_plotting
+
+def _cdu_optimal_plot(plant, controller, parameters, 
+                        setpoints, plot_range):
+    """Data to plot.
+    z: 4 outputs with setpoints. y:90 outputs. u:32 inputs.
+    """
+    # the x coordinate of the ylabels.
+    ylabel_xcoordinate = -0.25
+    # Get the arrays.
+    (t, z, y, u, pest, p, 
+      ulb, uub, zsp, ell) = _get_cdu_data_for_plotting(plant,  
+                                                       controller, setpoints,
+                                                       parameters, plot_range)
+    # Make the plots.
+    figures = plot_inputs(t, u, ulabels, ylabel_xcoordinate, ulb, uub)
+    figures += plot_outputs(t, y, ylabels, ylabel_xcoordinate)
+    figures += plot_controlled_outputs(t, z, zsp, zlabels, ylabel_xcoordinate)
+    figures += plot_disturbances(t, p, pest, 
+                                 pdlabels, ylabel_xcoordinate)
+    figures += plot_average_stage_costs(t, ell, 
+                            ylabel_xcoordinate)
+    # Return the list of figures.
+    return figures
+
+def plot_inputs(t, u, ulabels, ylabel_xcoordinate, 
+                ulb, uub):
+    """Return 4 figure objects which contain the plots of the inputs."""
+    num_pages = 2
+    num_rows = 8
+    num_cols = 2
+    input_index = 0
+    figs_and_axes = [plt.subplots(nrows=num_rows, ncols=num_cols,
+                                 sharex='col', figsize=figure_size_a4, 
+                                 gridspec_kw = dict(wspace=0.5))
+                            for _ in range(num_pages)]
+    for (page, row, column) in itertools.product(range(num_pages),
[…]

### 2020-09-05 cdu_neural_network.py

@@ -1,0 +1,12 @@
+# [depends] cdu_parameters.pickle cdu_train.pickle
+# [makes] pickle
+"""
+Script to run an on-line simulation for the double integrator example
+using the approximate NN controller.
+"""
+import sys
+sys.path.append('lib/')
+from controller_evaluation import _simulate_neural_networks
+
+# Load data and do an online simulation using the linear MPC controller.
+_simulate_neural_networks(plant_name='cdu', Nsim=2880, nnwithuprev=False)

### 2020-09-05 cdu_neural_network_unstd.py

@@ -1,0 +1,38 @@
+# [depends] cdu_parameters.pickle cdu_train_unstd.pickle
+# [makes] pickle
+"""
+Script to run an on-line simulation for the double integrator example
+using the approximate NN controller.
+"""
+import sys
+sys.path.append('lib/')
+from python_utils import (PickleTool, figure_size_a4)
+from matplotlib.backends.backend_pdf import PdfPages
+from cdu_comparision_plots import _cdu_cl_comparision_plots
+from controller_evaluation import _simulate_neural_network_unstd
+
+# Load data and do an online simulation using the linear MPC controller.
+(plants, controllers) = _simulate_neural_network_unstd(plant_name='cdu', 
+                                    Nsim=2880, nnwithuprev=False)
+
+# Load data and do an online simulation using the linear MPC controller.
+cdu_parameters = PickleTool.load(filename='cdu_parameters.pickle', 
+                                 type='read')
+scenarios = cdu_parameters['online_test_scenarios']
+plant_parameters = cdu_parameters['cdu_plant_parameters']
+
+mpc_parameters = PickleTool.load(filename='cdu_mpc.pickle', 
+                                        type='read')
+(mpc_plants, mpc_controllers) = (mpc_parameters['plants'], 
+                                 mpc_parameters['controllers'])
+figures = _cdu_cl_comparision_plots(scenarios, 
+                            mpc_plants, mpc_controllers,
+                            plants, controllers, 
+                            'NN-UNSTD',
+                            plant_parameters,
+                            (0, 2880))
+
+# Save the figures for the two simulations.
+with PdfPages('cdu_neural_network_unstd.pdf', 'w') as pdf_file:
+    for fig in figures:
+        pdf_file.savefig(fig)

### 2020-09-05 cdu_offline_data.py

@@ -1,0 +1,16 @@
+# [depends] cdu_parameters.pickle
+# [makes] pickle
+"""
+Script to generate offline data for training the neural net.
+"""
+import sys
+sys.path.append('lib/')
+from python_utils import PickleTool
+
+# Load data and do an online simulation using the linear MPC controller.
+task_number = int(sys.argv[1]) - 1
+cdu_parameters = PickleTool.load(filename='cdu_parameters.pickle', 
+                                 type='read')
+cdu_parameters['offline_simulator'].generate_data(task_number=task_number,   
+                    data_filename='cdu_offline_data.h5py',
+                    stdout_filename=str(task_number)+'-cdu_offline_data.txt')

### 2020-09-05 cdu_offline_data_post_processing.py

@@ -1,0 +1,14 @@
+"""
+Post process the offline generated dataset.
+"""
+import sys
+sys.path.append('lib/')
+from python_utils import H5pyTool
+import os
+import itertools
+import numpy as np
+from controller_evaluation import _post_process_data
+
+_post_process_data(data_filename='cdu_offline_data.h5py', 
+                   num_data_gen_task=int(sys.argv[1]),
+                   num_process_per_task=1)

### 2020-09-05 cdu_offline_plot.py

@@ -1,0 +1,166 @@
+# [depends] cdu_parameters.pickle cdu_offline_data.pickle
+"""
+Script to run an on-line simulation using the double integrator example
+using the optimal MPC controller.
+Since for the double integrator example, on-line simulation does not
+takes much time, both plotting and the simulation tasks are in
+the same script.
+"""
+import sys
+sys.path.append('lib/')
+import numpy as np
+import itertools
+from cdu_labels import ulabels, ylabels, zlabels, pdlabels
+import matplotlib.pyplot as plt
+from python_utils import (PickleTool, figure_size_a4)
+from matplotlib.backends.backend_pdf import PdfPages
+
+def _get_arrays_for_plotting(offline_data, parameters, num_samples):
+    """ Get the appropriate arrays for plotting."""
+
+    # Extract some parameters.
+    setpoints = parameters['offline_simulator'].setpoints
+    lb = parameters['cdu_plotting_parameters']['lb'] 
+    ub = parameters['cdu_plotting_parameters']['ub']
+    us = parameters['cdu_plotting_parameters']['us'] 
+    ys = parameters['cdu_plotting_parameters']['ys']
+    disturbance_indices = parameters['cdu_plotting_parameters']['disturbance_indices']
+
+    #  Get the H matrix.
+    (Ny, _) = parameters['plant'].C.shape
+    Nc = 4
+    (Nx, Nu) = parameters['plant'].B.shape
+    H = np.concatenate((np.zeros((Nc, Ny-Nc)), np.eye(Nc)), axis=1)
+
+    # Scaling for the inputs, outputs.
+    yscale = parameters['cdu_plotting_parameters']['yscale'].squeeze()
+    uscale = parameters['cdu_plotting_parameters']['uscale'].squeeze()
+    pscale = np.take(uscale, disturbance_indices).squeeze()
+    zscale = H @ yscale
+    
+    # Control inputs.
+    u = np.asarray(offline_data['useq'][0:num_samples, ...]).squeeze(axis=-1)[:, 0:Nu]*uscale + us.squeeze()
+
+    # Disturbances.
+    p = np.asarray(offline_data['d'][0:num_samples, ...])*pscale
+
+    # All the outputs.
+    y = np.asarray(offline_data['y'][0:num_samples, ...]).squeeze(axis=-1)*yscale + ys.squeeze()
+
+    # The time index.
+    t = np.arange(num_samples)
+
+    # Outputs without offset.
+    zs = H @ ys
[…]

### 2020-09-05 cdu_parameters.py

@@ -1,0 +1,231 @@
+# [makes] pickle
+""" 
+Generate the parameters for the offline data generation and 
+the online simulation for the crude distillation unit model. 
+"""
+#import custompath
+#custompath.add()
+import sys
+sys.path.append('lib/')
+import matio
+import scipy.linalg
+import numpy as np
+from python_utils import PickleTool
+from controller_evaluation import (sample_prbs_like, 
+                                   _get_satdlqr_controller,
+                                   _get_us_controller,
+                                   _get_short_horizon_controller)
+from linearMPC import (LinearPlantSimulator, LinearMPCController,
+                       OfflineSimulator)
+
+def _get_scaled_parameters(model, dist_indices, dist_scaling):
+    """ Get the scaling. Both u and y are scaled as:
+    unew = u/(0.5*(uub-ulb), ynew = y/(0.5*(yub-ylb))
+    and B = B*uscale, C = C/yscale.
+    """
+    # Extract out the things to be scaled.
+    A = model['A']
+    B = model['B']
+    C = model['C']
+    lb = dict(u=model['ulb']-model['us'], y=model['ylb']-model['ys'])
+    ub = dict(u=model['uub']-model['us'], y=model['yub']-model['ys'])
+    
+    # Get the scaling numbers.
+    uscale = 0.5*(ub['u']-lb['u'])
+    yscale = 0.5*(ub['y']-lb['y'])
+
+    # Scale the bounds.
+    lb['u'] = lb['u']/uscale
+    ub['u'] = ub['u']/uscale
+    lb['y'] = lb['y']/yscale
+    ub['y'] = ub['y']/yscale
+    
+    # Scale the matrices.
+    B = B @ np.diag(uscale.squeeze())
+    C = np.diag(1/yscale.squeeze()) @ C
+
+    # Get the plant disturbance model.
+    Bp = np.take(B, dist_indices, axis=1)#*dist_scaling
+
+    # Return the required parameters.
+    return (uscale, yscale, A, B, C, Bp, lb, ub)
+
+def _get_cdu_plant(model, dist_indices, dist_scaling):
+    """ Function to get the CDU plant and the scaling
+        for plotting. """
+    # Get the scaled model.
+    scaled_parameters = _get_scaled_parameters(model, dist_indices,
+                                              dist_scaling)
+    (uscale, yscale, A, B, C, Bp, lb, ub) = scaled_parameters
+
+    # The measurement error.
+    Rv = (1e-20)*np.eye(C.shape[0])
+
[…]

### 2020-09-05 cdu_satdlqr.py

@@ -1,0 +1,43 @@
+# [depends] cdu_parameters.pickle
+# [makes] pickle
+"""
+Script to run an on-line simulation using the double integrator example
+using the optimal MPC controller.
+Since for the double integrator example, on-line simulation does not
+takes much time, both plotting and the simulation tasks are in 
+the same script.
+"""
+import sys
+sys.path.append('lib/')
+import numpy as np
+from matplotlib.backends.backend_pdf import PdfPages
+from python_utils import PickleTool
+from controller_evaluation import _simulate_scenarios
+from cdu_comparision_plots import _cdu_cl_comparision_plots
+
+# Simulate all the scenarios.
+(plants, controllers) = _simulate_scenarios(plant_name='cdu', 
+                                            controller_name='satdlqr', 
+                                            Nsim=2880)
+
+# Now make the plots here.
+cdu_parameters = PickleTool.load(filename='cdu_parameters.pickle', 
+                                 type='read')
+scenarios = cdu_parameters['online_test_scenarios']
+plant_parameters = cdu_parameters['cdu_plant_parameters']
+
+mpc_parameters = PickleTool.load(filename='cdu_mpc.pickle', 
+                                        type='read')
+(mpc_plants, mpc_controllers) = (mpc_parameters['plants'], 
+                                 mpc_parameters['controllers'])
+figures = _cdu_cl_comparision_plots(scenarios, 
+                            mpc_plants, mpc_controllers,
+                            plants, controllers, 
+                            'satK',
+                            plant_parameters,
+                            (0, 2880))
+# Plot.
+# Create the Pdf figure object and save.
+with PdfPages('cdu_satdlqr.pdf', 'w') as pdf_file:
+    for fig in figures:
+        pdf_file.savefig(fig)

### 2020-09-05 cdu_satdlqr_plot.py

@@ -1,0 +1,235 @@
+# [depends] cdu_parameters.pickle cdu_optimal.pickle
+"""
+Script to run an on-line simulation using the double integrator example
+using the optimal MPC controller.
+Since for the double integrator example, on-line simulation does not
+takes much time, both plotting and the simulation tasks are in
+the same script.
+"""
+# import custompath
+# custompath.add()
+import sys
+sys.path.append('lib/')
+import numpy as np
+import plottools
+import itertools
+from cdu_labels import ulabels, ylabels, zlabels, pdlabels
+import matplotlib.pyplot as plt
+from python_utils import (PickleTool, figure_size_a4)
+from matplotlib.backends.backend_pdf import PdfPages
+
+def _get_arrays_for_plotting(optimal, satdlqr, 
+                             cdu_plotting_parameters, 
+                             setpoints, plot_range):
+    """ Get the appropriate arrays for plotting."""
+
+    # Get some plotting cosmetics.
+    yscale = cdu_plotting_parameters['yscale']
+    uscale = cdu_plotting_parameters['uscale']
+    lb = cdu_plotting_parameters['lb'] 
+    ub = cdu_plotting_parameters['ub']
+    us = cdu_plotting_parameters['us'] 
+    ys = cdu_plotting_parameters['ys']
+    disturbance_indices = cdu_plotting_parameters['disturbance_indices']
+
+    (start, end) = plot_range
+    #  Get the H matrix.
+    (Ny, _) = optimal.C.shape
+    Nc = 4
+    H = np.concatenate((np.zeros((Nc, Ny-Nc)), np.eye(Nc)), axis=1)
+
+    # Scaling for the inputs, outputs.
+    pscale = np.take(uscale, disturbance_indices).squeeze()
+    yscale = yscale.squeeze()
+    uscale = uscale.squeeze()
+    zscale = (H @ yscale[:, np.newaxis]).squeeze()
+    
+    # States.
+    x_opt = np.asarray(optimal.x[start:end]).squeeze()
+    x_satdlqr = np.asarray(satdlqr.x[start:end]).squeeze()
+
+    # Control inputs.
+    u_opt = np.asarray(optimal.u[start:end]).squeeze()*uscale + us.squeeze()
+    u_satdlqr = np.asarray(satdlqr.u[start:end]).squeeze()*uscale + us.squeeze()
+
+    # Disturbances.
+    p = np.asarray(optimal.p[start:end]).squeeze()*pscale
+
+    # All the outputs.
[…]

### 2020-09-05 cdu_short_horizon.py

@@ -1,0 +1,43 @@
+# [depends] cdu_parameters.pickle
+# [makes] pickle
+"""
+Script to run an on-line simulation using the double integrator example
+using the optimal MPC controller.
+Since for the double integrator example, on-line simulation does not
+takes much time, both plotting and the simulation tasks are in 
+the same script.
+"""
+import sys
+sys.path.append('lib/')
+import numpy as np
+from matplotlib.backends.backend_pdf import PdfPages
+from python_utils import PickleTool
+from controller_evaluation import _simulate_scenarios
+from cdu_comparision_plots import _cdu_cl_comparision_plots
+
+# Simulate all the scenarios.
+(plants, controllers) = _simulate_scenarios(plant_name='cdu', 
+                                    controller_name='short_horizon', 
+                                    Nsim=2880)
+
+# Now make the plots here.
+cdu_parameters = PickleTool.load(filename='cdu_parameters.pickle', 
+                                 type='read')
+scenarios = cdu_parameters['online_test_scenarios']
+plant_parameters = cdu_parameters['cdu_plant_parameters']
+
+mpc_parameters = PickleTool.load(filename='cdu_mpc.pickle', 
+                                        type='read')
+(mpc_plants, mpc_controllers) = (mpc_parameters['plants'], 
+                                 mpc_parameters['controllers'])
+figures = _cdu_cl_comparision_plots(scenarios, 
+                            mpc_plants, mpc_controllers,
+                            plants, controllers, 
+                            'SH',
+                            plant_parameters,
+                            (0, 2880))
+# Plot.
+# Create the Pdf figure object and save.
+with PdfPages('cdu_short_horizon.pdf', 'w') as pdf_file:
+    for fig in figures:
+        pdf_file.savefig(fig)

### 2020-09-05 cdu_train.py

@@ -1,0 +1,119 @@
+# [makes] pickle
+"""
+Script to train the neural network controller for the 
+CDU example.
+Pratyush Kumar, pratyushkumar@ucsb.edu
+"""
+import os
+import sys
+import numpy as np
+sys.path.append('lib/')
+import time
+import itertools
+import tensorflow as tf
+from python_utils import (PickleTool, H5pyTool)
+from LinearMPCLayers import RegulatorModel
+from controller_evaluation import _get_data_for_training
+
+# Set the tensorflow graph-level seed.
+tf.random.set_seed(1)
+
+def create_nn_controller(*, regulator_dims):
+    """ Create an instantiation of 
+        the neural network controller and return."""
+    # Get the shapes.
+    Nx = 252
+    Nu = 32
+    # Create the keras model instance.
+    nn_controller = RegulatorModel(Nx=Nx, Nu=Nu,
+                                   regulator_dims=regulator_dims,
+                                   nnwithuprev=False)
+    # Compile the nn controller.
+    nn_controller.compile(optimizer='adam', loss='mean_squared_error')
+    # Return the compiled controller.
+    return nn_controller
+
+def train_nn_controller(nn_controller, data, 
+                        stdout_filename, ckpt_path):
+    """ Function to train the NN controller."""
+    # Std out.
+    sys.stdout = open(stdout_filename, 'w')
+    # Create the checkpoint callback.
+    checkpoint_callback = tf.keras.callbacks.ModelCheckpoint(filepath=ckpt_path,
+                                                    monitor='val_loss',
+                                                    save_best_only=True,
+                                                    save_weights_only=True,
+                                                    verbose=1)
+    
+    # Call the fit method to train.
+    tstart = time.time()
+    nn_controller.fit(x=[data['x'], data['xs'], data['us']], 
+                      y=[data['u']], 
+                      epochs=500,
+                      batch_size=2048,
+                      validation_split=0.1,
+                      callbacks = [checkpoint_callback])
+    tend = time.time()
+    training_time = tend - tstart
+    # Return the NN controller.
+    return (nn_controller, training_time)
+
+# Get the raw data for training.
+raw_data = H5pyTool.load_training_data(filename='cdu_offline_data.h5py')
+(scaled_data, xscale) = _get_data_for_training(data=raw_data, 
+                                           num_samples=120000, 
+                                           scale=True)
+
+# Arrange the number of samples and the dimensions of the NN controller.
[…]

### 2020-09-05 cdu_train_post_processing.py

@@ -1,0 +1,9 @@
+"""
+Post process the trained dataset.
+"""
+import sys
+sys.path.append('lib/')
+from controller_evaluation import _post_process_trained_data
+
+_post_process_trained_data(data_filename='cdu_train.pickle', 
+                           num_architectures=int(sys.argv[1]))

### 2020-09-05 cdu_train_unstd.py

@@ -1,0 +1,90 @@
+# [makes] pickle
+"""
+Script to train an unstructured neural network controller for the 
+crude distillation unit example.
+Pratyush Kumar, pratyushkumar@ucsb.edu
+"""
+import sys
+sys.path.append('lib/')
+import numpy as np
+import os
+import time
+import itertools
+import tensorflow as tf
+from python_utils import (PickleTool, H5pyTool)
+from LinearMPCLayers import UnstdRegulatorModel
+from controller_evaluation import _get_data_for_training
+
+# Set the tensorflow graph-level seed.
+tf.random.set_seed(1)
+
+def create_nn_controller(*, regulator_dims):
+    """Create an instantiation of the neural network controller and return."""
+    Nx = 252
+    Nu = 32
+    # Create the keras model instance.
+    nn_controller = UnstdRegulatorModel(Nx=Nx, Nu=Nu,
+                                       regulator_dims=regulator_dims,
+                                       nnwithuprev=False)
+    # Compile the nn controller.
+    nn_controller.compile(optimizer='adam', loss='mean_squared_error')
+    # Return the compiled controller.
+    return nn_controller
+
+def train_nn_controller(nn_controller, data, stdout_filename, ckpt_path):
+    """ Function to train the controller."""
+    # Std out.
+    sys.stdout = open(stdout_filename, 'w')
+    # Create the checkpoint callback.
+    checkpoint_callback = tf.keras.callbacks.ModelCheckpoint(filepath=ckpt_path,
+                                                monitor='val_loss',
+                                                save_best_only=True,
+                                                save_weights_only=True,
+                                                verbose=1)
+    # Call the fit method to train.
+    tstart = time.time()
+    nn_controller.fit(x=[data['x'], data['xs'], data['us']], 
+                      y=[data['u']], 
+                      epochs=1500,
+                      batch_size=2048,
+                      validation_split=0.1,
+                      callbacks=[checkpoint_callback])
+    tend = time.time()
+    training_time = tend - tstart
+    return (nn_controller, training_time)
+
+# Get the raw data for training.
+num_sample = 357600
+raw_data = H5pyTool.load_training_data(filename='cdu_offline_data.h5py')
+(training_data, xscale) = _get_data_for_training(data=raw_data, 
+                                           num_samples=num_sample, 
+                                           scale=True)
+
+# Get a NN controller.
+regulator_dims = [536, 832, 832, 832, 32]
[…]

### 2020-09-05 cdu_us.py

@@ -1,0 +1,43 @@
+# [depends] cdu_parameters.pickle
+# [makes] pickle
+"""
+Script to run an on-line simulation using the double integrator example
+using the optimal MPC controller.
+Since for the double integrator example, on-line simulation does not
+takes much time, both plotting and the simulation tasks are in 
+the same script.
+"""
+import sys
+sys.path.append('lib/')
+import numpy as np
+from matplotlib.backends.backend_pdf import PdfPages
+from python_utils import PickleTool
+from controller_evaluation import _simulate_scenarios
+from cdu_comparision_plots import _cdu_cl_comparision_plots
+
+# Simulate all the scenarios.
+(plants, controllers) = _simulate_scenarios(plant_name='cdu', 
+                                            controller_name='us', 
+                                            Nsim=2880)
+
+# Now make the plots here.
+cdu_parameters = PickleTool.load(filename='cdu_parameters.pickle', 
+                                 type='read')
+scenarios = cdu_parameters['online_test_scenarios']
+plant_parameters = cdu_parameters['cdu_plant_parameters']
+
+mpc_parameters = PickleTool.load(filename='cdu_mpc.pickle', 
+                                        type='read')
+(mpc_plants, mpc_controllers) = (mpc_parameters['plants'], 
+                                 mpc_parameters['controllers'])
+figures = _cdu_cl_comparision_plots(scenarios, 
+                            mpc_plants, mpc_controllers,
+                            plants, controllers, 
+                            'us',
+                            plant_parameters,
+                            (0, 2880))
+# Plot.
+# Create the Pdf figure object and save.
+with PdfPages('cdu_us.pdf', 'w') as pdf_file:
+    for fig in figures:
+        pdf_file.savefig(fig)

### 2020-09-05 cstrs_comparision_plots.py

@@ -1,0 +1,322 @@
+# [depends] cstrs_parameters.pickle cstrs_mpc.pickle cstrs_us.pickle
+# [depends] cstrs_satdlqr.pickle cstrs_short_horizon.pickle cstrs_train.pickle
+# [depends] cstrs_neural_network.pickle
+""" 
+Script to make plots for comparing the 
+performance of the optimal MPC controller
+and the NN MPC controller.
+"""
+import sys
+sys.path.append('lib/')
+import plottools
+import itertools
+import numpy as np
+import matplotlib.pyplot as plt
+from cstrs_labels import (ylabels, zlabels, ulabels, pdlabels)
+from python_utils import (PickleTool, figure_size_cl, figure_size_metrics)
+from matplotlib.backends.backend_pdf import PdfPages
+from controller_evaluation import (plot_cl_performance_and_comp_times,
+                        plot_nn_vs_num_samples_performance,
+                        _load_data_for_plots, _set_font_size,
+                        _get_best_nn_plant_controllers)
+
+def _get_cstr_data_for_plotting(plant, controller, setpoints,
+                                parameters, plot_range):
+    """ Get the appropriate arrays for plotting."""
+    # Get some plotting cosmetics.
+    yscale = parameters['yscale']
+    pscale = parameters['pscale']
+    uscale = parameters['uscale']
+    ulb = parameters['lb']['u'][:, np.newaxis] 
+    uub = parameters['ub']['u'][:, np.newaxis]
+    us = parameters['us'] 
+    ys = parameters['C'] @ parameters['xs']
+    ps = parameters['ps']
+    H = parameters['H'] 
+    exp_dist_indices = parameters['exp_dist_indices']
+    # Start and end for plotting
+    (start, end) = plot_range
+    q_indices = (1, 3, 5)
+    # Get the plant arrays.
+    y = np.asarray(plant.y[start:end]).squeeze()*yscale + ys
+    z = y @ H.T
+    u = np.asarray(plant.u[start:end]).squeeze()*uscale + us
+    u[:, q_indices] = u[:, q_indices]/1000
+    p = np.asarray(plant.p[start:end]).squeeze()*pscale + ps
+    t = np.asarray(plant.t[start:end]).squeeze()/3600
+    # Get the controller arrays.
+    pest = np.asarray(controller.target_selector.dhats[start:end]).squeeze()
+    pest = pest*pscale[exp_dist_indices, np.newaxis].squeeze()
+    pest = pest + ps[exp_dist_indices, np.newaxis].squeeze()
[…]

### 2020-09-05 cstrs_mpc.py

@@ -1,0 +1,18 @@
+# [depends] cstrs_parameters.pickle
+# [makes] pickle
+"""
+Script to run an on-line simulation using the double integrator example
+using the optimal MPC controller.
+Since for the double integrator example, on-line simulation does not
+takes much time, both plotting and the simulation tasks are in 
+the same script.
+"""
+import sys
+sys.path.append('lib/')
+from python_utils import PickleTool
+from controller_evaluation import _simulate_scenarios
+
+# Simulate all the scenarios.
+_simulate_scenarios(plant_name='cstrs', 
+                    controller_name='mpc',
+                    Nsim=4320)

### 2020-09-05 cstrs_mpc_plot.py

@@ -1,0 +1,148 @@
+# [depends] cstrs_parameters.pickle cstrs_mpc.pickle
+"""
+Script to run an on-line simulation using the double integrator example
+using the optimal MPC controller.
+Since for the double integrator example, on-line simulation does not
+takes much time, both plotting and the simulation tasks are in
+the same script.
+"""
+import sys
+sys.path.append('lib/')
+import numpy as np
+import itertools
+from cstrs_labels import (ylabels, ulabels, zlabels, pdlabels)
+import matplotlib.pyplot as plt
+from python_utils import (PickleTool, figure_size_a4)
+from matplotlib.backends.backend_pdf import PdfPages
+from cstrs_comparision_plots import _get_cstr_data_for_plotting
+
+def _cstrs_optimal_plot(plant, controller, parameters, 
+                        setpoints, plot_range):
+    """Data to plot.
+    z: 4 outputs with setpoints. y:90 outputs. u:32 inputs.
+    """
+    # the x coordinate of the ylabels.
+    ylabel_xcoordinate = -0.25
+    # Get the arrays.
+    (t, z, y, u, pest, p, 
+      ulb, uub, zsp, ell) = _get_cstr_data_for_plotting(plant,  
+                                                        controller, setpoints,
+                                                        parameters, plot_range)
+    # Make the plots.
+    figures = plot_inputs(t, u, ulabels, ylabel_xcoordinate, ulb, uub)
+    figures += plot_outputs(t, y, ylabels, ylabel_xcoordinate)
+    figures += plot_controlled_outputs(t, z, zsp, zlabels, ylabel_xcoordinate)
+    figures += plot_disturbances(t, p, pest, parameters['exp_dist_indices'], 
+                                 pdlabels, ylabel_xcoordinate)
+    figures += plot_average_stage_costs(t, ell, 
+                            ylabel_xcoordinate)
+    # Return the list of figures.
+    return figures
+
+def plot_inputs(t, u, ulabels, ylabel_xcoordinate, ulb, uub):
+    """Return 4 figure objects which contain the plots of the inputs."""
+    input_index = 0
+    num_rows = 3
+    num_cols = 2
+    (figure, axes) = plt.subplots(nrows=num_rows, ncols=num_cols,
+                                 sharex='col', figsize=figure_size_a4, 
+                                 gridspec_kw = dict(wspace=0.5))
[…]

### 2020-09-05 cstrs_neural_network.py

@@ -1,0 +1,12 @@
+# [depends] cstrs_parameters.pickle cstrs_train.pickle
+# [makes] pickle
+"""
+Script to run an on-line simulation for the double integrator example
+using the approximate NN controller.
+"""
+import sys
+sys.path.append('lib/')
+from controller_evaluation import _simulate_neural_networks
+
+# Load data and do an online simulation using the linear MPC controller.
+_simulate_neural_networks(plant_name='cstrs', Nsim=4320)

### 2020-09-05 cstrs_neural_network_unstd.py

@@ -1,0 +1,38 @@
+# [depends] cstrs_parameters.pickle cstrs_train_unstd.pickle
+# [makes] pickle
+"""
+Script to run an on-line simulation for the 
+CSTRs with flash example using the approximate NN controller.
+"""
+import sys
+sys.path.append('lib/')
+from python_utils import (PickleTool, figure_size_a4)
+from matplotlib.backends.backend_pdf import PdfPages
+from cstrs_comparision_plots import _cstrs_cl_comparision_plots
+from controller_evaluation import _simulate_neural_network_unstd
+
+# Load data and do an online simulation using the linear MPC controller.
+(plants, controllers) = _simulate_neural_network_unstd(plant_name='cstrs', 
+                                    Nsim=4320, nnwithuprev=True)
+
+# Now make the plots here.
+cstrs_parameters = PickleTool.load(filename='cstrs_parameters.pickle', 
+                                        type='read')
+scenarios = cstrs_parameters['online_test_scenarios']
+plant_parameters = cstrs_parameters['cstrs_plant_parameters']
+
+mpc_parameters = PickleTool.load(filename='cstrs_mpc.pickle', 
+                                        type='read')
+(mpc_plants, mpc_controllers) = (mpc_parameters['plants'], 
+                                 mpc_parameters['controllers'])
+figures = _cstrs_cl_comparision_plots(scenarios, 
+                            mpc_plants, mpc_controllers,
+                            plants, controllers, 
+                            'NN-UNSTD',
+                            plant_parameters,
+                            (0, 4320))
+
+# Create the Pdf figure object and save.
+with PdfPages('cstrs_neural_network_unstd.pdf', 'w') as pdf_file:
+    for fig in figures:
+        pdf_file.savefig(fig)

### 2020-09-05 cstrs_offline_data.py

@@ -1,0 +1,16 @@
+# [depends] cstrs_parameters.pickle
+# [makes] pickle
+"""
+Script to generate offline data for training the neural net.
+"""
+import sys
+sys.path.append('lib/')
+from python_utils import PickleTool
+
+# Load data and do an online simulation using the linear MPC controller.
+task_number = int(sys.argv[1]) - 1
+cstrs_parameters = PickleTool.load(filename='cstrs_parameters.pickle', 
+                                   type='read')
+cstrs_parameters['offline_simulator'].generate_data(task_number=task_number,   
+                    data_filename='cstrs_offline_data.h5py',
+                    stdout_filename=str(task_number)+'-cstrs_offline_data.txt')

### 2020-09-05 cstrs_offline_data_post_processing.py

@@ -1,0 +1,14 @@
+"""
+Post process the offline generated dataset.
+"""
+import sys
+sys.path.append('lib/')
+from python_utils import H5pyTool
+import os
+import itertools
+import numpy as np
+from controller_evaluation import _post_process_data
+
+_post_process_data(data_filename='cstrs_offline_data.h5py', 
+                   num_data_gen_task=int(sys.argv[1]),
+                   num_process_per_task=1)

### 2020-09-05 cstrs_offline_plot.py

@@ -1,0 +1,58 @@
+# [depends] cstrs_offline_data.pickle
+"""
+Script to run an on-line simulation using the double integrator example
+using the optimal MPC controller.
+Since for the double integrator example, on-line simulation does not
+takes much time, both plotting and the simulation tasks are in 
+the same script.
+"""
+import sys
+sys.path.append('../lib/')
+import numpy as np
+from cstrs_optimal_plot import (plot_inputs, plot_states, 
+                                plot_outputs, plot_disturbances)
+from cstrs_labels import (xlabels, ylabels, ulabels, pdlabels)
+import matplotlib.pyplot as plt
+from python_utils import (PickleTool, figure_size_a4)
+from matplotlib.backends.backend_pdf import PdfPages
+
+def _get_arrays_for_plotting(raw_data, num_samples):
+    """ Convert lists to numpy array."""
+    # Get the data arrays for plotting.
+    x = raw_data['x'][:num_samples, :].squeeze()
+    u = raw_data['useq'][:num_samples, 0:6].squeeze()
+    d = raw_data['d'][:num_samples, :].squeeze()
+    ysp = raw_data['rsp'][:num_samples, :].squeeze()
+    y = raw_data['y'][:num_samples, :].squeeze()
+    t = np.arange(0, num_samples)
+    ulb = np.tile(np.NaN, (num_samples, u.shape[1]))
+    uub = np.tile(np.NaN, (num_samples, u.shape[1]))
+    return (x, u, d, ysp, y, t, ulb, uub)
+
+def _cstrs_plot_offline_data(offline_simulator, num_samples):
+    """ Get the offline data for plotting."""
+    ylabel_xcoordinate = -0.25
+    (x, u, d, ysp, y, t, ulb, uub) = _get_arrays_for_plotting(offline_simulator, num_samples)
+
+    # Make the Plots.
+    figures = plot_inputs(t, u, ulabels, ylabel_xcoordinate, ulb, uub)
+    figures += plot_outputs(t, y, ysp, ylabels, ylabel_xcoordinate)
+    figures += plot_states(t, x, xlabels, ylabel_xcoordinate)
+    figures += plot_disturbances(t, d, pdlabels, ylabel_xcoordinate)
+    return figures
+
+def main():
+    """ The Main Function. """
+    # Load data and do an online simulation using the linear MPC controller.
+    cstrs_offline_data = PickleTool.load(filename='cstrs_offline_data.pickle', type='read')
+    # Make the plot. 
[…]

### 2020-09-05 cstrs_parameters.py

@@ -1,0 +1,419 @@
+# [makes] pickle
+""" 
+Generate necessary parameters for the offline data generation and 
+the online simulation of the CSTRs in series with a Flash model.
+"""
+import sys
+sys.path.append('lib/')
+import mpctools as mpc
+import numpy as np
+from python_utils import PickleTool
+from controller_evaluation import (sample_prbs_like,
+                                   _get_us_controller,
+                                   _get_satdlqr_controller,
+                                   _get_short_horizon_controller)
+from linearMPC import (LinearMPCController, 
+                       OfflineSimulator,
+                       LinearPlantSimulator)
+from nonlinearMPC import NonlinearPlantSimulator
+
+def _cstrs_ode(x, u, p, parameters):
+
+    # Extract the parameters.
+    alphaA = parameters['alphaA']
+    alphaB = parameters['alphaB']
+    alphaC = parameters['alphaC']
+    pho = parameters['pho']
+    Cp = parameters['Cp']
+    Ar = parameters['Ar']
+    Am = parameters['Am']
+    Ab = parameters['Ab']
+    kr = parameters['kr']
+    km = parameters['km']
+    kb = parameters['kb']
+    delH1 = parameters['delH1']
+    delH2 = parameters['delH2']
+    EbyR = parameters['EbyR']
+    k1star = parameters['k1star']
+    k2star = parameters['k2star']
+    Td = parameters['Td']
+    uscale = parameters['uscale']
+    pscale = parameters['pscale']
+    xs = parameters['xs']
+    us = parameters['us']
+    ps = parameters['ps']
+
+    # Extract the plant states into meaningful names.
+    x = x + xs
+    (Hr, xAr, xBr, Tr) = x[0:4]
+    (Hm, xAm, xBm, Tm) = x[4:8]
+    (Hb, xAb, xBb, Tb) = x[8:12]
+    (F0, Qr, F1, Qm, D, Qb) = (u*uscale + us)[0:6]
+    (xA0, xB0, xA1, xB1, T0) = (p*pscale + ps)[0:5]
+
+    # The flash vapor phase mass fractions.
+    denominator = alphaA*xAb + alphaB*xBb + alphaC*(1 - xAb - xBb) 
+    xAd = alphaA*xAb/denominator
[…]

### 2020-09-05 cstrs_satdlqr.py

@@ -1,0 +1,43 @@
+# [depends] cstrs_parameters.pickle
+# [makes] pickle
+"""
+Script to run an on-line simulation using the double integrator example
+using the optimal MPC controller.
+Since for the double integrator example, on-line simulation does not
+takes much time, both plotting and the simulation tasks are in 
+the same script.
+"""
+import sys
+sys.path.append('lib/')
+import numpy as np
+from matplotlib.backends.backend_pdf import PdfPages
+from python_utils import PickleTool
+from controller_evaluation import _simulate_scenarios
+from cstrs_comparision_plots import _cstrs_cl_comparision_plots
+
+# Simulate all the scenarios.
+(plants, controllers) = _simulate_scenarios(plant_name='cstrs', 
+                                          controller_name='satdlqr', 
+                                          Nsim=4320)
+
+# Now make the plots here.
+cstrs_parameters = PickleTool.load(filename='cstrs_parameters.pickle', 
+                                        type='read')
+scenarios = cstrs_parameters['online_test_scenarios']
+plant_parameters = cstrs_parameters['cstrs_plant_parameters']
+
+mpc_parameters = PickleTool.load(filename='cstrs_mpc.pickle', 
+                                        type='read')
+(mpc_plants, mpc_controllers) = (mpc_parameters['plants'], 
+                                 mpc_parameters['controllers'])
+figures = _cstrs_cl_comparision_plots(scenarios, 
+                            mpc_plants, mpc_controllers,
+                            plants, controllers, 
+                            'sat(Kx)',
+                            plant_parameters,
+                            (0, 4320))
+# Plot.
+# Create the Pdf figure object and save.
+with PdfPages('cstrs_satdlqr.pdf', 'w') as pdf_file:
+    for fig in figures:
+        pdf_file.savefig(fig)

### 2020-09-05 cstrs_short_horizon.py

@@ -1,0 +1,43 @@
+# [depends] cstrs_parameters.pickle
+# [makes] pickle
+"""
+Script to run an on-line simulation using the double integrator example
+using the optimal MPC controller.
+Since for the double integrator example, on-line simulation does not
+takes much time, both plotting and the simulation tasks are in 
+the same script.
+"""
+import sys
+sys.path.append('lib/')
+import numpy as np
+from matplotlib.backends.backend_pdf import PdfPages
+from python_utils import PickleTool
+from controller_evaluation import _simulate_scenarios
+from cstrs_comparision_plots import _cstrs_cl_comparision_plots
+
+# Simulate all the scenarios.
+(plants, controllers) = _simulate_scenarios(plant_name='cstrs', 
+                                    controller_name='short_horizon', 
+                                    Nsim=4320)
+
+# Now make the plots here.
+cstrs_parameters = PickleTool.load(filename='cstrs_parameters.pickle', 
+                                        type='read')
+scenarios = cstrs_parameters['online_test_scenarios']
+plant_parameters = cstrs_parameters['cstrs_plant_parameters']
+
+mpc_parameters = PickleTool.load(filename='cstrs_mpc.pickle', 
+                                        type='read')
+(mpc_plants, mpc_controllers) = (mpc_parameters['plants'], 
+                                 mpc_parameters['controllers'])
+figures = _cstrs_cl_comparision_plots(scenarios, 
+                            mpc_plants, mpc_controllers,
+                            plants, controllers, 
+                            'SH',
+                            plant_parameters,
+                            (0, 4320))
+# Plot.
+# Create the Pdf figure object and save.
+with PdfPages('cstrs_short_horizon.pdf', 'w') as pdf_file:
+    for fig in figures:
+        pdf_file.savefig(fig)

### 2020-09-05 cstrs_train.py

@@ -1,0 +1,118 @@
+# [makes] pickle
+"""
+Script to train the neural network controller for the 
+CSTRs example.
+Pratyush Kumar, pratyushkumar@ucsb.edu
+"""
+import os
+import sys
+import numpy as np
+sys.path.append('lib/')
+import time
+import itertools
+import tensorflow as tf
+from python_utils import (PickleTool, H5pyTool)
+from LinearMPCLayers import RegulatorModel
+from controller_evaluation import _get_data_for_training
+
+# Set the tensorflow graph-level seed.
+tf.random.set_seed(1)
+
+def create_nn_controller(*, regulator_dims):
+    """ Create an instantiation of 
+        the neural network controller and return."""
+    # Get the shapes.
+    Nx = 12
+    Nu = 6
+    # Create the keras model instance.
+    nn_controller = RegulatorModel(Nx=Nx, Nu=Nu,
+                                   regulator_dims=regulator_dims)
+    # Compile the nn controller.
+    nn_controller.compile(optimizer='adam', loss='mean_squared_error')
+    # Return the compiled controller.
+    return nn_controller
+
+def train_nn_controller(nn_controller, data, 
+                        stdout_filename, ckpt_path):
+    """ Function to train the NN controller."""
+    # Std out.
+    sys.stdout = open(stdout_filename, 'w')
+    # Create the checkpoint callback.
+    checkpoint_callback = tf.keras.callbacks.ModelCheckpoint(filepath=ckpt_path,
+                                                    monitor='val_loss',
+                                                    save_best_only=True,
+                                                    save_weights_only=True,
+                                                    verbose=1)
+    
+    # Call the fit method to train.
+    tstart = time.time()
+    nn_controller.fit(x=[data['x'], data['uprev'], data['xs'], data['us']], 
+                      y=[data['u']], 
+                      epochs=500,
+                      batch_size=1024,
+                      validation_split=0.1,
+                      callbacks = [checkpoint_callback])
+    tend = time.time()
+    training_time = tend - tstart
+    # Return the NN controller.
+    return (nn_controller, training_time)
+
+# Get the raw data for training.
+raw_data = H5pyTool.load_training_data(filename='cstrs_offline_data.h5py')
+(scaled_data, xscale) = _get_data_for_training(data=raw_data, 
+                                           num_samples=120000, 
+                                           scale=True)
+
+# Arrange the number of samples and the dimensions of the NN controller.
+num_samples = [num_sample for num_sample in range(24000, 120001, 24000)]
[…]

### 2020-09-05 cstrs_train_post_processing.py

@@ -1,0 +1,9 @@
+"""
+Post process the trained dataset.
+"""
+import sys
+sys.path.append('lib/')
+from controller_evaluation import _post_process_trained_data
+
+_post_process_trained_data(data_filename='cstrs_train.pickle', 
+                           num_architectures=int(sys.argv[1]))

### 2020-09-05 cstrs_train_unstd.py

@@ -1,0 +1,90 @@
+# [makes] pickle
+"""
+Script to train an unstructured neural network controller for the 
+double integrator example.
+Pratyush Kumar, pratyushkumar@ucsb.edu
+"""
+import sys
+sys.path.append('lib/')
+import numpy as np
+import os
+import time
+import itertools
+import tensorflow as tf
+from python_utils import (PickleTool, H5pyTool)
+from LinearMPCLayers import UnstdRegulatorModel
+from controller_evaluation import _get_data_for_training
+
+# Set the tensorflow graph-level seed.
+tf.random.set_seed(1)
+
+def create_nn_controller(*, regulator_dims):
+    """Create an instantiation of the neural network controller and return."""
+    Nx = 12
+    Nu = 6
+    # Create the keras model instance.
+    nn_controller = UnstdRegulatorModel(Nx=Nx, Nu=Nu,
+                                       regulator_dims=regulator_dims,
+                                       nnwithuprev=True)
+    # Compile the nn controller.
+    nn_controller.compile(optimizer='adam', loss='mean_squared_error')
+    # Return the compiled controller.
+    return nn_controller
+
+def train_nn_controller(nn_controller, data, stdout_filename, ckpt_path):
+    """ Function to train the controller."""
+    # Std out.
+    sys.stdout = open(stdout_filename, 'w')
+    # Create the checkpoint callback.
+    checkpoint_callback = tf.keras.callbacks.ModelCheckpoint(filepath=ckpt_path,
+                                                monitor='val_loss',
+                                                save_best_only=True,
+                                                save_weights_only=True,
+                                                verbose=1)
+    # Call the fit method to train.
+    tstart = time.time()
+    nn_controller.fit(x=[data['x'], data['uprev'], data['xs'], data['us']], 
+                      y=[data['u']], 
+                      epochs=2000,
+                      batch_size=1024,
+                      validation_split=0.1,
+                      callbacks=[checkpoint_callback])
+    tend = time.time()
+    training_time = tend - tstart
+    return (nn_controller, training_time)
+
+# Get the raw data for training.
+num_sample = 150000
+raw_data = H5pyTool.load_training_data(filename='cstrs_offline_data.h5py')
+(training_data, xscale) = _get_data_for_training(data=raw_data, 
+                                           num_samples=num_sample, 
+                                           scale=True)
+
+# Get a NN controller.
+regulator_dims = [36, 224, 224, 224, 6]
[…]

### 2020-09-05 cstrs_us.py

@@ -1,0 +1,42 @@
+# [depends] cstrs_parameters.pickle
+# [makes] pickle
+"""
+Script to run an on-line simulation using the double integrator example
+using the optimal MPC controller.
+Since for the double integrator example, on-line simulation does not
+takes much time, both plotting and the simulation tasks are in 
+the same script.
+"""
+import sys
+sys.path.append('lib/')
+import numpy as np
+from matplotlib.backends.backend_pdf import PdfPages
+from python_utils import PickleTool
+from controller_evaluation import _simulate_scenarios
+from cstrs_comparision_plots import _cstrs_cl_comparision_plots
+
+# Simulate all the scenarios.
+(plants, controllers) = _simulate_scenarios(plant_name='cstrs', 
+                    controller_name='us', 
+                    Nsim=4320)
+
+# Now make the plots here.
+cstrs_parameters = PickleTool.load(filename='cstrs_parameters.pickle', 
+                                        type='read')
+scenarios = cstrs_parameters['online_test_scenarios']
+plant_parameters = cstrs_parameters['cstrs_plant_parameters']
+mpc_parameters = PickleTool.load(filename='cstrs_mpc.pickle', 
+                                        type='read')
+(mpc_plants, mpc_controllers) = (mpc_parameters['plants'], 
+                                 mpc_parameters['controllers'])
+figures = _cstrs_cl_comparision_plots(scenarios, 
+                            mpc_plants, mpc_controllers,
+                            plants, controllers, 
+                            'us',
+                            plant_parameters,
+                            (0, 4320))
+# Plot.
+# Create the Pdf figure object and save.
+with PdfPages('cstrs_us.pdf', 'w') as pdf_file:
+    for fig in figures:
+        pdf_file.savefig(fig)

### 2020-09-05 lib/LinearMPCLayers.py

@@ -1,0 +1,170 @@
+"""
+Custom Neural Network layers for performing
+experiments and comparisions with the MPC optimization problem.
+Pratyush Kumar, pratyushkumar@ucsb.edu
+"""
+import sys
+import time
+import math
+import numpy as np
+import tensorflow as tf
+from linearMPC import LinearMPCController
+from python_utils import PickleTool
+tf.keras.backend.set_floatx('float64')
+
+class RegulatorLayerWithUprev(tf.keras.layers.Layer):
+    """
+    Linear MPC Regulator layer.
+    Input to the layer: (x, xs*input_horizon, us*input_horizon)
+    Output of the layer: (u*output_horizon).
+    """
+
+    def __init__(self, layer_dims, trainable=True, name=None):
+        super(RegulatorLayerWithUprev, self).__init__(trainable, name)
+
+        # Create a list which will contain all the internal dense layers.
+        self._layers = []
+
+        # Layers leading upto the final layer.
+        for dim in layer_dims[:-1]:
+            self._layers.append(tf.keras.layers.Dense(dim, activation='relu'))
+        self._layers.append(tf.keras.layers.Dense(
+            layer_dims[-1], use_bias=False))
+
+    # The structured call function.
+    # The final output is:
+    # u = [us;us;...] + K(x, uprev, xs, us) - K(xs, us, xs, us)
+    def call(self, inputs):
+
+        # Get the inputs.
+        [x, uprev, xs, us] = inputs        
+
+        # Propagate through the layers.
+        layer_input = tf.concat((x, uprev, xs, us), axis=-1)
+        for layer in self._layers[:-1]:
+            layer_input = layer(layer_input)
+        output1 = self._layers[-1](layer_input)
+
+        # The output of the layer when the input is (xs, us, xs, us).
+        layer_input = tf.concat((xs, us, xs, us), axis=-1)
+        for layer in self._layers[:-1]:
+            layer_input = layer(layer_input)
+        output2 = self._layers[-1](layer_input)
+
+        # Compute the final output.
+        output2 = tf.negative(output2)
+        final_output = tf.math.add(output1, output2)
+        final_output = tf.math.add(us, final_output)
+        return final_output
+
+    def get_config(self):
+        return super().get_config()
+
+class RegulatorLayerWithoutUprev(tf.keras.layers.Layer):
+    """
+    Linear MPC Regulator layer.
+    Input to the layer: (x, xs*input_horizon, us*input_horizon)
[…]

### 2020-09-05 lib/cdu_labels.py

@@ -1,0 +1,32 @@
+"""
+Script to store the 32 input labels, the 90 output labels,
+the 4 controlled output labels, and the 3 disturbance labels
+for the crude distillation unit example. 
+"""
+
+ulabels = [f'$u_{{{i+1}}}$' for i in range(32)]
+
+ylabels = [f'$y_{{{i+1}}}$' for i in range(90)]
+
+zlabels = ['NAPHTHA', 
+           'KEROSENE-FLASH',
+           'KEROSENE', 
+           'DIESEL']
+
+pdlabels = ['$p_1 (\Delta u_{1})$',
+            '$p_2 (\Delta u_{4})$', 
+            '$p_3 (\Delta u_{5})$',
+            '$p_4 (\Delta u_{6})$',
+            '$p_5 (\Delta u_{7})$', 
+            '$p_6 (\Delta u_{12})$', 
+            '$p_7 (\Delta u_{19})$', 
+            '$p_8 (\Delta u_{20})$',
+            '$p_9 (\Delta u_{24})$', 
+            '$p_{10} (\Delta u_{26})$', 
+            '$p_{11} (\Delta u_{28})$', 
+            '$p_{12} (\Delta u_{31})$',
+            '$p_{13} (\Delta u_{32})$',
+            '$p_{11} (\Delta u_{28})$', 
+            '$p_{12} (\Delta u_{31})$',
+            '$p_{13} (\Delta u_{32})$']
+

### 2020-09-05 lib/controller_evaluation.py

@@ -1,0 +1,1093 @@
+"""
+Module for controller evaluation on different plant models
+with different controllers. 
+Author: Pratyush Kumar, pratyushkumar@ucsb.edu
+"""
+import time
+import sys
+import plottools
+import cvxopt as cvx
+import numpy as np 
+import scipy
+import itertools
+from linearMPC import (DenseQPRegulator, online_simulation,
+                       LinearMPCController, dlqr)
+import matplotlib.pyplot as plt
+from python_utils import (figure_size_a4, PickleTool,
+                          H5pyTool)
+from matplotlib.backends.backend_pdf import PdfPages
+
+def _sample_repeats(num_change, num_simulation_steps,
+                       mean_change, sigma_change):
+    """ Sample the number of times a repeat in each
+    of the sampled vector is required."""
+    repeat = sigma_change*np.random.randn(num_change-1) + mean_change
+    repeat = np.floor(repeat)
+    repeat = np.where(repeat<=0., 0., repeat)
+    repeat = np.append(repeat, num_simulation_steps-np.int(np.sum(repeat)))
+    return repeat.astype(int)
+
+def sample_prbs_like(*, num_change, num_steps, 
+                    lb, ub, mean_change, sigma_change, seed=1):
+    """Sample a PRBS like sequence.
+    num_change: Number of changes in the signal.
+    num_simulation_steps: Number of steps in the signal.
+    mean_change: mean_value after which a 
+                 change in the signal is desired.
+    sigma_change: standard deviation of changes in the signal.
+    """
+    signal_dimension = lb.shape[0]
+    lb = lb.squeeze() # Squeeze the vectors.
+    ub = ub.squeeze() # Squeeze the vectors.
+    np.random.seed(seed)
+    values = (ub-lb)*np.random.rand(num_change, signal_dimension) + lb
+    repeat = _sample_repeats(num_change, num_steps,
+                             mean_change, sigma_change)
+    return np.repeat(values, repeat, axis=0)
+
+def _get_best_nn_plant_controllers(nn_plants, nn_controllers, 
+                             performance_loss,
+                             num_architectures,
+                             num_nns_per_arch, 
+                             num_scenarios):
+    """ Return the NN controllers for each architecture
+        that use larget amount of data."""
+    best_nn_plants = []
+    best_nn_controllers = []
+    best_nn_indices = np.argmin(performance_loss, axis=1)
+    for (arch, scenario) in itertools.product(range(num_architectures), 
[…]

### 2020-09-05 lib/cstrs_labels.py

@@ -1,0 +1,21 @@
+"""
+Script to store the 6 input labels, the 6 output labels,
+the 12 state output labels, and the 5 disturbance labels
+for the cstrs with flash example. 
+"""
+
+ylabels = ['$H_{r}$', '$x_{Ar}$', '$x_{Br}$', '$T_{r}$',
+           '$H_{m}$', '$x_{Am}$', '$x_{Bm}$', '$T_{m}$',
+           '$H_{b}$', '$x_{Ab}$', '$x_{Bb}$', '$T_{b}$']
+
+zlabels = ['$H_{r}$ (m)', '$T_{r}$ (K)',
+           '$H_{m}$ (m)', '$T_{m}$ (K)',
+           '$H_{b}$ (m)', '$T_{b}$ (K)']
+
+ulabels = ['$F_{0}$ (Kg/s)', '$Q_{r} \ (10^3$ kW)',
+           '$F_{1}$ (Kg/s)', '$Q_{m} \ (10^3$ kW)',
+           '$D$ (Kg/s)', '$Q_{b} \ (10^3$ kW)']
+
+pdlabels = ['$x_{A0}$', '$x_{B0}$',
+           '$x_{A1}$', '$x_{B1}$',
+           '$T_{0}$']

### 2020-09-05 lib/linearMPC.py

@@ -1,0 +1,880 @@
+""" Module for solving linear MPC problems
+    and offline data generation for neural network training."""
+
+import sys
+import time
+import os
+import concurrent.futures
+import multiprocessing
+import numpy as np
+import cvxopt as cvx
+import scipy.linalg
+import itertools
+from python_utils import H5pyTool
+
+def array_to_matrix(*arrays):
+    """Convert nummpy arrays to cvxopt matrices."""
+    matrices = []
+    for array in arrays:
+        matrices.append(cvx.matrix(array))
+    return tuple(matrices)
+
+def dlqr(A,B,Q,R,M=None):
+    """
+    Get the discrete-time LQR for the given system.
+    Stage costs are
+        x'Qx + 2*x'Mu + u'Ru
+    with M = 0 if not provided.
+    """
+    # For M != 0, we can simply redefine A and Q to give a problem with M = 0.
+    if M is not None:
+        RinvMT = scipy.linalg.solve(R,M.T)
+        Atilde = A - B.dot(RinvMT)
+        Qtilde = Q - M.dot(RinvMT)
+    else:
+        Atilde = A
+        Qtilde = Q
+        M = np.zeros(B.shape)
+    Pi = scipy.linalg.solve_discrete_are(Atilde,B,Qtilde,R)
+    K = -scipy.linalg.solve(B.T.dot(Pi).dot(B) + R, B.T.dot(Pi).dot(A) + M.T)
+    return (K, Pi)
+
+def dlqe(A,C,Q,R):
+    """
+    Get the discrete-time Kalman filter for the given system.
+    """
+    P = scipy.linalg.solve_discrete_are(A.T,C.T,Q,R)
+    L = scipy.linalg.solve(C.dot(P).dot(C.T) + R, C.dot(P)).T
+    return (L, P)
+
+def c2d(A, B, sample_time):
+    """ Custom c2d function for linear systems."""
+    
+    # First construct the incumbent matrix
+    # to take the exponential.
+    (Nx, Nu) = B.shape
+    M1 = np.concatenate((A, B), axis=1)
+    M2 = np.zeros((Nu, Nx+Nu))
+    M = np.concatenate((M1, M2), axis=0)
+    Mexp = scipy.linalg.expm(M*sample_time)
+
+    # Return the extracted matrices.
+    Ad = Mexp[:Nx, :Nx]
+    Bd = Mexp[:Nx, -Nu:]
+    return (Ad, Bd)
+
[…]

### 2020-09-05 lib/matio.py

@@ -1,0 +1,136 @@
+"""
+io functions for mat files.
+"""
+import sys
+import numpy as np
+import scipy.io as sio
+
+def iteritems(d):
+    """Returns iteritems of teh given dict."""
+    if sys.version_info[0] >= 3:
+        ret = d.items
+    else:
+        ret = d.iteritems
+    return ret()
+
+# =============================================================================
+# The following three functions from http://stackoverflow.com/questions/7008608
+# with some additional modifications.
+# =============================================================================
+def loadmat(filename, scalararray=False, asdict=True, asrecarray=False, squeeze=True):
+    """
+    Loads a mat file with sensible  behavior for nested scalar structs.
+    
+    This function should be called instead of direct spio.loadmat
+    as it cures the problem of not properly recovering python dictionaries
+    from mat files. It calls the function check keys to cure all entries
+    which are still mat-objects.
+    
+    Optional argument scalararray is a boolean flag: if True, scalar values
+    are wrapped in the numpy array data type; if False (default), then they
+    are returned as native python floats.
+    """
+    data = sio.loadmat(filename, struct_as_record=asrecarray,
+                       squeeze_me=squeeze)
+    if asdict:
+        data = _check_keys(data, scalararray, asrecarray)
+    return data
+
+def _check_keys(d, scalararray=False, recarray=False):
+    """
+    checks if entries in dictionary are mat-objects. If yes
+    todict is called to change them to nested dictionaries
+    """
+    for (key, item) in iteritems(d):
+        d[key] = _process_elem(item, scalararray, recarray)
+    return d
+
+def _todict(matobj, scalararray, recarray):
+    """
+    A recursive function which constructs from matobjects nested dictionaries.
+    """
+    if recarray:
+        # More "modern" numpy data type.
+        def get(d, k):
+            v = d[k]
+            if hasattr(v, "shape") and v.shape == ():
+                v = v[()]
+            return v
+        keys = list(matobj.dtype.fields.keys())
+    else:
+        # Older surrogate of Matlab structs.
+        def get(d, k):
+            return d.__dict__[k]
+        keys = matobj._fieldnames
+    d = {}
+    for k in keys:
+        elem = get(matobj, k)
+        d[k] = _process_elem(elem, scalararray, recarray)
+    return d
[…]

### 2020-09-05 lib/nonlinearMPC.py

@@ -1,0 +1,486 @@
+"""
+Script that contains custom python classes to solve
+nonlinear tracking MPC problems using Casadi/IPOPT.
+Author:Pratyush Kumar, pratyushkumar@ucsb.edu
+"""
+import time
+import numpy as np
+import mpctools as mpc
+import scipy.linalg
+
+class NonlinearPlantSimulator:
+    """Custom class for simulating non-linear plants."""
+    def __init__(self, *, fxup, hx, Rv, Nx, Nu, Np, Ny, 
+                 sample_time, x0):
+        
+        # Set attributes.
+        self.fxup = mpc.DiscreteSimulator(fxup, sample_time,
+                                          [Nx, Nu, Np], ["x", "u", "p"])
+        self.hx = mpc.getCasadiFunc(hx, [Nx], ["x"], funcname="hx")
+        (self.Nx, self.Nu, self.Ny, self.Np) = (Nx, Nu, Ny, Np)
+        self.measurement_noise_std = np.sqrt(np.diag(Rv)[:, np.newaxis])
+        self.sample_time = sample_time
+
+        # Create lists to save data.
+        self.x = [x0]
+        self.u = []
+        self.p = []
+        self.y = [np.asarray(self.hx(x0)) + 
+                 self.measurement_noise_std*np.random.randn(self.Ny, 1)]
+        self.t = [0.]
+
+    def step(self, u, p):
+        """ Inject the control input into the plant."""
+        x = self.fxup.sim(self.x[-1], u, p)[:, np.newaxis]
+        y = np.asarray(self.hx(x))
+        y = y + self.measurement_noise_std*np.random.randn(self.Ny, 1)
+        self._append_data(x, u, p, y)
+        return y
+
+    def _append_data(self, x, u, p, y):
+        """ Append the data into the lists.
+        Used for plotting in the specific subclasses.
+        """
+        self.x.append(x)
+        self.u.append(u)
+        self.p.append(p)
+        self.y.append(y)
+        self.t.append(self.t[-1]+self.sample_time)
+
+class NonlinearMHEEstimator:
+
+    def __init__(self, *, fxuw, hx, N, Nx, Nu, Ny,
+                 xprior, u, y, P0inv, Qwinv, Rvinv):
+        """ Class to construct and perform state estimation
+        using moving horizon estimation. 
+        
+        Problem setup:
+        The current time is T
+        Measurement available: u_[T-N:T-1], y_[T-N:T]
+
[…]

### 2020-09-05 lib/python_utils.py

@@ -1,0 +1,58 @@
+""" Custom python utilities. 
+Pratyush Kumar, pratyushkumar@ucsb.edu
+"""
+
+import numpy as np
+import pickle
+import h5py 
+import os
+
+figure_size_a4 = (8, 10)
+figure_size_cl = (8, 8)
+figure_size_metrics = (8, 5)
+
+class PickleTool:
+    """Class which contains a few static methods for saving and
+    loading pkl data files conveniently."""
+    @staticmethod
+    def load(filename, type='write'):
+        """Wrapper to load data."""
+        if type == 'read':
+            with open(filename, "rb") as stream:
+                return pickle.load(stream)
+        if type == 'write':
+            with open(filename, "wb") as stream:
+                return pickle.load(stream)
+    
+    @staticmethod
+    def save(data_object, filename):
+        """Wrapper to pickle a data object."""
+        with open(filename, "wb") as stream:
+            pickle.dump(data_object, stream)
+
+    @staticmethod
+    def get_nn_memory_footprint(regulator_weights, filename):
+        """Save the NN weights and get the memomry footprint
+           in kB."""
+        with open(filename, "wb") as stream:
+            pickle.dump(regulator_weights, stream)
+        return os.path.getsize(filename)/1024
+
+class H5pyTool:
+    """Class which contains a few static methods for saving and
+    loading h5py data files conveniently."""
+    @staticmethod
+    def load_training_data(filename):
+        """Wrapper to load data."""
+        with h5py.File(filename, "r") as stream:
+            dictionary = {}
+            for key in list(stream.keys()):
+                dictionary[key] = np.asarray(stream.get(key))
+            return dictionary
+    
+    @staticmethod
+    def save_training_data(dictionary, filename):
+        """Wrapper to pickle a data object."""
+        with h5py.File(filename, "w") as stream:
+            for (key, value) in dictionary.items():
+                stream.create_dataset(key, data=value)

### 2020-09-05 script/getdependencies.py
paper draft.

@@ -37,10 +37,11 @@ SPECIALDIRS = {"FIGURE": ["build/figures/{}/".format(d) for d in
                "SCRIPT": ["script/"], "LIB" : ["lib/"], "SRC" : [""]}
 SPECIALS = {"THISFIGURE" : "%FIGURE%/{}.pdf", "THISMAT" : "{}.mat",
             "THISTEX" : "{}.tex", "THISGNUPLOT" : "{}.gnuplot",
-            "THISDAT" : "{}.dat", "THISPDF" : "{}.pdf"}
+            "THISDAT" : "{}.dat", "THISPDF" : "{}.pdf",
+            "THISPICKLE" : "{}.pickle"}
 
 # Define set for new-style [makes]; "[makes] *" gets mapped to "%THIS*%". 
-MAKES_SPECIALS = {"figure", "gnuplot", "mat", "dat", "tex", "pdf"}
+MAKES_SPECIALS = {"figure", "gnuplot", "mat", "dat", "tex", "pdf", "pickle"}
 
 # Set default [makes] based on file extensions.
 DEFAULT_MAKES = {".py": "figure", ".m": "mat", ".jl": "mat",

### 2020-09-05 paper.tex
add a thesis.
some final changes for the first draft.

@@
 
-To gauge the performance of NNs in 
-the validation simulations, and the offline
+To gauge the performance of the NNs in 
+the validation simulations, computational 
+speedups over online QP based MPC, the offline
 computational effort required to build the NNs,
+and the memory required for the deployment of NNs,  
 the following metrics are examined:
@@
 nonlinear ordinary differential equations (ODEs) available in 
-\cite*{stewart:venkat:rawlings:wright:pannocchia:2010}.
+\cite*{venkat:2006}, Appendix.
 The model has 12 states 
@@
 A linear discrete time model with the chosen sample time
-is obtained at the steady state shown in the table 
+is obtained at the steady state shown in the Table 
 \ref{table:cstrs_pars}.
@@
 nodes in each hidden 
-layer respectively. For validation simulations, 
+layer respectively. For the validation simulations, 
 setpoint and disturbance signals 
@@
 is three hidden layers with 224 nodes in each hidden layer. 
-An additional scaling of $x$ and $x_s$ is performed for the 
+An additional scaling of the 
+states and target steady states ($x$ , $x_s$) is performed for the 
 NN training as $x := 2x/(x_{\textnormal{max}} - x_{\textnormal{min}})$ and 
@@
 are the maximum and minimum values of the state 
-observed in the training data.
+observed in the generated training data.
 This scaling is also performed in real-time 
@@
 controller and the degradation in the performance 
-is quantified with the $\%$ performance loss metric.
+is quantified with the $\%$ performance loss metric
+shown in the Table \ref{table:cstrs}.
 
@@
 shows a histogram of online computation times
-of the NNs and QP solver in the above validation
-simulation. The average and worst-case speedups
-obtained using NNs are summarized in the 
+of the NNs and the QP solver 
+CVXOPT. The average and worst-case speedups
+obtained using the NNs are summarized in the 
 Table \ref{table:cstrs}. The QP solver takes 
@@
 The $\%$ performance loss 
-obtained using the four heuristic controllers, 
-their corresponding speedups, time required to 
-train each NN, number of parameters in each NN, 
+obtained using the four fast controllers other 
+than the structured NNs, 
+their corresponding 
+computational speedups, the maximum time required to 
+train each NN, the number of parameters in each NN, 
 and the memory required to store  
@@
 is exactly the same as the optimal feedback law
-at steady states, and the training process improves the 
-approximation of the optimal feedback law
-by the NN only for the transient states.
+at the steady states, and that simplifies
+the optimal feedback law approximation problem
+since the training process only has to improve the 
+NN control law for the transient states.
 
@@
 The Figure \ref{fig:cdu_statistics} shows the 
-statistics for the simulation study performed for this 
+statistics obtained in the simulation study performed for this 
 example. The data requirements to obtain 
@@
 histogram of online computation times 
-of the NNs and QP solver.
+of the NNs and the QP solver CVXOPT.
 The Table \ref{table:cdu} gives a summary of 
-the maximum time required to train the NNs, number of parameters
-in each NN, memory footprint of the NNs, and 
-the $\%$ performance loss metric obtained by 
+the maximum time required to train the NNs, 
+the number of parameters
+in each NN, the memory footprint of the NNs, and 
+the $\%$ performance loss obtained by 
 the structured NNs, SS, satK, and SH 
@@
 The offline data generation and training times 
-for the NNs shows that this large-scale example
+to build the NNs show that this large dimensional example
 is tractable with the proposed NN approach.
@@
 performance index, the performance 
-degradation by the NNs compared with 
+degradation by the NNs relative to 
 the optimal MPC controller is negligible.
-The sampling of the state-space for NN training
-for one particular operational scenario 
-with the corresponding setpoint and disturbance signals 
-is the rule to obtain scalability of the NN controllers.
+The sampling of the state-space with 
+the setpoint and disturbance signals
+for one particular operational scenario,
+combined with the offset-free NN structure
+are key steps for scalability in this example.
 
@@
 The proposed no online optimization-based
-methods in the literature such as storing 
+methods to-date in the literature such as storing 
 the entire MPC feedback law 
@@
 
-The key features for scalability of the proposed approach 
+The key features for the scalability of the proposed approach 
 are the structure of NN and data generation for only the
 typical plant operational scenarios. 
-The NN design approach was demonstrated to scale on a
+The NN design approach was demonstrated to scale on an
 industrial crude distillation unit model with state and
@@
 a control-sample horizon length of 145 in the QP. 
-Parallel computing was used for the data 
-generation and graphical processing units for the NN 
-training. After the offline design phase, NNs execute MPC 
+After the offline design phase, NNs execute MPC 
 about three to five orders of magnitude faster than an 
@@
 with less than 1$\%$ performance degradation in the closed-loop. 
-The NNs are easily deployable on memory constrained hardware.
-Robustness properties
-of NNs were established under bounded approximation errors of the optimal 
-feedback law, that provides some theoretical support 
+Parallel computing can be used for the data generation step
+if solving QPs for each sampled state starts to take long 
+amounts of time.
+After the training process, 
+the NNs are easily deployable on memory constrained hardware.
+We established conditions under which the 
+NN controllers are robust to state estimation errors 
+and process disturbances,
+that provides some theoretical support 
 to practitioners interested in the deployment of NNs.
@@
 consortium for funding support.
-The computational facilities purchased with funds from the National Science Foundation (CNS-1725797) and administered by the Center for Scientific Computing (CSC) was used for the simulation 
+The computational facilities purchased with funds from the National Science Foundation (CNS-1725797) 
+and administered by the Center for Scientific Computing (CSC) was used for the simulation 
 studies presented in this article. 
-The CSC is supported by the California NanoSystems Institute and the Materials Research Science and Engineering Center 
+The CSC is supported by the California NanoSystems 
+Institute and the Materials Research Science and Engineering Center 
 (MRSEC; NSF DMR 1720256) at UC Santa Barbara.
@@
 \bibliographystyle{elsarticle-num-names}
-\bibliography{abbreviations,articles,books,unpub,proceedings}
+\bibliography{articles,books,unpub,proceedings}
 \end{document}

### 2020-09-05 paper.tex
send the draft.

@@
 combined with the offset-free NN structure
-are key steps for scalability in this example.
+are the key steps for scalability in this example.
 

### 2020-09-05 paper.tex
minor edit.

@@
 To gauge the performance of the NNs in 
-the validation simulations, computational 
+the validation simulations, the computational 
 speedups over online QP based MPC, the offline

### 2020-10-21 paper.tex
update files.

--- 2020-09-05 paper.tex
@@
 \usepackage{units}
+\usepackage{xcolor}
 %% The lineno packages adds line numbers. Start line numbering with
@@
 Second, we discuss the data generation procedure 
-to sample the relevant state-space for the network 
+to sample the relevant state space for the network 
 training based on anticipated online setpoint changes and
@@
 distillation unit model with 252 states, 32 control inputs, 
-and a control-sample horizon length of 145. Parallel computing 
+and a control-sample horizon length of 140. Parallel computing 
 is used for data generation and graphical processing units are used for
-network training. 
+network training. All the anticipated plant operational scenarios 
+with setpoints and disturbances that may change for 
+a reasonable duration of operation must be sampled for NN training.
 After the offline design phase, 
@@
 Model predictive control (MPC) is an online 
-optimization-based feedback control technology. A dynamic model 
+optimization based feedback control technology. A dynamic model 
 of the plant is used to make forecasts of the plant measurements
 in response to the actuator movements, and an optimization
-is solved in real-time to determine the optimal actuator
+is solved in real time to determine the optimal actuator
 move to be applied to the plant. For linear plant models, 
@@
 An alternative strategy to 
-real-time optimization for the deployment of MPC 
+real time optimization for the deployment of MPC 
 is to characterize the MPC feedback law
 as a piecewise affine function defined on 
-polyhedral partitions of the state-space, 
+polyhedral partitions of the state space, 
 and use the feedback law online
@@
 seron:goodwin:dedona:2003}.
-The real-time computation in this approach is 
-reduced to a table look-up in the state-space
+The real time computation in this approach is 
+reduced to a table look-up in the state space
 based on the current value of parameters 
 in the QP such as the state estimate and some 
-steady state targets that are computed for 
+steady-state targets that are computed for 
 offset-free control. The number of polyhedral 
-partitions of the state-space grows exponentially
-with model dimensions, thereby prohibiting 
-the deployment of this strategy on large systems.
+partitions of the state space grows exponentially
+with model dimensions, however. Thereby prohibiting 
+the deployment of this strategy on large-scale 
+systems.
 
@@
 \citep*{montufar:pascanu:cho:bengio:2014}
-and execute MPC faster in real-time than QP solvers. 
+and execute MPC faster in real time than QP solvers. 
 The proposed NN design approach in 
@@
 in these problems:
-i) In a large dimensional state-space,   
+i) In a large dimensional state space,   
 the entire set of feasible states of the QP cannot be sampled  
 densely for the NN training. This issue is 
-a type of the curse of dimensionality.
-ii) One may sample the state-space partially
+a form of the curse of dimensionality.
+ii) One may sample the state space partially
 to avoid this problem, but the time required for the 
@@
 computing, and the former issue by sampling the 
-state-space for the typical plant operational scenarios.
+state space for typical plant operational scenarios.
 The following feature must be present in the large-scale
@@
 such that the entire large
-dimensional state-space is not visited during that
+dimensional state space is not visited during that
 operation mode. 
@@
 this article discusses the design of NNs
-as an alternative to real-time optimization in MPC, 
+as an alternative to real time optimization in MPC, 
 with an emphasis on large applications which 
@@
 We present a new feedforward network architecture to obtain
-offset-free closed-loop performance with NNs.
+offset-free closed-loop performance with the NNs.
 Additionally, we use the input-to-state
@@
 
-The closely related work by \cite*{chen:wang:atanasov:kumar:morari:2019}
+The related work by \cite*{chen:wang:atanasov:kumar:morari:2019}
 demonstrates the scalability of NNs 
 to approximate the MPC feedback law on systems with 
-large state dimensions. The 
-size of problems and the setpoint 
-tracking offset-free MPC problem   
-considered in this 
-article is not addressed in this work. 
+state dimensions upto thirty-six. The setpoint 
+tracking offset-free MPC problem and state 
+dimensions upto two-fifty considered in this 
+article is not addressed in that work. 
 \cite*{drgona:picard:kvasnica:helsen:2018}
@@
 reduced using principal component analysis, and the 
-NN controller 
-is developed in a low dimensional state-space.
+NN controller is developed in a low dimensional state space.
 
@@
 offset-free linear MPC. 
-In section \ref{sec:controller_design},
+In Section \ref{sec:controller_design},
 we discuss the NN 
@@
 We present the robustness property
-of NNs in section \ref{sec:robustness}.
+of NNs in Section \ref{sec:robustness}.
 Then, we present simulation studies
 on two large process control examples
-in section \ref{sec:simulation_studies}
+in Section \ref{sec:simulation_studies}
 and conclude at the end of this article.
@@
 is of class $\mathcal{K}$ if it is continuous, zero 
-at zero, and strictly increasing. It is of class 
+at zero, and strictly increasing. This function is of class 
 $\mathcal{K}_{\infty}$ if it is of class $\mathcal{K}$
@@
 \end{align}
-in which ($x_s, u_s$) is the 
-target steady state pair, ($u_{sp}, r_{sp}$) 
-are the input and controlled measurement setpoints,
-and ($\underline{u}, \overline{u}$) are the 
-actuator bounds.
+in which
+($x_s, u_s$) is the 
+target steady state pair,
+$r=Hy$ are the controlled measurements
+chosen as some subset 
+or a linear combination of all the measurements,
+($\underline{u}, \overline{u}$) are the 
+actuator bounds, and
+($u_{sp}, r_{sp}$) are the input and 
+controlled measurement setpoints.
 The equality constraint $r_{sp} = H(Cx_s + C_d\hat{d})$
-can be difficult to satisfy exactly in real-time 
+can be difficult to satisfy exactly in real time 
 depending on the controlled measurement setpoint 
@@
 only the controlled measurement setpoint ($r_{sp}$) 
-changes in real-time.
+changes in real time.
 
@@
 in which $\hat{x}$ is the state estimate after the current measurement,
+$N$ is the control 
+horizon length, and
 ($\tilde{x}, \tilde{u}$) are the state and control 
@@
 \mathbf{\tilde{u}}^0(0;\hat{x}, x_s, u_s) + u_s$, 
-that is applied to the plant. This feedback law is a function of the 
-state estimate and target steady state pair. A rate-of-change 
+which is applied to the plant. This feedback law is a function of the 
+state estimate and target steady-state pair. A rate-of-change 
 penalty on the control can be imposed in the QP objective
@@
 as well in addition to the state estimate
-and target steady state pair.
+and target steady-state pair.
 
@@
 is the future control trajectory $\mathbf{\tilde{u}}$, 
-and the QP solver CVXOPT \citep*{vandenberghe:2010}
+and the QP solver CVXOPT \citep*{vandenberghe:2010},
+which is tailored for dense problems
 is used for NN data generations and timing 
 comparisons with online QP based MPC.
+Any improvement in the QP formulation
+and solution algorithm is advantageous
+for both the online QP based MPC 
+and NN approaches
+as fast QP solvers reduce the 
+offline data generation time required for the 
+design of NNs.
 
@@
 usually small compared to the 
-regulator QP, that consumes most of the online computation time. We
-focus on designing a NN that approximates the 
+regulator QP, which consumes most of the online computation time. 
+Therefore we focus on designing a NN that approximates the 
 MPC feedback law ($\kappa_N(x, x_s, u_s)$)
-for an operationally relevant set of states and steady state targets, 
+for an operationally relevant set of states and steady-state targets, 
 such that the NN 
@@
 for one fixed steady state. The approach has not been 
-demonstrated to scale for the size of model dimensions 
+demonstrated to scale to the size of model dimensions 
 and the setpoint tracking 
@@
 An issue with this strategy 
-is that the NN has no knowledge about any information 
-of the MPC feedback law, and can require large amounts
+is that the NN has no knowledge about 
+the MPC feedback law, and can require large amounts
 of training data in large state dimensions 
@@
 setpoint tracking MPC problem considered in this article, 
-the NN control law must be such that at steady state 
+the NN control law must be such that at steady-state 
 operations, the NN maintains the plant at the desired steady state
@@
 in which we use $\kappa_{NN}(\cdot)$ to denote the NN control law.
-To incorporate this information in a NN, we present the following
+To incorporate this information in a NN, we introduce the following
 architecture
@@
 $h$ is the number of hidden layers, 
-and $i \in \bbI_{1:h}$. The parameters 
-to be optimized using training data are ($W_i, b_i$) 
+and $i \in \bbI_{1:h}$. 
+The parameters to be optimized using 
+training data are ($W_i, b_i$) 
 and $W_{h+1}$, which are matrices 
-of appropriate dimensions. The software tensorflow 
+of appropriate dimensions.
+At steady-states
+when $x=x_s$ in $z_0$, this structured network
+outputs $u_s$ regardless of the choice of weights.
+The software tensorflow 
 \citep{abadi:agarwal:barham:brevdo:et-al:2015} is used 
@@
 ($W_i, b_i$) and $W_{h+1}$ 
-are appropriately adjusted. After 
+are appropriately adjusted. Even after 
 training, the control produced by 
-the NN may not obey the hard actuator constraints,
+the NN may not satisfy the hard actuator constraints,
 and the saturation function 
@@
 set of feasible states for the MPC QP 
-defined by equations \ref{eqn:regulator}
-to \ref{eqn:regulator_constraints}
+defined by \eqref{eqn:regulator}-\eqref{eqn:regulator_constraints}
 is the entire $n$-dimensional state space $\bbR^n$.
@@
 The domain of the MPC control law ($\kappa_N(x, x_s, u_s)$)
-is therefore the state-space 
-$\bbR^{n}$ and the possible set of steady state 
-target pairs.
-Sampling this entire domain of the
+is therefore the state space 
+$\bbR^{n}$ and the possible set of steady-state 
+target pairs. Sampling this entire domain of the
 MPC control law for NN training is difficult in larger 
-dimensions and not required for practical applications.
+dimensions and we show in Section 
+\ref{sec:simulation_studies} that it is
+not required for practical applications.
 
@@
 a majority of the large-scale petrochemical plants
-operate in scenarios. Each operational scenario is driven 
+operate in a relatively small number of operating regimes
+or scenarios. Each operational scenario is driven 
 by a selected few controlled measurement 
@@
 and some large magnitude disturbances
-which change frequently, 
+may change frequently, 
 while the setpoints for 
 the other measurements remain constant for long periods 
-of time. The states and steady state targets 
+of time. The states and steady-state targets 
 spanned in a closed-loop 
@@
 than the entire domain of the MPC control law.
-This operation style of large chemical plants
+This type of operation of large chemical plants
 can be exploited, and we propose the 
@@
     selector and regulator QPs for the transient states
-    and steady state targets encountered in the simulation. 
+    and steady-state targets encountered in the simulation. 
 \end{enumerate}
@@
 that the NN does not encounter 
-the same states and steady state 
+the same states and steady-state 
 target pairs used for the training. But similar
@@
 serially due to the long time required to solve 
-each QP. For these large problems, 
+each QP (minutes). For these large problems, 
 several PRBS signals of the setpoints 
 and disturbances are generated and 
-multiple simulations are performed parallelized over 
+multiple simulations are performed in parallel over 
 several cores in a CPU and across multiple CPUs as well.
-The data generated from all the simulations is collected
+The data generated from all the simulations are collected
 and used for the NN training.
@@
     J (\theta) = \dfrac{1}{2}\sum_{j=1}^{N_{tr}} 
-    [\kappa_{NN}(x, x_s, u_s; \theta) - \kappa_N(x, x_s, u_s)]^2 
+[\kappa_{NN}(x_j, x_{sj}, u_{sj}; \theta) - \kappa_N(x_j, x_{sj}, u_{sj})]^2 
 \end{align}
@@
 to be optimized, ($W_i, b_i, W_{h+1}$)
-for $i \in \bbI_{1:h}$, and $N_{tr}$ is the number of training 
+for $i \in \bbI_{1:h}$, subscript $j$ is used 
+to denote the training sample index, and 
+$N_{tr}$ is the number of training 
 samples. The stochastic optimization algorithm Adam 
 \citep*{kingma:ba:2014} is used for all the NN training
-performed in the case studies in this article.
+performed in the case studies in this article. We do not 
+consider any regularization penalty in the training objective. 
+The recent empirical and theoretical works in the machine learning 
+literature have shown that NNs with large number of parameters 
+have good interpolation capabilities 
+\citep*{belkin:hsu:ma:mandal:2019, zhang:bengio:hardt:recht:vinyals:2017, 
+arora:simon:hu:li:wang:2019, allen-zhu:li:liang:2019} 
+without any form of explicit regularization during training.
+The generalization abilities of 
+NNs for the architectures considered in this article
+is examined in the 
+simulations presented in the Section \ref{sec:simulation_studies}.
 
 \section{Robustness of neural networks} \label{sec:robustness}
+
+\begin{figure*}[!h]
+    \centering
+	\includegraphics[page=1, 
+		width=0.7\textwidth, 
+        height=0.5\textheight]{cstrs_comparision_plots.pdf}    
+        \caption{Transient closed-loop actuator trajectories of the CSTRs with 
+        flash separator example with the NN and optimal MPC controllers.}   
+    \label{fig:cl_cstrs_inputs}
+\end{figure*}
+
+\begin{figure*}[!h]
+    \centering
+	\includegraphics[page=2, 
+		width=0.7\textwidth, 
+		height=0.5\textheight]{cstrs_comparision_plots.pdf}
+        \caption{Transient closed-loop controlled measurement 
+        trajectories of the CSTRs with 
+        flash separator example with the NN and optimal MPC controllers.}      \label{fig:cl_cstrs_outputs}
+\end{figure*}
 
@@
 the NN controller to be robust to disturbances. 
-The Theorem \ref{thm:nnrobustness} states this 
+Theorem \ref{thm:nnrobustness} states this 
 allowable approximation error and the size 
@@
 as $\mathcal{X}_N = \textnormal{lev}_{Nd + \tau} \ V_N^0(x)$.
-In which, $N$ is the control 
-horizon length used in the QP, $\tau$ is a level
+In which, $\tau$ is a level
 set parameter of the terminal region chosen as
@@
 
-We use the following
-definitions of
-robust positive invariance of a set
-with respect to disturbances, 
-input-to-state stability (ISS), ISS-Lyapunov function,
-and the available result 
-on the ISS property of a system if it admits 
-an ISS-Lyapunov function
-(\cite*{jiang:wang:2001, 
-rawlings:mayne:diehl:2017}, Appendix B).
-
-\begin{definition} \label{def:robust_pos_invariance}
-(Robust positive invariance). A closed set $X$ is 
-robustly positive invariant for the system $x^+ = f(x, w)$, 
-$w \in \bbW$ if $x \in X$ 
-implies $f(x, w) \in X$ for all $w \in \bbW$.
-\end{definition}
-
-\begin{definition} \label{def:iss}
-(Input-to-state stability (ISS)). $\bbW$ is a compact 
-set containing the origin and that $X$ is a closed robustly
-positive invariant set for $x^+ = f(x, w)$, $w \in \bbW$. This
-system is ISS in $X$ if there exist functions 
-$\beta(\cdot) \in \mathcal{K}\mathcal{L}$ and 
-$\sigma(\cdot) \in \mathcal{K}$, such that for all
-$x \in X$ and $w(i) \in \bbW$, $i \in \bbI_{0:k-1}$, 
-$\vert \psi(k; x, \mathbf{w}_k) \vert \leq \beta(\vert x\vert, k) 
-+ \sigma(\vert \vert \mathbf{w}_k\vert \vert)$, in which 
-$\psi(k; x, \mathbf{w}_k)$ is the solution of the system 
-at time $k$.
-\end{definition}
-
-\begin{definition} \label{def:iss_lyapunov_func}
-(ISS-Lyapunov function). A function $V : X \rightarrow \bbR_{\geq 0}$
-is an ISS-Lyapunov function in $X$ for the system $x^+ = f(x, w)$, $w \in \bbW$
-if there exist functions $\alpha_1(\cdot), \alpha_2(\cdot), \alpha_3(\cdot) 
-\in \mathcal{K}_{\infty}$ and $\sigma(\cdot) \in \mathcal{K}$
-such that for all $x \in X$ and $w \in \bbW$
-\begin{align*}
-    \alpha_1(\vert x \vert) \leq & V(x) \leq \alpha_2(\vert x \vert) \\
-    V(f(x, w)) &- V(x) \leq -\alpha_3(\vert x \vert) + \sigma(\vert w \vert)
-\end{align*}
-\end{definition}
-
-\begin{prop} \label{prop:lyapunov_implies_iss}
-(ISS-Lyapunov function implies ISS). $\bbW$ is a compact
-set containing the origin and that $X$ is a closed robustly
-positive invariant set for $x^+ = f(x, w)$, $w \in \bbW$. If 
-$f(\cdot)$ is continuous and there exists a continuous 
-ISS-Lyapunov function in $X$ for the system $x^+ = f(x, w)$, $w \in \bbW$, 
-then the system is ISS in $X$.
-\end{prop}
-
-Additionally, we require the following two 
-useful propositions from 
-\cite*{allan:bates:risbeck:rawlings:2017} and 
-\cite*{rawlings:ji:2012},
-to bound values of continuous functions and an
-inequality for $\mathcal{K}$ functions respectively.
-
-\begin{prop} \label{prop:continuous_funcs}
-    Let $C \subseteq D \subseteq \bbR^n$, $C$ compact, 
-    $D$ closed, and $f : D \rightarrow \bbR^n$ continuous.  
-    Then there exists a $\sigma(\cdot) \in \mathcal{K}_{\infty}$
-    such that for all $x \in C$ and $y \in D$, we have that 
-    $\vert f(x) - f(y) \vert \leq \sigma(\vert x-y \vert)$.
-\end{prop}
-
-\begin{prop} \label{prop:Kfunction_inequality}
-    Let $\sigma(\cdot) \in \mathcal{K}$, the following holds 
-    for all $a_i \in \bbR_{\geq 0}$, $i \in \bbI_{1:n}$ 
-    \begin{align*}
-        \sigma(a_1 + a_2 + \cdot \cdot + a_n) \leq \sigma(na_1) + 
-        \sigma(na_2) + \cdot \cdot + \sigma(na_n)
-    \end{align*}    
-\end{prop}
-
-The above definitions and propositions 
-are used to establish the 
-following theoretical property for the perturbed
-linear system \ref{eq:perturbed_sys}.
-
-\begin{figure*}[!h]
-    \centering
-	\includegraphics[page=1, 
-		width=0.7\textwidth, 
-		height=0.5\textheight]{cstrs_comparision_plots.pdf}
-    \caption{Transient closed-loop actuator trajectories of the CSTRs with 
-    flash separator example with the NN and optimal MPC controllers.}  
-    \label{fig:cl_cstrs_inputs}
-\end{figure*}
-
-\begin{figure*}[!h]
-    \centering
-	\includegraphics[page=2, 
-		width=0.7\textwidth, 
-		height=0.5\textheight]{cstrs_comparision_plots.pdf}
-        \caption{Transient closed-loop controlled measurement 
-        trajectories of the CSTRs with 
-        flash separator example with the NN and optimal MPC controllers.}  
-    \label{fig:cl_cstrs_outputs}
-\end{figure*}
-
 \begin{thm} \label{thm:nnrobustness}
@@
 $\vert\vert \mathbf{w}_k \vert\vert \leq \delta_2$,
-and $\vert e_{NN}(\hat{x}) \vert \leq \delta_3$
+and $\vert e_{NN}(\hat{x}) \vert \leq \delta_3$,
 for all $\hat{x}$ in the set $S := \textnormal{lev}_{\rho} \ V_N^0(\hat{x})$,
@@
 
-\textbf{Proof:}
-We proceed in two steps. First, 
-we show that there exist constants $\delta_1, \delta_2, \delta_3 > 0$
-such that the set $S$ is robustly positive invariant. Then, we 
-show that $V_N^0(\hat{x})$ is an ISS Lyapunov function for 
-the perturbed system on this set $S$. Denote 
-$\tilde{x}^+ = A\hat{x} + B\kappa_N(\hat{x})$ as the nominal 
-state evolution using the optimal MPC controller, 
-and $d(k) = [ e_{NN}(\hat{x}(k))'B', w(k)', e(k)', e(k+1)']'$
-as the combination of all the disturbances at a given time $k$.
-
-To show robust positive invariance of $S$,  
-we establish that if $V_N^0(\hat{x}) \leq \rho$, 
-then $V_N^0(\hat{x}^+) \leq \rho$.
-Since the optimal 
-cost function ($V_N^0(\hat{x})$) is continuous,
-using $\bbR^n$ as the closed set ($\hat{x}^+ \in \bbR^n$) 
-and $S$ as the compact set ($\tilde{x} \in S$),
-from proposition \ref{prop:continuous_funcs} we have
-\begin{align}
-    \vert V_N^0(\hat{x}^+) - V_N^0(\tilde{x}^+) \vert &\leq 
-    \sigma_1(\vert \hat{x}^+ - \tilde{x}^+ \vert)  \nonumber  \\
-    \vert V_N^0(\hat{x}^+) - V_N^0(\tilde{x}^+) \vert &\leq 
-   \sigma_1(\vert B \vert\vert e_{NN}(\hat{x}) \vert + \vert w \vert 
-   \nonumber \\
-   & + \vert A\vert\vert e \vert +  \vert e^+ \vert) \nonumber \\
-    \vert V_N^0(\hat{x}^+) - V_N^0(\tilde{x}^+) \vert &\leq 
-   \sigma_1(\vert d \vert + \vert d \vert + \vert A \vert\vert d \vert + \vert d \vert) := \sigma_2(\vert d \vert)
-   \label{eq:optimal_cost_bound}
-\end{align}
-in which $\sigma_2(s) := \sigma_1(\vert A\vert s +3s)$, and the last inequality 
-follows because $\vert a \vert \leq \vert [a', b']' \vert$, in which $a$ and $b$
-are both vectors.
-We partition $S$ in outer and inner parts based on 
-the value of the optimal cost $V_N^0(\hat{x})$, and bound the 
-combination of disturbances $d$ in each part 
-such that $V_N^0(\hat{x}^+) \leq \rho$. \\
-Case 1: $\rho/2 \leq V_N^0(\hat{x}) \leq \rho $. Using the 
-upper bound on the optimal cost, we have 
-$\rho/(2c_2) \leq \vert \hat{x} \vert^2$ for all $\hat{x}$ 
-in this part of $S$. To analyze the worst-case disturbance, 
-we have from the equation \eqref{eq:optimal_cost_bound} that 
-$V_N^0(\hat{x}^+) \leq V_N^0(\tilde{x}^+) + \sigma_2(\vert d \vert) $.
-From nominal MPC cost decrease, we obtain  
-$V_N^0(\hat{x}^+) \leq V_N^0(\hat{x}) - c_1\vert \hat{x} \vert^2 + \sigma_2(\vert d \vert)$. Thus, if $\sigma_2(\vert d \vert) \leq \rho c_1/(2c_2)$, 
-at all times in this outer part of $S$, we have 
-$V_N^0(\hat{x}^+) \leq \rho$. \\
-Case 2: $V_N^0(\hat{x}) \leq \rho/2 $. From 
-equation \eqref{eq:optimal_cost_bound} and nominal MPC 
-cost decrease, we have for this part of $S$ that 
-$V_N^0(\hat{x}^+) \leq \rho/2 + \sigma_2(\vert d \vert)$.
-Thus, if $\sigma_2(\vert d \vert) \leq \rho/2$, 
-at all times in this inner part of $S$, we have 
-$V_N^0(\hat{x}^+) \leq \rho$.
-
-Therefore, if 
-$\vert d \vert \leq \textnormal{min} \{ \sigma_2^{-1}(\rho c_1/(2c_2)), 
-\sigma_2^{-1}(\rho/2)\} := \delta_{\textnormal{max}}$ 
-at all times, then the set $S$ is 
-robustly positive invariant. The constants 
-$\delta_1, \delta_2$, and $\delta_3$ are 
-$\delta_{\textnormal{max}}/4$ each. The optimal
-MPC cost function obeys
-\begin{align*}
-    V_N^0(\hat{x}^+) - V_N^0(\hat{x}) &\leq 
-    -c_1\vert \hat{x} \vert^2 + \sigma_2(\vert d \vert)
-\end{align*}
-in the robustly positive invariant set $S$,
-disturbance set $\vert d \vert \leq \delta_{\textnormal{max}}$,
-and from the Definition \ref{def:iss_lyapunov_func},
-satisfies the requirements of an ISS-Lyapunov function.
-Hence, using the Proposition \ref{prop:lyapunov_implies_iss}, 
-the perturbed linear system \ref{eq:perturbed_sys} is
-ISS (Definition \ref{def:iss}), 
-and there exist functions 
-$\beta(\cdot) \in \mathcal{K}\mathcal{L}$ and 
-$\sigma(\cdot) \in \mathcal{K}$, such that 
-$\vert \phi_d(k; \hat{x}) \vert \leq \beta(\vert \hat{x} \vert, k) 
-+ \sigma(\vert\vert \mathbf{d}_k\vert\vert)$. Using the Proposition
-\ref{prop:Kfunction_inequality}, we have 
-\begin{align*}
-    \vert \phi_d(k; \hat{x}) \vert & \leq \beta(\vert \hat{x} \vert, k) \\
-    + &\sigma(3\vert B\vert\bar{e}_{NN}) + 
-    \sigma(3\vert \vert \mathbf{w}_k \vert \vert)
-    + \sigma(3(\vert A\vert + 1)\vert \vert \mathbf{e}_{k+1} \vert\vert)
-\end{align*}
-Therefore, the bound in the Theorem \ref{thm:nnrobustness} is established with 
-$\alpha_e(s) := \sigma(3(\vert A\vert + 1)s)$, 
-$\alpha_w(s) := \sigma(3s)$, and
-$\alpha_n(s) := \sigma(3\vert B\vert s)$.
-
+The proof of this theorem along with the required 
+input-to-state stability definitions is provided 
+in Appendix \ref{app:theorem1}.
 In the nominal case, 
@@
 approximation error ($\bar{e}_{NN}$) 
-in the state-space of interest and 
+in the state space of interest and 
 strengthen the bounds on the closed-loop states.
@@
 \section{Simulation studies} \label{sec:simulation_studies}
+
 In this section, two case studies are presented 
@@
 After the offline design of NNs,
-validation simulations are performed with 
-setpoints and disturbances not present 
-in the training data but within the same range 
-of values chosen to generate the training data.
+two types of validation simulations 
+are performed: (i) with setpoints 
+and disturbances not present in the training 
+data but within the same range of values used to 
+generate the training data, (ii) with extra setpoint 
+signals assumed to be
+unknown during the offline network design phase.
+Both these types of simulations are conducted to 
+analyze the interpolation and extrapolation 
+abilities of the NNs, and are referred subsequently as 
+simulations with expected and unexpected plant behaviors.
+
 The closed-loop performance of the 
@@
 c) short horizon controller (SH): an MPC problem
-with short control horizon is solved online, 
+with a short control horizon is solved online, 
 d) Unstructured NN (NN-UNS): a standard feedforward network is 
@@
 
-To gauge the performance of the NNs in 
-the validation simulations, computational 
-speedups over online QP based MPC, the offline
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth, 
+                     height=0.22\textheight]{cstrs_with_flash.pdf}
+    \caption{Schematic of the CSTRs with a flash separator model}
+    \label{fig:schematic_cstrs}
+\end{figure}
+
+To gauge the performance of NNs in 
+the validation simulations, the offline
 computational effort required to build the NNs, 
@@
 \begin{itemize}
-    \item Controller performance index \\
-    $\Lambda_k = \dfrac{1}{k}\sum_{t=1}^{k} \big(\vert x(t) - x_{s} (t) \vert^2_{Q} + \vert u(t) - u_{s} (t) \vert^2_{R} \big)$
-    \item \% Performance loss = $100(\Lambda^{F}_{N_{t}} - \Lambda^{MPC}_{N_{t}})/\Lambda^{MPC}_{N_{t}}$
+    \item Controller performance index
+    \begin{align*}        
+    \Lambda_k = \dfrac{1}{k}\sum_{t=1}^{k} & \big(\vert x(t) - x_{s} (t) \vert^2_{Q} \\
+        & + \vert u(t) - u_{s} (t) \vert^2_{R} + \vert \Delta u(t) \vert^2_{S}\big)         
+    \end{align*}
+    \item \% Performance loss = $100(\Lambda^{\textnormal{F}}_{N_{t}} - \Lambda^{\textnormal{MPC}}_{N_{t}})/\Lambda^{\textnormal{MPC}}_{N_{t}}$
     \item Average and worst-case speedups
     \item Data generation and NN training times
-    \item Memory required to store the weights of NNs
+    \item Memory required to store the weights of the NNs
 \end{itemize}
-in which $N_t$ is the number of simulation time steps,  
-$\Lambda^{F}_{N_{t}}$ and $\Lambda^{MPC}_{N_{t}}$
+Here, $N_t$ is the number of simulation time steps,  
+$\Lambda^{\textnormal{F}}_{N_{t}}$ and 
+$\Lambda^{\textnormal{MPC}}_{N_{t}}$
 are the average stage costs obtained 
@@
 Tesla V100-SXM2 GPU that has 32 GB memory.
+
 \begin{table*}[t]
@@
         \thead{Number of \\ Parameters} & 
-        \thead{Memory \\ footprint (mB)} & \thead{Training \\ time (min)} &
-        \thead{\% Performance\\ loss} & \thead{Average \\ speedup} & \thead{Worst case \\ speedup} \\
-        \hline
-    SS &  &  & &  & 106.39 \% &  & \\ 
-    satK &  &  &  &  & 27.61 \% & $2.59 \times 10^5$ & 
-    $3.16 \times 10^4$ \\ 
-    SH &  &  &  &  & 2.46 \% & $5.66 \times 10^3$ & $1.88 \times 10^2$ \\ 
-    NN-UNS &  &  &  &  & 107.28 \% & $3.17 \times 10^4$ & $6.19 \times 10^3$ \\ 
-NN-3-448 & [72, 448, 448, 448, 6] & $1.18 \times 10^5$ & 0.84 & 12.7 & 0.27 \% & $2.34 \times 10^4$ & $7.18 \times 10^3$ \\ 
-NN-3-480 & [72, 480, 480, 480, 6]  & $1.34 \times 10^5$ & 0.96  & 12.6 & 0.28 \% & $2.12 \times 10^4$ & $3.12 \times 10^3$ \\ 
-NN-3-512 & [72, 512, 512, 512, 6]  & $1.51 \times 10^5$ & 1.08  & 14.3 & 0.16 \% & $1.91 \times 10^4$ & $2.14 \times 10^3$ \\ 
-NN-3-544 & [72, 544, 544, 544, 6]  & $1.71 \times 10^5$ & 1.22  & 18.6 & 0.39 \% & $1.80 \times 10^4$ & $4.03 \times 10^3$ \\ 
+    \thead{Memory \\ footprint \\ (mB)} & \thead{Training \\ time \\ (min)} &
+        \thead{\% Performance\\ losses \\ Expected, Unexpected \\ plant behaviors} & \thead{Average \\ speedup} & \thead{Worst case \\ speedup} \\
+        \hline
+    SS &  &  & &  & 85.18\%, 106.39 \% &  & \\ 
+    satK &  &  &  &  & 41.03\%, 27.61 \% & $2.47 \times 10^5$ & 
+    $3.07 \times 10^5$ \\ 
+    SH &  &  &  &  & 1.61\%, 2.46 \% & $3.75 \times 10^3$ & $8.4 \times 10^1$ \\ 
+    NN-UNS &  &  &  &  & 80.49\%, 73.29 \% & $9.31 \times 10^4$ & $4.99 \times 10^3$ \\ 
+NN-3-448 & [72, 448, 448, 448, 6] & $1.10 \times 10^5$ & 0.84 & 13.02 & 0.28 \%, 5.57 \% & $5.26 \times 10^4$ & $1.45 \times 10^3$ \\ 
+NN-3-480 & [72, 480, 480, 480, 6]  & $1.26 \times 10^5$ & 0.96  & 12.51 & 0.34 \%, 7.58\% & $5.09 \times 10^4$ & $1.53 \times 10^4$ \\ 
+NN-3-512 & [72, 512, 512, 512, 6]  & $1.42 \times 10^5$ & 1.08  & 12.77 & 0.16 \%, 5.90 \% & $4.62 \times 10^4$ & $1.58 \times 10^4$ \\ 
         \hline
@@
 \begin{figure*}[!h]
-    \includegraphics[page=21,
+    \includegraphics[page=31,
         width=0.5\textwidth, 
-        height=0.3\textheight]{cstrs_comparision_plots.pdf} \hfill
-    \includegraphics[page=23,
+        height=0.28\textheight]{cstrs_comparision_plots.pdf} \hfill
+    \includegraphics[page=34,
         width=0.5\textwidth, 
-        height=0.3\textheight]{cstrs_comparision_plots.pdf} \vfill
+        height=0.28\textheight]{cstrs_comparision_plots.pdf} \vfill
     \vspace{-0.1in}
-    \begin{center}\includegraphics[page=22,
+    \begin{center}\includegraphics[page=33,
         width=0.5\textwidth, 
-        height=0.3\textheight]{cstrs_comparision_plots.pdf}\end{center}
+        height=0.28\textheight]{cstrs_comparision_plots.pdf}
+    \end{center}
     \vspace{-0.2in}
     \caption{Simulation statistics for the  
-    CSTRs with a flash separator example. Data requirements to obtain accurate NN controllers (top left), online computation times of the NNs and 
+    CSTRs with a flash separator example. Data requirement to obtain accurate NN controllers (top left), online computation times of the NNs and 
     MPC controller (top right), 
@@
 and validation simulations are 
-shown in Table \ref{table:cstrs_pars}.
-
-\begin{figure}[h]
+shown in Table \ref{table:cstrs_pars}, Appendix \ref{app:cstrs_pars}.
+
+A linear discrete time model with the chosen sample time
+is obtained at the steady state shown in the Table 
+\ref{table:cstrs_pars}.
+This model, inputs and outputs are scaled 
+for the MPC controller such that the input 
+constraints satisfy
+$\overline{u} - \underline{u} = \mathbf{2}$.
+The tuning parameters and 
+control horizon length for the regulator are chosen as
+$Q = 10^3 C'C$, $R = 0.1 I$, $S = 0.1 I$, 
+and $N = 450$.
+A total $1.5 \times 10^5$ samples of 
+($x, u_{-1}, x_s, u_s, \kappa_N(\cdot)$) 
+is generated for NN training, parallelized in 100 
+separate offline simulations. The time consumed 
+for this data generation step was 4.2 hours.
+The setpoint of the 
+height of the second CSTR ($H_m$) is assumed 
+to be fixed during this data generation process, 
+and is included as an additional setpoint
+in the validation simulations for the 
+unexpected plant behavior case.
+
+Three structured NN architectures 
+are considered. Each NN
+has three hidden layers with 
+448 (NN-3-448), 480 (NN-3-480), 
+and 512 (NN-3-512)
+nodes in each hidden 
+layer respectively. For validation simulations, 
+two sets of setpoint and disturbance signals 
+with 24 setpoint changes and 48 disturbance changes 
+are generated for 4320 timesteps (12 hours), 
+each for the expected and unexpected 
+plant behavior cases. 
+The short horizon MPC controller is constructed with a 
+horizon length of $N = 10$, and the architecture 
+of the unstructured NN considered 
+is three hidden layers with 224 nodes in each hidden layer. 
+An additional scaling of $x$ and $x_s$ is performed for the 
+NN training as $x := 2x/(x_{\textnormal{max}} - x_{\textnormal{min}})$ and 
+$x_s := 2x_s/(x_{\textnormal{max}} - x_{\textnormal{min}})$,
+in which $x_{\textnormal{max}}$ and $x_{\textnormal{min}}$
+are the maximum and minimum values of the state 
+observed in the training data.
+This scaling is also performed in real time 
+when the NN is used to compute the actuator move.
+
+First, the amount of data required to obtain an accurate 
+NN controller is studied. To this aim, NNs with 
+the three chosen architectures are trained with 
+incremental increases of 
+$10^4$ training samples starting from $4 \times 10^4$
+to $1.5 \times 10^5$ samples. 
+A batch size of 1024 samples is used in Adam, 
+and all the NNs are trained for 2000 epochs. 
+The NNs after training are used in validation simulations
+with the setpoint and disturbance
+signals generated for the expected plant behavior
+case. The closed-loop performance is 
+compared with the optimal MPC 
+controller and the $\%$ performance loss obtained
+is plotted in Figure \ref{fig:cstrs_statistics} (top left)
+as a function of the number of training samples.
+All the trained NNs provide less than $1 \%$ loss in 
+this performance metric after training with 
+about $9 \times 10^4$ samples. The best $\%$ performance
+loss obtained by the NNs is summarized in
+Table \ref{table:cstrs}.
+
+Second, the above trained NNs with the best 
+performance losses are used in validation simulations
+with the setpoint and disturbance signals generated 
+for the unexpected plant behavior case. The 
+$\%$ performance losses obtained in these simulations 
+are also summarized in the Table \ref{table:cstrs},
+and the performance degrades from 
+less than $1\%$ to $5-8\%$. 
+This deterioration in the performance is due to some unseen
+($x, u_{-1}, x_s, u_s$) encountered in real-time by the NN
+resulting from the setpoint changes of the height 
+of the second CSTR, which was assumed to be fixed 
+during the data generation. 
+These simulations illustrate that one must not 
+expect the NNs to extrapolate outside the training data.
+The practical implication of this study is that 
+all possible plant scenarios with the 
+setpoints and disturbances 
+must be identified a-priori the deployment of NNs, and 
+should be used to generate the training data.
+
+\begin{table*}[t]
+    \caption{Summary of the simulation study for the 
+    industrial crude distillation unit example.}
+    %\centering
+\begin{tabular}{ |c|c|c|c|c|c|c|c| }
+          \hline
+          Controller & \thead{Structured network \\ architecture} & 
+          \thead{Number of \\ Parameters} & 
+          \thead{Memory \\ footprint \\ (mB)} & \thead{Training \\ time \\ (min)} &
+          \thead{\% Performance\\ loss} & \thead{Average \\ speedup} & \thead{Worst case \\ speedup} \\
+          \hline
+      SS &  &  & &  & 120.59 \% &  & \\ 
+  satK &  &  &   &  & 13.07 \% & $4.83 \times 10^5$ & $1.51 \times 10^5$ \\ 
+  SH &  &  &  &  & 1.56 \% & $6.66 \times 10^3$  & $2.51 \times 10^3$ \\ 
+  NN-3-1664 & [1072, 1664, 1664, 1664, 32] & $1.85 \times 10^6$ & 14.18 & 52.66 & 0.29 \% & $1.52 \times 10^4$ & $6.57 \times 10^3$  \\ 
+  NN-3-1792 & [1072, 1792, 1792, 1792, 32]  & $2.11 \times 10^6$ & 16.15  & 55.27 & 0.43 \% & $1.33 \times 10^4$ & $5.25 \times 10^3$ \\ 
+  NN-3-1920 & [1072, 1920, 1920, 1920, 32]  & $2.39 \times 10^6$ & 18.24  & 59.24 & 0.59 \% & $1.18 \times 10^4$ & $4.48 \times 10^3$ \\ 
+  NN-3-2048 & [1072, 2048, 2048, 2048, 32]  & $2.68 \times 10^6$ & 20.46  & 66.58 & 0.48 \% & $1.09 \times 10^4$ & $3.54 \times 10^3$\\ 
+\hline
+\end{tabular}
+\label{table:cdu}      
+\end{table*}
+
+\begin{figure*}[!h]
+    \includegraphics[page=41,
+        width=0.5\textwidth, 
+        height=0.28\textheight]{cdu_comparision_plots.pdf} \hfill
+    \includegraphics[page=43,
+        width=0.5\textwidth, 
+        height=0.28\textheight]{cdu_comparision_plots.pdf} \vfill
+    \vspace{-0.1in}
+    \begin{center}\includegraphics[page=42,
+        width=0.5\textwidth, 
+        height=0.28\textheight]{cdu_comparision_plots.pdf}\end{center}
+    \vspace{-0.2in}
+    \caption{Simulation statistics for the industrial 
+    crude distillation unit example. Data requirement to obtain accurate NN controllers (top left), online computation times of the NNs and 
+    MPC controller (top right), 
+    and the controller performance index obtained with the NNs, 
+    satK and MPC controllers (center bottom).}	
+    \label{fig:cdu_statistics}
+\end{figure*}
+
+\begin{figure}[!h]
     \centering
-    \includegraphics[width=0.5\textwidth, 
-                     height=0.22\textheight]{cstrs_with_flash.pdf}
-    \caption{Schematic of the CSTRs with a flash separator model}
-    \label{fig:schematic_cstrs}
+    \includegraphics[width=0.45\textwidth, 
+                     height=0.25\textheight]{cdu.pdf}
+    \caption{Schematic of the industrial crude distillation unit model}
+    \label{fig:schematic_cdu}
 \end{figure}
 
+Third, the transient closed-loop 
+performance of the trained NNs is examined
+for one particular validation 
+simulation for the expected plant behavior case. 
+Figures \ref{fig:cl_cstrs_inputs} and \ref{fig:cl_cstrs_outputs}
+show the transient actuator 
+and controlled measurements obtained with the NN-3-448 and 
+optimal MPC controllers for a simulation period of 2 hours.
+The Figure \ref{fig:cstrs_statistics} (center bottom)
+shows the transient values of the controller performance index
+obtained in this validation simulation
+with the three structured NNs, SS, satK 
+and optimal MPC controllers for the full 
+simulation period of 12 hours. The closed-loop 
+performance obtained using NNs is almost same as the optimal MPC 
+controller and the degradation in the performance 
+is quantified with the $\%$ performance loss metric.
+
+Fourth, the online computational benefits of NNs 
+over the QP based MPC is analyzed. The Figure 
+\ref{fig:cstrs_statistics} (top right)
+shows a histogram of online computation times
+of the NNs and QP solver in one validation
+simulation. The average and worst-case speedups
+obtained using NNs are summarized in the 
+Table \ref{table:cstrs}. The QP solver takes 
+about 8 to 13 seconds in this example and all the 
+NNs compute the control in just 0.1 to 4
+milliseconds, and are easily deployable in the 
+sample time of 10 seconds.
+
+The $\%$ performance loss 
+obtained using the four heuristic controllers, 
+their corresponding speedups, maximum time required to 
+train each NN, number of parameters in each NN, 
+and the memory required to store  
+the weights of the NNs is summarized in the 
+Table \ref{table:cstrs}. The 
+$85 \%$ performance loss 
+reported for the unstructured
+NN corresponds to training with $1.5 \times 10^5$  
+samples and the performance is unacceptable 
+for an industrial application. 
+The noticeable performance improvement with the
+structured NNs is because the control law 
+is exactly the same as the optimal feedback law
+at steady-states, and that simplifies
+the optimal feedback law approximation problem
+since the training process only has to improve the 
+NN control law for the transient conditions.
+
+\subsection{Large-scale crude distillation unit}
+
+The scalability of the proposed NN design 
+approach is next demonstrated on an industrial crude 
+distillation unit model \citep*{pannocchia:rawlings:wright:2007} 
+with 252 states, 32 controls, and 90 measurements. The 
+schematic of this model is shown in Figure \ref{fig:schematic_cdu}, 
+which is a typical crude unit found in petrochemical refineries.
+The plant model is linear, input and outputs are scaled 
+for the MPC regulator as in the previous example.
+Only four measurements that represent 
+the quality of the crude side products have setpoints, 
+and five disturbances are used on the crude composition, 
+fuel gas quality, and steam header pressure. 
+The sample time for the measurements is 1 min. The tuning 
+parameters and control horizon length for the 
+MPC regulator are chosen as $Q = 2C'C$, $R = 0.1I$, 
+and $N = 140$. A total $3.6 \times 10^5$ 
+samples of ($x, x_s, u_s, \kappa_N(\cdot)$)
+are generated for the NN training, parallelized over 
+149 offline simulations. The time consumed 
+for this data generation step was 
+27.8 hours.
+
+Four structured NN architectures 
+are considered for this example. Each NN
+has three hidden layers, with 
+1664 (NN-3-1664), 1792 (NN-3-1792), 
+1920 (NN-3-1920), and 2048 (NN-3-2048) 
+nodes in each hidden layer respectively. 
+For the validation simulations, one set of
+setpoint and disturbance signals for the expected 
+plant behavior case is generated
+with 24 setpoint changes and 48 disturbance changes 
+for 2880 timesteps (2 days). 
+The short horizon MPC controller is constructed with a 
+horizon length of $N = 3$. 
+The states and target steady-states 
+($x$, $x_s$) are scaled for the NN training
+as in the previous example.
+
+Figure \ref{fig:cdu_statistics} shows the 
+statistics for the simulation study performed for this 
+example.
+The data requirement to obtain 
+an accurate NN controller is shown in top left.
+The batch size 
+in Adam was chosen as 2048 samples, and all the NNs 
+are trained for 1500 epochs.
+The transient controller performance index 
+for one validation simulation
+obtained with the four structured NNs,
+satK, and MPC controllers is shown in center bottom.
+The top right plot shows the 
+histogram of online computation times 
+of the NNs and QP solver.
+Table \ref{table:cdu} gives a summary of 
+the maximum time required to train the NNs, number of parameters
+in each NN, memory footprint of the NNs, and 
+the $\%$ performance loss metric obtained by 
+the structured NNs, SS, satK, and SH 
+controllers in the validation simulations.
+
+The offline data generation and training times 
+for the NNs shows that this large-scale example
+is tractable with the proposed NN approach.
+This large example is challenging, 
+since on average the QP solver CVXOPT requires 
+35 seconds, and 
+47 seconds in the worst-case. By comparison,  
+all the NNs execute MPC in about 2 
+to 7 milliseconds.
+As observed from the plot of the transient controller 
+performance index, the performance 
+degradation by the NNs relative to 
+the optimal MPC controller is negligible.
+The sampling of the state space with 
+the setpoint and disturbance signals
+for one particular operational scenario,
+combined with the offset-free NN structure
+are the key steps for scalability in this example.
+
+\section{Conclusion} \label{sec:conclusion}
+Neural networks have been demonstrated 
+to approximate the MPC feedback law
+for treating large-scale, linear MPC applications
+that may be out of reach with QP solvers. 
+The proposed no online optimization based
+methods to date in the literature such as storing 
+the entire MPC feedback law 
+and sampling the large dimensional state space 
+for the NN training are not tractable for the problems 
+considered in this article.
+
+The key features for the scalability of the proposed approach 
+are the structure of NN and data generation for only
+typical plant operational scenarios. 
+The NN design approach was demonstrated to scale on an
+industrial crude distillation unit model with state and
+control dimensions of 252 and 32 respectively, and 
+a control-sample horizon length of 140. 
+After the offline design phase, NNs execute MPC 
+about three to five orders of magnitude faster than an 
+available QP solver 
+with less than 1$\%$ performance degradation in the closed-loop.
+The deployment decision of the NNs 
+must be based on the ability to reliably identify 
+and sample the anticipated plant operational scenarios 
+with setpoints and large magnitude disturbances
+that may change for a reasonable duration of operation.
+Parallel computing can be used for
+the offline data generation step if
+solving QPs for each sampled state starts to take 
+excessive amounts of time.
+After the training process, 
+the NNs are easily deployable on memory constrained 
+hardware. We established conditions under which the 
+NN controllers are robust to state estimation errors 
+and process disturbances,
+provides some theoretical support 
+to practitioners interested in the deployment of NNs.
+
+\section*{Acknowledgement}
+%The authors acknowledge Professor Stephen J. Wright 
+%at the University of Wisconsin, Madison
+%for helpful discussions on machine learning topics and providing 
+%a detailed feedback on this article.
+The funding for this work was provided by the industrial
+members of the Texas-Wisconsin-California Control 
+Consortium (TWCCC).
+The computational facilities purchased with funds from the National Science Foundation (CNS-1725797) and 
+administered by the Center for Scientific Computing (CSC) was used for the simulation 
+studies presented in this article. 
+The CSC is supported by the California NanoSystems Institute and the Materials 
+Research Science and Engineering Center 
+(MRSEC; NSF DMR 1720256) at UC Santa Barbara.
+
+%% New version of the num-names style
+\bibliographystyle{elsarticle-num-names}
+\bibliography{abbreviations,articles,books,unpub,proceedings}
+
+\section*{Appendix}
+\renewcommand{\thesubsection}{\Alph{subsection}}
+
+\subsection{Proof of Theorem \ref{thm:nnrobustness}} \label{app:theorem1}
+
+We use the following
+definitions of
+robust positive invariance of a set
+with respect to disturbances, 
+input-to-state stability (ISS), ISS-Lyapunov function,
+and the available result 
+on the ISS property of a system if it admits 
+an ISS-Lyapunov function
+(\cite*{jiang:wang:2001, 
+rawlings:mayne:diehl:2017}, Appendix B).
+
+\begin{definition} \label{def:robust_pos_invariance}
+(Robust positive invariance). A closed set $X$ is 
+robustly positive invariant for the system $x^+ = f(x, w)$, 
+$w \in \bbW$ if $x \in X$ 
+implies $f(x, w) \in X$ for all $w \in \bbW$.
+\end{definition}
+
+\begin{definition} \label{def:iss}
+(Input-to-state stability (ISS)). $\bbW$ is a compact 
+set containing the origin and that $X$ is a closed robustly
+positive invariant set for the 
+system $x^+ = f(x, w)$, $w \in \bbW$. This
+system is ISS in $X$ if there exist functions 
+$\beta(\cdot) \in \mathcal{K}\mathcal{L}$ and 
+$\sigma(\cdot) \in \mathcal{K}$, such that for all
+$x \in X$ and $w(i) \in \bbW$, $i \in \bbI_{0:k-1}$, 
+$\vert \psi(k; x, \mathbf{w}_k) \vert \leq \beta(\vert x\vert, k) 
++ \sigma(\vert \vert \mathbf{w}_k\vert \vert)$, in which 
+$\psi(k; x, \mathbf{w}_k)$ is the solution of the system 
+at time $k$, starting from an initial state $x$, and with the
+disturbance sequence $\mathbf{w}_k$ affecting the system.
+\end{definition}
+
+\begin{definition} \label{def:iss_lyapunov_func}
+(ISS-Lyapunov function). A function $V : X \rightarrow \bbR_{\geq 0}$
+is an ISS-Lyapunov function in $X$ for the system $x^+ = f(x, w)$, $w \in \bbW$
+if there exist functions $\alpha_1(\cdot), \alpha_2(\cdot), \alpha_3(\cdot) 
+\in \mathcal{K}_{\infty}$ and $\sigma(\cdot) \in \mathcal{K}$
+such that for all $x \in X$ and $w \in \bbW$
+\begin{align*}
+    \alpha_1(\vert x \vert) \leq & V(x) \leq \alpha_2(\vert x \vert) \\
+    V(f(x, w)) &- V(x) \leq -\alpha_3(\vert x \vert) + \sigma(\vert w \vert)
+\end{align*}
+\end{definition}
+
+\begin{prop} \label{prop:lyapunov_implies_iss}
+(ISS-Lyapunov function implies ISS). $\bbW$ is a compact
+set containing the origin and that $X$ is a closed robustly
+positive invariant set for $x^+ = f(x, w)$, $w \in \bbW$. If 
+$f(\cdot)$ is continuous and there exists a continuous 
+ISS-Lyapunov function in $X$ for the system $x^+ = f(x, w)$, $w \in \bbW$, 
+then the system is ISS in $X$.
+\end{prop}
+
+Additionally, we require the following two 
+useful propositions from 
+\cite*{allan:bates:risbeck:rawlings:2017} and 
+\cite*{rawlings:ji:2012},
+to bound values of continuous functions and an
+inequality for $\mathcal{K}$ functions respectively.
+
+\begin{prop} \label{prop:continuous_funcs}
+    Let $C \subseteq D \subseteq \bbR^n$, $C$ compact, 
+    $D$ closed, and $f : D \rightarrow \bbR^n$ continuous.  
+    Then there exists a $\sigma(\cdot) \in \mathcal{K}_{\infty}$,
+    such that for all $x \in C$ and $y \in D$, we have that 
+    $\vert f(x) - f(y) \vert \leq \sigma(\vert x-y \vert)$.
+\end{prop}
+
+\begin{prop} \label{prop:Kfunction_inequality}
+    Let $\sigma(\cdot) \in \mathcal{K}$, the following holds 
+    for all $a_i \in \bbR_{\geq 0}$, $i \in \bbI_{1:n}$ 
+    \begin{align*}
+        \sigma(a_1 + a_2 + \cdot \cdot + a_n) \leq \sigma(na_1) + 
+        \sigma(na_2) + \cdot \cdot + \sigma(na_n)
+    \end{align*}    
+\end{prop}
+
+\textbf{Proof of Theorem \ref{thm:nnrobustness}:}
+We proceed in two steps. First, 
+we show that there exist constants $\delta_1, \delta_2, \delta_3 > 0$
+such that the set $S$ is robustly positive invariant. Then, we 
+show that $V_N^0(\hat{x})$ is an ISS Lyapunov function for 
+the perturbed system \eqref{eq:perturbed_sys} on this set $S$. Denote 
+$\tilde{x}^+ = A\hat{x} + B\kappa_N(\hat{x})$ as the nominal 
+state evolution using the optimal MPC controller, 
+and $d(k) = [ e_{NN}(\hat{x}(k))'B', w(k)', e(k)', e(k+1)']'$
+as the combination of all the disturbances at a given time $k$.
+
+To show robust positive invariance of $S$,  
+we establish that if $V_N^0(\hat{x}) \leq \rho$, 
+then $V_N^0(\hat{x}^+) \leq \rho$.
+Since the optimal 
+cost function ($V_N^0(\hat{x})$) is continuous,
+using $\bbR^n$ as the closed set ($\hat{x}^+ \in \bbR^n$) 
+and $S$ as the compact set ($\tilde{x} \in S$),
+from proposition \ref{prop:continuous_funcs} we have
+for some $\sigma_1(\cdot) \in \mathcal{K}_{\infty}$
+\begin{align}
+    \vert V_N^0(\hat{x}^+) - V_N^0(\tilde{x}^+) \vert &\leq 
+    \sigma_1(\vert \hat{x}^+ - \tilde{x}^+ \vert)  \nonumber  \\
+    &\leq 
+   \sigma_1(\vert B e_{NN}(\hat{x}) \vert + \vert w \vert 
+   \nonumber \\
+   & + \vert A\vert\vert e \vert +  \vert e^+ \vert) \nonumber \\
+     &\leq 
+   \sigma_1(\vert d \vert + \vert d \vert + \vert A \vert\vert d \vert + \vert d \vert) := \sigma_2(\vert d \vert)
+   \label{eq:optimal_cost_bound}
+\end{align}
+in which $\sigma_2(s) := \sigma_1(\vert A\vert s +3s)$, and the last inequality 
+follows because $\vert a \vert \leq \vert [a', b']' \vert$, in which $a$ and $b$
+are both vectors, and $\sigma_2(\cdot) \in \mathcal{K}_{\infty}$.
+We partition $S$ in outer and inner parts based on 
+the value of the optimal cost $V_N^0(\hat{x})$, and bound the 
+combination of disturbances $d$ in each part 
+such that $V_N^0(\hat{x}^+) \leq \rho$. \\
+Case 1: $\rho/2 \leq V_N^0(\hat{x}) \leq \rho $. Using the 
+upper bound on the optimal cost, we have 
+$\rho/(2c_2) \leq \vert \hat{x} \vert^2$ for all $\hat{x}$ 
+in this part of $S$. To analyze the worst-case disturbance, 
+we have from the equation \eqref{eq:optimal_cost_bound} that 
+$V_N^0(\hat{x}^+) \leq V_N^0(\tilde{x}^+) + \sigma_2(\vert d \vert) $.
+From nominal MPC cost decrease, we obtain  
+$V_N^0(\hat{x}^+) \leq V_N^0(\hat{x}) - c_1\vert \hat{x} \vert^2 + \sigma_2(\vert d \vert)$. Thus, if $\sigma_2(\vert d \vert) \leq \rho c_1/(2c_2)$, 
+at all times in this outer part of $S$, we have 
+$V_N^0(\hat{x}^+) \leq \rho$. \\
+Case 2: $V_N^0(\hat{x}) \leq \rho/2 $. From 
+equation \eqref{eq:optimal_cost_bound} and nominal MPC 
+cost decrease, we have for this part of $S$ that 
+$V_N^0(\hat{x}^+) \leq \rho/2 + \sigma_2(\vert d \vert)$.
+Thus, if $\sigma_2(\vert d \vert) \leq \rho/2$, 
+at all times in this inner part of $S$, we have 
+$V_N^0(\hat{x}^+) \leq \rho$.
+
+Therefore, if 
+$\vert d \vert \leq \textnormal{min} \{ \sigma_2^{-1}(\rho c_1/(2c_2)), 
+\sigma_2^{-1}(\rho/2)\} := \delta_{\textnormal{max}}$ 
+at all times, then the set $S$ is 
+robustly positive invariant. Since $c_1 \leq c_2$, 
+$\delta_{\textnormal{max}} = \sigma_2^{-1}(\rho c_1/(2c_2))$.
+The constants $\delta_1$ and $\delta_2$ are
+$\delta_{\textnormal{max}}/4$ each, 
+and $\delta_3$ is $\delta_{\textnormal{max}}/(4\vert B \vert)$.
+The optimal MPC cost function satisfies
+\begin{align*}
+    V_N^0(\hat{x}^+) - V_N^0(\hat{x}) &\leq 
+    -c_1\vert \hat{x} \vert^2 + \sigma_2(\vert d \vert)
+\end{align*}
+in the robustly positive invariant set $S$ and
+the disturbance set $\vert d \vert \leq \delta_{\textnormal{max}}$.
+Since the optimal cost function also satisfies the upper and lower bounds
+$c_1\vert x \vert^2 \leq V_N^0(x) \leq c_2\vert x \vert^2$,
+from the Definition \ref{def:iss_lyapunov_func},
+it satisfies the requirements of an ISS-Lyapunov function.
+Hence, using the Proposition \ref{prop:lyapunov_implies_iss}, 
+the perturbed linear system \eqref{eq:perturbed_sys} is
+ISS (Definition \ref{def:iss}), 
+and there exist functions 
+$\beta(\cdot) \in \mathcal{K}\mathcal{L}$ and 
+$\sigma(\cdot) \in \mathcal{K}$, such that 
+$\vert \phi_d(k; \hat{x}) \vert \leq \beta(\vert \hat{x} \vert, k) 
++ \sigma(\vert\vert \mathbf{d}_k\vert\vert)$. Using the Proposition
+\ref{prop:Kfunction_inequality} and the definition of 
+$d(k)$, we have 
+\begin{align*}
+    \vert \phi_d(k; \hat{x}) \vert & \leq \beta(\vert \hat{x} \vert, k)
+    + \sigma(\vert B\vert\bar{e}_{NN} + \vert \vert \mathbf{w}_k \vert \vert
+    + 2\vert \vert \mathbf{e}_{k+1} \vert \vert) \\
+     & \leq \beta(\vert \hat{x} \vert, k) \\
+    & +\sigma(3\vert B\vert\bar{e}_{NN}) + 
+    \sigma(3\vert \vert \mathbf{w}_k \vert \vert)
+    + \sigma(6\vert \vert \mathbf{e}_{k+1} \vert\vert)
+\end{align*}
+Therefore, the bound in the Theorem \ref{thm:nnrobustness} is established with 
+$\alpha_e(s) := \sigma(6s)$, 
+$\alpha_w(s) := \sigma(3s)$,
+$\alpha_n(s) := \sigma(3\vert B\vert s)$, and 
+$\alpha_e(\cdot), \alpha_w(\cdot), \alpha_n(\cdot) \in \mathcal{K}$.
+
+\subsection{Parameters used in the CSTRs example} \label{app:cstrs_pars}
+
 \renewcommand{\arraystretch}{1.1}
-\begin{table}[h]
+\begin{table}[!h]
     \centering
@@
         \hline
-        $F_0$ & (1.5, 2.5) & \unitfrac{kg}{m$^3$} & 
+        $F_0$ & (1.5, 2.5) & \unitfrac{kg}{sec} & 
         $Q_r$ & (-500, 500) & \unit{kW} \\ 
-        $F_1$ & (0.5, 1.5) & \unitfrac{kg}{m$^3$} & 
+        $F_1$ & (0.5, 1.5) & \unitfrac{kg}{sec} & 
         $Q_m$ & (-500, 500) & \unit{kW} \\ 
-        $D$ & (29.5, 30.5) & \unitfrac{kg}{m$^3$} & 
+        $D$ & (29.5, 30.5) & \unitfrac{kg}{sec} & 
         $Q_b$ & (-500, 500) & \unit{kW} \\ 
@@
         \hline
-        $H_r$ & 163.8 & \unit{m} & $F_0$ & 2 & \unitfrac{kg}{m$^3$} \\ 
-        $x_{Ar}$ & 0.40 &  & $F_1$ & 0 & \unitfrac{kg}{m$^3$} \\ 
-        $x_{Br}$ & 0.54 &  & $D$ & 1 & \unitfrac{kg}{m$^3$} \\ 
+        $H_r$ & 163.8 & \unit{m} & $F_0$ & 2 & \unitfrac{kg}{sec} \\ 
+        $x_{Ar}$ & 0.40 &  & $F_1$ & 1 & \unitfrac{kg}{sec} \\ 
+        $x_{Br}$ & 0.54 &  & $D$ & 30 & \unitfrac{kg}{sec} \\ 
         $T_r$ & 313.1 & \unit{K} & $Q_r$ & 0
@@
 
-A linear discrete time model with the chosen sample time
-is obtained at the steady state shown in the Table 
-\ref{table:cstrs_pars}.
-This model, inputs and outputs are scaled 
-for the MPC controller such that
-$\overline{u} - \underline{u} = \mathbf{2}$ and
-$\overline{y} - \underline{y} = \mathbf{2}$.
-The tuning parameters and 
-control horizon length for the regulator are chosen as
-$Q = 10^3 C'C$, $R = 0.1 I$, $S = 0.1 I$, 
-and $N = 450$.
-A total $1.5 \times 10^5$ samples of 
-($x, u_{-1}, x_s, u_s, \kappa_N(\cdot)$) 
-is generated for NN training, parallelized in 100 
-separate offline simulations. The time consumed 
-for this data generation step was 4.9 hours.
-
-Four structured NN architectures 
-are considered. Each NN
-has three hidden layers with 
-448 (NN-3-448), 480 (NN-3-480), 
-512 (NN-3-512), and 544 (NN-3-544) 
-nodes in each hidden 
-layer respectively. For the validation simulations, 
-setpoint and disturbance signals 
-with 24 setpoint changes and 48 disturbance changes 
-is generated for 4320 timesteps (12 hours). 
-The short horizon MPC controller is constructed with a 
-horizon length of $N = 10$, and the architecture 
-of the unstructured NN considered 
-is three hidden layers with 224 nodes in each hidden layer. 
-An additional scaling of the 
-states and target steady states ($x$ , $x_s$) is performed for the 
-NN training as $x := 2x/(x_{\textnormal{max}} - x_{\textnormal{min}})$ and 
-$x_s := 2x_s/(x_{\textnormal{max}} - x_{\textnormal{min}})$,
-in which $x_{\textnormal{max}}$ and $x_{\textnormal{min}}$
-are the maximum and minimum values of the state 
-observed in the generated training data.
-This scaling is also performed in real-time 
-when the NN is used to compute the actuator move.
-
-First, the amount of data required to obtain an accurate 
-NN controller is studied. To this aim, the four chosen NN 
-architectures are trained with incremental increases of 
-$10^4$ training samples starting from $4 \times 10^4$
-to $1.5 \times 10^5$ samples. The trained NNs 
-are then used in validation simulations
-with the generated validation setpoint and disturbance
-signals. The closed-loop performance is compared with the optimal MPC 
-controller and the $\%$ performance loss obtained
-is plotted in Figure \ref{fig:cstrs_statistics} (top left)
-as a function of the number of training samples.
-All the trained NNs provide less than $1 \%$ loss in 
-this performance metric after training with 
-about $10^5$ samples. The best $\%$ performance
-loss obtained by the NNs is summarized in
-Table \ref{table:cstrs}.
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=0.45\textwidth, 
-                     height=0.25\textheight]{cdu.pdf}
-    \caption{Schematic of the industrial crude distillation unit model}
-    \label{fig:schematic_cdu}
-\end{figure}
-
-\begin{table*}[t]
-    \caption{Summary of the simulation study for the 
-    industrial crude distillation unit example.}
-    %\centering
-\begin{tabular}{ |c|c|c|c|c|c|c|c| }
-          \hline
-          Controller & \thead{Structured network \\ architecture} & 
-          \thead{Number of \\ Parameters} & 
-          \thead{Memory \\ footprint (mB)} & \thead{Training \\ time (min)} &
-          \thead{\% Performance\\ loss} & \thead{Average \\ speedup} & \thead{Worst case \\ speedup} \\
-          \hline
-      SS &  &  & &  & 120.59 \% &  & \\ 
-  satK &  &  &   &  & 13.07 \% & $4.05 \times 10^5$ & $1.06 \times 10^5$ \\ 
-  SH &  &  &  &  & 1.56 \% & $7.18 \times 10^3$  & $2.57 \times 10^3$ \\ 
-  NN-3-1664 & [1072, 1664, 1664, 1664, 32] & $1.85 \times 10^6$ & 14.18 & 61.76 & 0.61 \% & $1.62 \times 10^4$ & $5.45 \times 10^3$  \\ 
-  NN-3-1792 & [1072, 1792, 1792, 1792, 32]  & $2.11 \times 10^6$ & 16.15  & 56.37 & 0.71 \% & $1.42 \times 10^4$ & $5.30 \times 10^3$ \\ 
-  NN-3-1920 & [1072, 1920, 1920, 1920, 32]  & $2.39 \times 10^6$ & 18.24  & 56.25 & 0.34 \% & $1.28 \times 10^4$ & $4.22 \times 10^3$ \\ 
-  NN-3-2048 & [1072, 2048, 2048, 2048, 32]  & $2.68 \times 10^6$ & 20.46  & 66.01 & 0.47 \% & $1.13 \times 10^4$ & $4.42 \times 10^3$\\ 
-\hline
-\end{tabular}
-\label{table:cdu}      
-\end{table*}
-
-\begin{figure*}[!h]
-    \includegraphics[page=41,
-        width=0.5\textwidth, 
-        height=0.3\textheight]{cdu_comparision_plots.pdf} \hfill
-    \includegraphics[page=43,
-        width=0.5\textwidth, 
-        height=0.3\textheight]{cdu_comparision_plots.pdf} \vfill
-    \vspace{-0.1in}
-    \begin{center}\includegraphics[page=42,
-        width=0.5\textwidth, 
-        height=0.3\textheight]{cdu_comparision_plots.pdf}\end{center}
-    \vspace{-0.2in}
-    \caption{Simulation statistics for the industrial 
-    crude distillation unit example. Data requirements to obtain accurate NN controllers (top left), online computation times of the NNs and 
-    MPC controller (top right), 
-    and the controller performance index obtained with the NNs, 
-    satK and MPC controllers (center bottom).}
-	\label{fig:cdu_statistics}
-\end{figure*}
-
-Second, the transient closed-loop 
-performance of the trained NNs is examined
-for one particular simulation. The Figures 
-\ref{fig:cl_cstrs_inputs} and \ref{fig:cl_cstrs_outputs}
-show the transient actuator 
-and controlled outputs obtained with the NN-3-448 and 
-optimal MPC controllers for a simulation period of 2 hours.
-The Figure \ref{fig:cstrs_statistics} (center bottom)
-shows the transient values of the controller performance index
-obtained in this validation simulation
-with the four structured NNs, SS, satK 
-and optimal MPC controllers for the full 
-simulation period of 12 hours. The closed-loop 
-performance obtained using NNs is almost same as the optimal MPC 
-controller and the degradation in the performance 
-is quantified with the $\%$ performance loss metric
-shown in the Table \ref{table:cstrs}.
-
-Third, the online computational benefits of NNs 
-over the QP based MPC is analyzed. The Figure 
-\ref{fig:cstrs_statistics} (top right)
-shows a histogram of online computation times
-of the NNs and the QP solver 
-CVXOPT. The average and worst-case speedups
-obtained using the NNs are summarized in the 
-Table \ref{table:cstrs}. The QP solver takes 
-about 9 to 14 seconds in this example and all the 
-NNs compute the control in just 0.4 to 3 milliseconds, 
-and are conveniently deployable in the 
-sample time of 10 seconds.
-
-The $\%$ performance loss 
-obtained using the four fast controllers other 
-than the structured NNs, 
-their corresponding 
-computational speedups, the maximum time required to 
-train each NN, the number of parameters in each NN, 
-and the memory required to store  
-the weights of each NN is summarized in the 
-Table \ref{table:cstrs}. The $\%$ performance loss 
-reported for the unstructured
-NN is after training with $1.5 \times 10^5$  
-samples and the performance is unacceptable 
-for an industrial application. 
-This noticeable performance improvement with the
-structured NNs is because the control law 
-is exactly the same as the optimal feedback law
-at the steady states, and that simplifies
-the optimal feedback law approximation problem
-since the training process only has to improve the 
-NN control law for the transient states.
-
-\subsection{Large-scale crude distillation unit}
-
-The scalability of the proposed NN design 
-approach is demonstrated on an industrial crude 
-distillation unit model \citep*{pannocchia:rawlings:wright:2007} 
-with 252 states, 32 controls, and 90 measurements. The 
-schematic of this model is shown in the Figure \ref{fig:schematic_cdu}, 
-that is a typical crude unit found in petrochemical refineries.
-The plant model is linear, input and outputs are scaled 
-for the MPC regulator similar to the previous example.
-Four measurements which represent 
-the quality of the crude side products have setpoints, 
-and five disturbances are used on the crude composition, 
-fuel gas quality, and steam header pressure. 
-The sample time for the measurements is 1 min. The tuning 
-parameters and control horizon length for the 
-MPC regulator are chosen as $Q = 2C'C$, $R = 0.1I$, 
-and $N = 145$. A total $3.576 \times 10^5$ 
-samples of ($x, x_s, u_s, \kappa_N(\cdot)$)
-are generated for the NN training, parallelized over 
-149 offline simulations. The time consumed 
-for this data generation step was 27.8 hours.
-
-Four structured NN architectures 
-are considered for this example. Each NN
-has three hidden layers, with 
-1664 (NN-3-1664), 1792 (NN-3-1792), 
-1920 (NN-3-1920), and 2048 (NN-3-2048) 
-nodes in each hidden layer respectively. 
-For the validation simulations, 
-setpoint and disturbance signals 
-with 24 setpoint changes and 48 disturbance changes 
-is generated for 2880 timesteps (2 days). 
-The short horizon MPC controller is constructed with a 
-horizon length of $N = 3$. 
-The states and target steady states 
-($x$, $x_s$) are scaled for the NN training
-similar to the previous example.
-
-The Figure \ref{fig:cdu_statistics} shows the 
-statistics obtained in the simulation study performed for this 
-example. The data requirements to obtain 
-an accurate NN controller is shown in top left.
-The transient controller performance index 
-for one validation simulation
-obtained with the four structured NNs,
-satK, and MPC controllers is shown in center bottom.
-The top right plot shows the 
-histogram of online computation times 
-of the NNs and the QP solver CVXOPT.
-The Table \ref{table:cdu} gives a summary of 
-the maximum time required to train the NNs, 
-the number of parameters
-in each NN, the memory footprint of the NNs, and 
-the $\%$ performance loss obtained by 
-the structured NNs, SS, satK, and SH 
-controllers in the validation simulations.
-
-The offline data generation and training times 
-to build the NNs show that this large dimensional example
-is tractable with the proposed NN approach.
-This large example is challenging, 
-since on average the QP solver CVXOPT takes 37 seconds
-and 57 seconds in the worst-case. In comparison,  
-all the NNs execute MPC in about 2 to 6 milliseconds.
-As observed from the plot of the transient controller 
-performance index, the performance 
-degradation by the NNs relative to 
-the optimal MPC controller is negligible.
-The sampling of the state-space with 
-the setpoint and disturbance signals
-for one particular operational scenario,
-combined with the offset-free NN structure
-are key steps for scalability in this example.
-
-\section{Conclusion} \label{sec:conclusion}
-Neural networks have been demonstrated 
-to approximate the MPC feedback law
-for treating large-scale, linear MPC applications
-that may be challeging with QP solvers. 
-The proposed no online optimization-based
-methods to-date in the literature such as storing 
-the entire MPC feedback law 
-and sampling the large dimensional state-space 
-for the NN training are not tractable for the size of problems 
-considered in this article.
-
-The key features for the scalability of the proposed approach 
-are the structure of NN and data generation for only the
-typical plant operational scenarios. 
-The NN design approach was demonstrated to scale on an
-industrial crude distillation unit model with state and
-control dimensions of 252 and 32 respectively, and 
-a control-sample horizon length of 145 in the QP. 
-After the offline design phase, NNs execute MPC 
-about three to five orders of magnitude faster than an 
-available QP solver 
-with less than 1$\%$ performance degradation in the closed-loop. 
-Parallel computing can be used for the data generation step
-if solving QPs for each sampled state starts to take long 
-amounts of time.
-After the training process, 
-the NNs are easily deployable on memory constrained hardware.
-We established conditions under which the 
-NN controllers are robust to state estimation errors 
-and process disturbances,
-that provides some theoretical support 
-to practitioners interested in the deployment of NNs.
-
-As larger and wide range of
-control applications are considered by practitioners, 
-the presented NN controller design approach 
-provides a new method to address MPC applications.
-
-\section*{Acknowledgement}
-The authors would like to acknowledge the industrial
-members of the Texas-Wisconsin-California Control (TWCCC)
-consortium for funding support.
-The computational facilities purchased with funds from the National Science Foundation (CNS-1725797) 
-and administered by the Center for Scientific Computing (CSC) was used for the simulation 
-studies presented in this article. 
-The CSC is supported by the California NanoSystems 
-Institute and the Materials Research Science and Engineering Center 
-(MRSEC; NSF DMR 1720256) at UC Santa Barbara.
-
-%% New version of the num-names style
-\bibliographystyle{elsarticle-num-names}
-\bibliography{articles,books,unpub,proceedings}
 \end{document}

### 2020-10-21 cdu_mpc.py

@@ -1,4 +1,6 @@
 # [depends] cdu_parameters.pickle
+# [depends] %LIB%/python_utils.py
+# [depends] %LIB%/controller_evaluation.py
 # [makes] pickle
 """
 Script to run an on-line simulation using the double integrator example
@@ -8,7 +10,7 @@ takes much time, both plotting and the simulation tasks are in
 the same script.
 """
 import sys
-sys.path.append('lib/')
+sys.path.append('../lib/')
 from python_utils import PickleTool
 from controller_evaluation import _simulate_scenarios
 

### 2020-10-21 cdu_mpc_plot.py

@@ -1,184 +1,0 @@
-# [depends] cdu_parameters.pickle cdu_mpc.pickle
-"""
-Script to run an on-line simulation using the double integrator example
-using the optimal MPC controller.
-Since for the double integrator example, on-line simulation does not
-takes much time, both plotting and the simulation tasks are in
-the same script.
-"""
-import sys
-sys.path.append('lib/')
-import numpy as np
-import itertools
-from cdu_labels import (ylabels, ulabels, zlabels, pdlabels)
-import matplotlib.pyplot as plt
-from python_utils import (PickleTool, figure_size_a4)
-from matplotlib.backends.backend_pdf import PdfPages
-from cdu_comparision_plots import _get_cdu_data_for_plotting
-
-def _cdu_optimal_plot(plant, controller, parameters, 
-                        setpoints, plot_range):
-    """Data to plot.
-    z: 4 outputs with setpoints. y:90 outputs. u:32 inputs.
-    """
-    # the x coordinate of the ylabels.
-    ylabel_xcoordinate = -0.25
-    # Get the arrays.
-    (t, z, y, u, pest, p, 
-      ulb, uub, zsp, ell) = _get_cdu_data_for_plotting(plant,  
-                                                       controller, setpoints,
-                                                       parameters, plot_range)
-    # Make the plots.
-    figures = plot_inputs(t, u, ulabels, ylabel_xcoordinate, ulb, uub)
-    figures += plot_outputs(t, y, ylabels, ylabel_xcoordinate)
-    figures += plot_controlled_outputs(t, z, zsp, zlabels, ylabel_xcoordinate)
-    figures += plot_disturbances(t, p, pest, 
-                                 pdlabels, ylabel_xcoordinate)
-    figures += plot_average_stage_costs(t, ell, 
-                            ylabel_xcoordinate)
-    # Return the list of figures.
-    return figures
-
-def plot_inputs(t, u, ulabels, ylabel_xcoordinate, 
-                ulb, uub):
-    """Return 4 figure objects which contain the plots of the inputs."""
-    num_pages = 2
-    num_rows = 8
-    num_cols = 2
-    input_index = 0
-    figs_and_axes = [plt.subplots(nrows=num_rows, ncols=num_cols,
-                                 sharex='col', figsize=figure_size_a4, 
-                                 gridspec_kw = dict(wspace=0.5))
-                            for _ in range(num_pages)]
-    for (page, row, column) in itertools.product(range(num_pages),
[…]

### 2020-10-21 cdu_neural_network.py

@@ -1,11 +1,12 @@
 # [depends] cdu_parameters.pickle cdu_train.pickle
+# [depends] %LIB%/controller_evaluation.py
 # [makes] pickle
 """
 Script to run an on-line simulation for the double integrator example
 using the approximate NN controller.
 """
 import sys
-sys.path.append('lib/')
+sys.path.append('../lib/')
 from controller_evaluation import _simulate_neural_networks
 
 # Load data and do an online simulation using the linear MPC controller.

### 2020-10-21 cdu_neural_network_unstd.py

@@ -1,38 +1,0 @@
-# [depends] cdu_parameters.pickle cdu_train_unstd.pickle
-# [makes] pickle
-"""
-Script to run an on-line simulation for the double integrator example
-using the approximate NN controller.
-"""
-import sys
-sys.path.append('lib/')
-from python_utils import (PickleTool, figure_size_a4)
-from matplotlib.backends.backend_pdf import PdfPages
-from cdu_comparision_plots import _cdu_cl_comparision_plots
-from controller_evaluation import _simulate_neural_network_unstd
-
-# Load data and do an online simulation using the linear MPC controller.
-(plants, controllers) = _simulate_neural_network_unstd(plant_name='cdu', 
-                                    Nsim=2880, nnwithuprev=False)
-
-# Load data and do an online simulation using the linear MPC controller.
-cdu_parameters = PickleTool.load(filename='cdu_parameters.pickle', 
-                                 type='read')
-scenarios = cdu_parameters['online_test_scenarios']
-plant_parameters = cdu_parameters['cdu_plant_parameters']
-
-mpc_parameters = PickleTool.load(filename='cdu_mpc.pickle', 
-                                        type='read')
-(mpc_plants, mpc_controllers) = (mpc_parameters['plants'], 
-                                 mpc_parameters['controllers'])
-figures = _cdu_cl_comparision_plots(scenarios, 
-                            mpc_plants, mpc_controllers,
-                            plants, controllers, 
-                            'NN-UNSTD',
-                            plant_parameters,
-                            (0, 2880))
-
-# Save the figures for the two simulations.
-with PdfPages('cdu_neural_network_unstd.pdf', 'w') as pdf_file:
-    for fig in figures:
-        pdf_file.savefig(fig)

### 2020-10-21 cdu_offline_data.py

@@ -1,10 +1,11 @@
 # [depends] cdu_parameters.pickle
+# [depends] %LIB%/python_utils.py
 # [makes] pickle
 """
 Script to generate offline data for training the neural net.
 """
 import sys
-sys.path.append('lib/')
+sys.path.append('../lib/')
 from python_utils import PickleTool
 
 # Load data and do an online simulation using the linear MPC controller.

### 2020-10-21 cdu_offline_plot.py

@@ -1,166 +1,0 @@
-# [depends] cdu_parameters.pickle cdu_offline_data.pickle
-"""
-Script to run an on-line simulation using the double integrator example
-using the optimal MPC controller.
-Since for the double integrator example, on-line simulation does not
-takes much time, both plotting and the simulation tasks are in
-the same script.
-"""
-import sys
-sys.path.append('lib/')
-import numpy as np
-import itertools
-from cdu_labels import ulabels, ylabels, zlabels, pdlabels
-import matplotlib.pyplot as plt
-from python_utils import (PickleTool, figure_size_a4)
-from matplotlib.backends.backend_pdf import PdfPages
-
-def _get_arrays_for_plotting(offline_data, parameters, num_samples):
-    """ Get the appropriate arrays for plotting."""
-
-    # Extract some parameters.
-    setpoints = parameters['offline_simulator'].setpoints
-    lb = parameters['cdu_plotting_parameters']['lb'] 
-    ub = parameters['cdu_plotting_parameters']['ub']
-    us = parameters['cdu_plotting_parameters']['us'] 
-    ys = parameters['cdu_plotting_parameters']['ys']
-    disturbance_indices = parameters['cdu_plotting_parameters']['disturbance_indices']
-
-    #  Get the H matrix.
-    (Ny, _) = parameters['plant'].C.shape
-    Nc = 4
-    (Nx, Nu) = parameters['plant'].B.shape
-    H = np.concatenate((np.zeros((Nc, Ny-Nc)), np.eye(Nc)), axis=1)
-
-    # Scaling for the inputs, outputs.
-    yscale = parameters['cdu_plotting_parameters']['yscale'].squeeze()
-    uscale = parameters['cdu_plotting_parameters']['uscale'].squeeze()
-    pscale = np.take(uscale, disturbance_indices).squeeze()
-    zscale = H @ yscale
-    
-    # Control inputs.
-    u = np.asarray(offline_data['useq'][0:num_samples, ...]).squeeze(axis=-1)[:, 0:Nu]*uscale + us.squeeze()
-
-    # Disturbances.
-    p = np.asarray(offline_data['d'][0:num_samples, ...])*pscale
-
-    # All the outputs.
-    y = np.asarray(offline_data['y'][0:num_samples, ...]).squeeze(axis=-1)*yscale + ys.squeeze()
-
-    # The time index.
-    t = np.arange(num_samples)
-
-    # Outputs without offset.
-    zs = H @ ys
[…]

### 2020-10-21 cdu_parameters.py

@@ -1,3 +1,6 @@
+# [depends] %LIB%/python_utils.py
+# [depends] %LIB%/linearMPC.py
+# [depends] %LIB%/controller_evaluation.py
 # [makes] pickle
 """ 
 Generate the parameters for the offline data generation and 
@@ -6,7 +9,7 @@ the online simulation for the crude distillation unit model.
 #import custompath
 #custompath.add()
 import sys
-sys.path.append('lib/')
+sys.path.append('../lib/')
 import matio
 import scipy.linalg
 import numpy as np
@@ -98,7 +101,7 @@ def _get_cdu_mpc_controller(plant, lb, ub):
     Q = 2*(plant.C.T @ plant.C)
     R = 0.1*np.eye(Nu)
     S = 0*np.eye(Nu)
-    N = 10
+    N = 140
     
     # The input constraints.
     ulb = lb['u']
@@ -131,13 +134,13 @@ def _get_cdu_offline_simulator(controller, dist_indices, dist_scaling,
     disturbance_ub = disturbance_ub*dist_scaling*conservative_factor
 
     # Generate the setpoints.
-    setpoints = sample_prbs_like(num_change=750, num_steps=Nsim, 
+    setpoints = sample_prbs_like(num_change=894, num_steps=Nsim, 
                                  lb=setpoint_lb, ub=setpoint_ub,
                                  mean_change=400, sigma_change=1, seed=seed)
     setpoints = np.concatenate((np.zeros((Nsim, Ny-Nz)), setpoints), axis=1)
 
     # Generate the disturbances. 
-    disturbances = sample_prbs_like(num_change=1500, num_steps=Nsim, 
+    disturbances = sample_prbs_like(num_change=1788, num_steps=Nsim, 
                                 lb=disturbance_lb, ub=disturbance_ub,
                                 mean_change=200, sigma_change=1, seed=seed+1)
 
@@ -207,7 +210,7 @@ if __name__ == "__main__":
     cdu_offline_simulator = _get_cdu_offline_simulator(cdu_mpc_controller,
                                                        dist_indices,
                                                        dist_scaling,
-                                                       lb, ub, Nsim=300000, 
+                                                       lb, ub, Nsim=357600, 
                                             num_data_gen_task=int(sys.argv[1]),
                                             num_process_per_task=1)
     cdu_scenarios = _get_cdu_online_scenarios(cdu_mpc_controller, 
@@ -219,12 +222,14 @@ if __name__ == "__main__":
                                 dist_indices=dist_indices, 
[…]

### 2020-10-21 cdu_satdlqr_plot.py

@@ -1,235 +1,0 @@
-# [depends] cdu_parameters.pickle cdu_optimal.pickle
-"""
-Script to run an on-line simulation using the double integrator example
-using the optimal MPC controller.
-Since for the double integrator example, on-line simulation does not
-takes much time, both plotting and the simulation tasks are in
-the same script.
-"""
-# import custompath
-# custompath.add()
-import sys
-sys.path.append('lib/')
-import numpy as np
-import plottools
-import itertools
-from cdu_labels import ulabels, ylabels, zlabels, pdlabels
-import matplotlib.pyplot as plt
-from python_utils import (PickleTool, figure_size_a4)
-from matplotlib.backends.backend_pdf import PdfPages
-
-def _get_arrays_for_plotting(optimal, satdlqr, 
-                             cdu_plotting_parameters, 
-                             setpoints, plot_range):
-    """ Get the appropriate arrays for plotting."""
-
-    # Get some plotting cosmetics.
-    yscale = cdu_plotting_parameters['yscale']
-    uscale = cdu_plotting_parameters['uscale']
-    lb = cdu_plotting_parameters['lb'] 
-    ub = cdu_plotting_parameters['ub']
-    us = cdu_plotting_parameters['us'] 
-    ys = cdu_plotting_parameters['ys']
-    disturbance_indices = cdu_plotting_parameters['disturbance_indices']
-
-    (start, end) = plot_range
-    #  Get the H matrix.
-    (Ny, _) = optimal.C.shape
-    Nc = 4
-    H = np.concatenate((np.zeros((Nc, Ny-Nc)), np.eye(Nc)), axis=1)
-
-    # Scaling for the inputs, outputs.
-    pscale = np.take(uscale, disturbance_indices).squeeze()
-    yscale = yscale.squeeze()
-    uscale = uscale.squeeze()
-    zscale = (H @ yscale[:, np.newaxis]).squeeze()
-    
-    # States.
-    x_opt = np.asarray(optimal.x[start:end]).squeeze()
-    x_satdlqr = np.asarray(satdlqr.x[start:end]).squeeze()
-
-    # Control inputs.
-    u_opt = np.asarray(optimal.u[start:end]).squeeze()*uscale + us.squeeze()
-    u_satdlqr = np.asarray(satdlqr.u[start:end]).squeeze()*uscale + us.squeeze()
-
-    # Disturbances.
-    p = np.asarray(optimal.p[start:end]).squeeze()*pscale
-
-    # All the outputs.
[…]

### 2020-10-21 cdu_train_unstd.py

@@ -1,90 +1,0 @@
-# [makes] pickle
-"""
-Script to train an unstructured neural network controller for the 
-crude distillation unit example.
-Pratyush Kumar, pratyushkumar@ucsb.edu
-"""
-import sys
-sys.path.append('lib/')
-import numpy as np
-import os
-import time
-import itertools
-import tensorflow as tf
-from python_utils import (PickleTool, H5pyTool)
-from LinearMPCLayers import UnstdRegulatorModel
-from controller_evaluation import _get_data_for_training
-
-# Set the tensorflow graph-level seed.
-tf.random.set_seed(1)
-
-def create_nn_controller(*, regulator_dims):
-    """Create an instantiation of the neural network controller and return."""
-    Nx = 252
-    Nu = 32
-    # Create the keras model instance.
-    nn_controller = UnstdRegulatorModel(Nx=Nx, Nu=Nu,
-                                       regulator_dims=regulator_dims,
-                                       nnwithuprev=False)
-    # Compile the nn controller.
-    nn_controller.compile(optimizer='adam', loss='mean_squared_error')
-    # Return the compiled controller.
-    return nn_controller
-
-def train_nn_controller(nn_controller, data, stdout_filename, ckpt_path):
-    """ Function to train the controller."""
-    # Std out.
-    sys.stdout = open(stdout_filename, 'w')
-    # Create the checkpoint callback.
-    checkpoint_callback = tf.keras.callbacks.ModelCheckpoint(filepath=ckpt_path,
-                                                monitor='val_loss',
-                                                save_best_only=True,
-                                                save_weights_only=True,
-                                                verbose=1)
-    # Call the fit method to train.
-    tstart = time.time()
-    nn_controller.fit(x=[data['x'], data['xs'], data['us']], 
-                      y=[data['u']], 
-                      epochs=1500,
-                      batch_size=2048,
-                      validation_split=0.1,
-                      callbacks=[checkpoint_callback])
-    tend = time.time()
-    training_time = tend - tstart
-    return (nn_controller, training_time)
-
-# Get the raw data for training.
-num_sample = 357600
-raw_data = H5pyTool.load_training_data(filename='cdu_offline_data.h5py')
-(training_data, xscale) = _get_data_for_training(data=raw_data, 
-                                           num_samples=num_sample, 
-                                           scale=True)
-
-# Get a NN controller.
-regulator_dims = [536, 832, 832, 832, 32]
[…]

### 2020-10-21 cdu_us.py

@@ -1,4 +1,6 @@
 # [depends] cdu_parameters.pickle
+# [depends] %LIB%/python_utils.py
+# [depends] %LIB%/controller_evaluation.py
 # [makes] pickle
 """
 Script to run an on-line simulation using the double integrator example
@@ -8,7 +10,7 @@ takes much time, both plotting and the simulation tasks are in
 the same script.
 """
 import sys
-sys.path.append('lib/')
+sys.path.append('../lib/')
 import numpy as np
 from matplotlib.backends.backend_pdf import PdfPages
 from python_utils import PickleTool

### 2020-10-21 cstrs_mpc_plot.py

@@ -1,148 +1,0 @@
-# [depends] cstrs_parameters.pickle cstrs_mpc.pickle
-"""
-Script to run an on-line simulation using the double integrator example
-using the optimal MPC controller.
-Since for the double integrator example, on-line simulation does not
-takes much time, both plotting and the simulation tasks are in
-the same script.
-"""
-import sys
-sys.path.append('lib/')
-import numpy as np
-import itertools
-from cstrs_labels import (ylabels, ulabels, zlabels, pdlabels)
-import matplotlib.pyplot as plt
-from python_utils import (PickleTool, figure_size_a4)
-from matplotlib.backends.backend_pdf import PdfPages
-from cstrs_comparision_plots import _get_cstr_data_for_plotting
-
-def _cstrs_optimal_plot(plant, controller, parameters, 
-                        setpoints, plot_range):
-    """Data to plot.
-    z: 4 outputs with setpoints. y:90 outputs. u:32 inputs.
-    """
-    # the x coordinate of the ylabels.
-    ylabel_xcoordinate = -0.25
-    # Get the arrays.
-    (t, z, y, u, pest, p, 
-      ulb, uub, zsp, ell) = _get_cstr_data_for_plotting(plant,  
-                                                        controller, setpoints,
-                                                        parameters, plot_range)
-    # Make the plots.
-    figures = plot_inputs(t, u, ulabels, ylabel_xcoordinate, ulb, uub)
-    figures += plot_outputs(t, y, ylabels, ylabel_xcoordinate)
-    figures += plot_controlled_outputs(t, z, zsp, zlabels, ylabel_xcoordinate)
-    figures += plot_disturbances(t, p, pest, parameters['exp_dist_indices'], 
-                                 pdlabels, ylabel_xcoordinate)
-    figures += plot_average_stage_costs(t, ell, 
-                            ylabel_xcoordinate)
-    # Return the list of figures.
-    return figures
-
-def plot_inputs(t, u, ulabels, ylabel_xcoordinate, ulb, uub):
-    """Return 4 figure objects which contain the plots of the inputs."""
-    input_index = 0
-    num_rows = 3
-    num_cols = 2
-    (figure, axes) = plt.subplots(nrows=num_rows, ncols=num_cols,
-                                 sharex='col', figsize=figure_size_a4, 
-                                 gridspec_kw = dict(wspace=0.5))
[…]

### 2020-10-21 cstrs_neural_network.py

@@ -1,11 +1,12 @@
 # [depends] cstrs_parameters.pickle cstrs_train.pickle
+# [depends] %LIB%/controller_evaluation.py
 # [makes] pickle
 """
 Script to run an on-line simulation for the double integrator example
 using the approximate NN controller.
 """
 import sys
-sys.path.append('lib/')
+sys.path.append('../lib/')
 from controller_evaluation import _simulate_neural_networks
 
 # Load data and do an online simulation using the linear MPC controller.

### 2020-10-21 cstrs_neural_network_unstd.py

@@ -1,11 +1,13 @@
 # [depends] cstrs_parameters.pickle cstrs_train_unstd.pickle
+# [depends] %LIB%/controller_evaluation.py
+# [depends] %LIB%/python_utils.py
 # [makes] pickle
 """
 Script to run an on-line simulation for the 
 CSTRs with flash example using the approximate NN controller.
 """
 import sys
-sys.path.append('lib/')
+sys.path.append('../lib/')
 from python_utils import (PickleTool, figure_size_a4)
 from matplotlib.backends.backend_pdf import PdfPages
 from cstrs_comparision_plots import _cstrs_cl_comparision_plots

### 2020-10-21 cstrs_offline_data.py

@@ -1,10 +1,11 @@
 # [depends] cstrs_parameters.pickle
+# [depends] %LIB%/python_utils.py
 # [makes] pickle
 """
 Script to generate offline data for training the neural net.
 """
 import sys
-sys.path.append('lib/')
+sys.path.append('../lib/')
 from python_utils import PickleTool
 
 # Load data and do an online simulation using the linear MPC controller.

### 2020-10-21 cstrs_offline_data_post_processing.py

@@ -1,8 +1,9 @@
+# [depends] %LIB%/controller_evaluation.py
 """
 Post process the offline generated dataset.
 """
 import sys
-sys.path.append('lib/')
+sys.path.append('../lib/')
 from python_utils import H5pyTool
 import os
 import itertools

### 2020-10-21 cstrs_offline_plot.py

@@ -1,58 +1,0 @@
-# [depends] cstrs_offline_data.pickle
-"""
-Script to run an on-line simulation using the double integrator example
-using the optimal MPC controller.
-Since for the double integrator example, on-line simulation does not
-takes much time, both plotting and the simulation tasks are in 
-the same script.
-"""
-import sys
-sys.path.append('../lib/')
-import numpy as np
-from cstrs_optimal_plot import (plot_inputs, plot_states, 
-                                plot_outputs, plot_disturbances)
-from cstrs_labels import (xlabels, ylabels, ulabels, pdlabels)
-import matplotlib.pyplot as plt
-from python_utils import (PickleTool, figure_size_a4)
-from matplotlib.backends.backend_pdf import PdfPages
-
-def _get_arrays_for_plotting(raw_data, num_samples):
-    """ Convert lists to numpy array."""
-    # Get the data arrays for plotting.
-    x = raw_data['x'][:num_samples, :].squeeze()
-    u = raw_data['useq'][:num_samples, 0:6].squeeze()
-    d = raw_data['d'][:num_samples, :].squeeze()
-    ysp = raw_data['rsp'][:num_samples, :].squeeze()
-    y = raw_data['y'][:num_samples, :].squeeze()
-    t = np.arange(0, num_samples)
-    ulb = np.tile(np.NaN, (num_samples, u.shape[1]))
-    uub = np.tile(np.NaN, (num_samples, u.shape[1]))
-    return (x, u, d, ysp, y, t, ulb, uub)
-
-def _cstrs_plot_offline_data(offline_simulator, num_samples):
-    """ Get the offline data for plotting."""
-    ylabel_xcoordinate = -0.25
-    (x, u, d, ysp, y, t, ulb, uub) = _get_arrays_for_plotting(offline_simulator, num_samples)
-
-    # Make the Plots.
-    figures = plot_inputs(t, u, ulabels, ylabel_xcoordinate, ulb, uub)
-    figures += plot_outputs(t, y, ysp, ylabels, ylabel_xcoordinate)
-    figures += plot_states(t, x, xlabels, ylabel_xcoordinate)
-    figures += plot_disturbances(t, d, pdlabels, ylabel_xcoordinate)
-    return figures
-
-def main():
-    """ The Main Function. """
-    # Load data and do an online simulation using the linear MPC controller.
-    cstrs_offline_data = PickleTool.load(filename='cstrs_offline_data.pickle', type='read')
-    # Make the plot. 
[…]

### 2020-10-21 cstrs_parameters.py

@@ -1,3 +1,7 @@
+# [depends] %LIB%/linearMPC.py
+# [depends] %LIB%/nonlinearMPC.py
+# [depends] %LIB%/controller_evaluation.py
+# [depends] %LIB%/python_utils.py
 # [makes] pickle
 """ 
 Generate necessary parameters for the offline data generation and 
@@ -296,10 +300,10 @@ def _get_cstrs_mpc_controller(plant, parameters,
     Q = 1e+3*(C.T @ C)
     R = 0.1*np.eye(Nu)
     S = 0.1*np.eye(Nu)
-    N = 30
+    N = 90
     ulb = parameters['lb']['u'][:, np.newaxis]
     uub = parameters['ub']['u'][:, np.newaxis]
-    
+
     # Return a linear MPC controller instance.
     return LinearMPCController(A=A, B=B, C=C, H=H,
                                Qwx=Qwx, Qwd=Qwd,
@@ -308,7 +312,7 @@ def _get_cstrs_mpc_controller(plant, parameters,
                                Q=Q, R=R, S=S, N=N, ulb=ulb, uub=uub)
 
 def _get_cstrs_offline_simulator(controller, parameters,
-                                 z_indices, exp_dist_indices,
+                                 z_indices, unexp_z_indices, exp_dist_indices,
                                  Nsim, num_data_gen_task, 
                                  num_process_per_task, 
                                  conservative_factor, seed):
@@ -321,13 +325,14 @@ def _get_cstrs_offline_simulator(controller, parameters,
 
     # Get the setpoints.
     setpoints_z = np.zeros((Nsim, parameters['Ny']))
-    setpoints_y = sample_prbs_like(num_change=750, num_steps=Nsim, 
+    setpoints_y = sample_prbs_like(num_change=1250, num_steps=Nsim, 
                              lb=setpoint_lb, ub=setpoint_ub,
                              mean_change=120, sigma_change=2, seed=seed)
     setpoints_z[:, z_indices] = setpoints_y[:, z_indices]
+    setpoints_z[:, unexp_z_indices] = np.zeros((Nsim, len(unexp_z_indices)))
 
     # Get the disturbances. 
-    disturbances = sample_prbs_like(num_change=1500, num_steps=Nsim, 
+    disturbances = sample_prbs_like(num_change=2500, num_steps=Nsim, 
                              lb=disturbance_lb, ub=disturbance_ub,
                              mean_change=60, sigma_change=5, seed=seed+1)
[…]

### 2020-10-21 cstrs_satdlqr.py

@@ -1,4 +1,6 @@
 # [depends] cstrs_parameters.pickle
+# [depends] %LIB%/controller_evaluation.py
+# [depends] %LIB%/python_utils.py
 # [makes] pickle
 """
 Script to run an on-line simulation using the double integrator example

### 2020-10-21 cstrs_train.py

@@ -1,3 +1,6 @@
+# [depends] %LIB%/LinearMPCLayers.py
+# [depends] %LIB%/controller_evaluation.py
+# [depends] %LIB%/python_utils.py
 # [makes] pickle
 """
 Script to train the neural network controller for the 
@@ -48,7 +51,7 @@ def train_nn_controller(nn_controller, data,
     tstart = time.time()
     nn_controller.fit(x=[data['x'], data['uprev'], data['xs'], data['us']], 
                       y=[data['u']], 
-                      epochs=500,
+                      epochs=2000,
                       batch_size=1024,
                       validation_split=0.1,
                       callbacks = [checkpoint_callback])
@@ -60,16 +63,18 @@ def train_nn_controller(nn_controller, data,
 # Get the raw data for training.
 raw_data = H5pyTool.load_training_data(filename='cstrs_offline_data.h5py')
 (scaled_data, xscale) = _get_data_for_training(data=raw_data, 
-                                           num_samples=120000, 
+                                           num_samples=150000, 
                                            scale=True)
 
 # Arrange the number of samples and the dimensions of the NN controller.
-num_samples = [num_sample for num_sample in range(24000, 120001, 24000)]
+num_samples = [num_sample for num_sample in range(40000, 150001, 10000)]
 data_generation_times = []
 training_times = []
 memory_footprints = []
-regulator_dims = [[36, 160, 160, 6], [36, 192, 192, 6],
-                  [36, 224, 224, 6], [36, 256, 256, 6]]
+regulator_dims = [[72, 224, 224, 224, 6],
+                  [72, 240, 240, 240, 6], 
+                  [72, 256, 256, 256, 6],
+                  [72, 272, 272, 272, 6]]
 trained_regulator_weights = []
 
 # Take input from the user about which architecture to train.

### 2020-10-21 cstrs_train_post_processing.py

@@ -1,8 +1,9 @@
+# [depends] %LIB%/controller_evaluation.py
 """
 Post process the trained dataset.
 """
 import sys
-sys.path.append('lib/')
+sys.path.append('../lib/')
 from controller_evaluation import _post_process_trained_data
 
 _post_process_trained_data(data_filename='cstrs_train.pickle', 

### 2020-10-21 cstrs_train_unstd.py

@@ -1,3 +1,6 @@
+# [depends] %LIB%/LinearMPCLayers.py
+# [depends] %LIB%/controller_evaluation.py
+# [depends] %LIB%/python_utils.py
 # [makes] pickle
 """
 Script to train an unstructured neural network controller for the 
@@ -5,7 +8,7 @@ double integrator example.
 Pratyush Kumar, pratyushkumar@ucsb.edu
 """
 import sys
-sys.path.append('lib/')
+sys.path.append('../lib/')
 import numpy as np
 import os
 import time
@@ -61,7 +64,7 @@ raw_data = H5pyTool.load_training_data(filename='cstrs_offline_data.h5py')
                                            scale=True)
 
 # Get a NN controller.
-regulator_dims = [36, 224, 224, 224, 6]
+regulator_dims = [72, 224, 224, 224, 6]
 nn_controller = create_nn_controller(regulator_dims=regulator_dims)
 
 # Train the NN controller.

### 2020-10-21 lib/controller_evaluation.py

@@ -17,6 +17,8 @@ from python_utils import (figure_size_a4, PickleTool,
                           H5pyTool)
 from matplotlib.backends.backend_pdf import PdfPages
 
+plt.rcParams.update({'figure.max_open_warning': 0})
+
 def _sample_repeats(num_change, num_simulation_steps,
                        mean_change, sigma_change):
     """ Sample the number of times a repeat in each
@@ -198,7 +200,7 @@ def plot_cl_performance_and_comp_times(time,
         axes_cl.set_xlim([np.min(time), np.max(time)])
         figure_cl.legend(labels=cl_legend_labels, 
                          loc=fig_cl_title_location, 
-                         ncol=1)
+                         ncol=2)
         # Set some plotting parameters for the histogram.
         axes_ct.set_xscale('log')
         axes_ct.set_yscale('linear')

### 2020-10-21 lib/cstrs_labels.py

@@ -8,13 +8,13 @@ ylabels = ['$H_{r}$', '$x_{Ar}$', '$x_{Br}$', '$T_{r}$',
            '$H_{m}$', '$x_{Am}$', '$x_{Bm}$', '$T_{m}$',
            '$H_{b}$', '$x_{Ab}$', '$x_{Bb}$', '$T_{b}$']
 
-zlabels = ['$H_{r}$ (m)', '$T_{r}$ (K)',
-           '$H_{m}$ (m)', '$T_{m}$ (K)',
-           '$H_{b}$ (m)', '$T_{b}$ (K)']
+zlabels = ['$H_{r}$(m)', '$T_{r}$(K)',
+           '$H_{m}$(m)', '$T_{m}$(K)',
+           '$H_{b}$(m)', '$T_{b}$(K)']
 
-ulabels = ['$F_{0}$ (Kg/s)', '$Q_{r} \ (10^3$ kW)',
-           '$F_{1}$ (Kg/s)', '$Q_{m} \ (10^3$ kW)',
-           '$D$ (Kg/s)', '$Q_{b} \ (10^3$ kW)']
+ulabels = ['$F_{0}$ (Kg/sec)', '$Q_{r} \ (10^3$ kW)',
+           '$F_{1}$ (Kg/sec)', '$Q_{m} \ (10^3$ kW)',
+           '$D$ (Kg/sec)', '$Q_{b} \ (10^3$ kW)']
 
 pdlabels = ['$x_{A0}$', '$x_{B0}$',
            '$x_{A1}$', '$x_{B1}$',

### 2020-10-21 cdu_comparision_plots.py
update a few more files.

@@ -1,6 +1,9 @@
 # [depends] cdu_parameters.pickle cdu_mpc.pickle cdu_us.pickle
 # [depends] cdu_satdlqr.pickle cdu_short_horizon.pickle cdu_train.pickle
 # [depends] cdu_neural_network.pickle
+# [depends] %LIB%/python_utils.py
+# [depends] %LIB%/cdu_labels.py
+# [depends] %LIB%/controller_evaluation.py
 """
 Script to run an on-line simulation using the double integrator example
 using the optimal MPC controller.
@@ -17,7 +20,7 @@ import numpy as np
 import itertools
 import matplotlib.pyplot as plt
 from cdu_labels import (ulabels, zlabels, ylabels, pdlabels)
-from python_utils import (PickleTool, figure_size_cl, 
+from python_utils import (PickleTool, figure_size_cl,
                          figure_size_a4, figure_size_metrics)
 from matplotlib.backends.backend_pdf import PdfPages
 from controller_evaluation import (plot_cl_performance_and_comp_times,
@@ -261,7 +264,7 @@ def main():
     """ Run these commands when this script is called."""
 
     # Set the fontize.
-    _set_font_size(paper_fontsize=14)
+    _set_font_size(paper_fontsize=16)
 
     # Get the parameters and the plant object which has the closed-loop data
     # for the two controllers.
@@ -317,8 +320,8 @@ def main():
                                              num_samples, 
                                              nn_labels,
                                              figure_size_metrics,
-                                             right_frac=0.75,
-                                             legend_title_location=(0.78, 0.4),
+                                             right_frac=0.9,
+                                             legend_title_location=(0.6, 0.5),
                                              ylabel_xcoordinate=-0.1,
                                              yaxis_log=False)
 
@@ -332,14 +335,14 @@ def main():
                          short_horizon_controllers, 
                          nn_plants, nn_controllers, performance_loss,
                          num_architectures, num_nns_per_architecture, 
-                         cl_xlabel = 'Time', 
+                         cl_xlabel = 'Time (min)', 
                          cl_legend_labels = ['MPC', 'satK'] + nn_labels,
-                         cl_right_frac = 0.75,
-                         ct_right_frac = 0.75, 
+                         cl_right_frac = 0.9,
+                         ct_right_frac = 0.9, 
                          ct_legend_labels = ['MPC'] + nn_labels,
                          figure_size=figure_size_metrics,
-                         fig_cl_title_location=(0.78, 0.3),
[…]

### 2020-10-21 cdu_train.py

@@ -1,3 +1,6 @@
+# [depends] %LIB%/LinearMPCLayers.py
+# [depends] %LIB%/controller_evaluation.py
+# [depends] %LIB%/python_utils.py
 # [makes] pickle
 """
 Script to train the neural network controller for the 
@@ -7,7 +10,7 @@ Pratyush Kumar, pratyushkumar@ucsb.edu
 import os
 import sys
 import numpy as np
-sys.path.append('lib/')
+sys.path.append('../lib/')
 import time
 import itertools
 import tensorflow as tf
@@ -37,7 +40,7 @@ def train_nn_controller(nn_controller, data,
                         stdout_filename, ckpt_path):
     """ Function to train the NN controller."""
     # Std out.
-    sys.stdout = open(stdout_filename, 'w')
+    sys.stdout = open(stdout_filename, 'a')
     # Create the checkpoint callback.
     checkpoint_callback = tf.keras.callbacks.ModelCheckpoint(filepath=ckpt_path,
                                                     monitor='val_loss',
@@ -49,9 +52,9 @@ def train_nn_controller(nn_controller, data,
     tstart = time.time()
     nn_controller.fit(x=[data['x'], data['xs'], data['us']], 
                       y=[data['u']], 
-                      epochs=500,
+                      epochs=1500,
                       batch_size=2048,
-                      validation_split=0.1,
+                      validation_split=0.05,
                       callbacks = [checkpoint_callback])
     tend = time.time()
     training_time = tend - tstart
@@ -61,16 +64,20 @@ def train_nn_controller(nn_controller, data,
 # Get the raw data for training.
 raw_data = H5pyTool.load_training_data(filename='cdu_offline_data.h5py')
 (scaled_data, xscale) = _get_data_for_training(data=raw_data, 
-                                           num_samples=120000, 
+                                           num_samples=357600, 
                                            scale=True)
 
 # Arrange the number of samples and the dimensions of the NN controller.
-num_samples = [num_sample for num_sample in range(24000, 120001, 24000)]
+num_samples = [20000]
+num_samples += [num_sample for num_sample in range(30000, 330001, 30000)]
+num_samples += [357600]
 data_generation_times = []
 training_times = []
 memory_footprints = []
-regulator_dims = [[536, 160, 160, 32], [536, 192, 192, 32],
-                  [536, 224, 224, 32], [536, 256, 256, 32]]
+regulator_dims = [[536, 832, 832, 832, 32],
[…]

### 2020-10-21 cdu_train_post_processing.py
add one more.

@@ -1,8 +1,9 @@
+# [depends] %LIB%/controller_evaluation.py
 """
 Post process the trained dataset.
 """
 import sys
-sys.path.append('lib/')
+sys.path.append('../lib/')
 from controller_evaluation import _post_process_trained_data
 
 _post_process_trained_data(data_filename='cdu_train.pickle', 

### 2020-10-21 cstrs_comparision_plots.py
add figure files.

@@ -1,6 +1,8 @@
 # [depends] cstrs_parameters.pickle cstrs_mpc.pickle cstrs_us.pickle
 # [depends] cstrs_satdlqr.pickle cstrs_short_horizon.pickle cstrs_train.pickle
 # [depends] cstrs_neural_network.pickle
+# [depends] %LIB%/controller_evaluation.py
+# [depends] %LIB%/cstrs_labels.py
 """ 
 Script to make plots for comparing the 
 performance of the optimal MPC controller
@@ -70,7 +72,7 @@ def _cstrs_cl_comparision_plots(scenarios,
     z: 4 outputs with setpoints. y:90 outputs. u:32 inputs.
     """
     # the x coordinate of the ylabels.
-    ylabel_xcoordinate = -0.28
+    ylabel_xcoordinate = -0.27
     figures = []
     for (scenario, mpc_plant, 
          mpc_controller, fast_plant,
@@ -135,7 +137,7 @@ def plot_inputs(t, u, ulabels, ylabel_xcoordinate,
     axes[2, 0].set_xlabel("Time (hr)")
     axes[2, 1].set_xlabel("Time (hr)")
     figure.legend(labels = ('MPC', fast_controller_name), 
-                  loc = (0.32, 0.9), ncol=2)
+                  loc = (0.31, 0.9), ncol=2)
     # Return the figure,
     return [figure]
 
@@ -161,7 +163,7 @@ def plot_controlled_outputs(t, z, zsp,
     axes[2, 0].set_xlabel("Time (hr)")
     axes[2, 1].set_xlabel("Time (hr)")
     figure.legend(labels = ('MPC', fast_controller_name), 
-                  loc = (0.32, 0.9), ncol=2)
+                  loc = (0.31, 0.9), ncol=2)
     # Return
     return [figure]
 
@@ -228,7 +230,7 @@ def main():
     """ Run these commands when this script is called."""
 
     # Set the fontize.
-    _set_font_size(paper_fontsize=14)
+    _set_font_size(paper_fontsize=16)
 
     # Get the parameters and the plant object which has the closed-loop data
     # for the two controllers.
@@ -284,8 +286,8 @@ def main():
                                              num_samples, 
                                              nn_labels,
                                              figure_size_metrics,
-                                             right_frac=0.75,
-                                             legend_title_location=(0.78, 0.4),
+                                             right_frac=0.9,
+                                             legend_title_location=(0.6, 0.5),
[…]

### 2020-10-21 paper.tex
minor change.

@@
 network training. All the anticipated plant operational scenarios 
-with setpoints and disturbances that may change for 
-a reasonable duration of operation must be sampled for NN training.
+with setpoints and disturbances that may change
+during operation must be sampled for NN training.
 After the offline design phase, 

### 2020-11-03 paper.tex
jbr edits on text

@@
 
+\usepackage{mpcsymbols}
+
 %\biboptions{longnamesfirst, semicolon}
@@
 % \biboptions{}
-\newcommand{\useq}{\mathbf{u}}
-\newcommand{\xseq}{\mathbf{x}}
-\newcommand{\bbR}{\mathbb{R}}
-\newcommand{\bbW}{\mathbb{W}}
-\newcommand{\bbU}{\mathbb{U}}
-\newcommand{\bbI}{\mathbb{I}}
-\newcommand{\bbX}{\mathbb{X}}
-\newcommand{\bbP}{\mathbb{P}}
 
@@
 \citep*{kouzoupis:frison:zanelli:diehl:2018, wright:2019}
-allowed practitioners to adopt MPC
-in process industries \citep*{qin:badgwell:2003, lahiri:2017}.
+allowed practitioners to apply MPC
+in the process industries \citep*{qin:badgwell:2003, lahiri:2017}.
 
@@
 partitions of the state space grows exponentially
-with model dimensions, however. Thereby prohibiting 
+with model dimensions, however, which prohibits
 the deployment of this strategy on large-scale 
@@
 densely for the NN training. This issue is 
-a form of the curse of dimensionality.
+a form of the well-known curse of dimensionality.
 ii) One may sample the state space partially
@@
 The focus of this article is on setpoint tracking 
-MPC problems relevant for deployment in process industries.
+MPC problems relevant for deployment in the process industries.
 We present a new feedforward network architecture to obtain
@@
 Additionally, we use the input-to-state
-stability results \citep*{sontag:wang:1995}
+stability results
 available in the MPC literature, and establish
@@
 disturbances. We present case studies 
-on process control examples which
+on process control examples that
 demonstrate the scalability of the proposed NN design 
@@
 to approximate the MPC feedback law on systems with 
-state dimensions upto thirty-six. The setpoint 
+state dimensions up to 36. The setpoint 
 tracking offset-free MPC problem and state 
-dimensions upto two-fifty considered in this 
+dimensions up to 250 considered in this 
 article is not addressed in that work. 
 \cite*{drgona:picard:kvasnica:helsen:2018}
-takes a different approach for the scalability
+take a different approach for the scalability
 of NN controllers, in which 
@@
 $\beta : \bbR_{\geq 0} \times \bbI_{\geq 0} \rightarrow \bbR_{\geq 0}$
-is of class $\mathcal{K} \mathcal{L}$ if it is continuous,
-for a fixed $k \in \bbI_{\geq 0}$, $\beta(\cdot, k)$ is of class $\mathcal{K}$,
-and for a fixed $s \geq 0$, $\beta(s, \cdot)$ is nonincreasing
+is of class $\mathcal{KL}$ if it is continuous,
+for each $k \in \bbI_{\geq 0}$, $\beta(\cdot, k)$ is of class $\mathcal{K}$,
+and for each $s \geq 0$, $\beta(s, \cdot)$ is nonincreasing
 and satisfies $\textnormal{lim}_{k \rightarrow \infty} \beta(s, k) = 0$.
 Given $V : X \rightarrow \bbR_{\geq 0}$ and $\tau > 0$, define 
-$\textnormal{lev}_{\tau} V = \{ x \in X | V(x) \leq \tau \}$.
+$\textnormal{lev}_{\tau} V = \{ x \in X \mid V(x) \leq \tau \}$.
 Bold symbols, e.g., $\mathbf{d}$ denote sequences, 
@@
 state operations and maintain
-them at their setpoints.
+the controlled variables at their setpoints.
 We assume in the rest of this 
@@
 The penalty matrix $P$ is chosen as the 
-optimal cost-to-go matrix of the unconstrained 
-linear quadratic infinite horizon problem.
+optimal cost-to-go matrix of the unconstrained infinite horizon 
+linear quadratic problem.
 The decision variable in this 
@@
 \cite*{chen:saulnier:atanasov:lee:kumar:pappas:morari:2018}
-for one fixed steady state. The approach has not been 
+for a single fixed steady state. The approach has not been 
 demonstrated to scale to the size of model dimensions 
@@
 architecture
-
-\begin{align*}
+\begin{align}
 z_0 &= \begin{bmatrix}
-    x', & x_s', & u_s', & x_s', & x_s', & u_s'
-    \end{bmatrix}'\\
+    x', & x_s', & u_s', & x_s', & x_s', & u_s' \end{bmatrix}'\notag \\
     f_i(z_{i-1}) &= \begin{bmatrix}
-        W_i & 0 \\
+        W_i & 0 \notag \\
         0 & W_i
           \end{bmatrix}z_{i-1}  + \begin{bmatrix}
-            b_i \\
+            b_i \notag 
             b_i
-            \end{bmatrix} \\
-    z_i &= g(f_i(z_{i-1})), \textnormal{for} \ i \in \bbI_{1:h} \\
+            \end{bmatrix} \notag\\
+    z_i &= g(f_i(z_{i-1})), \textnormal{for} \ i \in \bbI_{1:h} \notag \\
     u &= u_s + \begin{bmatrix}
   W_{h + 1}, & -W_{h + 1} \\
-    \end{bmatrix} z_h \\
-\end{align*}
+    \end{bmatrix} z_h
+\label{eq:NNstruct}
+\end{align}
 in which $g(a) = \textnormal{max} (0, a)$,
@@
 of appropriate dimensions.
-At steady-states
-when $x=x_s$ in $z_0$, this structured network
+At steady state, when $x=x_s$ in $z_0$, \eqref{eq:NNstruct}
 outputs $u_s$ regardless of the choice of weights.
@@
 target pairs. Sampling this entire domain of the
-MPC control law for NN training is difficult in larger 
-dimensions and we show in Section 
+MPC control law for NN training is difficult in large 
+dimension, and we show in Section 
 \ref{sec:simulation_studies} that it is
-not required for practical applications.
+also not required for practical applications.
 
@@
 than the entire domain of the MPC control law.
-This type of operation of large chemical plants
+This typical operation of large chemical plants
 can be exploited, and we propose the 
@@
 $x^+ = Ax + B\kappa_N(x)$ when no hard terminal region 
-constraint \citep*{limon:alamo:salas:camacho:2006}  
-is included in the QP can be characterized
-as $\mathcal{X}_N = \textnormal{lev}_{Nd + \tau} \ V_N^0(x)$.
-In which, $\tau$ is a level
-set parameter of the terminal region chosen as
+constraint is included in the QP
+can be characterized as $\mathcal{X}_N = \textnormal{lev}_{Nd + \tau} \
+V_N^0(x)$ \citep*{limon:alamo:salas:camacho:2006}.
+The parameter $\tau$ is the level set
+parameter of the terminal region chosen as
 $\bbX_f = \textnormal{lev}_{\tau} \ x'Px$, and $d > 0$
@@
 current and next timestep respectively. 
-We use $\phi_d(k;\hat{x})$ to denote a 
-solution of the perturbed system 
-at time $k$ starting from an initial state $\hat{x}$,
-and $\phi(k;x)$ to denote a solution 
-of the nominal system when the state estimation errors and process
-disturbances are zero starting 
-from an initial state $x$.
+We use $\phi_d(k;\hat{x})$ to denote a solution of the perturbed system  at time
+$k$ starting from an initial state $\hat{x}$; and $\phi(k;x)$ to denote a
+solution  of the nominal system starting  from an initial state $x$ when the
+state estimation errors and process disturbances are zero.
 
@@
 The proof of this theorem along with the required 
-input-to-state stability definitions is provided 
+input-to-state stability definitions are provided 
 in Appendix \ref{app:theorem1}.
@@
 in the state space of interest and 
-strengthen the bounds on the closed-loop states.
+reduce the bound on the closed-loop states.
 
@@
 In this section, two case studies are presented 
-which demonstrate the 
+that demonstrate the 
 scalability of the proposed NN design approach.
@@
 abilities of the NNs, and are referred subsequently as 
-simulations with expected and unexpected plant behaviors.
+simulations with \textit{expected} and \textit{unexpected} plant behaviors, respectively.
 
@@
 equivalently fast controllers as NNs are also compared
-in the validation simulations.
-a) steady state controller (SS): the solution
+in the validation simulations:
+(a) steady state controller (SS): the solution
 of the target selector is directly applied to the plant 
-$u = u_s$, b) saturated linear quadratic regulator (satK):
+$u = u_s$; (b) saturated linear quadratic regulator (satK):
 the unconstrained LQR gain 
 $K$ is computed and used in the control law 
-$u = \textnormal{sat}(K(x-x_s) + u_s, \underline{u}, \overline{u})$,
-c) short horizon controller (SH): an MPC problem
-with a short control horizon is solved online, 
-d) Unstructured NN (NN-UNS): a standard feedforward network is 
+$u = \textnormal{sat}(K(x-x_s) + u_s, \underline{u}, \overline{u})$;
+(c) short horizon controller (SH): an MPC problem
+with a short control horizon is solved online;
+(d) Unstructured NN (NN-UNS): a standard feedforward network is 
 trained with the triple ($x, x_s, u_s$) as the input
@@
 which is a typical crude unit found in petrochemical refineries.
-The plant model is linear, input and outputs are scaled 
+The plant model is linear, and input and outputs are scaled 
 for the MPC regulator as in the previous example.
@@
 The data requirement to obtain 
-an accurate NN controller is shown in top left.
+an accurate NN controller is shown in the top left.
 The batch size 
@@
 obtained with the four structured NNs,
-satK, and MPC controllers is shown in center bottom.
+satK, and MPC controllers is shown in the center bottom.
 The top right plot shows the 
@@
 that may be out of reach with QP solvers. 
-The proposed no online optimization based
-methods to date in the literature such as storing 
+The proposed methods avoiding online optimization
+to date in the literature, such as storing 
 the entire MPC feedback law 
 and sampling the large dimensional state space 
-for the NN training are not tractable for the problems 
+for the NN training, are not tractable for the problems 
 considered in this article.
@@
 The key features for the scalability of the proposed approach 
-are the structure of NN and data generation for only
+are the structure of the NN and data generation for only
 typical plant operational scenarios. 
@@
 
-\section*{Acknowledgement}
+\section*{Acknowledgment}
 %The authors acknowledge Professor Stephen J. Wright 

### 2020-11-03 paper.tex
fix norm, xhat, dhat, and steady state adjectives.

@@
 closed interval $[a, b]$). The Euclidean norm 
-is denoted by $\vert \cdot \vert$. A function 
+is denoted by $\norm{\cdot}$. A function 
 $\alpha : \bbR_{\geq 0} \rightarrow \bbR_{\geq 0}$
@@
 $\mathbf{d}$ for $k \in \bbI_{0:i-1}$.
-Define $\vert \vert \mathbf{d}_i \vert \vert = 
-\textnormal{max}_{k \in \bbI_{0:i-1}} \vert d(k) \vert$.
+Define $\norm{\norm{\mathbf{d}_i}} = 
+\textnormal{max}_{k \in \bbI_{0:i-1}} \norm{d(k)}$.
 For a given vector $a$, lower and upper bounds 
@@
 article that a Kalman filter can be constructed to 
-estimate the model state ($\hat{x}$) and disturbance ($\hat{d}$) 
+estimate the model state ($\xhat$) and disturbance ($\dhat$) 
 from measurements.
@@
     \end{bmatrix} &= \begin{bmatrix}
-        B_d\hat{d} \\
-        r_{sp} - HC_d\hat{d}
+        B_d\dhat \\
+        r_{sp} - HC_d\dhat
     \end{bmatrix} \\
@@
 ($x_s, u_s$) is the 
-target steady state pair,
+target steady-state pair,
 $r=Hy$ are the controlled measurements
@@
 controlled measurement setpoints.
-The equality constraint $r_{sp} = H(Cx_s + C_d\hat{d})$
+The equality constraint $r_{sp} = H(Cx_s + C_d\dhat)$
 can be difficult to satisfy exactly in real time 
@@
 Based on the state estimate and
-target steady state pair,
+target steady-state pair,
 the following QP is solved to determine the 
@@
 \begin{align}
-    \tilde{x}^+ &= A\tilde{x} + B\tilde{u}, \quad \tilde{x}(0) = \hat{x} - x_s \\
+    \tilde{x}^+ &= A\tilde{x} + B\tilde{u}, \quad \tilde{x}(0) = \xhat - x_s \\
     &\underline{u} \leq \tilde{u} + u_s \leq \overline{u}
@@
 \end{align}
-in which $\hat{x}$ is the state estimate after the current measurement,
+in which $\xhat$ is the state estimate after the current measurement,
 $N$ is the control 
@@
 ($\tilde{x}, \tilde{u}$) are the state and control 
-in deviation from the current steady state targets ($x_s, u_s$). 
+in deviation from the current steady-state targets ($x_s, u_s$). 
 The penalty matrix $P$ is chosen as the 
@@
 as the MPC feedback law,
-$\kappa_N(\hat{x}, x_s, u_s) = 
-\mathbf{\tilde{u}}^0(0;\hat{x}, x_s, u_s) + u_s$, 
+$\kappa_N(\xhat, x_s, u_s) = 
+\mathbf{\tilde{u}}^0(0;\xhat, x_s, u_s) + u_s$, 
 which is applied to the plant. This feedback law is a function of the 
@@
 function is continuous and satisfies 
-$c_1\vert x \vert^2 \leq V_N^0(x) \leq c_2\vert x \vert^2$
-and $V_N^0(x^+) - V_N^0(x) \leq -c_1\vert x \vert^2$ 
+$c_1\norm{x}^2 \leq V_N^0(x) \leq c_2\norm{x}^2$
+and $V_N^0(x^+) - V_N^0(x) \leq -c_1\norm{x}^2$ 
 for some $c_2 \geq c_1 > 0$.
 
-Assume that a state estimate ($\hat{x}$) is
+Assume that a state estimate ($\xhat$) is
 used by the NN to compute the control. 
@@
 \begin{align} \label{eq:perturbed_sys}
-    \hat{x}^+ = A\hat{x} + B\kappa_N(\hat{x}) + Be_{NN}(\hat{x}) + w - Ae + e^+
+    \xhat^+ = A\xhat + B\kappa_N(\xhat) + Be_{NN}(\xhat) + w - Ae + e^+
 \end{align}
-in which $\hat{x} = x + e$ is the state estimate, 
+in which $\xhat = x + e$ is the state estimate, 
 $w$ is a process disturbance, 
@@
 current and next timestep respectively. 
-We use $\phi_d(k;\hat{x})$ to denote a solution of the perturbed system  at time
-$k$ starting from an initial state $\hat{x}$; and $\phi(k;x)$ to denote a
+We use $\phi_d(k;\xhat)$ to denote a solution of the perturbed system  at time
+$k$ starting from an initial state $\xhat$; and $\phi(k;x)$ to denote a
 solution  of the nominal system starting  from an initial state $x$ when the
@@
 such that for all disturbance sequences
-satisfying $\vert\vert \mathbf{e}_{k+1} \vert\vert \leq \delta_1$,
-$\vert\vert \mathbf{w}_k \vert\vert \leq \delta_2$,
-and $\vert e_{NN}(\hat{x}) \vert \leq \delta_3$,
-for all $\hat{x}$ in the set $S := \textnormal{lev}_{\rho} \ V_N^0(\hat{x})$,
+satisfying $\norm{\norm{\mathbf{e}_{k+1}}} \leq \delta_1$,
+$\norm{\norm{\mathbf{w}_k}} \leq \delta_2$,
+and $\norm{e_{NN}(\xhat)} \leq \delta_3$,
+for all $\xhat$ in the set $S := \textnormal{lev}_{\rho} \ V_N^0(\xhat)$,
 we have the following bound 
-$\vert \phi_d(k; \hat{x}) \vert \leq \beta(\vert \hat{x} \vert, k) 
-+ \alpha_e(\vert \vert\mathbf{e}_{k+1} \vert \vert) + 
-\alpha_w(\vert \vert \mathbf{w}_k \vert \vert) + 
+$\norm{\phi_d(k; \xhat)} \leq \beta(\norm{\xhat}, k) 
++ \alpha_e(\norm{\norm{\mathbf{e}_{k+1}}}) + 
+\alpha_w(\norm{\norm{\mathbf{w}_k}}) + 
 \alpha_n(\bar{e}_{NN})$, 
 in which 
-$\bar{e}_{NN} = \textnormal{max}_{\hat{x} \in S} \vert e_{NN}(\hat{x}) \vert$.
+$\bar{e}_{NN} = \textnormal{max}_{\xhat \in S} \norm{e_{NN}(\xhat)}$.
 \end{thm}
@@
 The closed-loop states in this case have the bound
-$\vert \phi(k; x) \vert \leq \beta(\vert x \vert, k) + 
+$\norm{\phi(k; x)} \leq \beta(\norm{x}, k) + 
 \alpha_n(\bar{e}_{NN})$. Any additional value of 
@@
     \begin{align*}        
-    \Lambda_k = \dfrac{1}{k}\sum_{t=1}^{k} & \big(\vert x(t) - x_{s} (t) \vert^2_{Q} \\
-        & + \vert u(t) - u_{s} (t) \vert^2_{R} + \vert \Delta u(t) \vert^2_{S}\big)         
+    \Lambda_k = \dfrac{1}{k}\sum_{t=1}^{k} & \big(\norm{x(t) - x_{s} (t)}^2_{Q} \\
+        & + \norm{u(t) - u_{s} (t)}^2_{R} + \norm{\Delta u(t)}^2_{S}\big)         
     \end{align*}
@@
 $x \in X$ and $w(i) \in \bbW$, $i \in \bbI_{0:k-1}$, 
-$\vert \psi(k; x, \mathbf{w}_k) \vert \leq \beta(\vert x\vert, k) 
-+ \sigma(\vert \vert \mathbf{w}_k\vert \vert)$, in which 
+$\norm{\psi(k; x, \mathbf{w}_k)} \leq \beta(\norm{x}, k) 
++ \sigma(\norm{\norm{\mathbf{w}_k}})$, in which 
 $\psi(k; x, \mathbf{w}_k)$ is the solution of the system 
@@
 \begin{align*}
-    \alpha_1(\vert x \vert) \leq & V(x) \leq \alpha_2(\vert x \vert) \\
-    V(f(x, w)) &- V(x) \leq -\alpha_3(\vert x \vert) + \sigma(\vert w \vert)
+    \alpha_1(\norm{x}) \leq & V(x) \leq \alpha_2(\norm{x}) \\
+    V(f(x, w)) &- V(x) \leq -\alpha_3(\norm{x}) + \sigma(\norm{w})
 \end{align*}
@@
     such that for all $x \in C$ and $y \in D$, we have that 
-    $\vert f(x) - f(y) \vert \leq \sigma(\vert x-y \vert)$.
+    $\norm{f(x) - f(y)} \leq \sigma(\norm{x-y})$.
 \end{prop}
@@
 such that the set $S$ is robustly positive invariant. Then, we 
-show that $V_N^0(\hat{x})$ is an ISS Lyapunov function for 
+show that $V_N^0(\xhat)$ is an ISS Lyapunov function for 
 the perturbed system \eqref{eq:perturbed_sys} on this set $S$. Denote 
-$\tilde{x}^+ = A\hat{x} + B\kappa_N(\hat{x})$ as the nominal 
+$\tilde{x}^+ = A\xhat + B\kappa_N(\xhat)$ as the nominal 
 state evolution using the optimal MPC controller, 
-and $d(k) = [ e_{NN}(\hat{x}(k))'B', w(k)', e(k)', e(k+1)']'$
+and $d(k) = [ e_{NN}(\xhat(k))'B', w(k)', e(k)', e(k+1)']'$
 as the combination of all the disturbances at a given time $k$.
@@
 To show robust positive invariance of $S$,  
-we establish that if $V_N^0(\hat{x}) \leq \rho$, 
-then $V_N^0(\hat{x}^+) \leq \rho$.
+we establish that if $V_N^0(\xhat) \leq \rho$, 
+then $V_N^0(\xhat^+) \leq \rho$.
 Since the optimal 
-cost function ($V_N^0(\hat{x})$) is continuous,
-using $\bbR^n$ as the closed set ($\hat{x}^+ \in \bbR^n$) 
+cost function ($V_N^0(\xhat)$) is continuous,
+using $\bbR^n$ as the closed set ($\xhat^+ \in \bbR^n$) 
 and $S$ as the compact set ($\tilde{x} \in S$),
@@
 \begin{align}
-    \vert V_N^0(\hat{x}^+) - V_N^0(\tilde{x}^+) \vert &\leq 
-    \sigma_1(\vert \hat{x}^+ - \tilde{x}^+ \vert)  \nonumber  \\
+    \norm{V_N^0(\xhat^+) - V_N^0(\tilde{x}^+)} &\leq 
+    \sigma_1(\norm{\xhat^+ - \tilde{x}^+})  \nonumber  \\
     &\leq 
-   \sigma_1(\vert B e_{NN}(\hat{x}) \vert + \vert w \vert 
+   \sigma_1(\norm{B e_{NN}(\xhat)} + \norm{w} 
    \nonumber \\
-   & + \vert A\vert\vert e \vert +  \vert e^+ \vert) \nonumber \\
+   & + \norm{A}\norm{e} +  \norm{e^+}) \nonumber \\
      &\leq 
-   \sigma_1(\vert d \vert + \vert d \vert + \vert A \vert\vert d \vert + \vert d \vert) := \sigma_2(\vert d \vert)
+   \sigma_1(\norm{d} + \norm{d} + \norm{A}\norm{d} + \norm{d}) 
+   := \sigma_2(\norm{d})
    \label{eq:optimal_cost_bound}
 \end{align}
-in which $\sigma_2(s) := \sigma_1(\vert A\vert s +3s)$, and the last inequality 
-follows because $\vert a \vert \leq \vert [a', b']' \vert$, in which $a$ and $b$
+in which $\sigma_2(s) := \sigma_1(\norm{A} s +3s)$, and the last inequality 
+follows because $\norm{a} \leq \norm{[a', b']'}$, in which $a$ and $b$
 are both vectors, and $\sigma_2(\cdot) \in \mathcal{K}_{\infty}$.
 We partition $S$ in outer and inner parts based on 
-the value of the optimal cost $V_N^0(\hat{x})$, and bound the 
+the value of the optimal cost $V_N^0(\xhat)$, and bound the 
 combination of disturbances $d$ in each part 
-such that $V_N^0(\hat{x}^+) \leq \rho$. \\
-Case 1: $\rho/2 \leq V_N^0(\hat{x}) \leq \rho $. Using the 
+such that $V_N^0(\xhat^+) \leq \rho$. \\
+Case 1: $\rho/2 \leq V_N^0(\xhat) \leq \rho $. Using the 
 upper bound on the optimal cost, we have 
-$\rho/(2c_2) \leq \vert \hat{x} \vert^2$ for all $\hat{x}$ 
+$\rho/(2c_2) \leq \norm{\xhat}^2$ for all $\xhat$ 
 in this part of $S$. To analyze the worst-case disturbance, 
 we have from the equation \eqref{eq:optimal_cost_bound} that 
-$V_N^0(\hat{x}^+) \leq V_N^0(\tilde{x}^+) + \sigma_2(\vert d \vert) $.
+$V_N^0(\xhat^+) \leq V_N^0(\tilde{x}^+) + \sigma_2(\norm{d}) $.
 From nominal MPC cost decrease, we obtain  
-$V_N^0(\hat{x}^+) \leq V_N^0(\hat{x}) - c_1\vert \hat{x} \vert^2 + \sigma_2(\vert d \vert)$. Thus, if $\sigma_2(\vert d \vert) \leq \rho c_1/(2c_2)$, 
+$V_N^0(\xhat^+) \leq V_N^0(\xhat) - c_1\norm{\xhat}^2 + 
+\sigma_2(\norm{d})$. Thus, if $\sigma_2(\norm{d}) \leq \rho c_1/(2c_2)$, 
 at all times in this outer part of $S$, we have 
-$V_N^0(\hat{x}^+) \leq \rho$. \\
-Case 2: $V_N^0(\hat{x}) \leq \rho/2 $. From 
+$V_N^0(\xhat^+) \leq \rho$. \\
+Case 2: $V_N^0(\xhat) \leq \rho/2 $. From 
 equation \eqref{eq:optimal_cost_bound} and nominal MPC 
 cost decrease, we have for this part of $S$ that 
-$V_N^0(\hat{x}^+) \leq \rho/2 + \sigma_2(\vert d \vert)$.
-Thus, if $\sigma_2(\vert d \vert) \leq \rho/2$, 
+$V_N^0(\xhat^+) \leq \rho/2 + \sigma_2(\norm{d})$.
+Thus, if $\sigma_2(\norm{d}) \leq \rho/2$, 
 at all times in this inner part of $S$, we have 
-$V_N^0(\hat{x}^+) \leq \rho$.
+$V_N^0(\xhat^+) \leq \rho$.
 
 Therefore, if 
-$\vert d \vert \leq \textnormal{min} \{ \sigma_2^{-1}(\rho c_1/(2c_2)), 
+$\norm{d} \leq \textnormal{min} \{ \sigma_2^{-1}(\rho c_1/(2c_2)), 
 \sigma_2^{-1}(\rho/2)\} := \delta_{\textnormal{max}}$ 
@@
 $\delta_{\textnormal{max}}/4$ each, 
-and $\delta_3$ is $\delta_{\textnormal{max}}/(4\vert B \vert)$.
+and $\delta_3$ is $\delta_{\textnormal{max}}/(4\norm{B})$.
 The optimal MPC cost function satisfies
 \begin{align*}
-    V_N^0(\hat{x}^+) - V_N^0(\hat{x}) &\leq 
-    -c_1\vert \hat{x} \vert^2 + \sigma_2(\vert d \vert)
+    V_N^0(\xhat^+) - V_N^0(\xhat) &\leq 
+    -c_1\norm{\xhat}^2 + \sigma_2(\norm{d})
 \end{align*}
 in the robustly positive invariant set $S$ and
-the disturbance set $\vert d \vert \leq \delta_{\textnormal{max}}$.
+the disturbance set $\norm{d} \leq \delta_{\textnormal{max}}$.
 Since the optimal cost function also satisfies the upper and lower bounds
-$c_1\vert x \vert^2 \leq V_N^0(x) \leq c_2\vert x \vert^2$,
+$c_1\norm{x}^2 \leq V_N^0(x) \leq c_2\norm{x}^2$,
 from the Definition \ref{def:iss_lyapunov_func},
@@
 $\sigma(\cdot) \in \mathcal{K}$, such that 
-$\vert \phi_d(k; \hat{x}) \vert \leq \beta(\vert \hat{x} \vert, k) 
-+ \sigma(\vert\vert \mathbf{d}_k\vert\vert)$. Using the Proposition
+$\norm{\phi_d(k; \xhat)} \leq \beta(\norm{\xhat}, k) 
++ \sigma(\norm{\norm{\mathbf{d}_k}})$. Using the Proposition
 \ref{prop:Kfunction_inequality} and the definition of 
@@
 \begin{align*}
-    \vert \phi_d(k; \hat{x}) \vert & \leq \beta(\vert \hat{x} \vert, k)
-    + \sigma(\vert B\vert\bar{e}_{NN} + \vert \vert \mathbf{w}_k \vert \vert
-    + 2\vert \vert \mathbf{e}_{k+1} \vert \vert) \\
-     & \leq \beta(\vert \hat{x} \vert, k) \\
-    & +\sigma(3\vert B\vert\bar{e}_{NN}) + 
-    \sigma(3\vert \vert \mathbf{w}_k \vert \vert)
-    + \sigma(6\vert \vert \mathbf{e}_{k+1} \vert\vert)
+    \norm{\phi_d(k; \xhat)} & \leq \beta(\norm{\xhat}, k)
+    + \sigma(\norm{B}\bar{e}_{NN} + \norm{\norm{\mathbf{w}_k}}
+    + 2\norm{\norm{\mathbf{e}_{k+1}}}) \\
+     & \leq \beta(\norm{\xhat}, k) \\
+    & +\sigma(3\norm{B}\bar{e}_{NN}) + 
+    \sigma(3\norm{\norm{\mathbf{w}_k}})
+    + \sigma(6\norm{\norm{\mathbf{e}_{k+1}}})
 \end{align*}
@@
 $\alpha_w(s) := \sigma(3s)$,
-$\alpha_n(s) := \sigma(3\vert B\vert s)$, and 
+$\alpha_n(s) := \sigma(3\norm{B} s)$, and 
 $\alpha_e(\cdot), \alpha_w(\cdot), \alpha_n(\cdot) \in \mathcal{K}$.

### 2020-11-03 paper.tex
sat function.
linewidth and things.

@@
 
+\newcommand{\underl}[1]{\underline{#1}}
+\newcommand{\overl}[1]{\overline{#1}}
+\newcommand{\satlb}[1]{\textnormal{sat}(#1, \underline{#1}, \overline{#1})}
+\newcommand{\tif}{\textnormal{if}}
+
 \graphicspath{{./}{./figures/}{./figures/paper/}}
@@
 \begin{abstract}
-The design of neural networks (NNs) is presented 
-for treating large, linear model predictive control (MPC) applications that 
-are out of reach with available quadratic programming (QP)
-solvers. First, we introduce a new feedforward
-network architecture that enables practitioners to 
-obtain offset-free closed-loop performance with NNs.
-Second, we discuss the data generation procedure 
-to sample the relevant state space for the network 
-training based on anticipated online setpoint changes and
-plant disturbances. Third, we use the 
-input-to-state stability results 
-available in the MPC literature
-and establish robustness 
-properties of NN controllers.
-Finally, we present illustrative
-simulation studies on 
-process control examples. 
-We apply the NN design approach
+The design of neural networks (NNs) is presented for treating large, linear
+model predictive control (MPC) applications that are out of reach with available
+quadratic programming (QP) solvers. First, we introduce a new feedforward
+network architecture that enables practitioners to obtain offset-free
+closed-loop performance with NNs. Second, we discuss the data generation
+procedure to sample the relevant state space for the network training based on
+anticipated online setpoint changes and plant disturbances. Third, we use the
+input-to-state stability results available in the MPC literature and establish
+robustness properties of NN controllers. Finally, we present illustrative
+simulation studies on process control examples. We apply the NN design approach
 and compare the performance with online QP based MPC on an industrial crude
-distillation unit model with 252 states, 32 control inputs, 
-and a control-sample horizon length of 140. Parallel computing 
-is used for data generation and graphical processing units are used for
-network training. All the anticipated plant operational scenarios 
-with setpoints and disturbances that may change
-during operation must be sampled for NN training.
-After the offline design phase, 
-NNs execute MPC 
-three to five orders of magnitude faster
-than an available QP solver with less than $1\%$
-loss in the closed-loop performance.
+distillation unit model with 252 states, 32 control inputs, and a control-sample
+horizon length of 140. Parallel computing is used for data generation and
+graphical processing units are used for network training. All the anticipated
+plant operational scenarios with setpoints and disturbances that may change
+during operation must be sampled for NN training. After the offline design
+phase, NNs execute MPC three to five orders of magnitude faster than an
+available QP solver with less than $1\%$ loss in the closed-loop performance.
 \end{abstract}
@@
 
-Model predictive control (MPC) is an online 
-optimization based feedback control technology. A dynamic model 
-of the plant is used to make forecasts of the plant measurements
-in response to the actuator movements, and an optimization
-is solved in real time to determine the optimal actuator
-move to be applied to the plant. For linear plant models, 
-the optimization to be solved online is a quadratic program (QP).
-The development 
-of efficient QP algorithms 
-\citep*{kouzoupis:frison:zanelli:diehl:2018, wright:2019}
-allowed practitioners to apply MPC
-in the process industries \citep*{qin:badgwell:2003, lahiri:2017}.
-
-An alternative strategy to 
-real time optimization for the deployment of MPC 
-is to characterize the MPC feedback law
-as a piecewise affine function defined on 
-polyhedral partitions of the state space, 
-and use the feedback law online
-\citep*{bemporad:morari:dua:pistikopoulos:2002, 
-seron:goodwin:dedona:2003}.
-The real time computation in this approach is 
-reduced to a table look-up in the state space
-based on the current value of parameters 
-in the QP such as the state estimate and some 
-steady-state targets that are computed for 
-offset-free control. The number of polyhedral 
-partitions of the state space grows exponentially
-with model dimensions, however, which prohibits
-the deployment of this strategy on large-scale 
-systems.
-
-The MPC feedback law can be approximated using 
-parametric functions such as polynomials
-\citep*{kvasnica:lofberg:fikar:2011}, 
-various types of piecewise affine functions
-\citep*{bemporad:oliveri:poggi:storace:2011, wen:ma:ydstie:2009},
-and neural networks (NNs) \citep*{cavagnari:magni:scattolini:1999}.
-Among the
-function approximators, NNs that use the rectified linear unit 
-(ReLU) as the activation function 
-have gained attention recently 
-\citep*{chen:saulnier:atanasov:lee:kumar:pappas:morari:2018, 
-karg:lucia:2020, paulson:mesbah:2020, lovelett:dietrich:lee:kevrekidis:2020}
-to approximate
-the MPC feedback law due to their ability to represent complex 
-piecewise affine functions
-\citep*{montufar:pascanu:cho:bengio:2014}
-and execute MPC faster in real time than QP solvers. 
-The proposed NN design approach in 
-these works is to generate training 
-data for the NN by solving QPs offline
-for a set of feasible states of the QP, use the
-collected data to train a standard feedforward network, then 
-use the trained NN as the feedback controller online.
-
-To make progress in the size of control applications 
-achievable with MPC, large problems
-in which QP solvers fail to deliver the 
-control in the available sample time should be addressed.
-The scalability of the NN approach
-to such problems with large model dimensions and 
-control horizon length in the QP
-has not been demonstrated. Two issues arise 
-in these problems:
-i) In a large dimensional state space,   
-the entire set of feasible states of the QP cannot be sampled  
-densely for the NN training. This issue is 
-a form of the well-known curse of dimensionality.
-ii) One may sample the state space partially
-to avoid this problem, but the time required for the 
-data generation can still be impractical
-due to the long time required to solve a QP 
-for each sampled state. 
-We demonstrate in this article by case studies that
-this latter issue can be resolved for a large size 
-of problems with parallel 
-computing, and the former issue by sampling the 
-state space for typical plant operational scenarios.
-The following feature must be present in the large-scale
-application of interest for the partial sampling scheme 
-proposed in this article to be applicable:
-for a particular operating mode of the plant, 
-the number of frequently changing setpoints
-and large magnitude disturbances 
-must be reasonably small 
-such that the entire large
-dimensional state space is not visited during that
-operation mode. 
-The MPC feedback law 
-can then be reliably approximated using NNs
-for the different modes of plant operations driven by  
-their respective set
-of setpoint changes and disturbances.
-
-From the above viewpoint, 
-this article discusses the design of NNs
-as an alternative to real time optimization in MPC, 
-with an emphasis on large applications which 
-are challenging with QP solvers. 
-The focus of this article is on setpoint tracking 
-MPC problems relevant for deployment in the process industries.
-We present a new feedforward network architecture to obtain
-offset-free closed-loop performance with the NNs.
-Additionally, we use the input-to-state
-stability results
-available in the MPC literature, and establish
-conditions under which the NN controller 
-is robust to state estimation errors and process 
-disturbances. We present case studies 
-on process control examples that
-demonstrate the scalability of the proposed NN design 
-approach.
-
-The related work by \cite*{chen:wang:atanasov:kumar:morari:2019}
-demonstrates the scalability of NNs 
-to approximate the MPC feedback law on systems with 
-state dimensions up to 36. The setpoint 
-tracking offset-free MPC problem and state 
-dimensions up to 250 considered in this 
-article is not addressed in that work. 
+Model predictive control (MPC) is an online optimization based feedback control
+technology. A dynamic model of the plant is used to make forecasts of the plant
+measurements in response to the actuator movements, and an optimization is
+solved in real time to determine the optimal actuator move to be applied to the
+plant. For linear plant models, the optimization to be solved online is a
+quadratic program (QP). The development of efficient QP algorithms
+\citep*{kouzoupis:frison:zanelli:diehl:2018, wright:2019} allowed practitioners
+to apply MPC in the process industries \citep*{qin:badgwell:2003, lahiri:2017}.
+
+An alternative strategy to real time optimization for the deployment of MPC is
+to characterize the MPC feedback law as a piecewise affine function defined on
+polyhedral partitions of the state space, and use the feedback law online
+\citep*{bemporad:morari:dua:pistikopoulos:2002, seron:goodwin:dedona:2003}. The
+real time computation in this approach is reduced to a table look-up in the
+state space based on the current value of parameters in the QP such as the state
+estimate and some steady-state targets that are computed for offset-free
+control. The number of polyhedral partitions of the state space grows
+exponentially with model dimensions, however, which prohibits the deployment of
+this strategy on large-scale systems.
+
+The MPC feedback law can be approximated using parametric functions such as
+polynomials \citep*{kvasnica:lofberg:fikar:2011}, various types of piecewise
+affine functions \citep*{bemporad:oliveri:poggi:storace:2011,
+wen:ma:ydstie:2009}, and neural networks (NNs)
+\citep*{cavagnari:magni:scattolini:1999}. Among the function approximators, NNs
+that use the rectified linear unit (ReLU) as the activation function have gained
+attention recently \citep*{chen:saulnier:atanasov:lee:kumar:pappas:morari:2018,
+karg:lucia:2020, paulson:mesbah:2020, lovelett:dietrich:lee:kevrekidis:2020} to
+approximate the MPC feedback law due to their ability to represent complex
+piecewise affine functions \citep*{montufar:pascanu:cho:bengio:2014} and execute
+MPC faster in real time than QP solvers. The proposed NN design approach in
+these works is to generate training data for the NN by solving QPs offline for a
+set of feasible states of the QP, use the collected data to train a standard
+feedforward network, then use the trained NN as the feedback controller online.
+
+To make progress in the size of control applications achievable with MPC, large
+problems in which QP solvers fail to deliver the control in the available sample
+time should be addressed. The scalability of the NN approach to such problems
+with large model dimensions and control horizon length in the QP has not been
+demonstrated. Two issues arise in these problems: i) In a large dimensional
+state space, the entire set of feasible states of the QP cannot be sampled
+densely for the NN training. This issue is a form of the well-known curse of
+dimensionality. ii) One may sample the state space partially to avoid this
+problem, but the time required for the data generation can still be impractical
+due to the long time required to solve a QP for each sampled state. We
+demonstrate in this article by case studies that this latter issue can be
+resolved for a large size of problems with parallel computing, and the former
+issue by sampling the state space for typical plant operational scenarios. The
+following feature must be present in the large-scale application of interest for
+the partial sampling scheme proposed in this article to be applicable: for a
+particular operating mode of the plant, the number of frequently changing
+setpoints and large magnitude disturbances must be reasonably small such that
+the entire large dimensional state space is not visited during that operation
+mode. The MPC feedback law can then be reliably approximated using NNs for the
+different modes of plant operations driven by their respective set of setpoint
+changes and disturbances.
+
+From the above viewpoint, this article discusses the design of NNs as an
+alternative to real time optimization in MPC, with an emphasis on large
+applications which are challenging with QP solvers. The focus of this article is
+on setpoint tracking MPC problems relevant for deployment in the process
+industries. We present a new feedforward network architecture to obtain
+offset-free closed-loop performance with the NNs. Additionally, we use the
+input-to-state stability results available in the MPC literature, and establish
+conditions under which the NN controller is robust to state estimation errors
+and process disturbances. We present case studies on process control examples
+that demonstrate the scalability of the proposed NN design approach.
+
+The related work by \cite*{chen:wang:atanasov:kumar:morari:2019} demonstrates
+the scalability of NNs to approximate the MPC feedback law on systems with state
+dimensions up to 36. The setpoint tracking offset-free MPC problem and state
+dimensions up to 250 considered in this article is not addressed in that work. 
 \cite*{drgona:picard:kvasnica:helsen:2018}
-take a different approach for the scalability
-of NN controllers, in which 
-the dimensionality of the parameters in the MPC QP is first 
-reduced using principal component analysis, and the 
-NN controller is developed in a low dimensional state space.
-
-The rest of this article is organized as follows. 
-In the next section, we briefly review 
-offset-free linear MPC. 
-In Section \ref{sec:controller_design},
-we discuss the NN 
-controller design procedure.
-We present the robustness property
-of NNs in Section \ref{sec:robustness}.
-Then, we present simulation studies
-on two large process control examples
-in Section \ref{sec:simulation_studies}
-and conclude at the end of this article.
-
-Notation. The symbols $\bbI$ and $\bbR$ are 
-used to denote integers and reals respectively. 
-Subscripts denote restrictions 
-(e.g., $\bbR_{\geq 0}$ for nonnegative reals and 
-$\bbI_{a:b}$ for integers in the 
-closed interval $[a, b]$). The Euclidean norm 
-is denoted by $\norm{\cdot}$. A function 
-$\alpha : \bbR_{\geq 0} \rightarrow \bbR_{\geq 0}$
-is of class $\mathcal{K}$ if it is continuous, zero 
-at zero, and strictly increasing. This function is of class 
-$\mathcal{K}_{\infty}$ if it is of class $\mathcal{K}$
-and unbounded ($\alpha(s) \rightarrow \infty$ as 
-$s \rightarrow \infty$). A function
-$\beta : \bbR_{\geq 0} \times \bbI_{\geq 0} \rightarrow \bbR_{\geq 0}$
-is of class $\mathcal{KL}$ if it is continuous,
-for each $k \in \bbI_{\geq 0}$, $\beta(\cdot, k)$ is of class $\mathcal{K}$,
-and for each $s \geq 0$, $\beta(s, \cdot)$ is nonincreasing
-and satisfies $\textnormal{lim}_{k \rightarrow \infty} \beta(s, k) = 0$.
-Given $V : X \rightarrow \bbR_{\geq 0}$ and $\tau > 0$, define 
-$\textnormal{lev}_{\tau} V = \{ x \in X \mid V(x) \leq \tau \}$.
-Bold symbols, e.g., $\mathbf{d}$ denote sequences, 
-$d(k)$ denotes an element of $\mathbf{d}$ at time 
-$k \in \bbI_{\geq 0}$, and $\mathbf{d}_i$ 
-denotes the collection of elements of 
-$\mathbf{d}$ for $k \in \bbI_{0:i-1}$.
-Define $\norm{\norm{\mathbf{d}_i}} = 
-\textnormal{max}_{k \in \bbI_{0:i-1}} \norm{d(k)}$.
-For a given vector $a$, lower and upper bounds 
-($\underline{a}, \overline{a}$), define the saturation function 
-as $\textnormal{sat}(a, \underline{a}, \overline{a}) = 
-\{ a \ \textnormal{if} \ \underline{a} \leq a \leq \overline{a}; 
-\underline{a} \ \textnormal{if} \ a < \underline{a};
-\overline{a} \ \textnormal{if} \ \overline{a} < a \}$.
+take a different approach for the scalability of NN controllers, in which the
+dimensionality of the parameters in the MPC QP is first reduced using principal
+component analysis, and the NN controller is developed in a low dimensional
+state space.
+
+The rest of this article is organized as follows. In the next section, we
+briefly review offset-free linear MPC. In Section \ref{sec:controller_design},
+we discuss the NN controller design procedure. We present the robustness
+property of NNs in Section \ref{sec:robustness}. Then, we present simulation
+studies on two large process control examples in Section
+\ref{sec:simulation_studies} and conclude at the end of this article.
+
+Notation. The symbols $\bbI$ and $\bbR$ are used to denote integers and reals
+respectively. Subscripts denote restrictions (e.g., $\bbR_{\geq 0}$ for
+nonnegative reals and $\bbI_{a:b}$ for integers in the closed interval $[a,
+b]$). The Euclidean norm is denoted by $\norm{\cdot}$. A function $\alpha :
+\bbR_{\geq 0} \rightarrow \bbR_{\geq 0}$ is of class $\mathcal{K}$ if it is
+continuous, zero at zero, and strictly increasing. This function is of class
+$\mathcal{K}_{\infty}$ if it is of class $\mathcal{K}$ and unbounded ($\alpha(s)
+\rightarrow \infty$ as $s \rightarrow \infty$). A function $\beta : \bbR_{\geq
+0} \times \bbI_{\geq 0} \rightarrow \bbR_{\geq 0}$ is of class $\mathcal{KL}$ if
+it is continuous, for each $k \in \bbI_{\geq 0}$, $\beta(\cdot, k)$ is of class
+$\mathcal{K}$, and for each $s \geq 0$, $\beta(s, \cdot)$ is nonincreasing and
+satisfies $\textnormal{lim}_{k \rightarrow \infty} \beta(s, k) = 0$. Given $V :
+X \rightarrow \bbR_{\geq 0}$ and $\tau > 0$, define $\textnormal{lev}_{\tau} V =
+\{ x \in X \mid V(x) \leq \tau \}$. Bold symbols, e.g., $\mathbf{d}$ denote
+sequences, $d(k)$ denotes an element of $\mathbf{d}$ at time $k \in \bbI_{\geq
+0}$, and $\mathbf{d}_i$ denotes the collection of elements of $\mathbf{d}$ for
+$k \in \bbI_{0:i-1}$. Define $\norm{\norm{\mathbf{d}_i}} = \textnormal{max}_{k
+\in \bbI_{0:i-1}} \norm{d(k)}$. For a given vector $a$, lower and upper bounds
+($\underl{a}, \overl{a}$), define the saturation function as $\satlb{a} = \{ a \
+\tif \ \underl{a} \leq a \leq \overl{a}; \underl{a} \ \tif \ a < \underl{a};
+\overl{a} \ \tif \ \overl{a} < a \}$.
 
@@
 \subsection{Model}
-We consider a linear discrete time model augmented with an 
-integrating disturbance model \citep{pannocchia:rawlings:2003}
+We consider a linear discrete time model augmented with an integrating
+disturbance model \citep{pannocchia:rawlings:2003}
 \begin{align}\label{eq:ltimodel}
@@
 \end{align}
-in which $x \in \bbR^n$ is the state, 
-$u \in \bbR^m$ is the control input, and
-$d \in \bbR^d$ is the state of the disturbance
-model. The matrices $A \in \bbR^{n \times n}$, 
-$B \in \bbR^{n \times m}$,  
-$C \in \bbR^{p \times n}$ denote the actuator to measurement 
-model, and $B_d \in \bbR^{n \times d}$, $C_d \in \bbR^{p \times d}$
-is the disturbance model.
-The objective of the disturbance model
-is to remove offset in the controlled 
-plant measurements at steady
-state operations and maintain
-the controlled variables at their setpoints.
-We assume in the rest of this 
-article that a Kalman filter can be constructed to 
-estimate the model state ($\xhat$) and disturbance ($\dhat$) 
+in which $x \in \bbR^n$ is the state, $u \in \bbR^m$ is the control input, and
+$d \in \bbR^d$ is the state of the disturbance model. The matrices $A \in
+\bbR^{n \times n}$, $B \in \bbR^{n \times m}$,  
+$C \in \bbR^{p \times n}$ denote the actuator to measurement model, and $B_d \in
+\bbR^{n \times d}$, $C_d \in \bbR^{p \times d}$ is the disturbance model. The
+objective of the disturbance model is to remove offset in the controlled plant
+measurements at steady state operations and maintain the controlled variables at
+their setpoints. We assume in the rest of this article that a Kalman filter can
+be constructed to estimate the model state ($\xhat$) and disturbance ($\dhat$)
 from measurements.
@@
 \subsection{Target selector}
-Given the disturbance estimate, the
-input and controlled measurement setpoints,
+Given the disturbance estimate, the input and controlled measurement setpoints,
 we consider the following target selector QP
@@
 \end{align}
-in which
-($x_s, u_s$) is the 
-target steady-state pair,
-$r=Hy$ are the controlled measurements
-chosen as some subset 
-or a linear combination of all the measurements,
-($\underline{u}, \overline{u}$) are the 
-actuator bounds, and
-($u_{sp}, r_{sp}$) are the input and 
-controlled measurement setpoints.
-The equality constraint $r_{sp} = H(Cx_s + C_d\dhat)$
-can be difficult to satisfy exactly in real time 
-depending on the controlled measurement setpoint 
-and disturbance estimate. 
-Then, the hard setpoint equality constraint 
-can be relaxed and moved to the stage cost such 
-that the target selector computes a steady state
-to minimize the offset in the controlled measurements. 
-We assume for the simulation studies
-in this article that the input setpoint ($u_{sp}$)
-is fixed at some chosen steady state and 
-only the controlled measurement setpoint ($r_{sp}$) 
-changes in real time.
+in which ($x_s, u_s$) is the target steady-state pair, $r=Hy$ are the controlled
+measurements chosen as some subset or a linear combination of all the
+measurements, ($\underline{u}, \overline{u}$) are the actuator bounds, and
+($u_{sp}, r_{sp}$) are the input and controlled measurement setpoints. The
+equality constraint $r_{sp} = H(Cx_s + C_d\dhat)$ can be difficult to satisfy
+exactly in real time depending on the controlled measurement setpoint and
+disturbance estimate. Then, the hard setpoint equality constraint can be relaxed
+and moved to the stage cost such that the target selector computes a steady
+state to minimize the offset in the controlled measurements. We assume for the
+simulation studies in this article that the input setpoint ($u_{sp}$) is fixed
+at some chosen steady state and only the controlled measurement setpoint
+($r_{sp}$) changes in real time.
 
 \subsection{Regulator}
-Based on the state estimate and
-target steady-state pair,
-the following QP is solved to determine the 
-actuator move to be applied to the plant
+Based on the state estimate and target steady-state pair, the following QP is
+solved to determine the actuator move to be applied to the plant
 \begin{align} \label{eqn:regulator}
-    V_N(\tilde{x}(0), \mathbf{\tilde{u}}) = \dfrac{1}{2}\sum_{k=0}^{N-1} & \Big(|\tilde{x}(k)|^2_Q  + |\tilde{u}(k)|^2_R \Big) + \dfrac{1}{2}|\tilde{x}(N)|^2_P
+    V_N(\tilde{x}(0), \mathbf{\tilde{u}}) = \dfrac{1}{2}\sum_{k=0}^{N-1} & 
+    \Big(|\tilde{x}(k)|^2_Q  + |\tilde{u}(k)|^2_R \Big) + 
+    \dfrac{1}{2}|\tilde{x}(N)|^2_P
 \end{align}
@@
 \end{align}
-in which $\xhat$ is the state estimate after the current measurement,
-$N$ is the control 
-horizon length, and
-($\tilde{x}, \tilde{u}$) are the state and control 
-in deviation from the current steady-state targets ($x_s, u_s$). 
-The penalty matrix $P$ is chosen as the 
-optimal cost-to-go matrix of the unconstrained infinite horizon 
-linear quadratic problem.
-The decision variable in this 
-QP is the control sequence 
-$\mathbf{\tilde{u}} = [\tilde{u}(0)', \tilde{u}(1)', ..., \tilde{u}(N-1)']'$.
-The first move of the optimal solution is denoted 
-as the MPC feedback law,
-$\kappa_N(\xhat, x_s, u_s) = 
-\mathbf{\tilde{u}}^0(0;\xhat, x_s, u_s) + u_s$, 
-which is applied to the plant. This feedback law is a function of the 
-state estimate and target steady-state pair. A rate-of-change 
-penalty on the control can be imposed in the QP objective
-by augmenting the dynamic model with a surrogate state 
-for the control as discussed in \cite*{rao:rawlings:1999}. 
-In this case, 
-the control injected at the previous timestep
-($u_{-1}$) is supplied to the QP, 
-and the feedback law becomes a function of the previous control 
-as well in addition to the state estimate
-and target steady-state pair.
-
-Several algorithms have been proposed in the literature over
-the years to solve the above MPC regulator QP. 
-\cite*{kouzoupis:frison:zanelli:diehl:2018} and
-\cite*{wright:2019} give recent reviews on the development 
-of convex optimization algorithms to solve this linear MPC QP.
-For the simulation studies in this article, we eliminate the 
-state trajectory from the set of decision variables  
-and formulate a dense QP. The decision variable in the dense QP
-is the future control trajectory $\mathbf{\tilde{u}}$, 
-and the QP solver CVXOPT \citep*{vandenberghe:2010},
-which is tailored for dense problems
-is used for NN data generations and timing 
-comparisons with online QP based MPC.
-Any improvement in the QP formulation
-and solution algorithm is advantageous
-for both the online QP based MPC 
-and NN approaches
-as fast QP solvers reduce the 
-offline data generation time required for the 
-design of NNs.
+in which $\xhat$ is the state estimate after the current measurement, $N$ is the
+control horizon length, and ($\tilde{x}, \tilde{u}$) are the state and control
+in deviation from the current steady-state targets ($x_s, u_s$). The penalty
+matrix $P$ is chosen as the optimal cost-to-go matrix of the unconstrained
+infinite horizon linear quadratic problem. The decision variable in this QP is
+the control sequence $\mathbf{\tilde{u}} = [\tilde{u}(0)', \tilde{u}(1)', ...,
+\tilde{u}(N-1)']'$. The first move of the optimal solution is denoted as the MPC
+feedback law, $\kappa_N(\xhat, x_s, u_s) = \mathbf{\tilde{u}}^0(0;\xhat, x_s,
+u_s) + u_s$, which is applied to the plant. This feedback law is a function of
+the state estimate and target steady-state pair. A rate-of-change penalty on the
+control can be imposed in the QP objective by augmenting the dynamic model with
+a surrogate state for the control as discussed in \cite*{rao:rawlings:1999}. In
+this case, the control injected at the previous timestep ($u_{-1}$) is supplied
+to the QP, and the feedback law becomes a function of the previous control as
+well in addition to the state estimate and target steady-state pair.
+
+Several algorithms have been proposed in the literature over the years to solve
+the above MPC regulator QP. \cite*{kouzoupis:frison:zanelli:diehl:2018} and
+\cite*{wright:2019} give recent reviews on the development of convex
+optimization algorithms to solve this linear MPC QP. For the simulation studies
+in this article, we eliminate the state trajectory from the set of decision
+variables and formulate a dense QP. The decision variable in the dense QP is the
+future control trajectory $\mathbf{\tilde{u}}$, and the QP solver CVXOPT
+\citep*{vandenberghe:2010}, which is tailored for dense problems is used for NN
+data generations and timing comparisons with online QP based MPC. Any
+improvement in the QP formulation and solution algorithm is advantageous for
+both the online QP based MPC and NN approaches as fast QP solvers reduce the
+offline data generation time required for the design of NNs.
 
@@
 
-In the offset-free linear MPC algorithm discussed in the previous 
-section, the target selector QP is
-usually small compared to the 
-regulator QP, which consumes most of the online computation time. 
-Therefore we focus on designing a NN that approximates the 
-MPC feedback law ($\kappa_N(x, x_s, u_s)$)
-for an operationally relevant set of states and steady-state targets, 
-such that the NN 
-can be used online as the feedback controller 
-for the plant in place of solving the MPC regulator QP.
+In the offset-free linear MPC algorithm discussed in the previous section, the
+target selector QP is usually small compared to the regulator QP, which consumes
+most of the online computation time. Therefore we focus on designing a NN that
+approximates the MPC feedback law ($\kappa_N(x, x_s, u_s)$) for an operationally
+relevant set of states and steady-state targets, such that the NN can be used
+online as the feedback controller for the plant in place of solving the MPC
+regulator QP.
 
 \subsection{Structured neural network}
-An intuitive approach is to build a feedforward NN 
-that takes the triple ($x, x_s, u_s$) as its input 
-and outputs a control that is close to the optimal control. 
-This strategy has been proposed in \cite*{karg:lucia:2020} and 
+An intuitive approach is to build a feedforward NN that takes the triple ($x,
+x_s, u_s$) as its input and outputs a control that is close to the optimal
+control. This strategy has been proposed in \cite*{karg:lucia:2020} and 
 \cite*{chen:saulnier:atanasov:lee:kumar:pappas:morari:2018}
-for a single fixed steady state. The approach has not been 
-demonstrated to scale to the size of model dimensions 
-and the setpoint tracking 
-offset-free MPC problem considered in this article.
-An issue with this strategy 
-is that the NN has no knowledge about 
-the MPC feedback law, and can require large amounts
-of training data in large state dimensions 
-to obtain a reasonable controller. At a minimum,
-the MPC feedback law is such that at the origin, the 
-control action taken by the MPC controller is zero. For the 
-setpoint tracking MPC problem considered in this article, 
-the NN control law must be such that at steady-state 
-operations, the NN maintains the plant at the desired steady state
-such that the controlled measurements are at their setpoints.
-This structure implies $u_s = \kappa_{NN}(x = x_s, x_s, u_s)$, 
-in which we use $\kappa_{NN}(\cdot)$ to denote the NN control law.
-To incorporate this information in a NN, we introduce the following
-architecture
+for a single fixed steady state. The approach has not been demonstrated to scale
+to the size of model dimensions and the setpoint tracking offset-free MPC
+problem considered in this article. An issue with this strategy is that the NN
+has no knowledge about the MPC feedback law, and can require large amounts of
+training data in large state dimensions to obtain a reasonable controller. At a
+minimum, the MPC feedback law is such that at the origin, the control action
+taken by the MPC controller is zero. For the setpoint tracking MPC problem
+considered in this article, the NN control law must be such that at steady-state
+operations, the NN maintains the plant at the desired steady state such that the
+controlled measurements are at their setpoints. This structure implies $u_s =
+\kappa_{NN}(x = x_s, x_s, u_s)$, in which we use $\kappa_{NN}(\cdot)$ to denote
+the NN control law. To incorporate this information in a NN, we introduce the
+following architecture
 \begin{align}
@@
 \end{align}
-in which $g(a) = \textnormal{max} (0, a)$,
-is the ReLU operation applied element-wise on its vector input,
-$z_i$ is the output of each hidden layer
-of the network, $z_0$ is the input to the network, 
-$h$ is the number of hidden layers, 
-and $i \in \bbI_{1:h}$. 
-The parameters to be optimized using 
-training data are ($W_i, b_i$) 
-and $W_{h+1}$, which are matrices 
-of appropriate dimensions.
-At steady state, when $x=x_s$ in $z_0$, \eqref{eq:NNstruct}
-outputs $u_s$ regardless of the choice of weights.
-The software tensorflow 
-\citep{abadi:agarwal:barham:brevdo:et-al:2015} is used 
-for NN training purposes in this article,
-and the structured architecture can be built 
-with symbolic differentiation tools available in tensorflow.
-When a rate-of-change penalty on the control 
-is included in the regulator QP, 
-the input to the structured NN is modified to 
+in which $g(a) = \textnormal{max} (0, a)$, is the ReLU operation applied
+element-wise on its vector input, $z_i$ is the output of each hidden layer of
+the network, $z_0$ is the input to the network, $h$ is the number of hidden
+layers, and $i \in \bbI_{1:h}$. The parameters to be optimized using training
+data are ($W_i, b_i$) and $W_{h+1}$, which are matrices of appropriate
+dimensions. At steady state, when $x=x_s$ in $z_0$, \eqref{eq:NNstruct} outputs
+$u_s$ regardless of the choice of weights. The software tensorflow
+\citep{abadi:agarwal:barham:brevdo:et-al:2015} is used for NN training purposes
+in this article, and the structured architecture can be built with symbolic
+differentiation tools available in tensorflow. When a rate-of-change penalty on
+the control is included in the regulator QP, the input to the structured NN is
+modified to 
 \begin{align*}
@@
 \end{align*}
-in which $u_{-1}$ is the previous control applied 
-to the plant and the dimensions of the matrices 
-($W_i, b_i$) and $W_{h+1}$ 
-are appropriately adjusted. Even after 
-training, the control produced by 
-the NN may not satisfy the hard actuator constraints,
-and the saturation function 
-($\textnormal{sat}(\cdot, \underline{u}, \overline{u})$) 
-is applied to the output of the NN.
+in which $u_{-1}$ is the previous control applied to the plant and the
+dimensions of the matrices ($W_i, b_i$) and $W_{h+1}$ are appropriately
+adjusted. Even after training, the control produced by the NN may not satisfy
+the hard actuator constraints, and the saturation function
+($\textnormal{sat}(\cdot, \underline{u}, \overline{u})$) is applied to the
+output of the NN.
 
@@
 
-For one fixed steady state, the 
-set of feasible states for the MPC QP 
-defined by \eqref{eqn:regulator}-\eqref{eqn:regulator_constraints}
-is the entire $n$-dimensional state space $\bbR^n$.
-Additionally, the target steady state may change
-during the plant operation depending
-on the setpoint and disturbance estimate. 
-The domain of the MPC control law ($\kappa_N(x, x_s, u_s)$)
-is therefore the state space 
-$\bbR^{n}$ and the possible set of steady-state 
-target pairs. Sampling this entire domain of the
-MPC control law for NN training is difficult in large 
-dimension, and we show in Section 
-\ref{sec:simulation_studies} that it is
-also not required for practical applications.
-
-From a plant operations perspective,
-a majority of the large-scale petrochemical plants
-operate in a relatively small number of operating regimes
-or scenarios. Each operational scenario is driven 
-by a selected few controlled measurement 
-setpoints that depend on product demands
-and some large magnitude disturbances
-may change frequently, 
-while the setpoints for 
-the other measurements remain constant for long periods 
-of time. The states and steady-state targets 
-spanned in a closed-loop 
-operation per scenario is thereby considerably less 
-than the entire domain of the MPC control law.
-This typical operation of large chemical plants
-can be exploited, and we propose the 
-following data generation procedure 
-to perform offline simulations using the model to 
-collect the operationally 
-relevant set of ($x, x_s, u_s, \kappa_N(\cdot)$) 
-for the NN training:
+For one fixed steady state, the set of feasible states for the MPC QP defined by
+\eqref{eqn:regulator}-\eqref{eqn:regulator_constraints} is the entire
+$n$-dimensional state space $\bbR^n$. Additionally, the target steady state may
+change during the plant operation depending on the setpoint and disturbance
+estimate. The domain of the MPC control law ($\kappa_N(x, x_s, u_s)$) is
+therefore the state space $\bbR^{n}$ and the possible set of steady-state target
+pairs. Sampling this entire domain of the MPC control law for NN training is
+difficult in large dimension, and we show in Section
+\ref{sec:simulation_studies} that it is also not required for practical
+applications.
+
+From a plant operations perspective, a majority of the large-scale petrochemical
+plants operate in a relatively small number of operating regimes or scenarios.
+Each operational scenario is driven by a selected few controlled measurement
+setpoints that depend on product demands and some large magnitude disturbances
+may change frequently, while the setpoints for the other measurements remain
+constant for long periods of time. The states and steady-state targets spanned
+in a closed-loop operation per scenario is thereby considerably less than the
+entire domain of the MPC control law. This typical operation of large chemical
+plants can be exploited, and we propose the following data generation procedure
+to perform offline simulations using the model to collect the operationally
+relevant set of ($x, x_s, u_s, \kappa_N(\cdot)$) for the NN training:
 
 \begin{enumerate}
-    \item Determine the anticipated range of 
-    controlled measurement setpoint changes ($r_{sp}$)
-    to be made during the plant operational 
-    scenario. We denote 
-    this range of setpoints as ($\underline{r}_{sp}$, $\overline{r}_{sp}$).
-    \item Identify the set of physical disturbances ($d$) 
-    that may affect the plant and their range of values 
-    ($\underline{d}$, $\overline{d}$). We use 
-    physical disturbances in this article and assume that 
-    a disturbance model identification is performed 
-    to obtain the matrices $B_d$ and $C_d$.
-    \item Create pseudo random binary signals (PRBS)
-    of $r_{sp}$ and $d$ in their respective range of values.
-    \item Initialize the model at some chosen steady state.
-    Perform an offline simulation with the 
-    generated PRBS signals by solving the target
-    selector and regulator QPs for the transient states
-    and steady-state targets encountered in the simulation. 
+    \item Determine the anticipated range of controlled measurement setpoint
+    changes ($r_{sp}$) to be made during the plant operational scenario. We
+    denote this range of setpoints as ($\underline{r}_{sp}$,
+    $\overline{r}_{sp}$).
+    \item Identify the set of physical disturbances ($d$) that may affect the
+    plant and their range of values ($\underline{d}$, $\overline{d}$). We use
+    physical disturbances in this article and assume that a disturbance model
+    identification is performed to obtain the matrices $B_d$ and $C_d$.
+    \item Create pseudo random binary signals (PRBS) of $r_{sp}$ and $d$ in
+    their respective range of values.
+    \item Initialize the model at some chosen steady state. Perform an offline
+    simulation with the generated PRBS signals by solving the target selector
+    and regulator QPs for the transient states and steady-state targets
+    encountered in the simulation. 
 \end{enumerate}
 
-During the plant operation, it is expected 
-that the NN does not encounter 
-the same states and steady-state 
-target pairs used for the training. But similar
-values are expected since an 
-adequate model and appropriate 
-range of anticipated 
-setpoints and plant disturbances are 
-used for the data generation. 
-The NN during the closed-loop operation
-produces an interpolated actuator
-move that is applied to the plant.
-
-As we consider large
-MPC problem sizes in this article for the NN 
-controller, the data generation step
-can take impractical amounts of time if performed
-serially due to the long time required to solve 
-each QP (minutes). For these large problems, 
-several PRBS signals of the setpoints 
-and disturbances are generated and 
-multiple simulations are performed in parallel over 
-several cores in a CPU and across multiple CPUs as well.
-The data generated from all the simulations are collected
-and used for the NN training.
+During the plant operation, it is expected that the NN does not encounter the
+same states and steady-state target pairs used for the training. But similar
+values are expected since an adequate model and appropriate range of anticipated
+setpoints and plant disturbances are used for the data generation. The NN during
+the closed-loop operation produces an interpolated actuator move that is applied
+to the plant.
+
+As we consider large MPC problem sizes in this article for the NN controller,
+the data generation step can take impractical amounts of time if performed
+serially due to the long time required to solve each QP (minutes). For these
+large problems, several PRBS signals of the setpoints and disturbances are
+generated and multiple simulations are performed in parallel over several cores
+in a CPU and across multiple CPUs as well. The data generated from all the
+simulations are collected and used for the NN training.
 
 \subsection{Training}
-The following mean squared loss is minimized 
-to determine the weights for the NN controller
+The following mean squared loss is minimized to determine the weights for the NN
+controller
 \begin{align}
@@
 \end{align}
-in which $\theta$ is the set of parameters 
-to be optimized, ($W_i, b_i, W_{h+1}$)
-for $i \in \bbI_{1:h}$, subscript $j$ is used 
-to denote the training sample index, and 
-$N_{tr}$ is the number of training 
-samples. The stochastic optimization algorithm Adam 
-\citep*{kingma:ba:2014} is used for all the NN training
-performed in the case studies in this article. We do not 
-consider any regularization penalty in the training objective. 
-The recent empirical and theoretical works in the machine learning 
-literature have shown that NNs with large number of parameters 
-have good interpolation capabilities 
+in which $\theta$ is the set of parameters to be optimized, ($W_i, b_i,
+W_{h+1}$) for $i \in \bbI_{1:h}$, subscript $j$ is used to denote the training
+sample index, and $N_{tr}$ is the number of training samples. The stochastic
+optimization algorithm Adam \citep*{kingma:ba:2014} is used for all the NN
+training performed in the case studies in this article. We do not consider any
+regularization penalty in the training objective. The recent empirical and
+theoretical works in the machine learning literature have shown that NNs with
+large number of parameters have good interpolation capabilities
 \citep*{belkin:hsu:ma:mandal:2019, zhang:bengio:hardt:recht:vinyals:2017,
-arora:simon:hu:li:wang:2019, allen-zhu:li:liang:2019} 
-without any form of explicit regularization during training.
-The generalization abilities of 
-NNs for the architectures considered in this article
-is examined in the 
-simulations presented in the Section \ref{sec:simulation_studies}.
+arora:simon:hu:li:wang:2019, allen-zhu:li:liang:2019} without any form of
+explicit regularization during training. The generalization abilities of NNs for
+the architectures considered in this article is examined in the simulations
+presented in the Section \ref{sec:simulation_studies}.
 
@@
     \centering
-	\includegraphics[page=1, 
-		width=0.7\textwidth, 
+	\includegraphics[page=1, width=0.7\textwidth,
 		height=0.5\textheight]{cstrs_comparision_plots.pdf}    
@@
     \centering
-	\includegraphics[page=2, 
-		width=0.7\textwidth, 
-		height=0.5\textheight]{cstrs_comparision_plots.pdf}
-        \caption{Transient closed-loop controlled measurement 
-        trajectories of the CSTRs with 
-        flash separator example with the NN and optimal MPC controllers.}      \label{fig:cl_cstrs_outputs}
+	\includegraphics[page=2, width=0.7\textwidth,
+		height=0.5\textheight]{cstrs_comparision_plots.pdf} \caption{Transient
+		closed-loop controlled measurement trajectories of the CSTRs with flash
+		separator example with the NN and optimal MPC controllers.}
+		\label{fig:cl_cstrs_outputs}
 \end{figure*}
 
-The robustness property of NN controllers 
-is now presented. The optimal MPC controller
-designed for a nominal linear system ignoring disturbances
-is known to be inherently robust to bounded state 
-estimation errors and disturbances
-\citep*{heath:wills:2005, pannocchia:rawlings:wright:2011}. 
-The approximation
-error of the MPC feedback law by a NN can be viewed 
-as an additional disturbance, and the existing
-input-to-state stability
-results \citep*{sontag:wang:1995} are used to establish the 
-allowable approximation error in the NN for 
-the NN controller to be robust to disturbances. 
-Theorem \ref{thm:nnrobustness} states this 
-allowable approximation error and the size 
-of disturbances for which the NN controller is robust.
-
-The problem of steering the state of the linear 
-system (\ref{eq:ltimodel}) 
-to one fixed steady state ($x_s, u_s$) is considered. 
-For the analysis in this section, 
-the state and control are transformed in deviation variables 
-as $x := x - x_s$ and $u := u -u_s$,
-and define the control problem as regulation to the origin.
-The optimal MPC control law is denoted as $\kappa_N(x)$, 
-and the NN control law as
-$\kappa_{NN}(x) = \kappa_N(x) + e_{NN}(x)$, in which 
-$e_{NN}(x)$ is the approximation error 
-of the optimal control law by the network. Assume 
-in the analysis that the target steady state 
-is such that the unconstrained linear quadratic regulator (LQR)
-satisfies the actuator constraints 
-in a small neighborhood near the origin.
-
-As reviewed in \cite*{mayne:rawlings:rao:scokaert:2000},
-the nominal stability of MPC can be established
-using the optimal cost function ($V_N^0(x)$) of the QP
-as a Lyapunov function.
-The region of attraction of the closed-loop system 
-$x^+ = Ax + B\kappa_N(x)$ when no hard terminal region 
-constraint is included in the QP
-can be characterized as $\mathcal{X}_N = \textnormal{lev}_{Nd + \tau} \
-V_N^0(x)$ \citep*{limon:alamo:salas:camacho:2006}.
-The parameter $\tau$ is the level set
-parameter of the terminal region chosen as
-$\bbX_f = \textnormal{lev}_{\tau} \ x'Px$, and $d > 0$
-is a constant such that $\ell(x, u) \geq d$ for all 
-$x \in \bbR^n \setminus \bbX_f$ and 
-$\underline{u} \leq u+u_s \leq \overline{u}$.
-The parameter $\tau$ is chosen small enough such that
-the unconstrained LQR satisfies the actuator constraints 
-for all $x \in \bbX_f$. The optimal cost 
-function is continuous and satisfies 
-$c_1\norm{x}^2 \leq V_N^0(x) \leq c_2\norm{x}^2$
-and $V_N^0(x^+) - V_N^0(x) \leq -c_1\norm{x}^2$ 
-for some $c_2 \geq c_1 > 0$.
-
-Assume that a state estimate ($\xhat$) is
-used by the NN to compute the control. 
-To analyze robustness, the following perturbed
-linear system is considered
+The robustness property of NN controllers is now presented. The optimal MPC
+controller designed for a nominal linear system ignoring disturbances is known
+to be inherently robust to bounded state estimation errors and disturbances
+\citep*{heath:wills:2005, pannocchia:rawlings:wright:2011}. The approximation
+error of the MPC feedback law by a NN can be viewed as an additional
+disturbance, and the existing input-to-state stability results
+\citep*{sontag:wang:1995} are used to establish the allowable approximation
+error in the NN for the NN controller to be robust to disturbances. Theorem
+\ref{thm:nnrobustness} states this allowable approximation error and the size of
+disturbances for which the NN controller is robust.
+
+The problem of steering the state of the linear system (\ref{eq:ltimodel}) to
+one fixed steady state ($x_s, u_s$) is considered. For the analysis in this
+section, the state and control are transformed in deviation variables as $x := x
+- x_s$ and $u := u -u_s$, and define the control problem as regulation to the
+origin. The optimal MPC control law is denoted as $\kappa_N(x)$, and the NN
+control law as $\kappa_{NN}(x) = \kappa_N(x) + e_{NN}(x)$, in which $e_{NN}(x)$
+is the approximation error of the optimal control law by the network. Assume in
+the analysis that the target steady state is such that the unconstrained linear
+quadratic regulator (LQR) satisfies the actuator constraints in a small
+neighborhood near the origin.
+
+As reviewed in \cite*{mayne:rawlings:rao:scokaert:2000}, the nominal stability
+of MPC can be established using the optimal cost function ($V_N^0(x)$) of the QP
+as a Lyapunov function. The region of attraction of the closed-loop system $x^+
+= Ax + B\kappa_N(x)$ when no hard terminal region constraint is included in the
+QP can be characterized as $\mathcal{X}_N = \textnormal{lev}_{Nd + \tau} \
+V_N^0(x)$ \citep*{limon:alamo:salas:camacho:2006}. The parameter $\tau$ is the
+level set parameter of the terminal region chosen as $\bbX_f =
+\textnormal{lev}_{\tau} \ x'Px$, and $d > 0$ is a constant such that $\ell(x, u)
+\geq d$ for all $x \in \bbR^n \setminus \bbX_f$ and $\underline{u} \leq u+u_s
+\leq \overline{u}$. The parameter $\tau$ is chosen small enough such that the
+unconstrained LQR satisfies the actuator constraints for all $x \in \bbX_f$. The
+optimal cost function is continuous and satisfies $c_1\norm{x}^2 \leq V_N^0(x)
+\leq c_2\norm{x}^2$ and $V_N^0(x^+) - V_N^0(x) \leq -c_1\norm{x}^2$ for some
+$c_2 \geq c_1 > 0$.
+
+Assume that a state estimate ($\xhat$) is used by the NN to compute the control.
+To analyze robustness, the following perturbed linear system is considered
 \begin{align} \label{eq:perturbed_sys}
@@
 \end{align}
-in which $\xhat = x + e$ is the state estimate, 
-$w$ is a process disturbance, 
-and $e$, $e^+$ are the state estimation errors at the 
-current and next timestep respectively. 
-We use $\phi_d(k;\xhat)$ to denote a solution of the perturbed system  at time
-$k$ starting from an initial state $\xhat$; and $\phi(k;x)$ to denote a
-solution  of the nominal system starting  from an initial state $x$ when the
-state estimation errors and process disturbances are zero.
-
-\begin{thm} \label{thm:nnrobustness}
-For all $ 0 < \rho \leq Nd + \tau$, 
-there exist constants $\delta_1, \delta_2, \delta_3 > 0$, 
-functions $\beta(\cdot) \in \mathcal{K} \mathcal{L}$
-and $\alpha_e(\cdot) , \alpha_w(\cdot), \alpha_{n}(\cdot) \in \mathcal{K}$,
-such that for all disturbance sequences
+in which $\xhat = x + e$ is the state estimate, $w$ is a process disturbance,
+and $e$, $e^+$ are the state estimation errors at the current and next timestep
+respectively. We use $\phi_d(k;\xhat)$ to denote a solution of the perturbed
+system  at time $k$ starting from an initial state $\xhat$; and $\phi(k;x)$ to
+denote a solution  of the nominal system starting  from an initial state $x$
+when the state estimation errors and process disturbances are zero.
+
+\begin{thm} \label{thm:nnrobustness} For all $ 0 < \rho \leq Nd + \tau$, there
+exist constants $\delta_1, \delta_2, \delta_3 > 0$, functions $\beta(\cdot) \in
+\mathcal{K} \mathcal{L}$ and $\alpha_e(\cdot) , \alpha_w(\cdot),
+\alpha_{n}(\cdot) \in \mathcal{K}$, such that for all disturbance sequences
 satisfying $\norm{\norm{\mathbf{e}_{k+1}}} \leq \delta_1$,
-$\norm{\norm{\mathbf{w}_k}} \leq \delta_2$,
-and $\norm{e_{NN}(\xhat)} \leq \delta_3$,
-for all $\xhat$ in the set $S := \textnormal{lev}_{\rho} \ V_N^0(\xhat)$,
-we have the following bound 
-$\norm{\phi_d(k; \xhat)} \leq \beta(\norm{\xhat}, k) 
-+ \alpha_e(\norm{\norm{\mathbf{e}_{k+1}}}) + 
-\alpha_w(\norm{\norm{\mathbf{w}_k}}) + 
-\alpha_n(\bar{e}_{NN})$, 
-in which 
+$\norm{\norm{\mathbf{w}_k}} \leq \delta_2$, and $\norm{e_{NN}(\xhat)} \leq
+\delta_3$, for all $\xhat$ in the set $S := \textnormal{lev}_{\rho} \
+V_N^0(\xhat)$, we have the following bound $\norm{\phi_d(k; \xhat)} \leq
+\beta(\norm{\xhat}, k) + \alpha_e(\norm{\norm{\mathbf{e}_{k+1}}}) +
+\alpha_w(\norm{\norm{\mathbf{w}_k}}) + \alpha_n(\bar{e}_{NN})$, in which
 $\bar{e}_{NN} = \textnormal{max}_{\xhat \in S} \norm{e_{NN}(\xhat)}$.
@@
 
-The proof of this theorem along with the required 
-input-to-state stability definitions are provided 
-in Appendix \ref{app:theorem1}.
-In the nominal case, 
-the disturbance sequences $\mathbf{e}$ and $\mathbf{w}$ are zero.
-The closed-loop states in this case have the bound
-$\norm{\phi(k; x)} \leq \beta(\norm{x}, k) + 
-\alpha_n(\bar{e}_{NN})$. Any additional value of 
-the NN training is to reduce the worst 
-approximation error ($\bar{e}_{NN}$) 
-in the state space of interest and 
-reduce the bound on the closed-loop states.
+The proof of this theorem along with the required input-to-state stability
+definitions are provided in Appendix \ref{app:theorem1}. In the nominal case,
+the disturbance sequences $\mathbf{e}$ and $\mathbf{w}$ are zero. The
+closed-loop states in this case have the bound $\norm{\phi(k; x)} \leq
+\beta(\norm{x}, k) + \alpha_n(\bar{e}_{NN})$. Any additional value of the NN
+training is to reduce the worst approximation error ($\bar{e}_{NN}$) in the
+state space of interest and reduce the bound on the closed-loop states.
 
@@
 
-In this section, two case studies are presented 
-that demonstrate the 
-scalability of the proposed NN design approach.
-The closed-loop performance of NNs and computational benefits over 
-online QP based MPC are analyzed in these case studies.
-After the offline design of NNs,
-two types of validation simulations 
-are performed: (i) with setpoints 
-and disturbances not present in the training 
-data but within the same range of values used to 
-generate the training data, (ii) with extra setpoint 
-signals assumed to be
-unknown during the offline network design phase.
-Both these types of simulations are conducted to 
-analyze the interpolation and extrapolation 
-abilities of the NNs, and are referred subsequently as 
-simulations with \textit{expected} and \textit{unexpected} plant behaviors, respectively.
-
-The closed-loop performance of the 
-following alternative and 
-equivalently fast controllers as NNs are also compared
-in the validation simulations:
-(a) steady state controller (SS): the solution
-of the target selector is directly applied to the plant 
-$u = u_s$; (b) saturated linear quadratic regulator (satK):
-the unconstrained LQR gain 
-$K$ is computed and used in the control law 
-$u = \textnormal{sat}(K(x-x_s) + u_s, \underline{u}, \overline{u})$;
-(c) short horizon controller (SH): an MPC problem
-with a short control horizon is solved online;
-(d) Unstructured NN (NN-UNS): a standard feedforward network is 
-trained with the triple ($x, x_s, u_s$) as the input
-and then used as the feedback controller online.
+In this section, two case studies are presented that demonstrate the scalability
+of the proposed NN design approach. The closed-loop performance of NNs and
+computational benefits over online QP based MPC are analyzed in these case
+studies. After the offline design of NNs, two types of validation simulations
+are performed: (i) with setpoints and disturbances not present in the training
+data but within the same range of values used to generate the training data,
+(ii) with extra setpoint signals assumed to be unknown during the offline
+network design phase. Both these types of simulations are conducted to analyze
+the interpolation and extrapolation abilities of the NNs, and are referred
+subsequently as simulations with \textit{expected} and \textit{unexpected} plant
+behaviors, respectively.
+
+The closed-loop performance of the following alternative and equivalently fast
+controllers as NNs are also compared in the validation simulations: (a) steady
+state controller (SS): the solution of the target selector is directly applied
+to the plant $u = u_s$; (b) saturated linear quadratic regulator (satK): the
+unconstrained LQR gain $K$ is computed and used in the control law $u =
+\textnormal{sat}(K(x-x_s) + u_s, \underline{u}, \overline{u})$; (c) short
+horizon controller (SH): an MPC problem with a short control horizon is solved
+online; (d) Unstructured NN (NN-UNS): a standard feedforward network is trained
+with the triple ($x, x_s, u_s$) as the input and then used as the feedback
+controller online.
 
@@
 
-To gauge the performance of NNs in 
-the validation simulations, the offline
-computational effort required to build the NNs, 
-and the memory required for the deployment of NNs,
-the following metrics are examined:
+To gauge the performance of NNs in the validation simulations, the offline
+computational effort required to build the NNs, and the memory required for the
+deployment of NNs, the following metrics are examined:
 
@@
     \end{align*}
-    \item \% Performance loss = $100(\Lambda^{\textnormal{F}}_{N_{t}} - \Lambda^{\textnormal{MPC}}_{N_{t}})/\Lambda^{\textnormal{MPC}}_{N_{t}}$
+    \item \% Performance loss = $100(\Lambda^{\textnormal{F}}_{N_{t}} -
+    \Lambda^{\textnormal{MPC}}_{N_{t}})/\Lambda^{\textnormal{MPC}}_{N_{t}}$
     \item Average and worst-case speedups
@@
 Here, $N_t$ is the number of simulation time steps,  
-$\Lambda^{\textnormal{F}}_{N_{t}}$ and 
-$\Lambda^{\textnormal{MPC}}_{N_{t}}$
-are the average stage costs obtained 
-at the end of the simulation period by the 
-fast controllers and the MPC controller.
-The data generation and online timing comparisons are 
-performed on a computing cluster that has 
-several multi-core CPUs of clock speed 2.4GHz. 
-The NN trainings are performed on a 
-Tesla V100-SXM2 GPU that has 32 GB memory.
+$\Lambda^{\textnormal{F}}_{N_{t}}$ and $\Lambda^{\textnormal{MPC}}_{N_{t}}$ are
+the average stage costs obtained at the end of the simulation period by the fast
+controllers and the MPC controller. The data generation and online timing
+comparisons are performed on a computing cluster that has several multi-core
+CPUs of clock speed 2.4GHz. The NN trainings are performed on a Tesla V100-SXM2
+GPU that has 32 GB memory.
 
 \begin{table*}[t]
-    \caption{Summary of the simulation study for the
-    CSTRs with a flash separator example.}   
+    \caption{Summary of the simulation study for the CSTRs with a flash
+    separator example.}   
     \begin{tabular}{ |c|c|c|c|c|c|c|c| }
         \hline
-        Controller & \thead{Structured network \\ architecture} & 
-        \thead{Number of \\ Parameters} & 
-    \thead{Memory \\ footprint \\ (mB)} & \thead{Training \\ time \\ (min)} &
-        \thead{\% Performance\\ losses \\ Expected, Unexpected \\ plant behaviors} & \thead{Average \\ speedup} & \thead{Worst case \\ speedup} \\
+        Controller & \thead{Structured network \\ architecture} & \thead{Number
+        of \\ Parameters} & \thead{Memory \\ footprint \\ (mB)} &
+        \thead{Training \\ time \\ (min)} & \thead{\% Performance\\ losses \\
+        Expected, Unexpected \\ plant behaviors} & \thead{Average \\ speedup} &
+        \thead{Worst case \\ speedup} \\
         \hline
     SS &  &  & &  & 85.18\%, 106.39 \% &  & \\ 
-    satK &  &  &  &  & 41.03\%, 27.61 \% & $2.47 \times 10^5$ & 
-    $3.07 \times 10^5$ \\ 
+    satK &  &  &  &  & 41.03\%, 27.61 \% & $2.47 \times 10^5$ & $3.07 \times
+    10^5$ \\ 
     SH &  &  &  &  & 1.61\%, 2.46 \% & $3.75 \times 10^3$ & $8.4 \times 10^1$ \\
-    NN-UNS &  &  &  &  & 80.49\%, 73.29 \% & $9.31 \times 10^4$ & $4.99 \times 10^3$ \\ 
-NN-3-448 & [72, 448, 448, 448, 6] & $1.10 \times 10^5$ & 0.84 & 13.02 & 0.28 \%, 5.57 \% & $5.26 \times 10^4$ & $1.45 \times 10^3$ \\ 
-NN-3-480 & [72, 480, 480, 480, 6]  & $1.26 \times 10^5$ & 0.96  & 12.51 & 0.34 \%, 7.58\% & $5.09 \times 10^4$ & $1.53 \times 10^4$ \\ 
-NN-3-512 & [72, 512, 512, 512, 6]  & $1.42 \times 10^5$ & 1.08  & 12.77 & 0.16 \%, 5.90 \% & $4.62 \times 10^4$ & $1.58 \times 10^4$ \\ 
+
+    NN-UNS &  &  &  &  & 80.49\%, 73.29 \% & $9.31 \times 10^4$ & $4.99 \times
+    10^3$ \\ 
+NN-3-448 & [72, 448, 448, 448, 6] & $1.10 \times 10^5$ & 0.84 & 13.02 & 0.28 \%,
+5.57 \% & $5.26 \times 10^4$ & $1.45 \times 10^3$ \\ 
+NN-3-480 & [72, 480, 480, 480, 6]  & $1.26 \times 10^5$ & 0.96  & 12.51 & 0.34
+\%, 7.58\% & $5.09 \times 10^4$ & $1.53 \times 10^4$ \\ 
+NN-3-512 & [72, 512, 512, 512, 6]  & $1.42 \times 10^5$ & 1.08  & 12.77 & 0.16
+\%, 5.90 \% & $4.62 \times 10^4$ & $1.58 \times 10^4$ \\ 
         \hline
@@
 \begin{figure*}[!h]
-    \includegraphics[page=31,
-        width=0.5\textwidth, 
+    \includegraphics[page=31, width=0.5\textwidth,
         height=0.28\textheight]{cstrs_comparision_plots.pdf} \hfill
-    \includegraphics[page=34,
-        width=0.5\textwidth, 
+        \includegraphics[page=34, width=0.5\textwidth,
         height=0.28\textheight]{cstrs_comparision_plots.pdf} \vfill
     \vspace{-0.1in}
-    \begin{center}\includegraphics[page=33,
-        width=0.5\textwidth, 
+    \begin{center}\includegraphics[page=33, width=0.5\textwidth,
         height=0.28\textheight]{cstrs_comparision_plots.pdf}
@@
     \caption{Simulation statistics for the  
-    CSTRs with a flash separator example. Data requirement to obtain accurate NN controllers (top left), online computation times of the NNs and 
-    MPC controller (top right), 
-    and the controller performance index obtained with the NNs, 
-    SS, satK and MPC controllers (center bottom).}	
+    CSTRs with a flash separator example. Data requirement to obtain accurate NN
+    controllers (top left), online computation times of the NNs and MPC
+    controller (top right), and the controller performance index obtained with
+    the NNs, SS, satK and MPC controllers (center bottom).}	
     \label{fig:cstrs_statistics}
@@
 \subsection{CSTRs with a flash separator}
-For the first example, the two 
-stirred tank reactors in series with a flash separator
-depicted in Figure \ref{fig:schematic_cstrs} 
-is considered as the plant.
-In both the CSTRs, a desired product $B$ is produced 
-with the reaction $A \rightarrow B$, and an undesired 
-product $C$ is produced with the reaction $B \rightarrow C$. 
-The reactant $A$ is the major component in the 
-feed streams supplied to the 
-reactors. After the second CSTR, the reaction mixture is 
-sent to the non-adiabatic flash that separates the reactant $A$
-from the product $B$. The $A$ rich vapor phase 
-is recycled back to the first CSTR. 
-The plant is simulated using the set of 
-nonlinear ordinary differential equations (ODEs) available in 
-\cite*{venkat:2006}, Appendix.
-The model has 12 states 
-($H_r, x_{Ar}, x_{Br}, T_r, 
-H_m, x_{Am}, x_{Bm}, T_m, H_b, x_{Ab}, x_{Bb}, T_b$),
-6 control inputs 
-($F_0, F_1, D, Q_r, Q_m, Q_b$), and 5 disturbances
-($x_{A0}, x_{A1}, x_{B0}, x_{B1}, T_0$).
-The controlled measurements with setpoints are the heights
-and temperatures of the three units, and we
-assume that all the states are measured for this example. 
-The sample time for the measurements is chosen as 10 seconds. 
-The parameter values used to simulate the ODEs for the plant, 
-the actuator constraints, and the bounds of the controlled 
-measurements and disturbances used for the data generation 
-and validation simulations are 
+For the first example, the two stirred tank reactors in series with a flash
+separator depicted in Figure \ref{fig:schematic_cstrs} is considered as the
+plant. In both the CSTRs, a desired product $B$ is produced with the reaction $A
+\rightarrow B$, and an undesired product $C$ is produced with the reaction $B
+\rightarrow C$. The reactant $A$ is the major component in the feed streams
+supplied to the reactors. After the second CSTR, the reaction mixture is sent to
+the non-adiabatic flash that separates the reactant $A$ from the product $B$.
+The $A$ rich vapor phase is recycled back to the first CSTR. The plant is
+simulated using the set of nonlinear ordinary differential equations (ODEs)
+available in \cite*{venkat:2006}, Appendix. The model has 12 states ($H_r,
+x_{Ar}, x_{Br}, T_r, H_m, x_{Am}, x_{Bm}, T_m, H_b, x_{Ab}, x_{Bb}, T_b$), 6
+control inputs ($F_0, F_1, D, Q_r, Q_m, Q_b$), and 5 disturbances ($x_{A0},
+x_{A1}, x_{B0}, x_{B1}, T_0$). The controlled measurements with setpoints are
+the heights and temperatures of the three units, and we assume that all the
+states are measured for this example. The sample time for the measurements is
+chosen as 10 seconds. The parameter values used to simulate the ODEs for the
+plant, the actuator constraints, and the bounds of the controlled measurements
+and disturbances used for the data generation and validation simulations are
 shown in Table \ref{table:cstrs_pars}, Appendix \ref{app:cstrs_pars}.
 
-A linear discrete time model with the chosen sample time
-is obtained at the steady state shown in the Table 
-\ref{table:cstrs_pars}.
-This model, inputs and outputs are scaled 
-for the MPC controller such that the input 
-constraints satisfy
-$\overline{u} - \underline{u} = \mathbf{2}$.
-The tuning parameters and 
-control horizon length for the regulator are chosen as
-$Q = 10^3 C'C$, $R = 0.1 I$, $S = 0.1 I$, 
-and $N = 450$.
-A total $1.5 \times 10^5$ samples of 
-($x, u_{-1}, x_s, u_s, \kappa_N(\cdot)$) 
-is generated for NN training, parallelized in 100 
-separate offline simulations. The time consumed 
-for this data generation step was 4.2 hours.
-The setpoint of the 
-height of the second CSTR ($H_m$) is assumed 
-to be fixed during this data generation process, 
-and is included as an additional setpoint
-in the validation simulations for the 
-unexpected plant behavior case.
-
-Three structured NN architectures 
-are considered. Each NN
-has three hidden layers with 
-448 (NN-3-448), 480 (NN-3-480), 
-and 512 (NN-3-512)
-nodes in each hidden 
-layer respectively. For validation simulations, 
-two sets of setpoint and disturbance signals 
-with 24 setpoint changes and 48 disturbance changes 
-are generated for 4320 timesteps (12 hours), 
-each for the expected and unexpected 
-plant behavior cases. 
-The short horizon MPC controller is constructed with a 
-horizon length of $N = 10$, and the architecture 
-of the unstructured NN considered 
-is three hidden layers with 224 nodes in each hidden layer. 
-An additional scaling of $x$ and $x_s$ is performed for the 
-NN training as $x := 2x/(x_{\textnormal{max}} - x_{\textnormal{min}})$ and 
-$x_s := 2x_s/(x_{\textnormal{max}} - x_{\textnormal{min}})$,
-in which $x_{\textnormal{max}}$ and $x_{\textnormal{min}}$
-are the maximum and minimum values of the state 
-observed in the training data.
-This scaling is also performed in real time 
-when the NN is used to compute the actuator move.
-
-First, the amount of data required to obtain an accurate 
-NN controller is studied. To this aim, NNs with 
-the three chosen architectures are trained with 
-incremental increases of 
-$10^4$ training samples starting from $4 \times 10^4$
-to $1.5 \times 10^5$ samples. 
-A batch size of 1024 samples is used in Adam, 
-and all the NNs are trained for 2000 epochs. 
-The NNs after training are used in validation simulations
-with the setpoint and disturbance
-signals generated for the expected plant behavior
-case. The closed-loop performance is 
-compared with the optimal MPC 
-controller and the $\%$ performance loss obtained
-is plotted in Figure \ref{fig:cstrs_statistics} (top left)
-as a function of the number of training samples.
-All the trained NNs provide less than $1 \%$ loss in 
-this performance metric after training with 
-about $9 \times 10^4$ samples. The best $\%$ performance
-loss obtained by the NNs is summarized in
-Table \ref{table:cstrs}.
-
-Second, the above trained NNs with the best 
-performance losses are used in validation simulations
-with the setpoint and disturbance signals generated 
-for the unexpected plant behavior case. The 
-$\%$ performance losses obtained in these simulations 
-are also summarized in the Table \ref{table:cstrs},
-and the performance degrades from 
-less than $1\%$ to $5-8\%$. 
-This deterioration in the performance is due to some unseen
-($x, u_{-1}, x_s, u_s$) encountered in real-time by the NN
-resulting from the setpoint changes of the height 
-of the second CSTR, which was assumed to be fixed 
-during the data generation. 
-These simulations illustrate that one must not 
-expect the NNs to extrapolate outside the training data.
-The practical implication of this study is that 
-all possible plant scenarios with the 
-setpoints and disturbances 
-must be identified a-priori the deployment of NNs, and 
-should be used to generate the training data.
+A linear discrete time model with the chosen sample time is obtained at the
+steady state shown in the Table \ref{table:cstrs_pars}. This model, inputs and
+outputs are scaled for the MPC controller such that the input constraints
+satisfy $\overline{u} - \underline{u} = \mathbf{2}$. The tuning parameters and
+control horizon length for the regulator are chosen as $Q = 10^3 C'C$, $R = 0.1
+I$, $S = 0.1 I$, and $N = 450$. A total $1.5 \times 10^5$ samples of ($x,
+u_{-1}, x_s, u_s, \kappa_N(\cdot)$) is generated for NN training, parallelized
+in 100 separate offline simulations. The time consumed for this data generation
+step was 4.2 hours. The setpoint of the height of the second CSTR ($H_m$) is
+assumed to be fixed during this data generation process, and is included as an
+additional setpoint in the validation simulations for the unexpected plant
+behavior case.
+
+Three structured NN architectures are considered. Each NN has three hidden
+layers with 448 (NN-3-448), 480 (NN-3-480), and 512 (NN-3-512) nodes in each
+hidden layer respectively. For validation simulations, two sets of setpoint and
+disturbance signals with 24 setpoint changes and 48 disturbance changes are
+generated for 4320 timesteps (12 hours), each for the expected and unexpected
+plant behavior cases. The short horizon MPC controller is constructed with a
+horizon length of $N = 10$, and the architecture of the unstructured NN
+considered is three hidden layers with 224 nodes in each hidden layer. An
+additional scaling of $x$ and $x_s$ is performed for the NN training as $x :=
+2x/(x_{\textnormal{max}} - x_{\textnormal{min}})$ and $x_s :=
+2x_s/(x_{\textnormal{max}} - x_{\textnormal{min}})$, in which
+$x_{\textnormal{max}}$ and $x_{\textnormal{min}}$ are the maximum and minimum
+values of the state observed in the training data. This scaling is also
+performed in real time when the NN is used to compute the actuator move.
+
+First, the amount of data required to obtain an accurate NN controller is
+studied. To this aim, NNs with the three chosen architectures are trained with
+incremental increases of $10^4$ training samples starting from $4 \times 10^4$
+to $1.5 \times 10^5$ samples. A batch size of 1024 samples is used in Adam, and
+all the NNs are trained for 2000 epochs. The NNs after training are used in
+validation simulations with the setpoint and disturbance signals generated for
+the expected plant behavior case. The closed-loop performance is compared with
+the optimal MPC controller and the $\%$ performance loss obtained is plotted in
+Figure \ref{fig:cstrs_statistics} (top left) as a function of the number of
+training samples. All the trained NNs provide less than $1 \%$ loss in this
+performance metric after training with about $9 \times 10^4$ samples. The best
+$\%$ performance loss obtained by the NNs is summarized in Table
+\ref{table:cstrs}.
+
+Second, the above trained NNs with the best performance losses are used in
+validation simulations with the setpoint and disturbance signals generated for
+the unexpected plant behavior case. The $\%$ performance losses obtained in
+these simulations are also summarized in the Table \ref{table:cstrs}, and the
+performance degrades from less than $1\%$ to $5-8\%$. This deterioration in the
+performance is due to some unseen ($x, u_{-1}, x_s, u_s$) encountered in
+real-time by the NN resulting from the setpoint changes of the height of the
+second CSTR, which was assumed to be fixed during the data generation. These
+simulations illustrate that one must not expect the NNs to extrapolate outside
+the training data. The practical implication of this study is that all possible
+plant scenarios with the setpoints and disturbances must be identified a-priori
+the deployment of NNs, and should be used to generate the training data.
 
 \begin{table*}[t]
-    \caption{Summary of the simulation study for the 
-    industrial crude distillation unit example.}
+    \caption{Summary of the simulation study for the industrial crude
+    distillation unit example.}
     %\centering
@@
           Controller & \thead{Structured network \\ architecture} &
-          \thead{Number of \\ Parameters} & 
-          \thead{Memory \\ footprint \\ (mB)} & \thead{Training \\ time \\ (min)} &
-          \thead{\% Performance\\ loss} & \thead{Average \\ speedup} & \thead{Worst case \\ speedup} \\
+          \thead{Number of \\ Parameters} & \thead{Memory \\ footprint \\ (mB)}
+          & \thead{Training \\ time \\ (min)} & \thead{\% Performance\\ loss} &
+          \thead{Average \\ speedup} & \thead{Worst case \\ speedup} \\
           \hline
@@
   SH &  &  &  &  & 1.56 \% & $6.66 \times 10^3$  & $2.51 \times 10^3$ \\ 
-  NN-3-1664 & [1072, 1664, 1664, 1664, 32] & $1.85 \times 10^6$ & 14.18 & 52.66 & 0.29 \% & $1.52 \times 10^4$ & $6.57 \times 10^3$  \\ 
-  NN-3-1792 & [1072, 1792, 1792, 1792, 32]  & $2.11 \times 10^6$ & 16.15  & 55.27 & 0.43 \% & $1.33 \times 10^4$ & $5.25 \times 10^3$ \\ 
-  NN-3-1920 & [1072, 1920, 1920, 1920, 32]  & $2.39 \times 10^6$ & 18.24  & 59.24 & 0.59 \% & $1.18 \times 10^4$ & $4.48 \times 10^3$ \\ 
-  NN-3-2048 & [1072, 2048, 2048, 2048, 32]  & $2.68 \times 10^6$ & 20.46  & 66.58 & 0.48 \% & $1.09 \times 10^4$ & $3.54 \times 10^3$\\ 
+  NN-3-1664 & [1072, 1664, 1664, 1664, 32] & $1.85 \times 10^6$ & 14.18 & 52.66
+  & 0.29 \% & $1.52 \times 10^4$ & $6.57 \times 10^3$  \\ 
+  NN-3-1792 & [1072, 1792, 1792, 1792, 32]  & $2.11 \times 10^6$ & 16.15  &
+  55.27 & 0.43 \% & $1.33 \times 10^4$ & $5.25 \times 10^3$ \\ 
+  NN-3-1920 & [1072, 1920, 1920, 1920, 32]  & $2.39 \times 10^6$ & 18.24  &
+  59.24 & 0.59 \% & $1.18 \times 10^4$ & $4.48 \times 10^3$ \\ 
+  NN-3-2048 & [1072, 2048, 2048, 2048, 32]  & $2.68 \times 10^6$ & 20.46  &
+  66.58 & 0.48 \% & $1.09 \times 10^4$ & $3.54 \times 10^3$\\ 
 \hline
@@
 \begin{figure*}[!h]
-    \includegraphics[page=41,
-        width=0.5\textwidth, 
+    \includegraphics[page=41, width=0.5\textwidth,
         height=0.28\textheight]{cdu_comparision_plots.pdf} \hfill
-    \includegraphics[page=43,
-        width=0.5\textwidth, 
+        \includegraphics[page=43, width=0.5\textwidth,
         height=0.28\textheight]{cdu_comparision_plots.pdf} \vfill
     \vspace{-0.1in}
-    \begin{center}\includegraphics[page=42,
-        width=0.5\textwidth, 
+    \begin{center}\includegraphics[page=42, width=0.5\textwidth,
         height=0.28\textheight]{cdu_comparision_plots.pdf}\end{center}
     \vspace{-0.2in}
-    \caption{Simulation statistics for the industrial 
-    crude distillation unit example. Data requirement to obtain accurate NN controllers (top left), online computation times of the NNs and 
-    MPC controller (top right), 
-    and the controller performance index obtained with the NNs, 
-    satK and MPC controllers (center bottom).}	
+    \caption{Simulation statistics for the industrial crude distillation unit
+    example. Data requirement to obtain accurate NN controllers (top left),
+    online computation times of the NNs and MPC controller (top right), and the
+    controller performance index obtained with the NNs, satK and MPC controllers
+    (center bottom).}	
     \label{fig:cdu_statistics}
@@
     \centering
-    \includegraphics[width=0.45\textwidth, 
-                     height=0.25\textheight]{cdu.pdf}
+    \includegraphics[width=0.45\textwidth, height=0.25\textheight]{cdu.pdf}
     \caption{Schematic of the industrial crude distillation unit model}
@@
 
-Third, the transient closed-loop 
-performance of the trained NNs is examined
-for one particular validation 
-simulation for the expected plant behavior case. 
-Figures \ref{fig:cl_cstrs_inputs} and \ref{fig:cl_cstrs_outputs}
-show the transient actuator 
-and controlled measurements obtained with the NN-3-448 and 
-optimal MPC controllers for a simulation period of 2 hours.
-The Figure \ref{fig:cstrs_statistics} (center bottom)
-shows the transient values of the controller performance index
-obtained in this validation simulation
-with the three structured NNs, SS, satK 
-and optimal MPC controllers for the full 
-simulation period of 12 hours. The closed-loop 
-performance obtained using NNs is almost same as the optimal MPC 
-controller and the degradation in the performance 
+Third, the transient closed-loop performance of the trained NNs is examined for
+one particular validation simulation for the expected plant behavior case.
+Figures \ref{fig:cl_cstrs_inputs} and \ref{fig:cl_cstrs_outputs} show the
+transient actuator and controlled measurements obtained with the NN-3-448 and
+optimal MPC controllers for a simulation period of 2 hours. The Figure
+\ref{fig:cstrs_statistics} (center bottom) shows the transient values of the
+controller performance index obtained in this validation simulation with the
+three structured NNs, SS, satK and optimal MPC controllers for the full
+simulation period of 12 hours. The closed-loop performance obtained using NNs is
+almost same as the optimal MPC controller and the degradation in the performance
 is quantified with the $\%$ performance loss metric.
 
-Fourth, the online computational benefits of NNs 
-over the QP based MPC is analyzed. The Figure 
-\ref{fig:cstrs_statistics} (top right)
-shows a histogram of online computation times
-of the NNs and QP solver in one validation
-simulation. The average and worst-case speedups
-obtained using NNs are summarized in the 
-Table \ref{table:cstrs}. The QP solver takes 
-about 8 to 13 seconds in this example and all the 
-NNs compute the control in just 0.1 to 4
-milliseconds, and are easily deployable in the 
-sample time of 10 seconds.
-
-The $\%$ performance loss 
-obtained using the four heuristic controllers, 
-their corresponding speedups, maximum time required to 
-train each NN, number of parameters in each NN, 
-and the memory required to store  
-the weights of the NNs is summarized in the 
-Table \ref{table:cstrs}. The 
-$85 \%$ performance loss 
-reported for the unstructured
-NN corresponds to training with $1.5 \times 10^5$  
-samples and the performance is unacceptable 
-for an industrial application. 
-The noticeable performance improvement with the
-structured NNs is because the control law 
-is exactly the same as the optimal feedback law
-at steady-states, and that simplifies
-the optimal feedback law approximation problem
-since the training process only has to improve the 
-NN control law for the transient conditions.
+Fourth, the online computational benefits of NNs over the QP based MPC is
+analyzed. The Figure \ref{fig:cstrs_statistics} (top right) shows a histogram of
+online computation times of the NNs and QP solver in one validation simulation.
+The average and worst-case speedups obtained using NNs are summarized in the
+Table \ref{table:cstrs}. The QP solver takes about 8 to 13 seconds in this
+example and all the NNs compute the control in just 0.1 to 4 milliseconds, and
+are easily deployable in the sample time of 10 seconds.
+
+The $\%$ performance loss obtained using the four heuristic controllers, their
+corresponding speedups, maximum time required to train each NN, number of
+parameters in each NN, and the memory required to store  
+the weights of the NNs is summarized in the Table \ref{table:cstrs}. The $85 \%$
+performance loss reported for the unstructured NN corresponds to training with
+$1.5 \times 10^5$ samples and the performance is unacceptable for an industrial
+application. The noticeable performance improvement with the structured NNs is
+because the control law is exactly the same as the optimal feedback law at
+steady-states, and that simplifies the optimal feedback law approximation
+problem since the training process only has to improve the NN control law for
+the transient conditions.
 
@@
 
-The scalability of the proposed NN design 
-approach is next demonstrated on an industrial crude 
-distillation unit model \citep*{pannocchia:rawlings:wright:2007} 
-with 252 states, 32 controls, and 90 measurements. The 
-schematic of this model is shown in Figure \ref{fig:schematic_cdu}, 
-which is a typical crude unit found in petrochemical refineries.
-The plant model is linear, and input and outputs are scaled 
-for the MPC regulator as in the previous example.
-Only four measurements that represent 
-the quality of the crude side products have setpoints, 
-and five disturbances are used on the crude composition, 
-fuel gas quality, and steam header pressure. 
-The sample time for the measurements is 1 min. The tuning 
-parameters and control horizon length for the 
-MPC regulator are chosen as $Q = 2C'C$, $R = 0.1I$, 
-and $N = 140$. A total $3.6 \times 10^5$ 
-samples of ($x, x_s, u_s, \kappa_N(\cdot)$)
-are generated for the NN training, parallelized over 
-149 offline simulations. The time consumed 
-for this data generation step was 
-27.8 hours.
-
-Four structured NN architectures 
-are considered for this example. Each NN
-has three hidden layers, with 
-1664 (NN-3-1664), 1792 (NN-3-1792), 
-1920 (NN-3-1920), and 2048 (NN-3-2048) 
-nodes in each hidden layer respectively. 
-For the validation simulations, one set of
-setpoint and disturbance signals for the expected 
-plant behavior case is generated
-with 24 setpoint changes and 48 disturbance changes 
-for 2880 timesteps (2 days). 
-The short horizon MPC controller is constructed with a 
-horizon length of $N = 3$. 
-The states and target steady-states 
-($x$, $x_s$) are scaled for the NN training
-as in the previous example.
-
-Figure \ref{fig:cdu_statistics} shows the 
-statistics for the simulation study performed for this 
-example.
-The data requirement to obtain 
-an accurate NN controller is shown in the top left.
-The batch size 
-in Adam was chosen as 2048 samples, and all the NNs 
-are trained for 1500 epochs.
-The transient controller performance index 
-for one validation simulation
-obtained with the four structured NNs,
-satK, and MPC controllers is shown in the center bottom.
-The top right plot shows the 
-histogram of online computation times 
-of the NNs and QP solver.
-Table \ref{table:cdu} gives a summary of 
-the maximum time required to train the NNs, number of parameters
-in each NN, memory footprint of the NNs, and 
-the $\%$ performance loss metric obtained by 
-the structured NNs, SS, satK, and SH 
-controllers in the validation simulations.
-
-The offline data generation and training times 
-for the NNs shows that this large-scale example
-is tractable with the proposed NN approach.
-This large example is challenging, 
-since on average the QP solver CVXOPT requires 
-35 seconds, and 
-47 seconds in the worst-case. By comparison,  
-all the NNs execute MPC in about 2 
-to 7 milliseconds.
-As observed from the plot of the transient controller 
-performance index, the performance 
-degradation by the NNs relative to 
-the optimal MPC controller is negligible.
-The sampling of the state space with 
-the setpoint and disturbance signals
-for one particular operational scenario,
-combined with the offset-free NN structure
-are the key steps for scalability in this example.
+The scalability of the proposed NN design approach is next demonstrated on an
+industrial crude distillation unit model
+\citep*{pannocchia:rawlings:wright:2007} with 252 states, 32 controls, and 90
+measurements. The schematic of this model is shown in Figure
+\ref{fig:schematic_cdu}, which is a typical crude unit found in petrochemical
+refineries. The plant model is linear, and input and outputs are scaled for the
+MPC regulator as in the previous example. Only four measurements that represent
+the quality of the crude side products have setpoints, and five disturbances are
+used on the crude composition, fuel gas quality, and steam header pressure. The
+sample time for the measurements is 1 min. The tuning parameters and control
+horizon length for the MPC regulator are chosen as $Q = 2C'C$, $R = 0.1I$, and
+$N = 140$. A total $3.6 \times 10^5$ samples of ($x, x_s, u_s, \kappa_N(\cdot)$)
+are generated for the NN training, parallelized over 149 offline simulations.
+The time consumed for this data generation step was 27.8 hours.
+
+Four structured NN architectures are considered for this example. Each NN has
+three hidden layers, with 1664 (NN-3-1664), 1792 (NN-3-1792), 1920 (NN-3-1920),
+and 2048 (NN-3-2048) nodes in each hidden layer respectively. For the validation
+simulations, one set of setpoint and disturbance signals for the expected plant
+behavior case is generated with 24 setpoint changes and 48 disturbance changes
+for 2880 timesteps (2 days). The short horizon MPC controller is constructed
+with a horizon length of $N = 3$. The states and target steady-states ($x$,
+$x_s$) are scaled for the NN training as in the previous example.
+
+Figure \ref{fig:cdu_statistics} shows the statistics for the simulation study
+performed for this example. The data requirement to obtain an accurate NN
+controller is shown in the top left. The batch size in Adam was chosen as 2048
+samples, and all the NNs are trained for 1500 epochs. The transient controller
+performance index for one validation simulation obtained with the four
+structured NNs, satK, and MPC controllers is shown in the center bottom. The top
+right plot shows the histogram of online computation times of the NNs and QP
+solver. Table \ref{table:cdu} gives a summary of the maximum time required to
+train the NNs, number of parameters in each NN, memory footprint of the NNs, and
+the $\%$ performance loss metric obtained by the structured NNs, SS, satK, and
+SH controllers in the validation simulations.
+
+The offline data generation and training times for the NNs shows that this
+large-scale example is tractable with the proposed NN approach. This large
+example is challenging, since on average the QP solver CVXOPT requires 35
+seconds, and 47 seconds in the worst-case. By comparison,  
+all the NNs execute MPC in about 2 to 7 milliseconds. As observed from the plot
+of the transient controller performance index, the performance degradation by
+the NNs relative to the optimal MPC controller is negligible. The sampling of
+the state space with the setpoint and disturbance signals for one particular
+operational scenario, combined with the offset-free NN structure are the key
+steps for scalability in this example.
 
 \section{Conclusion} \label{sec:conclusion}
-Neural networks have been demonstrated 
-to approximate the MPC feedback law
-for treating large-scale, linear MPC applications
-that may be out of reach with QP solvers. 
-The proposed methods avoiding online optimization
-to date in the literature, such as storing 
-the entire MPC feedback law 
-and sampling the large dimensional state space 
-for the NN training, are not tractable for the problems 
+Neural networks have been demonstrated to approximate the MPC feedback law for
+treating large-scale, linear MPC applications that may be out of reach with QP
+solvers. The proposed methods avoiding online optimization to date in the
+literature, such as storing the entire MPC feedback law and sampling the large
+dimensional state space for the NN training, are not tractable for the problems
 considered in this article.
 
-The key features for the scalability of the proposed approach 
-are the structure of the NN and data generation for only
-typical plant operational scenarios. 
-The NN design approach was demonstrated to scale on an
-industrial crude distillation unit model with state and
-control dimensions of 252 and 32 respectively, and 
-a control-sample horizon length of 140. 
-After the offline design phase, NNs execute MPC 
-about three to five orders of magnitude faster than an 
-available QP solver 
-with less than 1$\%$ performance degradation in the closed-loop.
-The deployment decision of the NNs 
-must be based on the ability to reliably identify 
-and sample the anticipated plant operational scenarios 
-with setpoints and large magnitude disturbances
-that may change for a reasonable duration of operation.
-Parallel computing can be used for
-the offline data generation step if
-solving QPs for each sampled state starts to take 
-excessive amounts of time.
-After the training process, 
-the NNs are easily deployable on memory constrained 
-hardware. We established conditions under which the 
-NN controllers are robust to state estimation errors 
-and process disturbances,
-provides some theoretical support 
-to practitioners interested in the deployment of NNs.
+The key features for the scalability of the proposed approach are the structure
+of the NN and data generation for only typical plant operational scenarios. The
+NN design approach was demonstrated to scale on an industrial crude distillation
+unit model with state and control dimensions of 252 and 32 respectively, and a
+control-sample horizon length of 140. After the offline design phase, NNs
+execute MPC about three to five orders of magnitude faster than an available QP
+solver with less than 1$\%$ performance degradation in the closed-loop. The
+deployment decision of the NNs must be based on the ability to reliably identify
+and sample the anticipated plant operational scenarios with setpoints and large
+magnitude disturbances that may change for a reasonable duration of operation.
+Parallel computing can be used for the offline data generation step if solving
+QPs for each sampled state starts to take excessive amounts of time. After the
+training process, the NNs are easily deployable on memory constrained hardware.
+We established conditions under which the NN controllers are robust to state
+estimation errors and process disturbances, provides some theoretical support to
+practitioners interested in the deployment of NNs.
 
@@
 %a detailed feedback on this article.
-The funding for this work was provided by the industrial
-members of the Texas-Wisconsin-California Control 
-Consortium (TWCCC).
-The computational facilities purchased with funds from the National Science Foundation (CNS-1725797) and 
-administered by the Center for Scientific Computing (CSC) was used for the simulation 
-studies presented in this article. 
-The CSC is supported by the California NanoSystems Institute and the Materials 
-Research Science and Engineering Center 
-(MRSEC; NSF DMR 1720256) at UC Santa Barbara.
+The funding for this work was provided by the industrial members of the
+Texas-Wisconsin-California Control Consortium (TWCCC). The computational
+facilities purchased with funds from the National Science Foundation
+(CNS-1725797) and administered by the Center for Scientific Computing (CSC) was
+used for the simulation studies presented in this article. The CSC is supported
+by the California NanoSystems Institute and the Materials Research Science and
+Engineering Center (MRSEC; NSF DMR 1720256) at UC Santa Barbara.
 
@@
 
-We use the following
-definitions of
-robust positive invariance of a set
-with respect to disturbances, 
-input-to-state stability (ISS), ISS-Lyapunov function,
-and the available result 
-on the ISS property of a system if it admits 
-an ISS-Lyapunov function
-(\cite*{jiang:wang:2001, 
-rawlings:mayne:diehl:2017}, Appendix B).
-
-\begin{definition} \label{def:robust_pos_invariance}
-(Robust positive invariance). A closed set $X$ is 
-robustly positive invariant for the system $x^+ = f(x, w)$, 
-$w \in \bbW$ if $x \in X$ 
-implies $f(x, w) \in X$ for all $w \in \bbW$.
+We use the following definitions of robust positive invariance of a set with
+respect to disturbances, input-to-state stability (ISS), ISS-Lyapunov function,
+and the available result on the ISS property of a system if it admits an
+ISS-Lyapunov function (\cite*{jiang:wang:2001, rawlings:mayne:diehl:2017},
+Appendix B).
+
+\begin{definition} \label{def:robust_pos_invariance} (Robust positive
+invariance). A closed set $X$ is robustly positive invariant for the system $x^+
+= f(x, w)$, $w \in \bbW$ if $x \in X$ implies $f(x, w) \in X$ for all $w \in
+\bbW$.
 \end{definition}
 
-\begin{definition} \label{def:iss}
-(Input-to-state stability (ISS)). $\bbW$ is a compact 
-set containing the origin and that $X$ is a closed robustly
-positive invariant set for the 
-system $x^+ = f(x, w)$, $w \in \bbW$. This
-system is ISS in $X$ if there exist functions 
-$\beta(\cdot) \in \mathcal{K}\mathcal{L}$ and 
-$\sigma(\cdot) \in \mathcal{K}$, such that for all
-$x \in X$ and $w(i) \in \bbW$, $i \in \bbI_{0:k-1}$, 
-$\norm{\psi(k; x, \mathbf{w}_k)} \leq \beta(\norm{x}, k) 
-+ \sigma(\norm{\norm{\mathbf{w}_k}})$, in which 
-$\psi(k; x, \mathbf{w}_k)$ is the solution of the system 
-at time $k$, starting from an initial state $x$, and with the
-disturbance sequence $\mathbf{w}_k$ affecting the system.
+\begin{definition} \label{def:iss} (Input-to-state stability (ISS)). $\bbW$ is a
+compact set containing the origin and that $X$ is a closed robustly positive
+invariant set for the system $x^+ = f(x, w)$, $w \in \bbW$. This system is ISS
+in $X$ if there exist functions $\beta(\cdot) \in \mathcal{K}\mathcal{L}$ and
+$\sigma(\cdot) \in \mathcal{K}$, such that for all $x \in X$ and $w(i) \in
+\bbW$, $i \in \bbI_{0:k-1}$, $\norm{\psi(k; x, \mathbf{w}_k)} \leq
+\beta(\norm{x}, k) + \sigma(\norm{\norm{\mathbf{w}_k}})$, in which $\psi(k; x,
+\mathbf{w}_k)$ is the solution of the system at time $k$, starting from an
+initial state $x$, and with the disturbance sequence $\mathbf{w}_k$ affecting
+the system.
 \end{definition}
 
-\begin{definition} \label{def:iss_lyapunov_func}
-(ISS-Lyapunov function). A function $V : X \rightarrow \bbR_{\geq 0}$
-is an ISS-Lyapunov function in $X$ for the system $x^+ = f(x, w)$, $w \in \bbW$
-if there exist functions $\alpha_1(\cdot), \alpha_2(\cdot), \alpha_3(\cdot) 
-\in \mathcal{K}_{\infty}$ and $\sigma(\cdot) \in \mathcal{K}$
-such that for all $x \in X$ and $w \in \bbW$
+\begin{definition} \label{def:iss_lyapunov_func} (ISS-Lyapunov function). A
+function $V : X \rightarrow \bbR_{\geq 0}$ is an ISS-Lyapunov function in $X$
+for the system $x^+ = f(x, w)$, $w \in \bbW$ if there exist functions
+$\alpha_1(\cdot), \alpha_2(\cdot), \alpha_3(\cdot) \in \mathcal{K}_{\infty}$ and
+$\sigma(\cdot) \in \mathcal{K}$ such that for all $x \in X$ and $w \in \bbW$
 \begin{align*}
@@
 
-\begin{prop} \label{prop:lyapunov_implies_iss}
-(ISS-Lyapunov function implies ISS). $\bbW$ is a compact
-set containing the origin and that $X$ is a closed robustly
-positive invariant set for $x^+ = f(x, w)$, $w \in \bbW$. If 
-$f(\cdot)$ is continuous and there exists a continuous 
-ISS-Lyapunov function in $X$ for the system $x^+ = f(x, w)$, $w \in \bbW$, 
-then the system is ISS in $X$.
+\begin{prop} \label{prop:lyapunov_implies_iss} (ISS-Lyapunov function implies
+ISS). $\bbW$ is a compact set containing the origin and that $X$ is a closed
+robustly positive invariant set for $x^+ = f(x, w)$, $w \in \bbW$. If $f(\cdot)$
+is continuous and there exists a continuous ISS-Lyapunov function in $X$ for the
+system $x^+ = f(x, w)$, $w \in \bbW$, then the system is ISS in $X$.
 \end{prop}
 
-Additionally, we require the following two 
-useful propositions from 
-\cite*{allan:bates:risbeck:rawlings:2017} and 
-\cite*{rawlings:ji:2012},
-to bound values of continuous functions and an
-inequality for $\mathcal{K}$ functions respectively.
-
-\begin{prop} \label{prop:continuous_funcs}
-    Let $C \subseteq D \subseteq \bbR^n$, $C$ compact, 
-    $D$ closed, and $f : D \rightarrow \bbR^n$ continuous.  
-    Then there exists a $\sigma(\cdot) \in \mathcal{K}_{\infty}$,
-    such that for all $x \in C$ and $y \in D$, we have that 
-    $\norm{f(x) - f(y)} \leq \sigma(\norm{x-y})$.
+Additionally, we require the following two useful propositions from
+\cite*{allan:bates:risbeck:rawlings:2017} and \cite*{rawlings:ji:2012}, to bound
+values of continuous functions and an inequality for $\mathcal{K}$ functions
+respectively.
+
+\begin{prop} \label{prop:continuous_funcs} Let $C \subseteq D \subseteq \bbR^n$,
+    $C$ compact, $D$ closed, and $f : D \rightarrow \bbR^n$ continuous.  
+    Then there exists a $\sigma(\cdot) \in \mathcal{K}_{\infty}$, such that for
+    all $x \in C$ and $y \in D$, we have that $\norm{f(x) - f(y)} \leq
+    \sigma(\norm{x-y})$.
 \end{prop}
 
-\begin{prop} \label{prop:Kfunction_inequality}
-    Let $\sigma(\cdot) \in \mathcal{K}$, the following holds 
-    for all $a_i \in \bbR_{\geq 0}$, $i \in \bbI_{1:n}$ 
+\begin{prop} \label{prop:Kfunction_inequality} Let $\sigma(\cdot) \in
+    \mathcal{K}$, the following holds for all $a_i \in \bbR_{\geq 0}$, $i \in
+    \bbI_{1:n}$ 
     \begin{align*}
@@
 \textbf{Proof of Theorem \ref{thm:nnrobustness}:}
-We proceed in two steps. First, 
-we show that there exist constants $\delta_1, \delta_2, \delta_3 > 0$
-such that the set $S$ is robustly positive invariant. Then, we 
-show that $V_N^0(\xhat)$ is an ISS Lyapunov function for 
-the perturbed system \eqref{eq:perturbed_sys} on this set $S$. Denote 
-$\tilde{x}^+ = A\xhat + B\kappa_N(\xhat)$ as the nominal 
-state evolution using the optimal MPC controller, 
-and $d(k) = [ e_{NN}(\xhat(k))'B', w(k)', e(k)', e(k+1)']'$
-as the combination of all the disturbances at a given time $k$.
+We proceed in two steps. First, we show that there exist constants $\delta_1,
+\delta_2, \delta_3 > 0$ such that the set $S$ is robustly positive invariant.
+Then, we show that $V_N^0(\xhat)$ is an ISS Lyapunov function for the perturbed
+system \eqref{eq:perturbed_sys} on this set $S$. Denote $\tilde{x}^+ = A\xhat +
+B\kappa_N(\xhat)$ as the nominal state evolution using the optimal MPC
+controller, and $d(k) = [ e_{NN}(\xhat(k))'B', w(k)', e(k)', e(k+1)']'$ as the
+combination of all the disturbances at a given time $k$.
 
 To show robust positive invariance of $S$,  
-we establish that if $V_N^0(\xhat) \leq \rho$, 
-then $V_N^0(\xhat^+) \leq \rho$.
-Since the optimal 
-cost function ($V_N^0(\xhat)$) is continuous,
-using $\bbR^n$ as the closed set ($\xhat^+ \in \bbR^n$) 
-and $S$ as the compact set ($\tilde{x} \in S$),
-from proposition \ref{prop:continuous_funcs} we have
-for some $\sigma_1(\cdot) \in \mathcal{K}_{\infty}$
+we establish that if $V_N^0(\xhat) \leq \rho$, then $V_N^0(\xhat^+) \leq \rho$.
+Since the optimal cost function ($V_N^0(\xhat)$) is continuous, using $\bbR^n$
+as the closed set ($\xhat^+ \in \bbR^n$) and $S$ as the compact set ($\tilde{x}
+\in S$), from proposition \ref{prop:continuous_funcs} we have for some
+$\sigma_1(\cdot) \in \mathcal{K}_{\infty}$
 \begin{align}
@@
 in which $\sigma_2(s) := \sigma_1(\norm{A} s +3s)$, and the last inequality
-follows because $\norm{a} \leq \norm{[a', b']'}$, in which $a$ and $b$
-are both vectors, and $\sigma_2(\cdot) \in \mathcal{K}_{\infty}$.
-We partition $S$ in outer and inner parts based on 
-the value of the optimal cost $V_N^0(\xhat)$, and bound the 
-combination of disturbances $d$ in each part 
-such that $V_N^0(\xhat^+) \leq \rho$. \\
-Case 1: $\rho/2 \leq V_N^0(\xhat) \leq \rho $. Using the 
-upper bound on the optimal cost, we have 
-$\rho/(2c_2) \leq \norm{\xhat}^2$ for all $\xhat$ 
-in this part of $S$. To analyze the worst-case disturbance, 
-we have from the equation \eqref{eq:optimal_cost_bound} that 
-$V_N^0(\xhat^+) \leq V_N^0(\tilde{x}^+) + \sigma_2(\norm{d}) $.
-From nominal MPC cost decrease, we obtain  
-$V_N^0(\xhat^+) \leq V_N^0(\xhat) - c_1\norm{\xhat}^2 + 
-\sigma_2(\norm{d})$. Thus, if $\sigma_2(\norm{d}) \leq \rho c_1/(2c_2)$, 
-at all times in this outer part of $S$, we have 
-$V_N^0(\xhat^+) \leq \rho$. \\
-Case 2: $V_N^0(\xhat) \leq \rho/2 $. From 
-equation \eqref{eq:optimal_cost_bound} and nominal MPC 
-cost decrease, we have for this part of $S$ that 
-$V_N^0(\xhat^+) \leq \rho/2 + \sigma_2(\norm{d})$.
-Thus, if $\sigma_2(\norm{d}) \leq \rho/2$, 
-at all times in this inner part of $S$, we have 
-$V_N^0(\xhat^+) \leq \rho$.
-
-Therefore, if 
-$\norm{d} \leq \textnormal{min} \{ \sigma_2^{-1}(\rho c_1/(2c_2)), 
-\sigma_2^{-1}(\rho/2)\} := \delta_{\textnormal{max}}$ 
-at all times, then the set $S$ is 
-robustly positive invariant. Since $c_1 \leq c_2$, 
-$\delta_{\textnormal{max}} = \sigma_2^{-1}(\rho c_1/(2c_2))$.
-The constants $\delta_1$ and $\delta_2$ are
-$\delta_{\textnormal{max}}/4$ each, 
-and $\delta_3$ is $\delta_{\textnormal{max}}/(4\norm{B})$.
-The optimal MPC cost function satisfies
+follows because $\norm{a} \leq \norm{[a', b']'}$, in which $a$ and $b$ are both
+vectors, and $\sigma_2(\cdot) \in \mathcal{K}_{\infty}$. We partition $S$ in
+outer and inner parts based on the value of the optimal cost $V_N^0(\xhat)$, and
+bound the combination of disturbances $d$ in each part such that $V_N^0(\xhat^+)
+\leq \rho$. \\
+Case 1: $\rho/2 \leq V_N^0(\xhat) \leq \rho $. Using the upper bound on the
+optimal cost, we have $\rho/(2c_2) \leq \norm{\xhat}^2$ for all $\xhat$ in this
+part of $S$. To analyze the worst-case disturbance, we have from the equation
+\eqref{eq:optimal_cost_bound} that $V_N^0(\xhat^+) \leq V_N^0(\tilde{x}^+) +
+\sigma_2(\norm{d}) $. From nominal MPC cost decrease, we obtain  
+$V_N^0(\xhat^+) \leq V_N^0(\xhat) - c_1\norm{\xhat}^2 + \sigma_2(\norm{d})$.
+Thus, if $\sigma_2(\norm{d}) \leq \rho c_1/(2c_2)$, at all times in this outer
+part of $S$, we have $V_N^0(\xhat^+) \leq \rho$. \\
+Case 2: $V_N^0(\xhat) \leq \rho/2 $. From equation \eqref{eq:optimal_cost_bound}
+and nominal MPC cost decrease, we have for this part of $S$ that $V_N^0(\xhat^+)
+\leq \rho/2 + \sigma_2(\norm{d})$. Thus, if $\sigma_2(\norm{d}) \leq \rho/2$, at
+all times in this inner part of $S$, we have $V_N^0(\xhat^+) \leq \rho$.
+
+Therefore, if $\norm{d} \leq \textnormal{min} \{ \sigma_2^{-1}(\rho c_1/(2c_2)),
+\sigma_2^{-1}(\rho/2)\} := \delta_{\textnormal{max}}$ at all times, then the set
+$S$ is robustly positive invariant. Since $c_1 \leq c_2$,
+$\delta_{\textnormal{max}} = \sigma_2^{-1}(\rho c_1/(2c_2))$. The constants
+$\delta_1$ and $\delta_2$ are $\delta_{\textnormal{max}}/4$ each, and $\delta_3$
+is $\delta_{\textnormal{max}}/(4\norm{B})$. The optimal MPC cost function
+satisfies
 \begin{align*}
@@
 \end{align*}
-in the robustly positive invariant set $S$ and
-the disturbance set $\norm{d} \leq \delta_{\textnormal{max}}$.
-Since the optimal cost function also satisfies the upper and lower bounds
-$c_1\norm{x}^2 \leq V_N^0(x) \leq c_2\norm{x}^2$,
-from the Definition \ref{def:iss_lyapunov_func},
-it satisfies the requirements of an ISS-Lyapunov function.
-Hence, using the Proposition \ref{prop:lyapunov_implies_iss}, 
-the perturbed linear system \eqref{eq:perturbed_sys} is
-ISS (Definition \ref{def:iss}), 
-and there exist functions 
-$\beta(\cdot) \in \mathcal{K}\mathcal{L}$ and 
-$\sigma(\cdot) \in \mathcal{K}$, such that 
-$\norm{\phi_d(k; \xhat)} \leq \beta(\norm{\xhat}, k) 
-+ \sigma(\norm{\norm{\mathbf{d}_k}})$. Using the Proposition
-\ref{prop:Kfunction_inequality} and the definition of 
-$d(k)$, we have 
+in the robustly positive invariant set $S$ and the disturbance set $\norm{d}
+\leq \delta_{\textnormal{max}}$. Since the optimal cost function also satisfies
+the upper and lower bounds $c_1\norm{x}^2 \leq V_N^0(x) \leq c_2\norm{x}^2$,
+from the Definition \ref{def:iss_lyapunov_func}, it satisfies the requirements
+of an ISS-Lyapunov function. Hence, using the Proposition
+\ref{prop:lyapunov_implies_iss}, the perturbed linear system
+\eqref{eq:perturbed_sys} is ISS (Definition \ref{def:iss}), and there exist
+functions $\beta(\cdot) \in \mathcal{K}\mathcal{L}$ and $\sigma(\cdot) \in
+\mathcal{K}$, such that $\norm{\phi_d(k; \xhat)} \leq \beta(\norm{\xhat}, k) +
+\sigma(\norm{\norm{\mathbf{d}_k}})$. Using the Proposition
+\ref{prop:Kfunction_inequality} and the definition of $d(k)$, we have 
 \begin{align*}
@@
 Therefore, the bound in the Theorem \ref{thm:nnrobustness} is established with
-$\alpha_e(s) := \sigma(6s)$, 
-$\alpha_w(s) := \sigma(3s)$,
-$\alpha_n(s) := \sigma(3\norm{B} s)$, and 
-$\alpha_e(\cdot), \alpha_w(\cdot), \alpha_n(\cdot) \in \mathcal{K}$.
+$\alpha_e(s) := \sigma(6s)$, $\alpha_w(s) := \sigma(3s)$, $\alpha_n(s) :=
+\sigma(3\norm{B} s)$, and $\alpha_e(\cdot), \alpha_w(\cdot), \alpha_n(\cdot) \in
+\mathcal{K}$.
 
@@
         $\alpha_C$ & 0.5 &  & $\Delta H_1$ & -40 & \unitfrac{kJ}{kg} \\ 
-        $\rho$ & 50 & \unitfrac{kg}{m$^3$} & $\Delta H_2$ & -50 
-        & \unitfrac{kJ}{kg} \\ 
+        $\rho$ & 50 & \unitfrac{kg}{m$^3$} & $\Delta H_2$ & -50 &
+        \unitfrac{kJ}{kg} \\ 
         $C_p$ & 3 & \unitfrac{kJ}{kg-K} & $E/R$ & 150 & \unit{K} \\ 
@@
         \unit{sec$^{-1}$} \\ 
-        $A_m$ & 2 & \unit{m$^2$} & $k^{\star}_2$ & $1.8 \times 10^{-6}$ & \unit{sec$^{-1}$} \\ 
+        $A_m$ & 2 & \unit{m$^2$} & $k^{\star}_2$ & $1.8 \times 10^{-6}$ &
+        \unit{sec$^{-1}$} \\ 
         $A_b$ & 4 & \unit{m$^2$} & $T_d$ & 313 & \unit{K} \\ 
@@
         \hline
-        $F_0$ & (1.5, 2.5) & \unitfrac{kg}{sec} & 
-        $Q_r$ & (-500, 500) & \unit{kW} \\ 
-        $F_1$ & (0.5, 1.5) & \unitfrac{kg}{sec} & 
-        $Q_m$ & (-500, 500) & \unit{kW} \\ 
-        $D$ & (29.5, 30.5) & \unitfrac{kg}{sec} & 
-        $Q_b$ & (-500, 500) & \unit{kW} \\ 
+        $F_0$ & (1.5, 2.5) & \unitfrac{kg}{sec} & $Q_r$ & (-500, 500) &
+        \unit{kW} \\ 
+        $F_1$ & (0.5, 1.5) & \unitfrac{kg}{sec} & $Q_m$ & (-500, 500) &
+        \unit{kW} \\ 
+        $D$ & (29.5, 30.5) & \unitfrac{kg}{sec} & $Q_b$ & (-500, 500) &
+        \unit{kW} \\ 
         \hline
@@
         \hline
-        $H_r$ & (158.8, 168.8) & \unit{m} & 
-        $T_r$ & (303, 323) & \unit{K} \\ 
-        $H_m$ & (169.2, 179.2) & \unit{m} & 
-        $T_m$ & (310, 316) & \unit{K} \\ 
-        $H_b$ & (2.2, 4.2) & \unit{m} & 
-        $T_b$ & (303, 323) & \unit{K} \\ 
+        $H_r$ & (158.8, 168.8) & \unit{m} & $T_r$ & (303, 323) & \unit{K} \\ 
+        $H_m$ & (169.2, 179.2) & \unit{m} & $T_m$ & (310, 316) & \unit{K} \\ 
+        $H_b$ & (2.2, 4.2) & \unit{m} & $T_b$ & (303, 323) & \unit{K} \\ 
         \hline
@@
         \hline
-        $x_{A0}$ & (0.7, 0.85) & & 
-        $x_{B1}$ & (0, 0.15) & \\ 
-        $x_{B0}$ & (0, 0.15) & & 
-        $T_0$ & (305, 321) & \unit{K} \\ 
-        $x_{A1}$ & (0.7, 0.85) & & 
-         & & \\ 
-        \hline       
-        \multicolumn{6}{ |c| }{Steady state used for linearization 
-        ($x_s, u_s, d_s$)} \\
+        $x_{A0}$ & (0.7, 0.85) & & $x_{B1}$ & (0, 0.15) & \\ 
+        $x_{B0}$ & (0, 0.15) & & $T_0$ & (305, 321) & \unit{K} \\ 
+        $x_{A1}$ & (0.7, 0.85) & & & & \\ 
+        \hline       
+        \multicolumn{6}{ |c| }{Steady state used for linearization ($x_s, u_s,
+        d_s$)} \\
         \hline
@@
         $x_{Br}$ & 0.54 &  & $D$ & 30 & \unitfrac{kg}{sec} \\ 
-        $T_r$ & 313.1 & \unit{K} & $Q_r$ & 0
-        & \unit{kW} \\ 
+        $T_r$ & 313.1 & \unit{K} & $Q_r$ & 0 & \unit{kW} \\ 
         $H_m$ & 174.2 & \unit{m} & $Q_m$ & 0 & \unit{KW} \\ 
-        $x_{Am}$ & 0.37 &  & $Q_b$ & 0 & 
-        \unit{kW} \\ 
+        $x_{Am}$ & 0.37 &  & $Q_b$ & 0 & \unit{kW} \\ 
         $x_{Bm}$ & 0.58 & & $x_{A0}$ & 0.8 &  \\ 
@@
         $H_b$ & 3.24 & \unit{m} &  $x_{A1}$&  0.8&  \\ 
-        $x_{Ab}$ & 0.15 &  & 
-        $x_{B1}$ & 0.1 &  \\ 
-        $x_{Bb}$ & 0.73 &  & 
-        $T_0$ & 313 & \unit{K} \\ 
-        $T_b$ & 313.7 & \unit{K} & 
-         & & \\ 
-        \hline
-    \end{tabular}}
-    \caption{Parameters used in the ODEs to 
-simulate the plant in the CSTRs in series
-with a flash separator example, 
-actuator constraints, 
-setpoint and disturbance bounds, 
-and the steady state used to obtain the 
+        $x_{Ab}$ & 0.15 &  & $x_{B1}$ & 0.1 &  \\ 
+        $x_{Bb}$ & 0.73 &  & $T_0$ & 313 & \unit{K} \\ 
+        $T_b$ & 313.7 & \unit{K} & & & \\ 
+        \hline
+    \end{tabular}} \caption{Parameters used in the ODEs to simulate the plant in
+    the CSTRs in series with a flash separator example, actuator constraints,
+    setpoint and disturbance bounds, and the steady state used to obtain the
     linear model for the MPC controller.}

### 2020-11-22 abstract.tex
incorporate SJW's changes and add abstract/coverletter.

\documentclass[xcolor=dvipsnames, 11pt]{article}

\usepackage[total={4.5in, 8in}]{geometry}
\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz,tikzsettings,bm}
\usetikzlibrary{shapes,arrows,positioning, calc}
\usepackage{almostfull}
\usepackage{subcaption}

\usepackage{physics}
\usepackage{pgfplots}
\usepackage{ragged2e}

\usepackage{authblk}

%% You should not need more than this for fancy math.
\usepackage{verbatim}
\usepackage{amsmath}   % Extra math commands and environments from the AMS
\usepackage{amssymb}   % Special symbols from the AMS
\usepackage{amsthm}    % Enhanced theorem and proof environments from the AMS
\usepackage{algorithmic}
\usepackage{latexsym}  % A few extra LaTeX symbols
\usepackage{makecell}
%\usepackage{lucidbry}
\input{stanacce}
\renewcommand{\baselinestretch}{1.0666}

%% The URL package is handy for typesetting URLs.  It does not define % an
%\email command because so many document styles already do that. % So we define
%one here that uses a typewriter font.
\usepackage{url}
%\DeclareRobustCommand{\email}{\begingroup \urlstyle{tt}\Url}
\providecommand{\email}{}
\renewcommand{\email}[1]{\texttt{#1}}

%% This provides various customized verbatim commands and % environments.  You
%probably don't need it.
\usepackage{fancyvrb}
\DefineShortVerb{\|} \VerbatimFootnotes
\DefineVerbatimEnvironment{code}{Verbatim}{%
  frame=single, framesep=1em, xleftmargin=1em, xrightmargin=1em, samepage=true,
  fontsize=\footnotesize}
\usepackage{upquote}

\newcommand{\useq}{\mathbf{u}} \newcommand{\xseq}{\mathbf{x}}
\newcommand{\bbR}{\mathbb{R}} \newcommand{\bbU}{\mathbb{U}}
\newcommand{\bbX}{\mathbb{X}}

\usepackage[authoryear,round,longnamesfirst]{natbib}

%% You won't normally need this definition in your documents, but it % is here
%so we can typeset the BibTeX logo correctly.
\makeatletter
\@ifundefined{BibTeX} {\def\BibTeX{{\rmfamily B\kern-.05em%
    \textsc{i\kern-.025em b}\kern-.08em%
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}}{}

\def\blfootnote{\xdef\@thefnmark{}\@footnotetext}
\makeatother

\setcounter{topnumber}{2}              %% 2
\setcounter{bottomnumber}{1}           %% 1
\setcounter{totalnumber}{3}            %% 3
\renewcommand{\topfraction}{0.9}       %% 0.7
\renewcommand{\bottomfraction}{0.9}    %% 0.3
\renewcommand{\textfraction}{0.1}      %% 0.2
\renewcommand{\floatpagefraction}{.7}  %% 0.5
\newlength{\graphwidth}
\setlength{\graphwidth}{0.8\columnwidth}

\usepackage{subfiles}

\graphicspath{{./}{./figures/}{./figures/paper/}}

\title{Abstract}
\author{Pratyush Kumar, James B. Rawlings, Stephen J. Wright}

\begin{document}

The design of neural networks (NNs) is presented for treating large, linear
model predictive control (MPC) applications that are out of reach with available
quadratic programming (QP) solvers. First, we introduce a new feedforward
network architecture that enables practitioners to obtain offset-free
closed-loop performance with NNs. Second, we discuss the data generation
procedure to sample the state space relevant to training the NNs based on
anticipated online setpoint changes and plant disturbances. Third, we use the
input-to-state stability results available in the MPC literature and establish
robustness properties of NN controllers. Finally, we present illustrative
simulation studies on process control examples. We apply the NN design approach
and compare the performance with online QP based MPC on an industrial crude
distillation unit model with 252 states, 32 control inputs, and a control-sample
horizon length of 140. Parallel computing is used for data generation and
graphical processing units are used for network training. All the anticipated
plant operational scenarios with setpoints and disturbances that may change
during operation must be sampled for NN training. After the offline design
phase, NNs execute MPC three to five orders of magnitude faster than an
available QP solver with less than $1\%$ loss in the closed-loop performance.

\end{document}

### 2020-11-22 paper.tex
incorporate SJW's changes and add abstract/coverletter.

@@
 closed-loop performance with NNs. Second, we discuss the data generation
-procedure to sample the relevant state space for the network training based on
+procedure to sample the state space relevant to training the NNs based on
 anticipated online setpoint changes and plant disturbances. Third, we use the
@@
 technology. A dynamic model of the plant is used to make forecasts of the plant
-measurements in response to the actuator movements, and an optimization is
-solved in real time to determine the optimal actuator move to be applied to the
-plant. For linear plant models, the optimization to be solved online is a
-quadratic program (QP). The development of efficient QP algorithms
+measurements in response to the actuator movements, and an optimization problem
+is solved in real time to determine the optimal actuator move to be applied to
+the plant. For linear plant models, the optimization problem is a quadratic
+program (QP). The development of efficient QP algorithms
 \citep*{kouzoupis:frison:zanelli:diehl:2018, wright:2019} allowed practitioners
@@
 with large model dimensions and control horizon length in the QP has not been
-demonstrated. Two issues arise in these problems: i) In a large dimensional
-state space, the entire set of feasible states of the QP cannot be sampled
-densely for the NN training. This issue is a form of the well-known curse of
-dimensionality. ii) One may sample the state space partially to avoid this
-problem, but the time required for the data generation can still be impractical
-due to the long time required to solve a QP for each sampled state. We
-demonstrate in this article by case studies that this latter issue can be
+demonstrated to date. Two issues arise in these problems: i) In a large
+dimensional state space, the entire set of feasible states of the QP cannot be
+sampled densely for the NN training. This issue is a form of the well-known
+curse of dimensionality. ii) One may sample the state space partially to avoid
+this problem, but the time required for the data generation can still be
+impractical due to the long time required to solve a QP for each sampled state.
+We demonstrate in this article by case studies that this latter issue can be
 resolved for a large size of problems with parallel computing, and the former
@@
 alternative to real time optimization in MPC, with an emphasis on large
-applications which are challenging with QP solvers. The focus of this article is
+applications that are challenging for QP solvers. The focus of this article is
 on setpoint tracking MPC problems relevant for deployment in the process
@@
 input-to-state stability results available in the MPC literature, and establish
-conditions under which the NN controller is robust to state estimation errors
+conditions under which NN controllers are robust to state estimation errors
 and process disturbances. We present case studies on process control examples
@@
 exactly in real time depending on the controlled measurement setpoint and
-disturbance estimate. Then, the hard setpoint equality constraint can be relaxed
-and moved to the stage cost such that the target selector computes a steady
-state to minimize the offset in the controlled measurements. We assume for the
-simulation studies in this article that the input setpoint ($u_{sp}$) is fixed
-at some chosen steady state and only the controlled measurement setpoint
+disturbance estimate. In this case, the hard setpoint equality constraint can be
+relaxed and moved to the stage cost such that the target selector computes a
+steady state to minimize the offset in the controlled measurements. We assume
+for the simulation studies in this article that the input setpoint ($u_{sp}$) is
+fixed at some chosen steady state and only the controlled measurement setpoint
 ($r_{sp}$) changes in real time.
@@
           \end{bmatrix}z_{i-1}  + \begin{bmatrix}
-            b_i \notag 
+            b_i \\
             b_i
@@
 pairs. Sampling this entire domain of the MPC control law for NN training is
-difficult in large dimension, and we show in Section
+difficult in large dimensions, and we show in Section
 \ref{sec:simulation_studies} that it is also not required for practical
@@
 to perform offline simulations using the model to collect the operationally
-relevant set of ($x, x_s, u_s, \kappa_N(\cdot)$) for the NN training:
+relevant set of ($x, x_s, u_s, \kappa_N(\cdot)$) for NN training.
 
@@
         \caption{Transient closed-loop actuator trajectories of the CSTRs with
-        flash separator example with the NN and optimal MPC controllers.}   
+        flash separator example with the NN and optimal MPC controllers. The
+        performance of NN and optimal MPC controllers are almost
+        indistinguishable.}   
     \label{fig:cl_cstrs_inputs}
@@
 		closed-loop controlled measurement trajectories of the CSTRs with flash
-		separator example with the NN and optimal MPC controllers.}
+		separator example with the NN and optimal MPC controllers. The
+		performance of NN and optimal MPC controllers are almost
+		indistinguishable.}
 		\label{fig:cl_cstrs_outputs}
@@
 
-The robustness property of NN controllers is now presented. The optimal MPC
+We now present the robustness properties of NN controllers. The optimal MPC
 controller designed for a nominal linear system ignoring disturbances is known
@@
 error in the NN for the NN controller to be robust to disturbances. Theorem
-\ref{thm:nnrobustness} states this allowable approximation error and the size of
-disturbances for which the NN controller is robust.
+\ref{thm:nnrobustness} states this allowable approximation error and specifies
+the size of disturbances for which the NN controller is robust.
 
@@
 section, the state and control are transformed in deviation variables as $x := x
-- x_s$ and $u := u -u_s$, and define the control problem as regulation to the
+- x_s$ and $u := u -u_s$, and we define the control problem as regulation to the
 origin. The optimal MPC control law is denoted as $\kappa_N(x)$, and the NN
@@
 level set parameter of the terminal region chosen as $\bbX_f =
-\textnormal{lev}_{\tau} \ x'Px$, and $d > 0$ is a constant such that $\ell(x, u)
-\geq d$ for all $x \in \bbR^n \setminus \bbX_f$ and $\underline{u} \leq u+u_s
+\textnormal{lev}_{\tau} \ x'Px$, $d > 0$ is a constant such that $\ell(x, u)
+\geq d$ for all $x \in \bbR^n \setminus \bbX_f$, and $\underline{u} \leq u+u_s
 \leq \overline{u}$. The parameter $\tau$ is chosen small enough such that the
@@
 training is to reduce the worst approximation error ($\bar{e}_{NN}$) in the
-state space of interest and reduce the bound on the closed-loop states.
+state space of interest and thus reduce the bound on the closed-loop states.
 
@@
 (ii) with extra setpoint signals assumed to be unknown during the offline
-network design phase. Both these types of simulations are conducted to analyze
+network design phase. Both these types of simulations shed light on 
 the interpolation and extrapolation abilities of the NNs, and are referred
@@
                      height=0.22\textheight]{cstrs_with_flash.pdf}
-    \caption{Schematic of the CSTRs with a flash separator model}
+    \caption{Schematic of the CSTRs with a flash separator model.}
     \label{fig:schematic_cstrs}
@@
         \hline
-        Controller & \thead{Structured network \\ architecture} & \thead{Number
-        of \\ Parameters} & \thead{Memory \\ footprint \\ (mB)} &
-        \thead{Training \\ time \\ (min)} & \thead{\% Performance\\ losses \\
+        Controller & \thead{Neural network \\ architecture} & \thead{Number of
+        \\ Parameters} & \thead{Memory \\ footprint \\ (mB)} & \thead{Training
+        \\ time \\ (min)} & \thead{\% Performance\\ losses \\
         Expected, Unexpected \\ plant behaviors} & \thead{Average \\ speedup} &
@@
 
-    NN-UNS &  &  &  &  & 80.49\%, 73.29 \% & $9.31 \times 10^4$ & $4.99 \times
-    10^3$ \\ 
+    NN-UNS & [36, 224, 224, 224, 6] & $1.10 \times 10^5$ &  &  & 80.49\%, 73.29 \% & $9.31 \times
+    10^4$ & $4.99 \times 10^3$ \\ 
 NN-3-448 & [72, 448, 448, 448, 6] & $1.10 \times 10^5$ & 0.84 & 13.02 & 0.28 \%,
@@
     controller (top right), and the controller performance index obtained with
-    the NNs, SS, satK and MPC controllers (center bottom).}	
+    the NNs, SS, satK and MPC controllers (center bottom).The performance of the
+    three NN and optimal MPC controllers are indistinguishable.}	
     \label{fig:cstrs_statistics}
@@
           \hline
-          Controller & \thead{Structured network \\ architecture} &
+          Controller & \thead{Neural network \\ architecture} &
           \thead{Number of \\ Parameters} & \thead{Memory \\ footprint \\ (mB)}
@@
   59.24 & 0.59 \% & $1.18 \times 10^4$ & $4.48 \times 10^3$ \\ 
-  NN-3-2048 & [1072, 2048, 2048, 2048, 32]  & $2.68 \times 10^6$ & 20.46  &
-  66.58 & 0.48 \% & $1.09 \times 10^4$ & $3.54 \times 10^3$\\ 
+  %NN-3-2048 & [1072, 2048, 2048, 2048, 32]  & $2.68 \times 10^6$ & 20.46  &
+  %66.58 & 0.48 \% & $1.09 \times 10^4$ & $3.54 \times 10^3$\\ 
 \hline
@@
     controller performance index obtained with the NNs, satK and MPC controllers
-    (center bottom).}	
+    (center bottom). The performance of the three NN and optimal MPC
+    controllers are indistinguishable.}	
     \label{fig:cdu_statistics}
@@
     \includegraphics[width=0.45\textwidth, height=0.25\textheight]{cdu.pdf}
-    \caption{Schematic of the industrial crude distillation unit model}
+    \caption{Schematic of the industrial crude distillation unit model.}
     \label{fig:schematic_cdu}
@@
 because the control law is exactly the same as the optimal feedback law at
-steady-states, and that simplifies the optimal feedback law approximation
+steady-states, which simplifies the optimal feedback law approximation
 problem since the training process only has to improve the NN control law for
@@
 
-Four structured NN architectures are considered for this example. Each NN has
-three hidden layers, with 1664 (NN-3-1664), 1792 (NN-3-1792), 1920 (NN-3-1920),
-and 2048 (NN-3-2048) nodes in each hidden layer respectively. For the validation
+Three structured NN architectures are considered for this example. Each NN has
+three hidden layers, with 1664 (NN-3-1664), 1792 (NN-3-1792), and 1920
+(NN-3-1920) nodes in each hidden layer respectively. For the validation
 simulations, one set of setpoint and disturbance signals for the expected plant
@@
 samples, and all the NNs are trained for 1500 epochs. The transient controller
-performance index for one validation simulation obtained with the four
+performance index for one validation simulation obtained with the three
 structured NNs, satK, and MPC controllers is shown in the center bottom. The top

### 2020-11-22 cdu_comparision_plots.py

@@ -65,9 +65,9 @@ def _get_cdu_data_for_plotting(plant, controller, setpoints,
     return (t, z, y, u, pest, p, ulb, uub, zsp, ell)
 
 def _cdu_cl_comparision_plots(scenarios, 
-                             mpc_plants, mpc_controllers,
-                             fast_plants, fast_controllers, 
-                             fast_controller_name,
+                              mpc_plants, mpc_controllers,
+                              fast_plants, fast_controllers, 
+                              fast_controller_name,
                              parameters,
                              plot_range):
     """Data to plot.
@@ -314,7 +314,7 @@ def main():
 
     # Make the plots for the closed loop metrics of NNs with 
     # increasing data.
-    performance_loss = cdu_neural_network['performance_loss']
+    performance_loss = cdu_neural_network['performance_loss'][:-1, ...]
     num_samples = cdu_train['num_samples']
     cl_metric_figures = plot_nn_vs_num_samples_performance(performance_loss,
                                              num_samples, 
@@ -329,6 +329,11 @@ def main():
     time = np.asarray(cdu_mpc['plants'][0].t[0:-1]).squeeze()
     nn_controllers = PickleTool.load(filename='cdu_neural_network.pickle', 
                                      type='read')['controllers']
+    # Slight modification to not plot the last architecture.
+    nn_plants = nn_plants[:(num_architectures-1)*len(num_samples)]
+    nn_controllers = nn_controllers[:(num_architectures-1)*len(num_samples)]
+    nn_labels = nn_labels[:-1]
+    num_architectures -= 1
     cl_ct_figures = plot_cl_performance_and_comp_times(time,
                          mpc_controllers,
                          us_controllers, satdlqr_controllers,

### 2020-11-22 cstrs_comparision_plots.py

@@ -226,8 +226,20 @@ def plot_average_stage_costs(t, ell,
     figure.legend(labels = ('MPC', fast_controller_name), loc = (0.45, 0.9))
     return [figure]
 
+def print_unstd_pars():
+
+    dim = [36, 224, 224, 224, 6]
+    (Nin, Nh, Nnh, Nout) = (dim[0], len(dim)-2, dim[1], dim[-1])
+    num_pars = Nin*Nnh + Nnh  + (Nnh**2)*(Nh-1) + Nnh*(Nh-1) + Nnh*Nout + Nout
+    print(""" Number of parameters in the 
+              unstructued architecture are: """ + str(num_pars))
+    return 
+
 def main():
     """ Run these commands when this script is called."""
+
+    # Print Num pars in the unstructured Architecture.
+    print_unstd_pars()
 
     # Set the fontize.
     _set_font_size(paper_fontsize=16)

### 2020-11-25 paper.tex
submitted the first draft.

@@
         flash separator example with the NN and optimal MPC controllers. The
-        performance of NN and optimal MPC controllers are almost
+        performance of the NN and optimal MPC controllers are almost
         indistinguishable.}   
@@
 		separator example with the NN and optimal MPC controllers. The
-		performance of NN and optimal MPC controllers are almost
+		performance of the NN and optimal MPC controllers are almost
 		indistinguishable.}
@@
 \section*{Acknowledgment}
-%The authors acknowledge Professor Stephen J. Wright 
-%at the University of Wisconsin, Madison
-%for helpful discussions on machine learning topics and providing 
-%a detailed feedback on this article.
 The funding for this work was provided by the industrial members of the

### 2021-02-04 review_replies.tex
working on review.

\documentclass[xcolor=dvipsnames, 11pt]{article}

\usepackage[total={5.5in, 8in}]{geometry}
\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\definecolor{blue}{HTML}{0000FF} 
\usepackage{tikz,tikzsettings,bm}
\usetikzlibrary{shapes,arrows,positioning, calc}
\usepackage{almostfull}
\usepackage{subcaption}

\usepackage{physics}
\usepackage{pgfplots}
\usepackage{ragged2e}

\usepackage{authblk}

%% You should not need more than this for fancy math.
\usepackage{verbatim}
\usepackage{amsmath}   % Extra math commands and environments from the AMS
\usepackage{amssymb}   % Special symbols from the AMS
\usepackage{amsthm}    % Enhanced theorem and proof environments from the AMS
\usepackage{algorithmic}
\usepackage{latexsym}  % A few extra LaTeX symbols
\usepackage{makecell}
%\usepackage{lucidbry}
\input{stanacce}
\renewcommand{\baselinestretch}{1.0666}

%% The URL package is handy for typesetting URLs.  It does not define % an
%\email command because so many document styles already do that. % So we define
%one here that uses a typewriter font.
\usepackage{url}
%\DeclareRobustCommand{\email}{\begingroup \urlstyle{tt}\Url}
\providecommand{\email}{}
\renewcommand{\email}[1]{\texttt{#1}}

%% This provides various customized verbatim commands and % environments.  You
%probably don't need it.
\usepackage{fancyvrb}
\DefineShortVerb{\|} \VerbatimFootnotes
\DefineVerbatimEnvironment{code}{Verbatim}{%
  frame=single, framesep=1em, xleftmargin=1em, xrightmargin=1em, samepage=true,
  fontsize=\footnotesize}
\usepackage{upquote}

\newcommand{\useq}{\mathbf{u}} \newcommand{\xseq}{\mathbf{x}}
\newcommand{\bbR}{\mathbb{R}} \newcommand{\bbU}{\mathbb{U}}
\newcommand{\bbX}{\mathbb{X}}
\newcommand{\reply}[1]{\textcolor{blue}{#1}}

\usepackage[authoryear,round,longnamesfirst]{natbib}

%% You won't normally need this definition in your documents, but it % is here
%so we can typeset the BibTeX logo correctly.
\makeatletter
\@ifundefined{BibTeX} {\def\BibTeX{{\rmfamily B\kern-.05em%
    \textsc{i\kern-.025em b}\kern-.08em%
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}}{}

\def\blfootnote{\xdef\@thefnmark{}\@footnotetext}
\makeatother

\setcounter{topnumber}{2}              %% 2
\setcounter{bottomnumber}{1}           %% 1
\setcounter{totalnumber}{3}            %% 3
\renewcommand{\topfraction}{0.9}       %% 0.7
\renewcommand{\bottomfraction}{0.9}    %% 0.3
\renewcommand{\textfraction}{0.1}      %% 0.2
\renewcommand{\floatpagefraction}{.7}  %% 0.5
\newlength{\graphwidth}
\setlength{\graphwidth}{0.8\columnwidth}

\usepackage{subfiles}

\graphicspath{{./}{./figures/}{./figures/paper/}}

\title{Reply to Reviewers}
\author{Pratyush Kumar, James B. Rawlings, Stephen J. Wright}

\begin{document}

\textbf{Reviewer 1}: The paper addresses two important open problems in neural network-based (NN) approximation of MPC problems for linear systems. These include: 1. obtaining offset-free setpoint tracking and 2. efficient data generation for offline training of NN approximations for offset-free MPC laws for large-scale systems. While the methods contribution of the paper may not be significant, the proposed methods are practical and the simulation demonstrations of the proposed ideas are very thorough and insightful. My comments are follows:

\reply{The authors thank the reviewer for their helpful comments}.

\begin{itemize}
  \item The idea of generating operationally relevant training data is clearly important and useful. Others have also proposed the idea of generating closed-loop data for training the NNs, including in the context of NN for offset-free MPC. However, in the proposed approach here (Section 3.2), the idea relies on knowing process disturbances a priori (and also determining the anticipated range of setpoints). How realistic is this assumption, especially w.r.t. unknown disturbances in an industrial setting that is of interest in this paper?

  \reply{Under the proposed methodology in this paper, a practitioner has to identify the large magnitude physical disturbances which can occur during the real-time operation and also the disturbance models $B_d$ and $C_d$ which describe how those disturbances affect the plant dynamics. We believe that this step is required for the control engineer to reliably characterize the operationally relevant state-space ($x, x_s, u_s$), which the neural network can encounter in an online operation. If one uses a disturbance model with hypothetical meaning for the disturbance model states, then it is unclear how the practitioner should sample the disturbances to obtain the operationally relevant state-space.}

  \reply{We believe that the above step, along with determining the anticipated range of setpoints is reasonable also for industrial settings. For example in the CSTRs example presented, the practitioner has to identify the primary disturbance sources such as feed temperatures and compositions, and a model which describes how these disturbances affect the plant dynamics. An extra model identification procedure will be required to obtain the disturbance model. The anticipated range of setpoints can be determined based on historical setpoint ranges or the engineer's judgement. The setpoint and disturbance ranges can also be made conservative so the network does not encounters states outside the training data.}

  \reply{We agree that the above are extra design burdens posed on the engineer compared to online optimization based MPC, however, the payoff is the ability of neural networks to do large-scale problems which may be challenging for QP solvers.}

  \item  The robustness analysis of NN-based MPC controllers using ISS results has been investigated before. I would suggest that the authors cite related past work on this, e.g., Learning-based robust model predictive control with state-dependent uncertainty by Soloperto et al. and few others. Furthermore, the robustness analysis should be followed by a validation step. For example, see the latter paper or the following papers: Data-Driven Scenario Optimization for Automated Controller Tuning with Probabilistic Performance Guarantees, Probabilistic performance validation of deep learning-based robust NMPC controllers. The authors are encouraged to comment on this.

  \reply{Thank you for mentioning those papers.}

  \reply{The paper ``Learning-based robust model predictive control with state-dependent uncertainty" does not analyzes the robustness of NN controllers of interest to our paper, and examines theoretical properties of robust MPC problems under state dependent uncertainties. We have added paragraph in section 4 citing a different related work from the same research group ``Learning an approximate model predictive controller with guarantees", and have highlighted the differences from our result.}

  \reply{We agree that in an industrial deployment setting, the neural network training should be followed by a validation step. This validation can be performed by examining the closed-loop performance metrics of the optimal MPC and NN controllers.}

  \item Why state constraints were not considered in the QP problem (5)-(7)?

  \reply{In the industrial setting of interest in this paper, }

  \item While the memory footprint of the NN controllers can be very important, for example, in embedded control applications, the authors are encouraged to motivate why the memory footprint can be relevant in the industrial context considered in the paper.
\end{itemize}

\textbf{Reviewer 2}: Really nice and potentially impactful contribution; work provides clear evidence that NNs (provided that one uses a carefully chosen data representation) can effectively capture MPC laws. I have the following comments/suggestions/requests (not in order). \\

\reply{The authors thank the reviewer for their helpful comments}.

\begin{itemize}
  \item the input data representation is very clever; I do agree that selecting a proper representation is the key question to answer in any application (the NN architecture is secondary). Nice contribution.

  \reply{Thank you for the comment.}

  \item under the proposed architecture, now the state estimator becomes the bottleneck; please add a remark that this is an open issue and provide ideas on how this could be handled (in the future work session).

  \reply{Discuss with Jim.}

  \item in future work, please comment on how to potentially deal with state constraints (e.g., penalty terms?). This is an issue that might limit applicability.

  \reply{Discuss with Jim.}

  \item in future work, please comment on how to deal with other important aspects of MPC design; for instance, what would happen if one changes the objective from quadratic to linear? my expectation is that now the solution is degenerate and this might complicate the learning process.

  \reply{Discuss with Jim.}

  \item In (8), for completeness, please provide a short proof that the system delivers the state-state action if x=xs; Also, please comment if the property holds for any activation function or what properties of the activation function are needed. I think that the data representation is the key contribution of this paper; as such, it would be good to elaborate on the reasoning behind its derivation (or if there are alternative ways to obtain the same outcome).

  \reply{TODO.}

  \item it is not clear what is the contribution in Theorem 1; is the theorem new? is the proof new? what makes this unique to the NN setting under study? Please add more detail.

  \reply{TODO.}

  \item define "lev" notation \\
  \reply{We defined the "lev" notation in the Notation paragraph on page 2.}

  \item in future work, comment on what changes could be needed to handle nonlinearities? alternative activation functions?; also, comment on how to potentially deal with time-dependent trajectories or factors that will affect performance. Of course, maybe this is not known yet, but would be good to highlight the open questions.

  \reply{Discuss with Jim.}

  \item so a question that I have is about actual flops saved under NN MPC (related to energy and carbon savings, which is a current criticism of machine learning); all the complexity is going now into offline training and the computations in that phase are quite intense. Could you come up with an estimate that says; look, running an MPC controller for 1 year would require O($10^x$) flops; doing the training and 1-yr execution with NN would require O($10^y$) flops.  Yes, having reduced on-line time is great, but the training computations needed are gigantic and now think about developing multiple controllers all at once; there might be lots of energy wasted there because, in training the NN, you might be anticipating states that will never be visited online.

  \reply{TODO.}

  \item related to the previous comment; would be good to add a short perspective on how computational hardware could change under this approach. instead of having regular CPUs for MPC, now you need clusters for training and small processors for execution. I actually think that your approach is more effective cost-wise, but an argument should be made.

  \reply{Discuss with Jim.}

  \item in general, I think it would be good to add a discussion on benefits of on-line MPC vs NN MPC; the on-line version is clearly more flexible in the formulations that you can use.

  \item in figure 4 and 5, I would recommend comparing the controllers using cumulative frequency plots (as opposed to frequency plots); this is the common approach used in benchmarking optimization algorithms and it is easier to visualize.

  \item in table 1and 2, mB should be MB. \\
  \reply{This change is done in the updated version of the paper.}

  \item I encourage the authors to share their code.

\end{itemize}

\end{document}

### 2021-02-04 paper.tex
working on review.

@@
 
+The related work by \cite{hertneck:kohler:trimpe:allgower:2018} examines the robustness of nonlinear systems in feedback with approximate MPC controllers.
+The MPC control law approximation error is treated as an input disturbance, and a robust MPC formulation based on constraint tightening procedures is used to establish the allowable approximation error.
+The robustness of NN controllers trained with samples of the nominal MPC control law in presence of process disturbances and state estimation errors is not established in that paper.
+
 The problem of steering the state of the linear system (\ref{eq:ltimodel}) to
@@
 behaviors, respectively.
+
+The validation simulations are performed directly with the plant model for the case studies in this section.
+For industrial deployment, the NN training should be followed by an offline validation step of the trained network to verify the quality of the NN controller before online deployment.
+This validation can be performed by: a) quantifying the mean squared error (MSE) of the trained NN controller on test data generated using the optimal MPC, b) examining closed-loop performance metrics in simulations carried out with the linear model used in MPC and the optimal MPC and NN controllers.
+Additional probabilistic validation techniques for NNs trained using robust MPC solutions for nonlinear problems are proposed in \cite{karg:alamo:lucia:2019} and \cite{hertneck:kohler:trimpe:allgower:2018}.
 
@@
         Controller & \thead{Neural network \\ architecture} & \thead{Number of
-        \\ Parameters} & \thead{Memory \\ footprint \\ (mB)} & \thead{Training
+        \\ Parameters} & \thead{Memory \\ footprint \\ (MB)} & \thead{Training
         \\ time \\ (min)} & \thead{\% Performance\\ losses \\
@@
 
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=0.45\textwidth, height=0.25\textheight]{cdu.pdf}
+    \caption{Schematic of the industrial crude distillation unit model.}
+    \label{fig:schematic_cdu}
+\end{figure}
+
 Second, the above trained NNs with the best performance losses are used in
@@
           Controller & \thead{Neural network \\ architecture} &
-          \thead{Number of \\ Parameters} & \thead{Memory \\ footprint \\ (mB)}
+          \thead{Number of \\ Parameters} & \thead{Memory \\ footprint \\ (MB)}
           & \thead{Training \\ time \\ (min)} & \thead{\% Performance\\ loss} &
@@
 \end{figure*}
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=0.45\textwidth, height=0.25\textheight]{cdu.pdf}
-    \caption{Schematic of the industrial crude distillation unit model.}
-    \label{fig:schematic_cdu}
-\end{figure}
 

### 2021-02-04 paper.tex
more edits.

@@
 \subsection{Training}
-The following mean squared loss is minimized to determine the weights for the NN
-controller
+
+The following mean squared error (MSE) is minimized to determine the weights for
+the NN controller
 \begin{align}
@@
 
-The related work by \cite{hertneck:kohler:trimpe:allgower:2018} examines the robustness of nonlinear systems in feedback with approximate MPC controllers.
-The MPC control law approximation error is treated as an input disturbance, and a robust MPC formulation based on constraint tightening procedures is used to establish the allowable approximation error.
-The robustness of NN controllers trained with samples of the nominal MPC control law in presence of process disturbances and state estimation errors is not established in that paper.
+The related work by \cite{hertneck:kohler:trimpe:allgower:2018} examines the
+robustness of nonlinear systems in feedback with approximate MPC controllers.
+The MPC control law approximation error is treated as an input disturbance, and
+a robust MPC formulation based on constraint tightening procedures is used to
+establish the allowable approximation error. The robustness of NN controllers
+trained with samples of the nominal MPC control law in presence of process
+disturbances and state estimation errors has not been established to date in the
+literature.
 
@@
 
-The validation simulations are performed directly with the plant model for the case studies in this section.
-For industrial deployment, the NN training should be followed by an offline validation step of the trained network to verify the quality of the NN controller before online deployment.
-This validation can be performed by: a) quantifying the mean squared error (MSE) of the trained NN controller on test data generated using the optimal MPC, b) examining closed-loop performance metrics in simulations carried out with the linear model used in MPC and the optimal MPC and NN controllers.
-Additional probabilistic validation techniques for NNs trained using robust MPC solutions for nonlinear problems are proposed in \cite{karg:alamo:lucia:2019} and \cite{hertneck:kohler:trimpe:allgower:2018}.
+The validation simulations are performed directly with the plant model for the
+case studies in this section. For industrial deployment, the NN training should
+be followed by an offline validation step of the trained network to verify the
+quality of the NN controller before online deployment. This validation can be
+performed by: a) quantifying the MSE of the trained NN controller on test data
+generated using the optimal MPC, b) examining closed-loop performance metrics in
+simulations carried out with the linear model used in MPC and the optimal MPC
+and NN controllers. Additional probabilistic validation techniques for NNs
+trained using robust MPC solutions for nonlinear problems are proposed in
+\cite{karg:alamo:lucia:2019} and \cite{hertneck:kohler:trimpe:allgower:2018}.
 
@@
 to $1.5 \times 10^5$ samples. A batch size of 1024 samples is used in Adam, and
-all the NNs are trained for 2000 epochs. The NNs after training are used in
-validation simulations with the setpoint and disturbance signals generated for
-the expected plant behavior case. The closed-loop performance is compared with
-the optimal MPC controller and the $\%$ performance loss obtained is plotted in
-Figure \ref{fig:cstrs_statistics} (top left) as a function of the number of
-training samples. All the trained NNs provide less than $1 \%$ loss in this
-performance metric after training with about $9 \times 10^4$ samples. The best
-$\%$ performance loss obtained by the NNs is summarized in Table
-\ref{table:cstrs}.
+all the NNs are trained for 2000 epochs. For all the NN training performed,
+10$\%$ of the training dataset is kept as a buffer dataset, which is monitored
+during training and the network weights are updated only when the MSE decreases
+on this buffer dataset after every training epoch. The NNs after
+training are used in validation simulations with the setpoint and disturbance
+signals generated for the expected plant behavior case. The closed-loop
+performance is compared with the optimal MPC controller and the $\%$ performance
+loss obtained is plotted in Figure \ref{fig:cstrs_statistics} (top left) as a
+function of the number of training samples. All the trained NNs provide less
+than $1 \%$ loss in this performance metric after training with about $9 \times
+10^4$ samples. The best $\%$ performance loss obtained by the NNs is summarized
+in Table \ref{table:cstrs}.
 
@@
 controller is shown in the top left. The batch size in Adam was chosen as 2048
-samples, and all the NNs are trained for 1500 epochs. The transient controller
-performance index for one validation simulation obtained with the three
-structured NNs, satK, and MPC controllers is shown in the center bottom. The top
-right plot shows the histogram of online computation times of the NNs and QP
-solver. Table \ref{table:cdu} gives a summary of the maximum time required to
-train the NNs, number of parameters in each NN, memory footprint of the NNs, and
-the $\%$ performance loss metric obtained by the structured NNs, SS, satK, and
-SH controllers in the validation simulations.
+samples, and all the NNs are trained for 1500 epochs. For all the NN training,
+the size of the buffer dataset was chosen as 5$\%$ of the training dataset. The
+transient controller performance index for one validation simulation obtained
+with the three structured NNs, satK, and MPC controllers is shown in the center
+bottom. The top right plot shows the histogram of online computation times of
+the NNs and QP solver. Table \ref{table:cdu} gives a summary of the maximum time
+required to train the NNs, number of parameters in each NN, memory footprint of
+the NNs, and the $\%$ performance loss metric obtained by the structured NNs,
+SS, satK, and SH controllers in the validation simulations.
 
@@
 practitioners interested in the deployment of NNs.
+
+Future research in the area of approximating MPC control laws using NNs can
+focus on developing methods for approximating the target selector QP solution,
+systematically handling state constraints, extensions to nonlinear MPC problems,
+and establishing conditions for guaranteed closed-loop stability with NN
+controllers.
 

### 2021-02-05 paper.tex
add source code section.
update paper.tex

@@
 %%
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
+%% It may be distributed under the conditions of the LaTeX Project Public %
+%License, either version 1.2 of this license or (at your option) any % later
+%version.  The latest version of this license is in %
+%http://www.latex-project.org/lppl.txt % and version 1.2 or later is part of all
+%distributions of LaTeX % version 1999/12/01 or later.
 %%
-%% Template article for Elsevier's document class `elsarticle'
-%% with numbered style bibliographic references
+%% Template article for Elsevier's document class `elsarticle' % with numbered
+%style bibliographic references
 %%
-%% $Id: elsarticle-template-1-num.tex 149 2009-10-08 05:01:15Z rishi $
-%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-1-num.tex $
+%% $Id: elsarticle-template-1-num.tex 149 2009-10-08 05:01:15Z rishi $ % $URL:
+%http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-1-num.tex $
 %%
@@
 
-%% Use the option review to obtain double line spacing
-%% \documentclass[preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
+%% Use the option review to obtain double line spacing %
+%\documentclass[preprint,review,12pt]{elsarticle}
+
+%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn % for a
+%journal layout: % \documentclass[final,1p,times]{elsarticle} %
+%\documentclass[final,1p,times,twocolumn]{elsarticle} %
+%\documentclass[final,3p,times]{elsarticle} %
+%\documentclass[final,3p,times,twocolumn]{elsarticle} %
+%\documentclass[final,5p,times]{elsarticle} %
+%\documentclass[final,5p,times,twocolumn]{elsarticle}
 
@@
 \usepackage{xcolor}
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers after \end{frontmatter}.
+\usepackage[hidelinks=true]{hyperref}
+
+%% The lineno packages adds line numbers. Start line numbering with %
+%\begin{linenumbers}, end it with \end{linenumbers}. Or switch it on % for the
+%whole article with \linenumbers after \end{frontmatter}.
 \usepackage{lineno}
@@
 
-%\biboptions{longnamesfirst, semicolon}
-%% natbib.sty is loaded by default. However, natbib options can be
-%% provided with \biboptions{...} command. Following options are
-%% valid:
-
-%%   round  -  round parentheses are used (default)
-%%   square -  square brackets are used   [option]
-%%   curly  -  curly braces are used      {option}
-%%   angle  -  angle brackets are used    <option>
-%%   semicolon  -  multiple citations separated by semi-colon
-%%   colon  - same as semicolon, an earlier confusion
-%%   comma  -  separated by comma
-%%   numbers-  selects numerical citations
-%%   super  -  numerical citations as superscripts
-%%   sort   -  sorts multiple citations according to order in ref. list
-%%   sort&compress   -  like sort, but also compresses numerical citations
-%%   compress - compresses without sorting
+%\biboptions{longnamesfirst, semicolon} % natbib.sty is loaded by default.
+%However, natbib options can be % provided with \biboptions{...} command.
+%Following options are % valid:
+
+%%   round  -  round parentheses are used (default) %   square -  square
+%brackets are used   [option] %   curly  -  curly braces are used      {option}
+%%   angle  -  angle brackets are used    <option> %   semicolon  -  multiple
+%citations separated by semi-colon %   colon  - same as semicolon, an earlier
+%confusion %   comma  -  separated by comma %   numbers-  selects numerical
+%citations %   super  -  numerical citations as superscripts %   sort   -  sorts
+%multiple citations according to order in ref. list %   sort&compress   -  like
+%sort, but also compresses numerical citations %   compress - compresses without
+%sorting
 %%
@@
 
-\newcommand{\underl}[1]{\underline{#1}}
-\newcommand{\overl}[1]{\overline{#1}}
+\newcommand{\underl}[1]{\underline{#1}} \newcommand{\overl}[1]{\overline{#1}}
 \newcommand{\satlb}[1]{\textnormal{sat}(#1, \underline{#1}, \overline{#1})}
@@
 
-\title{Industrial, large-scale model predictive control 
-with structured neural networks}
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for the associated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for the associated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for the associated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
+\title{Industrial, large-scale model predictive control with structured neural
+networks}
+
+%% use the tnoteref command within \title for footnotes; % use the tnotetext
+%command for the associated footnote; % use the fnref command within \author or
+%\address for footnotes; % use the fntext command for the associated footnote; %
+%use the corref command within \author for corresponding author footnotes; % use
+%the cortext command for the associated footnote; % use the ead command for the
+%email address, % and the form \ead[url] for the home page:
 %%
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
+%% \title{Title\tnoteref{label1}} % \tnotetext[label1]{}
 \author[label1]{Pratyush Kumar\corref{cor1}}
 \ead{pratyushkumar@ucsb.edu}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
+%% \ead[url]{home page} % \fntext[label2]{}
 \cortext[cor1]{Corresponding Author}
@@
 \begin{keyword}
-Model predictive control \sep machine learning \sep 
-deep neural networks \sep large-scale problems
+Model predictive control \sep machine learning \sep deep neural networks \sep
+large-scale problems
 \end{keyword}
@@
 input-to-state stability results available in the MPC literature, and establish
-conditions under which NN controllers are robust to state estimation errors
-and process disturbances. We present case studies on process control examples
-that demonstrate the scalability of the proposed NN design approach.
+conditions under which NN controllers are robust to state estimation errors and
+process disturbances. We present case studies on process control examples that
+demonstrate the scalability of the proposed NN design approach.
 
@@
 dimensions. At steady state, when $x=x_s$ in $z_0$, \eqref{eq:NNstruct} outputs
-$u_s$ regardless of the choice of weights. The software tensorflow
+$u_s$ regardless of the choice of weights as the output of all hidden layers
+($z_i$) have same subvector repeated in the upper and lower half and
+$\begin{bmatrix} W_{h + 1}, & -W_{h+ 1} \\
+      \end{bmatrix} z_h$ equals zero. The software tensorflow
 \citep{abadi:agarwal:barham:brevdo:et-al:2015} is used for NN training purposes
@@
 (ii) with extra setpoint signals assumed to be unknown during the offline
-network design phase. Both these types of simulations shed light on 
-the interpolation and extrapolation abilities of the NNs, and are referred
+network design phase. Both these types of simulations shed light on the
+interpolation and extrapolation abilities of the NNs, and are referred
 subsequently as simulations with \textit{expected} and \textit{unexpected} plant
@@
 
-    NN-UNS & [36, 224, 224, 224, 6] & $1.10 \times 10^5$ &  &  & 80.49\%, 73.29 \% & $9.31 \times
-    10^4$ & $4.99 \times 10^3$ \\ 
+    NN-UNS & [36, 224, 224, 224, 6] & $1.10 \times 10^5$ &  &  & 80.49\%, 73.29
+    \% & $9.31 \times 10^4$ & $4.99 \times 10^3$ \\ 
 NN-3-448 & [72, 448, 448, 448, 6] & $1.10 \times 10^5$ & 0.84 & 13.02 & 0.28 \%,
@@
 during training and the network weights are updated only when the MSE decreases
-on this buffer dataset after every training epoch. The NNs after
-training are used in validation simulations with the setpoint and disturbance
-signals generated for the expected plant behavior case. The closed-loop
-performance is compared with the optimal MPC controller and the $\%$ performance
-loss obtained is plotted in Figure \ref{fig:cstrs_statistics} (top left) as a
-function of the number of training samples. All the trained NNs provide less
-than $1 \%$ loss in this performance metric after training with about $9 \times
-10^4$ samples. The best $\%$ performance loss obtained by the NNs is summarized
-in Table \ref{table:cstrs}.
+on this buffer dataset after every training epoch. The NNs after training are
+used in validation simulations with the setpoint and disturbance signals
+generated for the expected plant behavior case. The closed-loop performance is
+compared with the optimal MPC controller and the $\%$ performance loss obtained
+is plotted in Figure \ref{fig:cstrs_statistics} (top left) as a function of the
+number of training samples. All the trained NNs provide less than $1 \%$ loss in
+this performance metric after training with about $9 \times 10^4$ samples. The
+best $\%$ performance loss obtained by the NNs is summarized in Table
+\ref{table:cstrs}.
 
@@
           \hline
-          Controller & \thead{Neural network \\ architecture} &
-          \thead{Number of \\ Parameters} & \thead{Memory \\ footprint \\ (MB)}
-          & \thead{Training \\ time \\ (min)} & \thead{\% Performance\\ loss} &
-          \thead{Average \\ speedup} & \thead{Worst case \\ speedup} \\
+          Controller & \thead{Neural network \\ architecture} & \thead{Number of
+          \\ Parameters} & \thead{Memory \\ footprint \\ (MB)} & \thead{Training
+          \\ time \\ (min)} & \thead{\% Performance\\ loss} & \thead{Average \\
+          speedup} & \thead{Worst case \\ speedup} \\
           \hline
@@
     controller performance index obtained with the NNs, satK and MPC controllers
-    (center bottom). The performance of the three NN and optimal MPC
-    controllers are indistinguishable.}	
+    (center bottom). The performance of the three NN and optimal MPC controllers
+    are indistinguishable.}	
     \label{fig:cdu_statistics}
@@
 because the control law is exactly the same as the optimal feedback law at
-steady-states, which simplifies the optimal feedback law approximation
-problem since the training process only has to improve the NN control law for
-the transient conditions.
+steady-states, which simplifies the optimal feedback law approximation problem
+since the training process only has to improve the NN control law for the
+transient conditions.
 
@@
 controller is shown in the top left. The batch size in Adam was chosen as 2048
-samples, and all the NNs are trained for 1500 epochs. For all the NN training,
-the size of the buffer dataset was chosen as 5$\%$ of the training dataset. The
-transient controller performance index for one validation simulation obtained
-with the three structured NNs, satK, and MPC controllers is shown in the center
-bottom. The top right plot shows the histogram of online computation times of
-the NNs and QP solver. Table \ref{table:cdu} gives a summary of the maximum time
-required to train the NNs, number of parameters in each NN, memory footprint of
-the NNs, and the $\%$ performance loss metric obtained by the structured NNs,
-SS, satK, and SH controllers in the validation simulations.
+samples, and all the NNs are trained for 1500 epochs. The size of the buffer
+dataset was chosen as 5$\%$ of the training dataset. The transient controller
+performance index for one validation simulation obtained with the three
+structured NNs, satK, and MPC controllers is shown in the center bottom. The top
+right plot shows the histogram of online computation times of the NNs and QP
+solver. Table \ref{table:cdu} gives a summary of the maximum time required to
+train the NNs, number of parameters in each NN, memory footprint of the NNs, and
+the $\%$ performance loss metric obtained by the structured NNs, SS, satK, and
+SH controllers in the validation simulations.
 
@@
 \section{Conclusion} \label{sec:conclusion}
+
 Neural networks have been demonstrated to approximate the MPC feedback law for
@@
 estimation errors and process disturbances, provides some theoretical support to
-practitioners interested in the deployment of NNs.
-
-Future research in the area of approximating MPC control laws using NNs can
-focus on developing methods for approximating the target selector QP solution,
-systematically handling state constraints, extensions to nonlinear MPC problems,
-and establishing conditions for guaranteed closed-loop stability with NN
+practitioners interested in the deployment of NNs. Future research may be
+focused to establish conditions for guaranteed closed-loop stability with NN
 controllers.
@@
 Engineering Center (MRSEC; NSF DMR 1720256) at UC Santa Barbara.
+
+\section*{Source code}
+The code for the simulation studies performed in this article can be found at:
+\url{https://github.com/pratyushkumar211/industrial_nnmpc_2021}
 
@@
 
-\textbf{Proof of Theorem \ref{thm:nnrobustness}:}
-We proceed in two steps. First, we show that there exist constants $\delta_1,
-\delta_2, \delta_3 > 0$ such that the set $S$ is robustly positive invariant.
-Then, we show that $V_N^0(\xhat)$ is an ISS Lyapunov function for the perturbed
-system \eqref{eq:perturbed_sys} on this set $S$. Denote $\tilde{x}^+ = A\xhat +
+\textbf{Proof of Theorem \ref{thm:nnrobustness}:} We proceed in two steps.
+First, we show that there exist constants $\delta_1, \delta_2, \delta_3 > 0$
+such that the set $S$ is robustly positive invariant. Then, we show that
+$V_N^0(\xhat)$ is an ISS Lyapunov function for the perturbed system
+\eqref{eq:perturbed_sys} on this set $S$. Denote $\tilde{x}^+ = A\xhat +
 B\kappa_N(\xhat)$ as the nominal state evolution using the optimal MPC

### 2021-02-11 paper.tex
sync a few files from master.

@@
 Model predictive control \sep machine learning \sep deep neural networks \sep
-large-scale problems
+large-scale systems \sep quadratic programming \sep inherent robustness
 \end{keyword}
@@
 dimensions. At steady state, when $x=x_s$ in $z_0$, \eqref{eq:NNstruct} outputs
-$u_s$ regardless of the choice of weights as the output of all hidden layers
-($z_i$) have same subvector repeated in the upper and lower half and
-$\begin{bmatrix} W_{h + 1}, & -W_{h+ 1} \\
-      \end{bmatrix} z_h$ equals zero. The software tensorflow
-\citep{abadi:agarwal:barham:brevdo:et-al:2015} is used for NN training purposes
-in this article, and the structured architecture can be built with symbolic
-differentiation tools available in tensorflow. When a rate-of-change penalty on
-the control is included in the regulator QP, the input to the structured NN is
-modified to 
+$u_s$ regardless of the choice of weights and the activation function, as the
+output of all hidden layers ($z_i$) have same subvector repeated in the upper
+and lower half and the term $\begin{bmatrix} W_{h + 1}, & -W_{h+ 1} \\
+      \end{bmatrix} z_h$ equals zero. The NN structure \eqref{eq:NNstruct} is
+equivalent to the difference in outputs of two standard NNs with inputs ($x,
+x_s, u_s$) and ($x_s, x_s, u_s$) respectively, with $u_s$ added to the final
+output. The software tensorflow \citep{abadi:agarwal:barham:brevdo:et-al:2015}
+is used for NN training purposes in this article, and the structured
+architecture can be built with symbolic differentiation tools available in
+tensorflow. When a rate-of-change penalty on the control is included in the
+regulator QP, the input to the structured NN is modified to 
 \begin{align*}
@@
 	\includegraphics[page=1, width=0.7\textwidth,
-		height=0.5\textheight]{cstrs_comparision_plots.pdf}    
+		height=0.46\textheight]{cstrs_comparision_plots.pdf}    
         \caption{Transient closed-loop actuator trajectories of the CSTRs with
@@
 	\includegraphics[page=2, width=0.7\textwidth,
-		height=0.5\textheight]{cstrs_comparision_plots.pdf} \caption{Transient
+		height=0.46\textheight]{cstrs_comparision_plots.pdf} \caption{Transient
 		closed-loop controlled measurement trajectories of the CSTRs with flash
@@
 establish the allowable approximation error. The robustness of NN controllers
-trained with samples of the nominal MPC control law in presence of process
+trained with samples of nominal MPC control laws in presence of process
 disturbances and state estimation errors has not been established to date in the
@@
 
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth,
+                     height=0.22\textheight]{cstrs_with_flash.pdf}
+    \caption{Schematic of the CSTRs with a flash separator model.}
+    \label{fig:schematic_cstrs}
+\end{figure}
+
 The validation simulations are performed directly with the plant model for the
@@
 performed by: a) quantifying the MSE of the trained NN controller on test data
-generated using the optimal MPC, b) examining closed-loop performance metrics in
-simulations carried out with the linear model used in MPC and the optimal MPC
-and NN controllers. Additional probabilistic validation techniques for NNs
-trained using robust MPC solutions for nonlinear problems are proposed in
+generated using the optimal MPC controller, b) examining closed-loop performance
+metrics in simulations carried out with the linear model used in MPC and the
+optimal MPC and NN controllers, similar to the simulations performed in this
+section with the plant model. Additional probabilistic validation techniques for
+NNs trained using robust MPC solutions for nonlinear models are proposed in
 \cite{karg:alamo:lucia:2019} and \cite{hertneck:kohler:trimpe:allgower:2018}.
@@
 controller online.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.5\textwidth,
-                     height=0.22\textheight]{cstrs_with_flash.pdf}
-    \caption{Schematic of the CSTRs with a flash separator model.}
-    \label{fig:schematic_cstrs}
-\end{figure}
 
@@
 CPUs of clock speed 2.4GHz. The NN trainings are performed on a Tesla V100-SXM2
-GPU that has 32 GB memory.
+GPU that has 32 GB memory. The code for the simulation studies are available at:
+\url{https://github.com/pratyushkumar211/industrial_nnmpc_2021}.
 
@@
 \subsection{CSTRs with a flash separator}
+
 For the first example, the two stirred tank reactors in series with a flash
@@
 
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=0.45\textwidth, height=0.25\textheight]{cdu.pdf}
+    \caption{Schematic of the industrial crude distillation unit model.}
+    \label{fig:schematic_cdu}
+\end{figure}
+
 First, the amount of data required to obtain an accurate NN controller is
@@
 to $1.5 \times 10^5$ samples. A batch size of 1024 samples is used in Adam, and
-all the NNs are trained for 2000 epochs. For all the NN training performed,
+all the NNs are trained for 2000 epochs. For all the NN trainings performed,
 10$\%$ of the training dataset is kept as a buffer dataset, which is monitored
@@
 \ref{table:cstrs}.
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=0.45\textwidth, height=0.25\textheight]{cdu.pdf}
-    \caption{Schematic of the industrial crude distillation unit model.}
-    \label{fig:schematic_cdu}
-\end{figure}
 
@@
 corresponding speedups, maximum time required to train each NN, number of
-parameters in each NN, and the memory required to store  
-the weights of the NNs is summarized in the Table \ref{table:cstrs}. The $85 \%$
-performance loss reported for the unstructured NN corresponds to training with
-$1.5 \times 10^5$ samples and the performance is unacceptable for an industrial
-application. The noticeable performance improvement with the structured NNs is
-because the control law is exactly the same as the optimal feedback law at
-steady-states, which simplifies the optimal feedback law approximation problem
-since the training process only has to improve the NN control law for the
-transient conditions.
+parameters in each NN, and the memory required to store the weights of the NNs
+is summarized in the Table \ref{table:cstrs}. The memory requirement shows that
+NNs are deployable on resource constrained hardware, which can be crucial for
+industrial deployment at regulatory control layers. The $85 \%$ performance loss
+reported for the unstructured NN corresponds to training with $1.5 \times 10^5$
+samples and the performance is unacceptable for an industrial application. The
+noticeable performance improvement with the structured NNs is because the
+control law is exactly the same as the optimal feedback law at steady-states,
+which simplifies the optimal feedback law approximation problem since the
+training process only has to improve the NN control law for the transient
+conditions.
 
@@
 estimation errors and process disturbances, provides some theoretical support to
-practitioners interested in the deployment of NNs. Future research may be
-focused to establish conditions for guaranteed closed-loop stability with NN
-controllers.
+practitioners interested in the deployment of NNs.
+
+The online QP based MPC was adopted by practitioners due to its ability to
+systematically handle multivariable systems, process constraints, improvements
+in QP solution algorithms, and has guaranteed stability properties. The
+additional computing hardware for training in large applications and sampling
+the plant operational scenarios are additional complexities required to design
+NN controllers. The advantage of NNs is their speed of MPC controller execution
+and convenience for deployment on memory constrained hardware. Future research
+may be focused to establish conditions for guaranteed closed-loop stability with
+NN controllers, systematically handling state constraints, approximating the
+target selector QP, and extensions to large, nonlinear MPC applications.
 
@@
 Engineering Center (MRSEC; NSF DMR 1720256) at UC Santa Barbara.
-
-\section*{Source code}
-The code for the simulation studies performed in this article can be found at:
-\url{https://github.com/pratyushkumar211/industrial_nnmpc_2021}
 

### 2021-02-11 cstrs_comparision_plots.py

@@ -137,7 +137,7 @@ def plot_inputs(t, u, ulabels, ylabel_xcoordinate,
     axes[2, 0].set_xlabel("Time (hr)")
     axes[2, 1].set_xlabel("Time (hr)")
     figure.legend(labels = ('MPC', fast_controller_name), 
-                  loc = (0.31, 0.9), ncol=2)
+                  loc = (0.30, 0.9), ncol=2)
     # Return the figure,
     return [figure]
 
@@ -163,7 +163,7 @@ def plot_controlled_outputs(t, z, zsp,
     axes[2, 0].set_xlabel("Time (hr)")
     axes[2, 1].set_xlabel("Time (hr)")
     figure.legend(labels = ('MPC', fast_controller_name), 
-                  loc = (0.31, 0.9), ncol=2)
+                  loc = (0.30, 0.9), ncol=2)
     # Return
     return [figure]
 

### 2021-02-11 lib/LinearMPCLayers.py

@@ -33,11 +33,14 @@ class RegulatorLayerWithUprev(tf.keras.layers.Layer):
 
     # The structured call function.
     # The final output is:
-    # u = [us;us;...] + K(x, uprev, xs, us) - K(xs, us, xs, us)
+    # u = us + StrucNN(x, uprev, xs, us)
+    # StrucNN := NN(x, uprev, xs, us) - NN(xs, us, xs, us)
+    # Note that the above difference is same as the structured 
+    # architecture presented in the paper.
     def call(self, inputs):
 
         # Get the inputs.
-        [x, uprev, xs, us] = inputs        
+        [x, uprev, xs, us] = inputs
 
         # Propagate through the layers.
         layer_input = tf.concat((x, uprev, xs, us), axis=-1)
@@ -81,7 +84,10 @@ class RegulatorLayerWithoutUprev(tf.keras.layers.Layer):
 
     # The structured call function.
     # The final output is:
-    # u = [us;us;...] + K(x, xs, us) - K(xs, xs, us)
+    # u = us + StrucNN(x, xs, us)
+    # StrucNN := NN(x, xs, us) - NN(xs, xs, us)
+    # Note that the above difference is same as the structured
+    # architecture presented in the paper.
     def call(self, inputs):
 
         # Get the inputs.
@@ -141,9 +147,7 @@ class UnstdRegulatorLayer(tf.keras.layers.Layer):
         for dim in layer_dims:
             self._layers.append(tf.keras.layers.Dense(dim, activation='relu'))
 
-    # The structured call function.
-    # The final output is:
-    # u = [us;us;...] + K(x, uprev, xs, us) - K(xs, us, xs, us)
+    # u = NN(x, xs, us)
     def call(self, inputs):
         # Propagate through the layers.
         output = tf.concat(inputs, axis=-1)

### 2021-02-11 paper.tex
minor updates.

@@
 \ref{thm:nnrobustness} states this allowable approximation error and specifies
-the size of disturbances for which the NN controller is robust.
+the size of disturbances for which the NN controller is robust. This result also
+holds for other approximate MPC controllers, which use different parametric
+functions to approximate the optimal control law such as polynomials and other
+piecewise affine functions.
 
@@
     \includegraphics[width=0.5\textwidth,
-                     height=0.22\textheight]{cstrs_with_flash.pdf}
+                     height=0.25\textheight]{cstrs_with_flash.pdf}
     \caption{Schematic of the CSTRs with a flash separator model.}
@@
     \includegraphics[page=31, width=0.5\textwidth,
-        height=0.28\textheight]{cstrs_comparision_plots.pdf} \hfill
+        height=0.27\textheight]{cstrs_comparision_plots.pdf} \hfill
         \includegraphics[page=34, width=0.5\textwidth,
-        height=0.28\textheight]{cstrs_comparision_plots.pdf} \vfill
+        height=0.27\textheight]{cstrs_comparision_plots.pdf} \vfill
     \vspace{-0.1in}
     \begin{center}\includegraphics[page=33, width=0.5\textwidth,
-        height=0.28\textheight]{cstrs_comparision_plots.pdf}
+        height=0.27\textheight]{cstrs_comparision_plots.pdf}
     \end{center}
@@
     \includegraphics[page=41, width=0.5\textwidth,
-        height=0.28\textheight]{cdu_comparision_plots.pdf} \hfill
+        height=0.27\textheight]{cdu_comparision_plots.pdf} \hfill
         \includegraphics[page=43, width=0.5\textwidth,
-        height=0.28\textheight]{cdu_comparision_plots.pdf} \vfill
+        height=0.27\textheight]{cdu_comparision_plots.pdf} \vfill
     \vspace{-0.1in}
     \begin{center}\includegraphics[page=42, width=0.5\textwidth,
-        height=0.28\textheight]{cdu_comparision_plots.pdf}\end{center}
+        height=0.27\textheight]{cdu_comparision_plots.pdf}\end{center}
     \vspace{-0.2in}

### 2021-04-29 paper.tex
sync with published version.

@@
 \usepackage[hidelinks=true]{hyperref}
+\usepackage{natbib}
+
+%\biboptions{authoryear,round}
 
@@
 
-\usepackage{mpcsymbols}
+% Define shortcuts in MPCSymbols.
+\newcommand{\bbI}{\mathbb{I}}
+\newcommand{\bbR}{\mathbb{R}}
+\newcommand{\norm}[1]{\left| #1 \right|}
+\newcommand{\xhat}{\hat{x}}
+\newcommand{\dhat}{\hat{d}}
+\newcommand{\xseq}{\mathbf{x}}
+\newcommand{\bbX}{\mathbb{X}}
+\newcommand{\bbW}{\mathbb{W}}
 
@@
 horizon length of 140. Parallel computing is used for data generation and
-graphical processing units are used for network training. All the anticipated
-plant operational scenarios with setpoints and disturbances that may change
-during operation must be sampled for NN training. After the offline design
-phase, NNs execute MPC three to five orders of magnitude faster than an
-available QP solver with less than $1\%$ loss in the closed-loop performance.
+graphical processing units are used for network training. Anticipated plant
+operational scenarios with setpoints and disturbances that may change during
+operation must be sampled for NN training. After the offline design phase, NNs
+execute MPC three to five orders of magnitude faster than an available QP solver
+with less than $1\%$ loss in the closed-loop performance.
 \end{abstract}
@@
 program (QP). The development of efficient QP algorithms
-\citep*{kouzoupis:frison:zanelli:diehl:2018, wright:2019} allowed practitioners
+\citep{kouzoupis:frison:zanelli:diehl:2018, wright:2019} allowed practitioners
 to apply MPC in the process industries \citep*{qin:badgwell:2003, lahiri:2017}.
@@
 polyhedral partitions of the state space, and use the feedback law online
-\citep*{bemporad:morari:dua:pistikopoulos:2002, seron:goodwin:dedona:2003}. The
+\citep{bemporad:morari:dua:pistikopoulos:2002, seron:goodwin:dedona:2003}. The
 real time computation in this approach is reduced to a table look-up in the
@@
 The MPC feedback law can be approximated using parametric functions such as
-polynomials \citep*{kvasnica:lofberg:fikar:2011}, various types of piecewise
-affine functions \citep*{bemporad:oliveri:poggi:storace:2011,
+polynomials \citep{kvasnica:lofberg:fikar:2011}, various types of piecewise
+affine functions \citep{bemporad:oliveri:poggi:storace:2011,
 wen:ma:ydstie:2009}, and neural networks (NNs)
-\citep*{cavagnari:magni:scattolini:1999}. Among the function approximators, NNs
+\citep{cavagnari:magni:scattolini:1999}. Among the function approximators, NNs
 that use the rectified linear unit (ReLU) as the activation function have gained
-attention recently \citep*{chen:saulnier:atanasov:lee:kumar:pappas:morari:2018,
+attention recently \citep{chen:saulnier:atanasov:lee:kumar:pappas:morari:2018,
 karg:lucia:2020, paulson:mesbah:2020, lovelett:dietrich:lee:kevrekidis:2020} to
 approximate the MPC feedback law due to their ability to represent complex
-piecewise affine functions \citep*{montufar:pascanu:cho:bengio:2014} and execute
+piecewise affine functions \citep{montufar:pascanu:cho:bengio:2014} and execute
 MPC faster in real time than QP solvers. The proposed NN design approach in
@@
 impractical due to the long time required to solve a QP for each sampled state.
-We demonstrate in this article by case studies that this latter issue can be
-resolved for a large size of problems with parallel computing, and the former
-issue by sampling the state space for typical plant operational scenarios. The
-following feature must be present in the large-scale application of interest for
-the partial sampling scheme proposed in this article to be applicable: for a
+We demonstrate in this article by case studies that the issue (ii) can be
+resolved for many size of problems with parallel computing, and the issue (i) by
+sampling the state space for typical plant operational scenarios. The following
+feature must be present in the large-scale application of interest for the
+partial sampling scheme proposed in this article to be applicable: For a
 particular operating mode of the plant, the number of frequently changing
-setpoints and large magnitude disturbances must be reasonably small such that
-the entire large dimensional state space is not visited during that operation
-mode. The MPC feedback law can then be reliably approximated using NNs for the
-different modes of plant operations driven by their respective set of setpoint
-changes and disturbances.
+setpoints and large magnitude disturbances must be small enough such that only a
+small fraction of the entire large dimensional state space is visited during
+that operation mode. The MPC feedback law can then be reliably approximated
+using NNs for the different modes of plant operations, each driven by their
+respective set of setpoint changes and disturbances.
 
@@
 alternative to real time optimization in MPC, with an emphasis on large
-applications that are challenging for QP solvers. The focus of this article is
-on setpoint tracking MPC problems relevant for deployment in the process
-industries. We present a new feedforward network architecture to obtain
-offset-free closed-loop performance with the NNs. Additionally, we use the
-input-to-state stability results available in the MPC literature, and establish
-conditions under which NN controllers are robust to state estimation errors and
-process disturbances. We present case studies on process control examples that
-demonstrate the scalability of the proposed NN design approach.
-
-The related work by \cite*{chen:wang:atanasov:kumar:morari:2019} demonstrates
-the scalability of NNs to approximate the MPC feedback law on systems with state
-dimensions up to 36. The setpoint tracking offset-free MPC problem and state
-dimensions up to 250 considered in this article is not addressed in that work. 
-\cite*{drgona:picard:kvasnica:helsen:2018}
-take a different approach for the scalability of NN controllers, in which the
+applications that are challenging for QP solvers. We focus on setpoint tracking
+MPC problems relevant to the process industries. We present a new feedforward
+network architecture to obtain offset-free closed-loop performance with the NNs.
+Additionally, we use the input-to-state stability results available in the MPC
+literature, and establish conditions under which NN controllers are robust to
+state estimation errors and process disturbances. We present case studies on
+process control examples that demonstrate the scalability of the proposed NN
+design approach.
+
+The related work of \cite{chen:wang:atanasov:kumar:morari:2019} demonstrates the
+scalability of NNs to approximate the MPC feedback law on systems with state
+dimensions up to 36, on the control problem of regulation to the origin. By
+contrast, our paper considers setpoint tracking offset-free MPC problem and
+state dimensions up to 250. \cite{drgona:picard:kvasnica:helsen:2018} take a
+different approach for the scalability of NN controllers, in which the
 dimensionality of the parameters in the MPC QP is first reduced using principal
@@
 we discuss the NN controller design procedure. We present the robustness
-property of NNs in Section \ref{sec:robustness}. Then, we present simulation
-studies on two large process control examples in Section
-\ref{sec:simulation_studies} and conclude at the end of this article.
+property of NNs in Section \ref{sec:robustness}. Section
+\ref{sec:simulation_studies} presents simulation studies on two large process
+control examples and some concluding thoughts appear in Section
+\ref{sec:conclusion}.
 
@@
 We consider a linear discrete time model augmented with an integrating
-disturbance model \citep{pannocchia:rawlings:2003}
+disturbance model \citep{pannocchia:rawlings:2003}:
 \begin{align}\label{eq:ltimodel}
-    x^+ = Ax + Bu + B_dd, \quad d^+ = d, \quad y = Cx + C_dd
+    x^+ = Ax + Bu + B_dd, \quad d^+ = d, \quad y = Cx + C_dd,
 \end{align}
@@
 \bbR^{n \times n}$, $B \in \bbR^{n \times m}$,  
-$C \in \bbR^{p \times n}$ denote the actuator to measurement model, and $B_d \in
+$C \in \bbR^{p \times n}$ denote the actuator to measurement model; and $B_d \in
 \bbR^{n \times d}$, $C_d \in \bbR^{p \times d}$ is the disturbance model. The
@@
 Given the disturbance estimate, the input and controlled measurement setpoints,
-we consider the following target selector QP
+we consider the following target selector QP:
 \begin{align}
@@
         r_{sp} - HC_d\dhat
-    \end{bmatrix} \\
-    \underline{u} \leq u_s \leq \overline{u}
+    \end{bmatrix}, \\
+    \underline{u} \leq u_s \leq \overline{u},
 \end{align}
@@
 disturbance estimate. In this case, the hard setpoint equality constraint can be
-relaxed and moved to the stage cost such that the target selector computes a
+relaxed and moved to the stage cost, such that the target selector computes a
 steady state to minimize the offset in the controlled measurements. We assume
@@
 Based on the state estimate and target steady-state pair, the following QP is
-solved to determine the actuator move to be applied to the plant
+solved to determine the actuator move to be applied to the plant:
 \begin{align} \label{eqn:regulator}
@@
 \begin{align}
-    \tilde{x}^+ &= A\tilde{x} + B\tilde{u}, \quad \tilde{x}(0) = \xhat - x_s \\
-    &\underline{u} \leq \tilde{u} + u_s \leq \overline{u}
+    \tilde{x}^+ &= A\tilde{x} + B\tilde{u}, \quad \tilde{x}(0) = \xhat - x_s, \label{eqn:model_eq} \\
+    &\underline{u} \leq \tilde{u} + u_s \leq \overline{u},
     \label{eqn:regulator_constraints}
@@
 the control sequence $\mathbf{\tilde{u}} = [\tilde{u}(0)', \tilde{u}(1)', ...,
-\tilde{u}(N-1)']'$. The first move of the optimal solution is denoted as the MPC
-feedback law, $\kappa_N(\xhat, x_s, u_s) = \mathbf{\tilde{u}}^0(0;\xhat, x_s,
-u_s) + u_s$, which is applied to the plant. This feedback law is a function of
-the state estimate and target steady-state pair. A rate-of-change penalty on the
-control can be imposed in the QP objective by augmenting the dynamic model with
-a surrogate state for the control as discussed in \cite*{rao:rawlings:1999}. In
-this case, the control injected at the previous timestep ($u_{-1}$) is supplied
-to the QP, and the feedback law becomes a function of the previous control as
-well in addition to the state estimate and target steady-state pair.
+\tilde{u}(N-1)']'$, and the state sequence $\tilde{\xseq}$ is fully determined
+by the model equality constraints \eqref{eqn:model_eq}. The first move of the
+optimal solution is denoted as the MPC feedback law, $\kappa_N(\xhat, x_s, u_s)
+= \mathbf{\tilde{u}}^0(0;\xhat, x_s, u_s) + u_s$, which is applied to the plant.
+This feedback law is a function of the state estimate and target steady-state
+pair. A rate-of-change penalty on the control can be imposed in the QP objective
+by augmenting the dynamic model with a surrogate state for the control as
+discussed in \cite{rao:rawlings:1999}. In this case, the control injected at the
+previous timestep ($u_{-1}$) is supplied to the QP, and the feedback law becomes
+a function of the previous control, in addition to the state estimate and target
+steady-state pair.
 
 Several algorithms have been proposed in the literature over the years to solve
-the above MPC regulator QP. \cite*{kouzoupis:frison:zanelli:diehl:2018} and
-\cite*{wright:2019} give recent reviews on the development of convex
-optimization algorithms to solve this linear MPC QP. For the simulation studies
-in this article, we eliminate the state trajectory from the set of decision
-variables and formulate a dense QP. The decision variable in the dense QP is the
-future control trajectory $\mathbf{\tilde{u}}$, and the QP solver CVXOPT
-\citep*{vandenberghe:2010}, which is tailored for dense problems is used for NN
-data generations and timing comparisons with online QP based MPC. Any
-improvement in the QP formulation and solution algorithm is advantageous for
-both the online QP based MPC and NN approaches as fast QP solvers reduce the
-offline data generation time required for the design of NNs.
+the above MPC regulator QP. \cite{kouzoupis:frison:zanelli:diehl:2018} and
+\cite{wright:2019} give recent reviews on the development of convex optimization
+algorithms to solve this linear MPC QP. For the simulation studies in this
+article, we eliminate the state trajectory from the set of decision variables
+and formulate a dense QP. The decision variable in the dense QP is the future
+control trajectory $\mathbf{\tilde{u}}$, and the QP solver CVXOPT
+\citep{vandenberghe:2010}, which is tailored for dense problems is used to
+generate data for NN training and for timing comparisons with online QP based
+MPC. Any improvement in the QP formulation and solution algorithm is
+advantageous for both the online QP based MPC and NN approaches, as fast QP
+solvers reduce the offline data generation time required for the design of NNs.
 
@@
 x_s, u_s$) as its input and outputs a control that is close to the optimal
-control. This strategy has been proposed in \cite*{karg:lucia:2020} and 
-\cite*{chen:saulnier:atanasov:lee:kumar:pappas:morari:2018}
+control. This strategy has been proposed in \cite{karg:lucia:2020} and 
+\cite{chen:saulnier:atanasov:lee:kumar:pappas:morari:2018}
 for a single fixed steady state. The approach has not been demonstrated to scale
@@
 the NN control law. To incorporate this information in a NN, we introduce the
-following architecture
+following architecture:
 \begin{align}
 z_0 &= \begin{bmatrix}
-    x', & x_s', & u_s', & x_s', & x_s', & u_s' \end{bmatrix}'\notag \\
+    x', & x_s', & u_s', & x_s', & x_s', & u_s' \end{bmatrix}', \notag \\
     f_i(z_{i-1}) &= \begin{bmatrix}
@@
             b_i
-            \end{bmatrix} \notag\\
-    z_i &= g(f_i(z_{i-1})), \textnormal{for} \ i \in \bbI_{1:h} \notag \\
+            \end{bmatrix}, \notag\\
+    z_i &= g(f_i(z_{i-1})), \textnormal{for} \ i \in \bbI_{1:h}, \notag \\
     u &= u_s + \begin{bmatrix}
   W_{h + 1}, & -W_{h + 1} \\
-    \end{bmatrix} z_h
+    \end{bmatrix} z_h,
 \label{eq:NNstruct}
@@
       \end{bmatrix} z_h$ equals zero. The NN structure \eqref{eq:NNstruct} is
-equivalent to the difference in outputs of two standard NNs with inputs ($x,
-x_s, u_s$) and ($x_s, x_s, u_s$) respectively, with $u_s$ added to the final
-output. The software tensorflow \citep{abadi:agarwal:barham:brevdo:et-al:2015}
-is used for NN training purposes in this article, and the structured
-architecture can be built with symbolic differentiation tools available in
-tensorflow. When a rate-of-change penalty on the control is included in the
-regulator QP, the input to the structured NN is modified to 
+equivalent to the difference in the outputs of a standard feedforward NN with
+inputs ($x, x_s, u_s$) and ($x_s, x_s, u_s$) respectively, with $u_s$ added to
+the final output. The software tensorflow
+\citep{abadi:agarwal:barham:brevdo:et-al:2015} is used for NN training; the
+structured architecture can be built with symbolic differentiation tools
+available in tensorflow.
+
+When a rate-of-change penalty on the control is included in the regulator QP,
+the input to the structured NN is modified to:
 \begin{align*}
@@
     x', & u_{-1}', & x_s', & u_s', & x_s', & u_s', & x_s', & u_s' \\
-    \end{bmatrix}'
+    \end{bmatrix}',
 \end{align*}
@@
 adjusted. Even after training, the control produced by the NN may not satisfy
-the hard actuator constraints, and the saturation function
+the hard actuator constraints, so the saturation function
 ($\textnormal{sat}(\cdot, \underline{u}, \overline{u})$) is applied to the
@@
 $n$-dimensional state space $\bbR^n$. Additionally, the target steady state may
-change during the plant operation depending on the setpoint and disturbance
+change during plant operation, depending on the setpoint and disturbance
 estimate. The domain of the MPC control law ($\kappa_N(x, x_s, u_s)$) is
@@
 pairs. Sampling this entire domain of the MPC control law for NN training is
-difficult in large dimensions, and we show in Section
-\ref{sec:simulation_studies} that it is also not required for practical
-applications.
-
-From a plant operations perspective, a majority of the large-scale petrochemical
-plants operate in a relatively small number of operating regimes or scenarios.
-Each operational scenario is driven by a selected few controlled measurement
-setpoints that depend on product demands and some large magnitude disturbances
-may change frequently, while the setpoints for the other measurements remain
-constant for long periods of time. The states and steady-state targets spanned
-in a closed-loop operation per scenario is thereby considerably less than the
-entire domain of the MPC control law. This typical operation of large chemical
-plants can be exploited, and we propose the following data generation procedure
-to perform offline simulations using the model to collect the operationally
-relevant set of ($x, x_s, u_s, \kappa_N(\cdot)$) for NN training.
+difficult in large dimensions; we show in Section \ref{sec:simulation_studies}
+that it is not required for practical applications.
+
+A majority of large-scale petrochemical plants operate in a relatively small
+number of operating regimes or scenarios. Each operational scenario is driven by
+a selected few controlled measurement setpoints that depend on product demands
+and some large magnitude disturbances that may change frequently, while the
+setpoints for other measurements remain constant for long periods of time. The
+states and steady-state targets spanned in a closed-loop operation per scenario
+is thereby considerably less than the entire domain of the MPC control law.
+These characteristics of typical operation of large chemical plants can be
+exploited, and we propose the following data generation procedure to perform
+offline simulations using the model to collect the operationally relevant set of
+($x, x_s, u_s, \kappa_N(\cdot)$) for NN training.
 
@@
 
-During the plant operation, it is expected that the NN does not encounter the
-same states and steady-state target pairs used for the training. But similar
-values are expected since an adequate model and appropriate range of anticipated
-setpoints and plant disturbances are used for the data generation. The NN during
-the closed-loop operation produces an interpolated actuator move that is applied
-to the plant.
+During plant operation, it is expected that the NN will encounter states and
+steady-state target pairs not used in training. But similar values are expected,
+since an adequate model and appropriate range of anticipated setpoints and plant
+disturbances are used for the data generation. During the closed-loop operation,
+the NN produces an interpolated actuator move that is applied to the plant.
 
@@
 the data generation step can take impractical amounts of time if performed
-serially due to the long time required to solve each QP (minutes). For these
+serially, due to the long time (minutes) required to solve each QP. For these
 large problems, several PRBS signals of the setpoints and disturbances are
@@
 The following mean squared error (MSE) is minimized to determine the weights for
-the NN controller
+the NN controller:
 \begin{align}
@@
 \end{align}
-in which $\theta$ is the set of parameters to be optimized, ($W_i, b_i,
-W_{h+1}$) for $i \in \bbI_{1:h}$, subscript $j$ is used to denote the training
-sample index, and $N_{tr}$ is the number of training samples. The stochastic
-optimization algorithm Adam \citep*{kingma:ba:2014} is used for all the NN
-training performed in the case studies in this article. We do not consider any
-regularization penalty in the training objective. The recent empirical and
-theoretical works in the machine learning literature have shown that NNs with
-large number of parameters have good interpolation capabilities
-\citep*{belkin:hsu:ma:mandal:2019, zhang:bengio:hardt:recht:vinyals:2017,
-arora:simon:hu:li:wang:2019, allen-zhu:li:liang:2019} without any form of
-explicit regularization during training. The generalization abilities of NNs for
-the architectures considered in this article is examined in the simulations
-presented in the Section \ref{sec:simulation_studies}.
+in which $\theta$ is the set of parameters, ($W_i, b_i, W_{h+1}$) for $i \in
+\bbI_{1:h}$, subscript $j$ is used to denote the training sample index, and
+$N_{tr}$ is the number of training samples. The stochastic optimization
+algorithm Adam \citep{kingma:ba:2014} is used for all the case studies in this
+article. We do not consider any regularization penalty in the training
+objective. The recent empirical and theoretical works in the machine learning
+literature have shown that NNs with large number of parameters have good
+interpolation capabilities \citep{belkin:hsu:ma:mandal:2019,
+zhang:bengio:hardt:recht:vinyals:2017, arora:simon:hu:li:wang:2019,
+allen-zhu:li:liang:2019} without any form of explicit regularization. The
+generalization abilities of NNs for the architectures considered in this article
+is examined in the simulations presented in the Section
+\ref{sec:simulation_studies}.
 
@@
 to be inherently robust to bounded state estimation errors and disturbances
-\citep*{heath:wills:2005, pannocchia:rawlings:wright:2011}. The approximation
+\citep{heath:wills:2005, pannocchia:rawlings:wright:2011}. The approximation
 error of the MPC feedback law by a NN can be viewed as an additional
-disturbance, and the existing input-to-state stability results
-\citep*{sontag:wang:1995} are used to establish the allowable approximation
+disturbance, and existing input-to-state stability results
+\citep{sontag:wang:1995} can be used to establish the allowable approximation
 error in the NN for the NN controller to be robust to disturbances. Theorem
-\ref{thm:nnrobustness} states this allowable approximation error and specifies
-the size of disturbances for which the NN controller is robust. This result also
-holds for other approximate MPC controllers, which use different parametric
-functions to approximate the optimal control law such as polynomials and other
-piecewise affine functions.
+\ref{thm:nnrobustness} below states this allowable approximation error and
+specifies the size of disturbances for which the NN controller is robust. This
+result also holds for other approximate MPC controllers, which use different
+parametric functions to approximate the optimal control law, such as polynomials
+and other piecewise affine functions.
 
@@
 
-As reviewed in \cite*{mayne:rawlings:rao:scokaert:2000}, the nominal stability
-of MPC can be established using the optimal cost function ($V_N^0(x)$) of the QP
-as a Lyapunov function. The region of attraction of the closed-loop system $x^+
-= Ax + B\kappa_N(x)$ when no hard terminal region constraint is included in the
-QP can be characterized as $\mathcal{X}_N = \textnormal{lev}_{Nd + \tau} \
-V_N^0(x)$ \citep*{limon:alamo:salas:camacho:2006}. The parameter $\tau$ is the
+As reviewed in \cite{mayne:rawlings:rao:scokaert:2000}, the nominal stability of
+MPC can be established using the optimal cost function ($V_N^0(x)$) of the QP as
+a Lyapunov function. The region of attraction of the closed-loop system $x^+ =
+Ax + B\kappa_N(x)$ when no hard terminal region constraint is included in the QP
+can be characterized as $\mathcal{X}_N = \textnormal{lev}_{Nd + \tau} \
+V_N^0(x)$ \citep{limon:alamo:salas:camacho:2006}. The parameter $\tau$ is the
 level set parameter of the terminal region chosen as $\bbX_f =
@@
 Assume that a state estimate ($\xhat$) is used by the NN to compute the control.
-To analyze robustness, the following perturbed linear system is considered
+To analyze robustness, the following perturbed linear system is considered:
 \begin{align} \label{eq:perturbed_sys}
-    \xhat^+ = A\xhat + B\kappa_N(\xhat) + Be_{NN}(\xhat) + w - Ae + e^+
+    \xhat^+ = A\xhat + B\kappa_N(\xhat) + Be_{NN}(\xhat) + w - Ae + e^+,
 \end{align}
 in which $\xhat = x + e$ is the state estimate, $w$ is a process disturbance,
-and $e$, $e^+$ are the state estimation errors at the current and next timestep
+and $e$, $e^+$ are the state estimation errors at the current and next timestep,
 respectively. We use $\phi_d(k;\xhat)$ to denote a solution of the perturbed
@@
 $\norm{\norm{\mathbf{w}_k}} \leq \delta_2$, and $\norm{e_{NN}(\xhat)} \leq
-\delta_3$, for all $\xhat$ in the set $S := \textnormal{lev}_{\rho} \
-V_N^0(\xhat)$, we have the following bound $\norm{\phi_d(k; \xhat)} \leq
+\delta_3$, and for all $\xhat$ in the set $S := \textnormal{lev}_{\rho} \
+V_N^0(\xhat)$, we have the bound $\norm{\phi_d(k; \xhat)} \leq
 \beta(\norm{\xhat}, k) + \alpha_e(\norm{\norm{\mathbf{e}_{k+1}}}) +
@@
 
-The proof of this theorem along with the required input-to-state stability
-definitions are provided in Appendix \ref{app:theorem1}. In the nominal case,
-the disturbance sequences $\mathbf{e}$ and $\mathbf{w}$ are zero. The
-closed-loop states in this case have the bound $\norm{\phi(k; x)} \leq
-\beta(\norm{x}, k) + \alpha_n(\bar{e}_{NN})$. Any additional value of the NN
-training is to reduce the worst approximation error ($\bar{e}_{NN}$) in the
-state space of interest and thus reduce the bound on the closed-loop states.
+The proof of this theorem and the required input-to-state stability definitions
+are provided in Appendix \ref{app:theorem1}. In the nominal case, the
+disturbance sequences $\mathbf{e}$ and $\mathbf{w}$ are zero, and the
+closed-loop states have the bound $\norm{\phi(k; x)} \leq \beta(\norm{x}, k) +
+\alpha_n(\bar{e}_{NN})$. An additional value of the NN training is to reduce the
+worst approximation error ($\bar{e}_{NN}$) in the state space of interest, thus
+reducing the bound on the closed-loop states.
 
@@
 
-The validation simulations are performed directly with the plant model for the
-case studies in this section. For industrial deployment, the NN training should
-be followed by an offline validation step of the trained network to verify the
-quality of the NN controller before online deployment. This validation can be
-performed by: a) quantifying the MSE of the trained NN controller on test data
-generated using the optimal MPC controller, b) examining closed-loop performance
-metrics in simulations carried out with the linear model used in MPC and the
-optimal MPC and NN controllers, similar to the simulations performed in this
-section with the plant model. Additional probabilistic validation techniques for
-NNs trained using robust MPC solutions for nonlinear models are proposed in
+The validation simulations are performed directly with the plant model for our
+case studies. For industrial deployment, the NN training should be followed by
+an offline validation step of the trained network to verify the quality of the
+NN controller prior to online deployment. This validation can be performed by:
+a) quantifying the MSE of the trained NN controller on test data generated using
+the optimal MPC controller, b) examining closed-loop performance metrics in
+simulations carried out with the linear model used in MPC and the optimal MPC
+and NN controllers, similar to the simulations performed in this section with
+the plant model. Additional probabilistic validation techniques for NNs trained
+using robust MPC solutions for nonlinear models are proposed in
 \cite{karg:alamo:lucia:2019} and \cite{hertneck:kohler:trimpe:allgower:2018}.
@@
     \Lambda_k = \dfrac{1}{k}\sum_{t=1}^{k} & \big(\norm{x(t) - x_{s} (t)}^2_{Q} \\
-        & + \norm{u(t) - u_{s} (t)}^2_{R} + \norm{\Delta u(t)}^2_{S}\big)         
+        & + \norm{u(t) - u_{s} (t)}^2_{R} + \norm{\Delta u(t)}^2_{S}\big);
     \end{align*}
     \item \% Performance loss = $100(\Lambda^{\textnormal{F}}_{N_{t}} -
-    \Lambda^{\textnormal{MPC}}_{N_{t}})/\Lambda^{\textnormal{MPC}}_{N_{t}}$
-    \item Average and worst-case speedups
-    \item Data generation and NN training times
-    \item Memory required to store the weights of the NNs
+    \Lambda^{\textnormal{MPC}}_{N_{t}})/\Lambda^{\textnormal{MPC}}_{N_{t}}$;
+    \item Average and worst-case speedups;
+    \item Data generation and NN training times;
+    \item Memory required to store the weights of the NNs.
 \end{itemize}
-Here, $N_t$ is the number of simulation time steps,  
+Here, $N_t$ is the number of simulation time steps, and
 $\Lambda^{\textnormal{F}}_{N_{t}}$ and $\Lambda^{\textnormal{MPC}}_{N_{t}}$ are
@@
 CPUs of clock speed 2.4GHz. The NN trainings are performed on a Tesla V100-SXM2
-GPU that has 32 GB memory. The code for the simulation studies are available at:
+GPU that has 32 GB memory. Code for the simulation studies is available at:
 \url{https://github.com/pratyushkumar211/industrial_nnmpc_2021}.
@@
 
-For the first example, the two stirred tank reactors in series with a flash
-separator depicted in Figure \ref{fig:schematic_cstrs} is considered as the
-plant. In both the CSTRs, a desired product $B$ is produced with the reaction $A
-\rightarrow B$, and an undesired product $C$ is produced with the reaction $B
-\rightarrow C$. The reactant $A$ is the major component in the feed streams
-supplied to the reactors. After the second CSTR, the reaction mixture is sent to
-the non-adiabatic flash that separates the reactant $A$ from the product $B$.
-The $A$ rich vapor phase is recycled back to the first CSTR. The plant is
-simulated using the set of nonlinear ordinary differential equations (ODEs)
-available in \cite*{venkat:2006}, Appendix. The model has 12 states ($H_r,
-x_{Ar}, x_{Br}, T_r, H_m, x_{Am}, x_{Bm}, T_m, H_b, x_{Ab}, x_{Bb}, T_b$), 6
-control inputs ($F_0, F_1, D, Q_r, Q_m, Q_b$), and 5 disturbances ($x_{A0},
-x_{A1}, x_{B0}, x_{B1}, T_0$). The controlled measurements with setpoints are
-the heights and temperatures of the three units, and we assume that all the
-states are measured for this example. The sample time for the measurements is
-chosen as 10 seconds. The parameter values used to simulate the ODEs for the
-plant, the actuator constraints, and the bounds of the controlled measurements
-and disturbances used for the data generation and validation simulations are
-shown in Table \ref{table:cstrs_pars}, Appendix \ref{app:cstrs_pars}.
+For the first example, the plant consists of two stirred tank reactors in series
+with a flash separator, depicted in Figure \ref{fig:schematic_cstrs}. In both
+the CSTRs, a desired product $B$ is produced with the reaction $A \rightarrow
+B$, and an undesired product $C$ is produced with the reaction $B \rightarrow
+C$. The reactant $A$ is the major component in the feed streams supplied to the
+reactors. After the second CSTR, the reaction mixture is sent to the
+non-adiabatic flash that separates the reactant $A$ from the product $B$. The
+$A$ rich vapor phase is recycled back to the first CSTR. The plant is simulated
+using the set of nonlinear ordinary differential equations (ODEs) available in
+\cite{venkat:2006}, Appendix. The model has 12 states ($H_r, x_{Ar}, x_{Br},
+T_r, H_m, x_{Am}, x_{Bm}, T_m, H_b, x_{Ab}, x_{Bb}, T_b$), 6 control inputs
+($F_0, F_1, D, Q_r, Q_m, Q_b$), and 5 disturbances ($x_{A0}, x_{A1}, x_{B0},
+x_{B1}, T_0$). The controlled measurements with setpoints are the heights and
+temperatures of the three units, and we assume that all the states are measured.
+The sample time for the measurements is chosen as 10 seconds. The parameter
+values used to simulate the ODEs for the plant, the actuator constraints, and
+the bounds of the controlled measurements and disturbances used for the data
+generation and validation simulations are shown in Table \ref{table:cstrs_pars},
+Appendix \ref{app:cstrs_pars}.
 
@@
 disturbance signals with 24 setpoint changes and 48 disturbance changes are
-generated for 4320 timesteps (12 hours), each for the expected and unexpected
-plant behavior cases. The short horizon MPC controller is constructed with a
-horizon length of $N = 10$, and the architecture of the unstructured NN
-considered is three hidden layers with 224 nodes in each hidden layer. An
+generated for 4320 timesteps (12 hours), one set each for the expected and
+unexpected plant behavior cases. The short horizon MPC controller is constructed
+with a horizon length of $N = 10$, and the architecture of the unstructured NN
+consists of three hidden layers with 224 nodes in each hidden layer. An
 additional scaling of $x$ and $x_s$ is performed for the NN training as $x :=
@@
 
-First, the amount of data required to obtain an accurate NN controller is
-studied. To this aim, NNs with the three chosen architectures are trained with
-incremental increases of $10^4$ training samples starting from $4 \times 10^4$
-to $1.5 \times 10^5$ samples. A batch size of 1024 samples is used in Adam, and
-all the NNs are trained for 2000 epochs. For all the NN trainings performed,
-10$\%$ of the training dataset is kept as a buffer dataset, which is monitored
-during training and the network weights are updated only when the MSE decreases
-on this buffer dataset after every training epoch. The NNs after training are
-used in validation simulations with the setpoint and disturbance signals
-generated for the expected plant behavior case. The closed-loop performance is
-compared with the optimal MPC controller and the $\%$ performance loss obtained
-is plotted in Figure \ref{fig:cstrs_statistics} (top left) as a function of the
-number of training samples. All the trained NNs provide less than $1 \%$ loss in
-this performance metric after training with about $9 \times 10^4$ samples. The
-best $\%$ performance loss obtained by the NNs is summarized in Table
-\ref{table:cstrs}.
-
-Second, the above trained NNs with the best performance losses are used in
-validation simulations with the setpoint and disturbance signals generated for
+First, we study the amount of data required to obtain an accurate NN controller
+is studied. To this aim, NNs with the three chosen architectures are trained
+with incremental increases of $10^4$ training samples, ranging from $4 \times
+10^4$ to $1.5 \times 10^5$ samples. A batch size of 1024 samples is used in
+Adam, and all the NNs are trained for 2000 epochs. For all the NN trainings
+performed, 10$\%$ of the training dataset is kept as a buffer dataset, which is
+monitored during training, and the network weights are updated only when the MSE
+decreases on this buffer dataset after every training epoch. The NNs after
+training are used in validation simulations with the setpoint and disturbance
+signals generated for the expected plant behavior case. The closed-loop
+performance is compared with the optimal MPC controller and the $\%$ performance
+loss obtained is plotted in Figure \ref{fig:cstrs_statistics} (top left) as a
+function of the number of training samples. All the trained NNs provide less
+than $1 \%$ loss in this performance metric after training with about $9 \times
+10^4$ samples. The best $\%$ performance loss obtained by the NNs is summarized
+in Table \ref{table:cstrs}.
+
+Second, we use the above trained NNs with the best performance losses in
+validation simulations, with the setpoint and disturbance signals generated for
 the unexpected plant behavior case. The $\%$ performance losses obtained in
@@
 the training data. The practical implication of this study is that all possible
-plant scenarios with the setpoints and disturbances must be identified a-priori
-the deployment of NNs, and should be used to generate the training data.
+plant scenarios with the setpoints and disturbances must be identified, prior to
+deployment of NNs, and should be used to generate the training data.
 
@@
 Figures \ref{fig:cl_cstrs_inputs} and \ref{fig:cl_cstrs_outputs} show the
-transient actuator and controlled measurements obtained with the NN-3-448 and
-optimal MPC controllers for a simulation period of 2 hours. The Figure
-\ref{fig:cstrs_statistics} (center bottom) shows the transient values of the
-controller performance index obtained in this validation simulation with the
+transient actuator and controlled measurements obtained with the NN-3-448
+architecture, and optimal MPC controllers for a simulation period of 2 hours.
+Figure \ref{fig:cstrs_statistics} (center bottom) shows the transient values of
+the controller performance index obtained in this validation simulation with the
 three structured NNs, SS, satK and optimal MPC controllers for the full
-simulation period of 12 hours. The closed-loop performance obtained using NNs is
-almost same as the optimal MPC controller and the degradation in the performance
-is quantified with the $\%$ performance loss metric.
+simulation period of 12 hours. Closed-loop performance obtained using NNs is
+almost the same as the optimal MPC controller and the degradation in the
+performance is quantified with the $\%$ performance loss metric.
 
 Fourth, the online computational benefits of NNs over the QP based MPC is
-analyzed. The Figure \ref{fig:cstrs_statistics} (top right) shows a histogram of
+analyzed. Figure \ref{fig:cstrs_statistics} (top right) shows a histogram of
 online computation times of the NNs and QP solver in one validation simulation.
@@
 reported for the unstructured NN corresponds to training with $1.5 \times 10^5$
-samples and the performance is unacceptable for an industrial application. The
+samples. Such performance is unacceptable for an industrial application. The
 noticeable performance improvement with the structured NNs is because the
@@
 The scalability of the proposed NN design approach is next demonstrated on an
-industrial crude distillation unit model
-\citep*{pannocchia:rawlings:wright:2007} with 252 states, 32 controls, and 90
-measurements. The schematic of this model is shown in Figure
-\ref{fig:schematic_cdu}, which is a typical crude unit found in petrochemical
-refineries. The plant model is linear, and input and outputs are scaled for the
-MPC regulator as in the previous example. Only four measurements that represent
-the quality of the crude side products have setpoints, and five disturbances are
-used on the crude composition, fuel gas quality, and steam header pressure. The
-sample time for the measurements is 1 min. The tuning parameters and control
-horizon length for the MPC regulator are chosen as $Q = 2C'C$, $R = 0.1I$, and
-$N = 140$. A total $3.6 \times 10^5$ samples of ($x, x_s, u_s, \kappa_N(\cdot)$)
-are generated for the NN training, parallelized over 149 offline simulations.
-The time consumed for this data generation step was 27.8 hours.
+industrial crude distillation unit model \citep{pannocchia:rawlings:wright:2007}
+with 252 states, 32 controls, and 90 measurements. The schematic of this model
+is shown in Figure \ref{fig:schematic_cdu}, which is a typical crude unit found
+in petrochemical refineries. The plant model is linear, and input and outputs
+are scaled for the MPC regulator as in the previous example. Only four
+measurements that represent the quality of the crude side products have
+setpoints, and five disturbances are used on the crude composition, fuel gas
+quality, and steam header pressure. The sample time for the measurements is 1
+min. The tuning parameters and control horizon length for the MPC regulator are
+chosen as $Q = 2C'C$, $R = 0.1I$, and $N = 140$. A total $3.6 \times 10^5$
+samples of ($x, x_s, u_s, \kappa_N(\cdot)$) are generated for the NN training,
+parallelized over 149 offline simulations. The time consumed for this data
+generation step was 27.8 hours.
 
@@
 The offline data generation and training times for the NNs shows that this
-large-scale example is tractable with the proposed NN approach. This large
-example is challenging, since on average the QP solver CVXOPT requires 35
-seconds, and 47 seconds in the worst-case. By comparison,  
+large-scale example is tractable with the proposed NN approach. This example is
+challenging, since on average the QP solver CVXOPT requires 35 seconds, and 47
+seconds in the worst-case. By comparison,  
 all the NNs execute MPC in about 2 to 7 milliseconds. As observed from the plot
@@
 operational scenario, combined with the offset-free NN structure are the key
-steps for scalability in this example.
+properties that enable scalability in this example.
 
@@
 Neural networks have been demonstrated to approximate the MPC feedback law for
-treating large-scale, linear MPC applications that may be out of reach with QP
-solvers. The proposed methods avoiding online optimization to date in the
-literature, such as storing the entire MPC feedback law and sampling the large
-dimensional state space for the NN training, are not tractable for the problems
-considered in this article.
+treating large-scale, linear MPC applications that may be out of reach with
+online QP solvers. The proposed methods avoiding online optimization to date in
+the literature, such as storing the entire MPC feedback law and sampling the
+large dimensional state space for the NN training, are not tractable for the
+problems considered in this article.
 
@@
 magnitude disturbances that may change for a reasonable duration of operation.
-Parallel computing can be used for the offline data generation step if solving
+Parallel computing can be used for the offline data generation step, if solving
 QPs for each sampled state starts to take excessive amounts of time. After the
@@
 We established conditions under which the NN controllers are robust to state
-estimation errors and process disturbances, provides some theoretical support to
-practitioners interested in the deployment of NNs.
+estimation errors and process disturbances, providing some theoretical support
+to practitioners interested in the deployment of NNs.
 
 The online QP based MPC was adopted by practitioners due to its ability to
-systematically handle multivariable systems, process constraints, improvements
-in QP solution algorithms, and has guaranteed stability properties. The
-additional computing hardware for training in large applications and sampling
-the plant operational scenarios are additional complexities required to design
-NN controllers. The advantage of NNs is their speed of MPC controller execution
-and convenience for deployment on memory constrained hardware. Future research
-may be focused to establish conditions for guaranteed closed-loop stability with
-NN controllers, systematically handling state constraints, approximating the
-target selector QP, and extensions to large, nonlinear MPC applications.
-
-\section*{Acknowledgment}
+systematically handle multivariable systems and process constraints, and the
+reliability of QP solution algorithms. The approach has guaranteed stability
+properties. The need for sampling the plant operational scenarios and additional
+computing hardware for training large applications are additional complexities
+that must be considered in the design of NN controllers. The advantage of NNs is
+their speed of MPC controller execution and convenience for deployment on memory
+constrained hardware. Future research may be focused to establish conditions for
+guaranteed closed-loop stability with NN controllers, systematically handling
+state constraints, approximating the target selector QP, and extensions to
+large, nonlinear MPC applications.
+
+\section*{Acknowledgments}
 The funding for this work was provided by the industrial members of the
@@
 facilities purchased with funds from the National Science Foundation
-(CNS-1725797) and administered by the Center for Scientific Computing (CSC) was
-used for the simulation studies presented in this article. The CSC is supported
-by the California NanoSystems Institute and the Materials Research Science and
-Engineering Center (MRSEC; NSF DMR 1720256) at UC Santa Barbara.
+(CNS-1725797, OAC-1925717) and administered by the Center for Scientific
+Computing (CSC) was used for the simulation studies presented in this article.
+The CSC is supported by the California NanoSystems Institute and the Materials
+Research Science and Engineering Center (MRSEC; NSF DMR 1720256) at UC Santa
+Barbara.
 
 %% New version of the num-names style
-\bibliographystyle{elsarticle-num-names}
-\bibliography{abbreviations,articles,books,unpub,proceedings}
+\bibliographystyle{abbrvnat}
+\bibliography{paper}
 
@@
 and the available result on the ISS property of a system if it admits an
-ISS-Lyapunov function (\cite*{jiang:wang:2001, rawlings:mayne:diehl:2017},
+ISS-Lyapunov function (\cite{jiang:wang:2001, rawlings:mayne:diehl:2017},
 Appendix B).
@@
 $\alpha_1(\cdot), \alpha_2(\cdot), \alpha_3(\cdot) \in \mathcal{K}_{\infty}$ and
-$\sigma(\cdot) \in \mathcal{K}$ such that for all $x \in X$ and $w \in \bbW$
+$\sigma(\cdot) \in \mathcal{K}$ such that for all $x \in X$ and $w \in \bbW$, we
+have
 \begin{align*}
-    \alpha_1(\norm{x}) \leq & V(x) \leq \alpha_2(\norm{x}) \\
-    V(f(x, w)) &- V(x) \leq -\alpha_3(\norm{x}) + \sigma(\norm{w})
+    \alpha_1(\norm{x}) \leq & V(x) \leq \alpha_2(\norm{x}), \\
+    V(f(x, w)) &- V(x) \leq -\alpha_3(\norm{x}) + \sigma(\norm{w}).
 \end{align*}
@@
 Additionally, we require the following two useful propositions from
-\cite*{allan:bates:risbeck:rawlings:2017} and \cite*{rawlings:ji:2012}, to bound
+\cite{allan:bates:risbeck:rawlings:2017} and \cite{rawlings:ji:2012}, to bound
 values of continuous functions and an inequality for $\mathcal{K}$ functions
@@
     \mathcal{K}$, the following holds for all $a_i \in \bbR_{\geq 0}$, $i \in
-    \bbI_{1:n}$ 
+    \bbI_{1:n}$:
     \begin{align*}
@@
 as the closed set ($\xhat^+ \in \bbR^n$) and $S$ as the compact set ($\tilde{x}
-\in S$), from proposition \ref{prop:continuous_funcs} we have for some
-$\sigma_1(\cdot) \in \mathcal{K}_{\infty}$
+\in S$), from Proposition \ref{prop:continuous_funcs} we have for some
+$\sigma_1(\cdot) \in \mathcal{K}_{\infty}$ that
 \begin{align}
-    \norm{V_N^0(\xhat^+) - V_N^0(\tilde{x}^+)} &\leq 
+    &\norm{V_N^0(\xhat^+) - V_N^0(\tilde{x}^+)} \leq 
     \sigma_1(\norm{\xhat^+ - \tilde{x}^+})  \nonumber  \\
     &\leq 
-   \sigma_1(\norm{B e_{NN}(\xhat)} + \norm{w} 
-   \nonumber \\
-   & + \norm{A}\norm{e} +  \norm{e^+}) \nonumber \\
+   \sigma_1(\norm{B e_{NN}(\xhat)} + \norm{w} + \norm{A}\norm{e} +  \norm{e^+}) \nonumber \\
      &\leq 
@@
 \mathcal{K}$, such that $\norm{\phi_d(k; \xhat)} \leq \beta(\norm{\xhat}, k) +
-\sigma(\norm{\norm{\mathbf{d}_k}})$. Using the Proposition
+\sigma(\norm{\norm{\mathbf{d}_k}})$. Using Proposition
 \ref{prop:Kfunction_inequality} and the definition of $d(k)$, we have 
